### 2013-11-05 draft.Rnw
setup document structure

\documentclass[a4paper,12pt]{report}
\usepackage{hyperref}

\begin{document}

\title{Preliminary Thesis Defence\\~\\ Supervisor: Jean-Louis Arcand\\ Second Reader: Love Vanderwalle}
\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva. bquast@gmail.com}}
\maketitle

\tableofcontents

\chapter*{Introduction}
jade

\chapter{South Africa}
a la duflo

\chapter{Surviving Andersonville}
Survival analysis

\chapter{Single-Agent Belief Distritutions}
examples

\chapter{Police Reform Conkary}
Guinea bla bla.

\chapter{Bitcoin remitances}
How I...

\chapter{Rare events}
black swans, dragon king

\chapter{Singh}
The difference between risk and uncertainty.

\end{document}

### 2013-11-05 draft.tex
setup document structure

\documentclass[a4paper,12pt]{report}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{hyperref}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\title{Preliminary Thesis Defence\\~\\ Supervisor: Jean-Louis Arcand\\ Second Reader: Love Vanderwalle}
\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva. bquast@gmail.com}}
\maketitle

\tableofcontents

\chapter*{Introduction}
jade

\chapter{South Africa}
a la duflo

\chapter{Surviving Andersonville}
Survival analysis

\chapter{Single-Agent Belief Distritutions}
examples

\chapter{Police Reform Conkary}
Guinea bla bla.

\chapter{Bitcoin remitances}
How I...

\chapter{Rare events}
black swans, dragon king

\chapter{Singh}
The difference between risk and uncertainty.

\end{document}

### 2013-11-13 draft.tex
fix title
first draft
test combine
draft combine try
new structure using subfiles

@@
-\documentclass[a4paper,12pt]{report}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[a4paper]{report}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth
@@
 \usepackage{alltt}
+\usepackage{subfiles}
 \usepackage{hyperref}
+
+\title{Preliminary Thesis Defence}
+%\subtitle{
+%\begin{tabular}{rl}
+%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
+%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
+%\end{tabular}
+%}
+
+\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}}
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 
-\title{Preliminary Thesis Defence\\~\\ Supervisor: Jean-Louis Arcand\\ Second Reader: Love Vanderwalle}
-\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva. bquast@gmail.com}}
 \maketitle
@@
 \chapter{Surviving Andersonville}
-Survival analysis
+article
 
@@
 \chapter{Police Reform Conkary}
-Guinea bla bla.
+\subfile{conakry.tex}
 
 \chapter{Bitcoin remitances}
-How I...
+\subfile{bitcoin.tex}
 
@@
 
-\chapter{Singh}
-The difference between risk and uncertainty.
+\chapter{Morris Shin 1998, Unique equilibrium in a model of self-fulfilling currency attacks}
+\subfile{MorrisShin.tex}
+
+\chapter*{End notes}
 

### 2013-11-13 draft.Rnw
fix title
first draft
test combine
draft combine try
merge, fix book problem

@@
-\documentclass[a4paper,12pt]{report}
+\documentclass[a4paper]{report}
+\usepackage{subfiles}
 \usepackage{hyperref}
+
+\title{Preliminary Thesis Defence}
+%\subtitle{
+%\begin{tabular}{rl}
+%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
+%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
+%\end{tabular}
+%}
+
+\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}}
 

### 2013-11-13 draft.Rnw
commit before merge
running again
remove abstracts from articles
update to scrbook

@@
-\documentclass[a4paper]{report}
+\documentclass[a4paper]{scrbook}
 \usepackage{subfiles}
@@
 \title{Preliminary Thesis Defence}
-%\subtitle{
-%\begin{tabular}{rl}
-%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
-%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
-%\end{tabular}
-%}
+\subtitle{
+\begin{tabular}{rl}
+Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
+Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
+\end{tabular}
+}
 
@@
 
+\frontmatter
 \maketitle
@@
 
-\chapter*{Introduction}
+\chapter{Introduction}
 jade
 
+\mainmatter
 \chapter{South Africa}
@@
 
-\chapter*{End notes}
+\backmatter
+\chapter{End notes}
 

### 2013-11-13 draft.tex
commit before merge
running again
remove abstracts from articles
removed \abstract from chapters
update to scrbook

@@
-\documentclass[a4paper]{report}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[a4paper]{scrbook}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth

### 2013-11-13 surviving.tex

\documentclass[draft.tex]{subfiles}

%\author{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}

\begin{document}

\chapter{Replication of: ``Surviving Andersonville: The Benefits of Social Networks in POW Camps''}

\section{Summary of the paper}
\textcite{costa2007surviving} tries to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps. To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.

The empirical specification for the longitudinal data that measures the effect of the size of the network is as follows:

\begin{equation} \label{eq:ht}
h(t) = \exp ( \beta_1 F + \beta_2 I + \beta_3 M )
\end{equation}

where $h$ is hazard at time $t$, $F$ is the number of friends (=social network), $I$ are individual characteristics and $M$ macro camp conditions. The number of friends is measured as the number of POWs of the same company and varies by month due to deaths or camp transfers. As it might capture the lagged mortality of the group, the authors use as second strategy the initial number of friends as a time-invariant proxy. In addition, they instrument for the number of friends using the number of net camp transfers combined with a dummy indicating whether the POW was transferred to account for omitted variables. 
The specification for the Andersonville data in turn is a probit model:

\begin{align}
\label{s1} Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F)\\
\label{s1b} Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j)
\end{align}

where \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.

The longitudinal data indicates that POWs had special characteristics. For instance, they were likely to be volunteers, and from companies with more wounded or dead. POWs with more friends were typically US-born and wealthier while Irish and older men had less friends. Concerning survival rates, Kaplan-Meier hazard rates show that POWs captured later (after 1963 when the Union and the Confederate Army stopped exchanging POWs) have lower survival rates. They also show that survival rates were higher for POWs with 10 or more friends. In addition, the rates show that it takes 50 days until there is a divergence in survival between POWs with and without friends. The exponential function estimates that an additional friend leads to a 0.98 times lower mortality hazard. An increase in the number of friends from 0 to 5 (5 to 10), decreases the predicted probability of death from 0.31 to 0.28 (0.26) while a spline specification provides evidence that the effect is greatest for the first two friends. In addition, survival is more likely for POWs that had survived at least one or two months. Factors increasing mortality are the number of men in the camp, low rank, high age, and height among others. Insignificant variables are for instance wealth and marital status. There is no evidence for individual heterogeneity. The use of a Weibull specification indicates no duration dependence (toughen up effects). Interestingly though, a Cox model gives no significant effect of friends which the authors interpret as a result of their loss of power due to the small sample size. Robustness checks, including the IV approach and the effect of friends transferred in, confirms the significant effect of friends. Finally, the cross-sectional results provide evidence that having the same last name, being from the same town for smaller towns, ethnic similarity and having a sergeant or a higher rank in one's network are all important factors in raising survival probabilities which in turn shows that the quality of social networks matters.

In summary, Costa and Kahn are able to show that quantity and quality of social networks mattered for survival in civil war POW camps. Potential explanations for this are the sharing of scarce resources, moral support and protection from other prisoners.

\section{Data}
The raw data for the first part of the paper is extracted from the Union Army dataset readily accessible at \url{http://www.cpe.uchicago.edu}. This dataset draws information from censuses, medical records and military pension records linking military, socioeconomic and health information for nearly $40,000$ white males that served in the Union Army during the Civil War. For the second part, the Andersonville database is available at \url{http://www.itd.nps.gov/cwss} but only as a ``searchable version'', which allows viewing the information for one soldier at a time, and more convenient formats are not readily available.

The datasets provided for the estimations alongside with the publication are already partially processed parts of the raw data available online. No clear guidance is given as to what steps were taken to go from the raw data to the files provided, and matching both things proved to be less than straightforward. In view of this, we decided to proceed with the replication using the files provided by the authors, pointing out along the way the cases where potential problems in them seemed likely given the raw data we observed. Taking those files as starting points, it is possible to reproduce the tables and graphs published in the paper, so in this sense we can say that the data set is complete. Originally, some of the data required by the published .do files was not included in the published data files, but the authors provided it promptly upon our request and added it subsequently to the online files of the publishing journal.

The data and .do files provided do not describe or label many of the variables used, nor does the limited variable description in the Appendix cover all of them. A very thorough description of the variables in the raw data set can be found at its online source, but the match between this and the variables in the files provided is not straightforward or complete, since some of them are already created by the authors from the raw data. The description of the data itself, mainly of the variables that are used most often, is succinct but adequate, with Table 1 and Table 2 presenting some relevant descriptive traits. Despite this, some attention should be drawn to the fact that some of the variables have a relevant share of missing values (only the highest number of observations is reported), a point that will be commented in detail later on.

\section{Stata code and interpretation}
All codes run to their full extent, and produce the estimations presented in the paper, with minor differences that we describe in detail below. The codes themselves are not commented at all and include plenty of estimations and specifications not included in the published paper, as well as unexplained data processing steps. No exporting commands were set up, or log files kept, which might be the root of some of the rounding and significance discrepancies we have found.

In what follows, all reproduced tables are presented with a comment on the differences found (in bold), whenever there were any.

\subsection{Tables}
Table 1: This table presents the means of most variables later used for estimation, dividing observations in POWs and NON POWs, to illustrate ex ante differences in observables between them.

\begin{table}[bt]
\centering
\caption{Characteristics of Soldiers by POW Status}
\label{characteristics}
\begin{tabular}{lllllll}
\hline
                           & All   & Obs.  & Never POW & Obs.  & POW   & Obs. \\
US born                    & 0.745 & 35007 & 0.745     & 31967 & 0.743 & 3040 \\
US born corrected          & 0.747 & 34941 & 0.745     & 31966 & 0.759 & 2975 \\
Irish                      & 0.087 & 34941 & 0.086     & 31966 & 0.102 & 2975 \\
German                     & 0.074 & 34941 & 0.075     & 31966 & 0.062 & 2975 \\
British                    & 0.039 & 34941 & 0.039     & 31966 & 0.033 & 2975 \\
Other                      & 0.054 & 34941 & 0.055     & 31966 & 0.043 & 2975 \\
Artisan                    & 0.2   & 34941 & 0.199     & 31966 & 0.211 & 2975 \\
Farmer corrected           & 0.505 & 34941 & 0.505     & 31966 & 0.508 & 2975 \\
Professional or proprietor & 0.075 & 34941 & 0.077     & 31966 & 0.061 & 2975 \\
Laborer                    & 0.212 & 34941 & 0.212     & 31966 & 0.212 & 2975 \\
Unknown                    & 0.007 & 34941 & 0.007     & 31966 & 0.008 & 2975 \\
Enlisted in 1861           & 0.21  & 35007 & 0.205     & 31967 & 0.263 & 3040 \\
Enlisted in 1861 corrected & 0.21  & 34878 & 0.205     & 31906 & 0.269 & 2972 \\
Enlisted in 1862                  & 0.344   & 34878 & 0.331   & 31906 & 0.487  & 2972 \\
Enlisted in 1863                  & 0.068   & 34878 & 0.066   & 31906 & 0.087  & 2972 \\
Enlisted in 1864                  & 0.256   & 34878 & 0.266   & 31906 & 0.147  & 2972 \\
Enlisted in 1865                  & 0.122   & 34878 & 0.132   & 31906 & 0.009  & 2972 \\
Volunteer                         & 0.909   & 34941 & 0.905   & 31966 & 0.951  & 2975 \\
Height in inches                  & 67.599  & 34941 & 67.589  & 31966 & 67.709 & 2975 \\
Household property income in 1860 & 534.155 & 13769 & 531.734 & 12509 & 558.2  & 1260 \\
Company birthplace fragmentation  & 0.642   & 34941 & 0.644   & 31966 & 0.62   & 2975 \\
Company occupation fragmentation  & 0.559   & 34941 & 0.558   & 31966 & 0.57   & 2975 \\
Fraction company died as non-POWs & 0.135   & 34941 & 0.131   & 31966 & 0.182  & 2975 \\
\end{tabular}
\end{table}

We have added to \autoref{characteristics} the number of observations per variable, not originally included in the paper, in order to highlight the fact that some of them have significant amounts of missing values, something that should be kept in mind later at the estimation stage. In this table, the case in point is Household property income in 1860, which is used in most of the specifications proposed, but as will be discussed for later tables, this is a pattern common to all the variables imported from census data. 
Additionally, considering the number of observations for each of the variables leads to the suggestion of a small correction for three of the dummy variables describing categories: US born, farmer and enlisted in 1861. The initial data file is missing these variables, which are likely to have been dropped as the basis category for estimation purposes in some other use of the data. They were then rebuilt in the .do file from the remaining categories in such a way that generated zeroes for some observations that should have been missing (except for farmer, which is not included at all in the file). For example: as provided by the code, US born has $35,007$ observations, whereas other nationality dummies, all built from the same original variable, have $34,941$. The correction proposed then, is to set these dummies to missing whenever the other categories of their class are missing, which slightly changes their descriptive statistics (for example the mean of US born goes from $0.745$ to $0.747$ when this correction is implemented).

Remaining discrepancies are minor and could be due to some kind of rounding difference. An alternative explanation for these differences is that the table was produced from a slightly different dataset. Considering that even the most populous variables present over 500 observations less than the amount declared in the paper, and the fact that one of the variables (farmer) is not included in the data file at all, we consider the second option to be more likely, which would also explain the minor differences in the means of Artisan, British, Height in inches, etc.

A last and minor comment is that the inclusion of the variable volunteer is surprising, since by sample design the Union Army dataset was restricted to white volunteer infantry regiments. The inclusion of this variable when comparing POWs and non POWs probably responds to the point raised in the paper about POWs not being representative of all soldiers, for example in ideology (p.1471). A variable that reflects that both POWs and non POWs volunteered in similar proportions would suggest homogeneity between POWs and non POWs in this dimension and, hence, increase  external validity. The similarities observed in Table 1 between POWs and non POWs in their mean of volunteer do not reflect that, since they are both close to one by construction. Any individuals not listed as volunteers, either correspond to the very few drafted men, or are actually soldiers that re-enlisted as commissioned officers, but were originally volunteers, as explained in the codebooks for the source data.

\autoref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.  It also presents separately their mean and standard errors for the subsamples of POWs with few (less than 3) and many friends (three or more).

\begin{sidewaystable}
\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity}
\label{friends}
\begin{tabular}{llllllllll}

                                  & \multicolumn{3}{l}{All} & \multicolumn{3}{l}{Few friends ($<3$)} & \multicolumn{3}{l}{Many friends ($>=3$)} \\
                                  & Mean                    & Std. err.                            & No. obs.                               & Mean & Std. err. & No. obs. & Mean & Std. err. & No. obs. \\
US born                           & 0.731                   & 0.444                                & 1976                                   & 0.708 & 0.455 & 990 & 0.754 & 0.431 & 986 \\
Irish                             & 0.12                    & 0.325                                & 1976                                   & 0.115 & 0.319 & 990 & 0.125 & 0.331 & 986 \\
German                            & 0.063                   & 0.243                                & 1976                                   & 0.081 & 0.273 & 990 & 0.045 & 0.207 & 986 \\
British                           & 0.034                   & 0.182                                & 1976                                   & 0.042 & 0.202 & 990 & 0.026 & 0.16 & 986 \\
Other                             & 0.05                    & 0.217                                & 1976                                   & 0.053 & 0.223 & 990 & 0.047 & 0.211 & 986 \\
Artisan                           & 0.209                   & 0.407                                & 1976                                   & 0.214 & 0.41 & 990 & 0.204 & 0.403 & 986 \\
Farmer                            & 0.421                   & 0.494                                & 1976                                   & 0.44 & 0.497 & 990 & 0.401 & 0.49 & 986 \\
Professional or propietor         & 0.07                    & 0.256                                & 1976                                   & 0.077 & 0.266 & 990 & 0.064 & 0.245 & 986 \\
Laborer                           & 0.266                   & 0.442                                & 1976                                   & 0.243 & 0.429 & 990 & 0.288 & 0.453 & 986 \\
Unknown                           & 0.034                   & 0.182                                & 1976                                   & 0.025 & 0.157 & 990 & 0.044 & 0.204 & 986 \\
Enlisted in big city              & 0.475                   & 0.5                                  & 1976                                   & 0.493 & 0.5 & 990 & 0.457 & 0.498 & 986 \\
Household property income in 1860 & 576.475                 & 1855.699                             & 817                                    & 483.609 & 1084.987 & 391 & 661.711 & 2348.676 & 426 \\
Age when captured                 & 25.96                   & 7.056                                & 1966                                   & 26.645 & 7.415 & 990 & 25.265 & 6.604 & 976 \\
Height when captured                 & 171.576 & 6.612 & 1925 & 171.79 & 6.384 & 974 & 171.356 & 6.833 & 951 \\
Commisoned or noncommisoned officer  & 0.076   & 0.266 & 1976 & 0.083  & 0.276 & 990 & 0.07    & 0.255 & 986 \\
Married in 1860                      & 0.257   & 0.437 & 817  & 0.276  & 0.448 & 391 & 0.239   & 0.427 & 426 \\
Wounded 10 days before capture       & 0.118   & 0.323 & 1976 & 0.148  & 0.356 & 990 & 0.088   & 0.284 & 986 \\
Fraction company dead before capture & 0.089   & 0.064 & 1976 & 0.093  & 0.07  & 990 & 0.085   & 0.057 & 986 \\
Company birthplace fragmentation     & 0.542   & 0.2   & 1923 & 0.547  & 0.193 & 985 & 0.536   & 0.206 & 938 \\
Company occupational fragmentation   & 0.596   & 0.173 & 1923 & 0.586  & 0.173 & 985 & 0.607   & 0.172 & 938 \\
\end{tabular}
\end{sidewaystable}

This table is almost exactly reproduced, except for the minor differences set in bold, which appear to be rounding differences (and a typo in the case of Laborer). The number of observations stated on the table in the paper (1923) corresponds to the last variable in this case as well, even though, as mentioned for the previous table, it is relevant to keep in mind that some of the other variables of interest show a considerably lower count of observations, as can be seen in the added columns. For this table, this is the case of variables Married in 1860 and Household property income in 1860, which are both variables from the 1860 census.
The main concern regarding this table is the process of organizing the data, particularly one step in which a merge to the file ``transfer.dta'' is conducted. This file contains the prisoner identifier variable, month, year, and a dummy variable reflecting whether the prisoner was transferred (transferin). This variable is not needed for \autoref{friends}, and we can only speculate that it was incorporated, as some other steps were, in an attempt to exactly reproduce the dataset used in \autoref{corrected}. The problem in this case is that the file ``transfer.dta'' contains duplicate observations, which in turn duplicates observations in the main data set via the merge, artificially inflating the number of observations in the data used for \autoref{friends}\footnote{Duplicate observations per month-year-prisoner are natural in the context of \autoref{corrected}, because in there capture time is measured per fortnight. Including additional observations because of this in a stage of data description such as this one is hardly appropriate.}.

If these duplicate observations are eliminated from the ``transfer.dta'' file before the merge, the statistics presented do not seem to defer significantly, and certainly neither do the conclusions drawn from them, but the number of observations in the subsample considered is significantly lower. This exercise is presented in the table below.

\begin{sidewaystable}
\centering
\caption{corrected}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{corrected}
\begin{tabular}{llllllllll}
\hline
                                  & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. \\
US born                           & 0.732   & 0.443     & 1470     & 0.715   & 0.452     & 727      & 0.748   & 0.434     & 743      \\
Irish                             & 0.122   & 0.327     & 1470     & 0.113   & 0.317     & 727      & 0.131   & 0.337     & 743      \\
German                            & 0.06    & 0.237     & 1470     & 0.074   & 0.262     & 727      & 0.046   & 0.209     & 743      \\
British                           & 0.034   & 0.181     & 1470     & 0.04    & 0.196     & 727      & 0.028   & 0.166     & 743      \\
Other                             & 0.05    & 0.219     & 1470     & 0.056   & 0.231     & 727      & 0.044   & 0.206     & 743      \\
Artisan                           & 0.212   & 0.409     & 1470     & 0.217   & 0.413     & 727      & 0.207   & 0.406     & 743      \\
Farmer                            & 0.427   & 0.495     & 1470     & 0.442   & 0.497     & 727      & 0.413   & 0.493     & 743      \\
Professional or proprietor        & 0.065   & 0.247     & 1470     & 0.073   & 0.26      & 727      & 0.058   & 0.234     & 743      \\
Laborer                           & 0.265   & 0.441     & 1470     & 0.242   & 0.429     & 727      & 0.287   & 0.453     & 743      \\
Unknown                           & 0.031   & 0.172     & 1470     & 0.026   & 0.16      & 727      & 0.035   & 0.184     & 743      \\
Enlisted in big city              & 0.48    & 0.5       & 1470     & 0.486   & 0.5       & 727      & 0.475   & 0.5       & 743      \\
Household property income in 1860 & 547.314 & 1637.903  & 615      & 476.274 & 1107.659  & 299      & 614.532 & 2014.738  & 316      \\
Age when captured                 & 25.834  & 6.931     & 1465     & 26.4    & 7.263     & 727      & 25.276  & 6.544     & 738      \\
Height when captured              & 171.526 & 6.624     & 1439     & 171.683 & 6.433     & 717      & 171.37  & 6.81      & 722      \\
Commisioned or noncommisioned officer\footnote{Related to the point about the variable Volunteer made before, the name Commisioned or non commissioned officer may be misleading, since commissioned officers are excluded from the sample by construction.} & 0.074 & 0.262 & 1470 & 0.078 & 0.269 & 727 & 0.07  & 0.255 & 743 \\
Married in 1860                       & 0.252 & 0.435 & 615  & 0.264 & 0.442 & 299 & 0.241 & 0.428 & 316 \\
Wounded 10 days before capture        & 0.125 & 0.331 & 1470 & 0.155 & 0.363 & 727 & 0.096 & 0.294 & 743 \\
Fraction company dead before capture  & 0.091 & 0.063 & 1470 & 0.094 & 0.069 & 727 & 0.089 & 0.056 & 743 \\
Company birthplace fragmentation      & 0.542 & 0.198 & 1442 & 0.55  & 0.189 & 723 & 0.534 & 0.207 & 719 \\
Company occupational fragmentation    & 0.593 & 0.175 & 1442 & 0.585 & 0.173 & 723 & 0.601 & 0.178 & 719 \\
\end{tabular}
\end{sidewaystable}

Two additional remarks related to this are: a) whenever month was larger than 12, it is set to missing, b) all observations marked as having occurred in 1861 are shifted to 1862. Neither month nor year are directly used for this table, but they are the matching points for the merge to the ``transfer.dta'' file discussed above. The file “transfer.dta” also contains month>12 and observations for 1861, and they are not replaced in a similar fashion, introducing some additional artificial matching problems into the merge operation.3 Besides the potential distortions in the merge that these asymmetric replacements may cause, the switch of 1861 to 1862 seems particularly surprising given that no explanation for it is offered.

Additionally, if the aim of this table is to have a general impression of the variables used in the main regressions (\autoref{corrected}), the same observations should have been considered in both accounts. This is not the case, since the observations with an unknown number of friends are dropped for this table, but not for the next one.

\autoref{corrected}: This table shows the results of the hazard rate analysis using a set of covariates described in the previous tables and alternating two measures of friends: number of friends at the time of the observation and initial number of friends.

\begin{sidewaystable}
\caption{Social Networks and Individual Characteristics on Mortality}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{social}
\begin{tabular}{lllllll}
\hline
                                         & \multicolumn{2}{l}{specification I} & \multicolumn{2}{l}{specification II} & \multicolumn{2}{l}{specification III} \\
VARIABLES                                & Hazard rate                         & Std. err.                            & Hazard rate                           & Std. err. & Hazard rate & Std. err. \\
Current number of friends                & 0.983                               & -0.008                               & 0.977++                               & -0.009 &  &  \\
Initial number of friends                &                                     &                                      &                                       &  & 0.976++ & -0.009 \\
Ln(number of prisoners in camp)          &                                     &                                      & 1.536++                               & -0.14 & 1.521++ & -0.139 \\
Fraction of company dying before capture & 1.091                               & -0.782                               & 0.892                                 & -0.636 & 0.63 & -0.449 \\
Professional or proprietor               & 0.567                               & -0.146                               & 0.563                                 & -0.143 & 0.556 & -0.141 \\
Artisan                                  & 0.944                               & -0.119                               & 0.947                                 & -0.119 & 0.937 & -0.117 \\
Laborer                                  & 1.298                               & -0.154                               & 1.295                                 & -0.152 & 1.287 & -0.152 \\
German                                   & 1.197                               & -0.215                               & 1.166                                 & -0.209 & 1.149 & -0.206 \\
Irish                                    & 0.768*                              & -0.121                               & 0.762*                                & -0.118 & 0.750* & -0.117 \\
British                       & 0.641*    & -0.171 & 0.654     & -0.174 & 0.656    & -0.177 \\
Other                         & 0.658*    & -0.154 & 0.645*    & -0.153 & 0.642*   & -0.151 \\
Sergeant, corporal or officer & 0.549++   & -0.115 & 0.543++   & -0.111 & 0.541++  & -0.111 \\
Age at captivity              & 1.045++   & -0.007 & 1.044++   & -0.007 & 1.044++  & -0.007 \\
Height at enlistment          & 1.01      & -0.007 & 1.01      & -0.007 & 1.011    & -0.007 \\
Observations                  & 23256     &        & 23256     &        & 23256    &        \\
Number of subjects            & 3026      &        & 3026      &        & 3026     &        \\
Log pseudo likelihood         & -1324.607 &        & -1308.229 &        & -1307.17 &        \\
\end{tabular}
\end{sidewaystable}

\autoref{corrected} is reproduced almost completely, except for the results in bold, for which the significance level differs from the one presented in the publication.

In this case, month larger than 12 is replaced by 99, and in this case as well this might generate distortions since an equivalent change was not performed in the file to which this is merged (``Died.dta''). The observations for which the number of friends is unknown are not dropped here, but set to zero. Whenever the number of deaths in the prisoners' company before capture is unknown, it is set to zero. Whenever the number of men in camp is unknown it is set to 40. Whenever the variables imported from the 1860 census are missing (i.e. there was no match to the census) they are still included in the regression by setting their value to zero in the case of dummy variables (married and illiterate), and by taking log(1+variable) in the case of Household property. In all of these cases, dummy variables are included in the regression indicating whether the data is actually missing (e.g. a dummy variable that takes value one if the observation was not matched to the 1860 census, link60). It is understandable that in order to maintain a healthy sample size, and to use as much of the information as possible, some assumptions are made, but the trade off related to this point is that these assumptions may create artificial noise in the data that would not be fully captured by these control dummies.

\autoref{social}: This table presents an alternative estimation strategy. As a benchmark, the effect of the number of friends in the camp is estimated including company fixed effects and the same covariates as before. To avoid endogeneity issues that may arise due to the potential correlation between the current number of friends and the prisoner’s own unobservable health (via its correlation to the lagged mortality of the group), an IV-hazard rate strategy is pursued next. The instruments chosen are the new number of friends the prisoner has in each period (the newly captured soldiers of his company) and a dummy variable that reflects whether the POW was transferred. Both variables clearly affect the number of friends a POW has, and are meant to be uncorrelated with his unobservable health, since transfers and the amount of newly captured men assigned to each camp were determined by camp needs or evolution of war events5. In the first stage, the number of friends is regressed on the instruments, as well as the whole set of covariates and fixed effects. The predicted residuals of this first stage are then included in the second stage, along with all covariates, fixed effects and the number of friends.  This procedure is repeated 100 times, preserving the coefficients and standard errors of the number of friends, the number of men in the camp and the residuals, as well as the R-squared of the first stage. The final result of this Montecarlo procedure is obtained by computing the mean of those variables among the 100 repetitions.

\begin{sidewaystable}
\caption{Effect of Social Networks on Mortality, with Company Fixed Effects and Instrumented}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{effect}
\begin{tabular}{lllll}
\hline
                                    & \multicolumn{2}{l}{Original} & \multicolumn{2}{l}{IV} \\
                                    & Haz. Rate                    & Std. Err.              & Haz. Rate & Std. Err. \\
Number of friends                   & 0.978*                       & -0.012                 & 0.895 & -0.055 \\
Ln(total number of men in the camp) & 1.437++                      & -0.122                 & 1.537 & -0.196 \\
Residual                            &                              &                        & 1.06 & -0.071 \\
\end{tabular}
\end{sidewaystable}

Here, the results are replicated entirely.

A concern raised is that it is not clear how the variable that reflects transfers was constructed, since this information is not directly provided in the raw data available online. In some cases, the variable that reflects the camp contains multiple entries per individual, and we can only assume that those were used to infer that the POW was transferred between those camps. This is most likely an accurate interpretation of the data, the only problem being that there is no information about the date of transfer, which makes the instrument weaker.

In the following section, the authors use The National Park Service's cross-sectional data of the population of Andersonville and estimate probit models of the probability of survival on the number of friends and various demographic characteristics as described in the summary.

\autoref{effect}: This table estimates the effect of social networks on probability of survival controlling for a large of variables that measure existing networks outside of the company.

\begin{sidewaystable}
\caption{Effect of social networks on probability of survival}\footnote{Like in the paper, the estimations exclude the two outlier companies. Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{effectsocial}
\begin{tabular}{lllllll}
\hline
                                                              &         &         &         &         & \multicolumn{2}{l}{From small town} \\
                                                              & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
Number of men in regiment÷10                                  & 9.157   & 0.004++ &         &         &                                     &  \\
                                                              & -10.358 & -0.001  &         &         &                                     &  \\
Number of men in company                                      & 12.899  &         & 0.003++ & 0.002++ & 0.003++                             & 0.002++ \\
                                                              & -15.39  &         & -0.001  & -0.001  & -0.001                              & -0.001 \\
Fraction of company with              rank sergeant or higher & 0.073   & 0.120++ & 0.128++ & 0.079   & 0.152                               & 0.085 \\
                                                              &         & -0.034  & -0.034  & -0.032  & -0.061                              & -0.056 \\
Number of men with same last name in regiment                 & 1.19    & 0.033++ & 0.033++ & 0.036++ & 0.018*                              & 0.023++ \\
                                                              & -0.599  & -0.007  & -0.007  & -0.006  & -0.009                              & -0.009 \\
Log(number of men in camp from same town)                     & 5.101   & -0.003  & -0.002  & 0       & 0.018*                              & 0.026++ \\
                                                              & -1.994  & -0.005  & -0.005  & -0.005  & -0.009                              & -0.008 \\
Dummy=1 if town population<9552                               & 0.423   & 0.037+  & 0.034+  & 0.032+  &                                     &  \\
                                                              &         & -0.014  & -0.014  & -0.013  &                                     &  \\
Private                                                       & 0.824   &         &         &         &                                     &  \\
Officer             & 0.003 & 0.347++ & 0.347++ & 0.354++ & 0.311++ & 0.328++ \\
                    &       & -0.027  & -0.027  & -0.021  & -0.038  & -0.025  \\
Sergeant            & 0.068 & 0.080++ & 0.080++ & 0.083++ & 0.084++ & 0.088++ \\
                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
Other rank          & 0.01  & 0.028   & 0.034   & 0.03    & 0.067   & 0.046   \\
                    &       & -0.03   & -0.03   & -0.03   & -0.049  & -0.05   \\
Corporal            & 0.078 & 0.055++ & 0.055++ & 0.046++ & 0.064++ & 0.054++ \\
                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
Irish surname       & 0.023 & 0.02    & 0.022   & 0.017   & 0.069   & 0.059*  \\
                    &       & -0.019  & -0.019  & -0.019  & -0.03   & -0.03   \\
German surname      & 0.043 & -0.009  & -0.009  & -0.016  & -0.001  & -0.025  \\
                    &       & -0.015  & -0.015  & -0.015  & -0.024  & -0.025  \\
French surname      & 0.028 & 0.028   & 0.028*  & 0.028   & 0.033   & 0.032   \\
                    &       & -0.017  & -0.017  & -0.017  & -0.027  & -0.028  \\
Continental surname & 0.029 & 0.006   & 0.007   & -0.004  & -0.021  & -0.029  \\
                    &       & -0.018  & -0.018  & -0.018  & -0.032  & -0.032  \\
State fixed effects? &       & N     & N     & Y     & N     & Y     \\
Pseudo R2            &       & 0.043 & 0.044 & 0.087 & 0.048 & 0.115 \\
Observations         & 31336 & 31336 & 31336 & 31330 & 12002 & 12002 \\
\end{tabular}
\end{sidewaystable}

All figures on the table are replicated perfectly. However, the coefficients in bold are estimated with different significance levels (even though the coefficients and their standard errors are the same). For example, we find that the coefficient on Dummy=1 if town population $<9,552$ is significant at the 5 percent level whereas the table in the original paper indicates that it is significant at the 1 percent level in specifications 1, 2, and 3. It is important to note that the difference is not always in the same direction. For instance, we find that the coefficient on French surname in specification 2 is significant at the 10 percent level whereas the original table does not show any significance. Thus, we suspect that this discrepancy might be due to rounding error.

\autoref{effectsocial}: Here, the authors estimate the same equation in logs and include the two outlier companies that were excluded in Table 5 to show the resulting nonlinearity. In the .do file, the outliers are dropped early on and thus their estimations never include these outliers. We save the dataset with the outliers at an early stage so that we can include them in the estimation.

\begin{sidewaystable}
\caption{Effect of social networks on probability of survival, logarithmic form}\footnote{Like in the paper, the estimations exclude the two outlier companies. Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{effectLog}
\begin{tabular}{lllllll}
\hline
                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
Log(number of men in regiment)                     & 3.865  & 0.014++ &         &         &                                     &  \\
                                                   & -1.29  & -0.005  &         &         &                                     &  \\
Log(number of men in company)                      & 2.052  &         & 0.021++ & 0.012   & 0.029                               & 0.022 \\
                                                   & -1.18  &         & -0.007  & -0.006  & -0.012                              & -0.009 \\
Fraction of company with rank sergeant or higher   & 0.072  & 0.134++ & 0.134++ & 0.08    & 0.153                               & 0.084 \\
                                                   & -0.127 & -0.034  & -0.034  & -0.032  & -0.061                              & -0.057 \\
Log(number of men with same last name in regiment) & 0.112  & 0.101++ & 0.095++ & 0.096++ & 0.061++                             & 0.063++ \\
                                                   & -0.305 & -0.012  & -0.012  & -0.011  & -0.018                              & -0.017 \\
Log(number of men in camp from same town)          & 5.114  & -0.004  & 0       & 0.002   & 0.024                               & 0.030++ \\
                                                   & -1.991 & -0.004  & -0.005  & -0.005  & -0.009                              & -0.008 \\
State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.114 \\
Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002                               & 12002 \\
                                                   &        &         &         &         &                                     &  \\
\end{tabular}
\end{sidewaystable}

The first thing to notice is that the number of observations is different. The original paper shows a total of 31,678 observations for the first three specifications, and a total of 12,025 observations for specifications 4 and 5. We have less number of observations mostly due to the 83 observations with missing Fraction of company with rank sergeant or higher variable. We don’t know how the authors included these observations in their estimation.  A minor difference in the first descriptive column is the mean for Log(number of men with same last name in regiment), which is $0.113$ in the paper paper and $0.112$ in our data.

All the coefficients in bold are slightly different from the original table; some are different only in their magnitude but some are also different in their level of significance. For example, the coefficient on Log(number of men in regiment) in specification 1 is $0.011$ with $5\%$ significance level in the paper, whereas we find a higher and more significant effect. Despite these quantitative differences, the results are not qualitatively different.

\autoref{effectLog}: Here, the authors estimate the effect of ethnic networks on probability of survival to show that the quality of the network matters.

\begin{sidewaystable}
\caption{Effect of ethnic network on probability of survival}\footnote{Company clustered standard errors. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{ethnic}
\begin{tabular}{lllllll}
\hline

                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
                                          & b                         & se                         & b                          & se & b & se \\
Number of men in company                  & 0.003*                    & 0.002                      & 0.003                      & 0.001 & 0.002 & 0.002 \\
Number of men of own ethnicity in company & 0.03                      & 0.036                      & 0.03                       & 0.013 & 0.019 & 0.026 \\
Dummy = 1 if Private                      & -0.046                    & 0.049                      & -0.078+                    & 0.037 & -0.093+ & 0.043 \\
From small town                           & 0.1                       & 0.04                       & 0.036                      & 0.031 & 0.054 & 0.036 \\
Captured 1864 or 1865                     & 0.239++                   & 0.077                      & 0.282++                    & 0.049 & 0.388++ & 0.058 \\
Pseudo R2                                 & 0.036                     &                            & 0.059                      &  & 0.058 &  \\
Joint significance test                   & 8.6                       &                            & 22.01                      &  & 3.2 &  \\
Observations                              & 735                       &                            & 1355                       &  & 869 &  \\
\end{tabular}
\end{sidewaystable}

The bold coefficients in \autoref{effectLog} are different in significance levels than what the authors report in their original table (all coefficients and standard errors are the same). The most striking one is the Captured 1864 or 1865 variable for French POWs where the authors find no significance at all and we find significance at the 1 percent level. Since this is too large of a difference to be a rounding error, we suspect that it is a typo.

\subsection{Robustness check - Logit instead of Probit}

As a robustness check, we estimate tables 5-7 with logit instead of probit and results are qualitatively similar. Bold coefficients below show differing levels of significance (only 1-level) when compared to probit.

\begin{sidewaystable}
\caption{Effect of social networks on probability of survival, logit}\footnote{There is no explanation in the paper as to why probit was preferred to logit.}
\label{logit}
\begin{tabular}{lllllll}
\hline
                                                 &         &         &         &         & \multicolumn{2}{l}{From small town} \\
                                                 & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
Number of men in regiment ÷10                    & 9.157   & 0.018++ &         &         &                                     &  \\
                                                 & -10.358 & -0.003  &         &         &                                     &  \\
Number of men in company                         & 12.899  &         & 0.013++ & 0.009++ & 0.014++                             & 0.010++ \\
                                                 & -15.39  &         & -0.003  & -0.002  & -0.004                              & -0.003 \\
Fraction of company with rank sergeant or higher & 0.073   & 0.495++ & 0.526++ & 0.336   & 0.647                               & 0.387 \\
                                                 &         & -0.145  & -0.144  & -0.139  & -0.266                              & -0.251 \\
Number of men with same last name in regiment    & 1.19    & 0.149++ & 0.147++ & 0.158++ & 0.081*                              & 0.101++ \\
                                                 & -0.599  & -0.03   & -0.03   & -0.028  & -0.042                              & -0.038 \\
Log(number of men in camp from same town)        & 5.101   & -0.012  & -0.01   & 0       & 0.075                               & 0.114++ \\
                                                 & -1.994  & -0.019  & -0.019  & -0.019  & -0.038                              & -0.034 \\
Dummy=1 if town population<9552                  & 0.423   & 0.154   & 0.145   & 0.133   &                                     &  \\
                                                 &         & -0.06   & -0.056  & -0.054  &                                     &  \\
Private                                          & 0.824   &         &         &         &                                     &  \\
Officer & 0.003 & 2.342++ & 2.339++ & 2.481++ & 2.043++ & 2.342++ \\
        &       & -0.454  & -0.455  & -0.426  & -0.562  & -0.502  \\
Sergeant             & 0.068 & 0.344++ & 0.344++ & 0.367++ & 0.377++ & 0.407++ \\
                     &       & -0.05   & -0.05   & -0.053  & -0.081  & -0.087  \\
Other rank           & 0.01  & 0.109   & 0.135   & 0.12    & 0.295   & 0.2     \\
                     &       & -0.128  & -0.128  & -0.132  & -0.232  & -0.231  \\
Corporal             & 0.078 & 0.236++ & 0.235++ & 0.201++ & 0.283++ & 0.244++ \\
                     &       & -0.046  & -0.046  & -0.048  & -0.077  & -0.084  \\
Irish surname        & 0.023 & 0.086   & 0.095   & 0.072   & 0.31    & 0.264*  \\
                     &       & -0.081  & -0.081  & -0.082  & -0.14   & -0.146  \\
German surname       & 0.043 & -0.039  & -0.036  & -0.07   & -0.003  & -0.111  \\
                     &       & -0.061  & -0.06   & -0.061  & -0.103  & -0.106  \\
French surname       & 0.028 & 0.113   & 0.117   & 0.119   & 0.14    & 0.152   \\
                     &       & -0.073  & -0.073  & -0.075  & -0.12   & -0.127  \\
Continental surname  & 0.029 & 0.026   & 0.031   & -0.015  & -0.093  & -0.126  \\
                     &       & -0.075  & -0.075  & -0.076  & -0.134  & -0.135  \\
State fixed effects? &       & N       & N       & Y       & N       & Y       \\
Pseudo R2            &       & 0.043   & 0.044   & 0.086   & 0.047   & 0.114   \\
Observations         & 31336 & 31336   & 31336   & 31330   & 12002   & 12002   \\
\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}
\caption{Effect of social networks on probability of survival, logarithmic form, logit}\footnote{Company clustered standard errors are in parentheses. The number of observations for the Fraction of company with rank sergeant or higher variable in the first column is 31605. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{logLogit}
\begin{tabular}{llllllllll}
\hline
                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
Log(number of men in regiment)                     & 3.865  & 0.057   &         &         &                                     &  \\
                                                   & -1.29  & -0.022  &         &         &                                     &  \\
Log(number of men in company)                      & 2.052  &         & 0.088++ & 0.047   & 0.124                               & 0.085 \\
                                                   & -1.18  &         & -0.028  & -0.024  & -0.051                              & -0.04 \\
Fraction of company with rank sergeant or higher   & 0.072  & 0.559++ & 0.552++ & 0.342   & 0.652                               & 0.383 \\
                                                   & -0.127 & -0.147  & -0.145  & -0.139  & -0.266                              & -0.251 \\
Log(number of men with same last name in regiment) & 0.112  & 0.438++ & 0.409++ & 0.416++ & 0.267++                             & 0.277++ \\
                                                   & -0.305 & -0.052  & -0.052  & -0.049  & -0.078                              & -0.074 \\
Log(number of men in camp from same town)          & 5.114  & -0.018  & 0       & 0.006   & 0.100++                             & 0.131++ \\
                                                   & -1.991 & -0.018  & -0.019  & -0.019  & -0.039                              & -0.036 \\
State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.113 \\
Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002 
\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}
\caption{Effect of ethnic networks on probability of survival, logit}\footnote{Standard errors are clustered on the company. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\label{ethLogit}
\begin{tabular}{lllllll}
\hline
                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
                                          & b                         & se                         & b                          & se & b & se \\
Number of men in company                  & 0.009                     & 0.007                      & 0.011*                     & 0.006 & -0.001 & 0.007 \\
Number of men of own ethnicity in company & 0.011                     & 0.11                       & 0.139                      & 0.06 & 0.154 & 0.116 \\
Dummy =1 if Private                       & -0.228                    & 0.214                      & -0.337+                    & 0.162 & -0.445+ & 0.2 \\
From small town                           & 0.417                     & 0.173                      & 0.154                      & 0.131 & 0.23 & 0.154 \\
Captured 1864 or 1865                     & 1.082++                   & 0.347                      & 1.223++                    & 0.227 & 1.826++ & 0.307 \\
Pseudo R2                                 & 0.032                     &                            & 0.058                      &  & 0.055 &  \\
Joint significance test                   & 3.81                      &                            & 18.22                      &  & 2.16 &  \\
Observations                              & 752                       &                            & 1357                       &  & 874 &  \\
\end{tabular}
\end{sidewaystable}

\section{Conclusion}
To sum up our replication, our key message is that while we do find small differences between our results and the published results of \textcite{costa2007surviving}, we find no evidence that would call their conclusions into question, either qualitatively or quantitatively.

Furthermore, the interpretation of the results seems convincing to us. While they cannot test for how friends ensured survival the mentioned explanations from the supply of food to moral support are very comprehensible. In addition, their study is clearly and quite literally made for survival analysis so we do not see space to improve upon the results by applying a different estimation technique. \textcite{costa2007surviving} also apply a wide set of survival analysis tools (e.g. from non-parametric to parametric estimation) so we did not come up with many ideas for robustifying their paper in this direction. Potential future extensions could build on the use of different data sets. A weakness of the paper is clearly that external validity is limited because the authors look at a civil war of the 19th century. For instance, looking at World War I or II data could prove to be fruitful and lead to further insight. While we tried to start with such an extension, we were not able to find a sufficient dataset within this period of time.

To come back to the differences between our replication and the original paper, we consider the most relevant issue the difference in significance levels. Interestingly, when looking into this matter in more detail we find that in almost all cases the p-values are at the margin which clearly points in the direction of a rounding error. We can only speculate that given the lack of exporting commands the reason for this is a certain degree of carelessness and, therefore, would like to emphasize the need of these very exporting commands. Nevertheless, and as mentioned before, the differences do not affect the general message of the paper.

%\appendix

\section{In-text estimation}
Most in-text estimations are not included in the .do files provided, therefore some of the results to follow do not exactly reproduce the ones published, probably due to differences in specifications. They can nonetheless generally be replicated in terms of signs and significance.

\paragraph{Probit statement}
page 1474, line 21 ``When we run a Probit, in which the dependent variable is POW status and the independent variables are economic and geographic characteristics and the number of men in the company who were ever wounded or who ever died, we find that these two company characteristics were the main predictors of POW status. The derivative on the number of men in the company who were ever wounded or who ever died, was $0.257$ (robust $= 0.257$) and the derivative on the number of men who were ever wounded was $0.139$ (robust $= 0.042$).''

\begin{table}[ht]
\centering
\caption{Determinants of POW Status}
\begin{tabular}{lll}
\hline
                          & Marginal Effect & Marginal Effect \\
\% in comp who died        & 0.359***        & 0.430***        \\
                          & -0.021          & -0.0331         \\
\% in comp who wounded     & 0.123***        & 0.140***        \\
                          & -0.0136         & -0.022          \\
Includes property in 1860 & No              & Yes             \\
Observations              & 34878           & 13754           \\
\end{tabular}
\end{table}

\paragraph{Comment on late capture}
page 1474, line 77 ``We also found no evidence of group surrender to become a POW - men who were captured in 1864 and 1865 had more friends, even though a group who surrendered during these years would have no hope of a quick exchange.''

\begin{sidewaystable}
\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity and Late or Early Capture}
\begin{tabular}{lllllllll}
\hline
                     & \multicolumn{4}{c}{Early capture} & \multicolumn{4}{c}{Late capture} \\
                     & \multicolumn{2}{c}{$< 3$}           & \multicolumn{2}{c}{$>= 3$}         & \multicolumn{2}{c}{$< 3$} & \multicolumn{2}{c}{$>= 3$} \\
                     & Mean                              & Std. err.                        & Mean & Std. err. & Mean & Std. err. & Mean & Std. err. \\
US born              & 0.706                             & 0.456                            & 0.77 & 0.421 & 0.709 & 0.455 & 0.738 & 0.44 \\
Irish                & 0.082                             & 0.275                            & 0.109 & 0.311 & 0.136 & 0.343 & 0.14 & 0.347 \\
German               & 0.108                             & 0.311                            & 0.046 & 0.21 & 0.064 & 0.244 & 0.043 & 0.204 \\
British              & 0.053                             & 0.224                            & 0.021 & 0.143 & 0.036 & 0.186 & 0.032 & 0.175 \\
Other                & 0.048                             & 0.213                            & 0.046 & 0.21 & 0.056 & 0.229 & 0.047 & 0.213 \\
Artisan              & 0.233                             & 0.423                            & 0.2 & 0.401 & 0.203 & 0.402 & 0.207 & 0.406 \\
Farmer               & 0.423                             & 0.495                            & 0.355 & 0.479 & 0.451 & 0.498 & 0.444 & 0.497 \\
Prof. or proprietor  & 0.09                              & 0.286                            & 0.075 & 0.264 & 0.069 & 0.253 & 0.053 & 0.225 \\
Laborer              & 0.235                             & 0.425                            & 0.288 & 0.453 & 0.248 & 0.432 & 0.288 & 0.453 \\
Unknown              & 0.019                             & 0.135                            & 0.081 & 0.274 & 0.029 & 0.169 & 0.008 & 0.089 \\
Enlisted in big city & 0.545                             & 0.499                            & 0.497 & 0.501 & 0.461 & 0.499 & 0.42 & 0.494 \\
Property inc in 1860 & 444.889                           & 1056.215                         & 703.517 & 2190.478 & 502.019 & 1099.896 & 620.684 & 2498.66 \\
Age when captured    & 26.079                            & 7.152                            & 24.848 & 6.588 & 26.995 & 7.558 & 25.658 & 6.601 \\
Height when captured & 171.518                           & 6.2                              & 171.377 & 6.914 & 171.959 & 6.495 & 171.338 & 6.765 \\
Officer              & 0.111                             & 0.315                            & 0.092 & 0.289 & 0.065 & 0.247 & 0.049 & 0.217 \\
Married in 1860      & 0.27                              & 0.446                            & 0.246 & 0.432 & 0.279 & 0.449 & 0.233 & 0.423 \\
Fraction company dead before capture & 0.056 & 0.054 & 0.057 & 0.046 & 0.116 & 0.069 & 0.112 & 0.054 \\
Company birthplace fragmentation     & 0.554 & 0.183 & 0.516 & 0.238 & 0.543 & 0.199 & 0.553 & 0.173 \\
Company occupational fragmentation   & 0.587 & 0.173 & 0.614 & 0.177 & 0.586 & 0.173 & 0.601 & 0.168 \\
\end{tabular}
\end{sidewaystable}

\paragraph{OLS statement}
page 1474 line 65 and footnote 22. ``When we ran an OLS regression of the number of friends on the covariates we later use in our hazard specification, we found that professionals and proprietors, the Irish, older men, and the recently wounded were less likely to have many friends, whereas those from a large city had more friends''... ``The coefficient on recently wounded was $-0.879$ ($= 0.397$).''

\begin{table}[ht]
\centering
\caption{Determinants of number of friends}
\begin{tabular}{ll}
\hline
Professional or proprietor     & -0.913***  \\
                               & -0.0979    \\
Irish                          & -0.267***  \\
                               & -0.0984    \\
Age at capture                 & -0.0391*** \\
                               & -0.00504   \\
Wounded 10 days before capture & -0.831***  \\
                               & -0.0876    \\
Large city                     & 0.553***   \\
                               & -0.0649    \\
Observations                   & 23256      \\
R-squared                      & 0.152      \\
\end{tabular}
\end{table}

\paragraph{Predicted probability of death}
page 1475, line 24. ``As the number of friends increases from 0 to 5, the predicted probability of death, using the second specification in Table 3, decreases from $0.31$ to $0.28$, and as the number of friends increases to $10$, the predicted mortality probability falls to $0.26$. (The mean number of friends in each month was $5.6$, with a standard deviation of $9.2$, and the median was $2$.)''

\begin{table}[ht]
\centering
\caption{Number of Friends}
\begin{tabular}{lll}
\hline
          & Initial & In estimation \\
Mean      & 5.58    & 2.87          \\
Std. Dev. & 9.22    & 5.12          \\
Median    & 2       & 1             \\
\end{tabular}
\end{table}

The summary statistics mentioned for the variable friends match the initial file, but not the data that is actually included in the regression.

\begin{figure}[ht]
\centering
\caption{Exponential specification}
\label{exponential}
\includegraphics[scale=0.65]{exponential.png}
\end{figure}

The file ``survival.dta'' contains the predicted survival probability for individuals with 0, 5 and 10 friends (evaluated at means for the other covariates). The statement did not specify a point in time, but we find a coincidence with the statement at $t=330.76$ (average days of imprisonment was $131.62$).

\paragraph{Table 3 with regiment fixed effects}
page 1476, line 2. ``Even when we included state of regiment fixed effects, the hazard ratio on the number of friends remained virtually unchanged (e.g. the hazard ratio on the initial number of friends was $0.976$, $=0.009$).''

\begin{sidewaystable}
\caption{Table 3 with regiment state effects}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\begin{tabular}{lllllll}
\hline
                                         & Hazard rate & Std. err & Hazard rate & Std. err & Hazard rate & Std. err \\
Number of friends                        & 0.984*      & -0.009   & 0.978       & -0.009   &             &          \\
Initial number of friends                &             &          &             &          & 0.976++     & -0.009   \\
Ln(number of prisoners in camp)          &             &          & 1.538++     & -0.141   & 1.525++     & -0.14    \\
Fraction of company dying before capture & 1.427       & -1.227   & 1.19        & -1.011   & 0.787       & -0.653   \\
Professional or proprietor               & 0.512       & -0.134   & 0.506++     & -0.131   & 0.502++     & -0.13    \\
Artisan                                  & 0.862       & -0.114   & 0.862       & -0.114   & 0.851       & -0.112   \\
Laborer                                  & 1.163       & -0.148   & 1.154       & -0.146   & 1.141       & -0.145   \\
German                                   & 1.135       & -0.213   & 1.116       & -0.21    & 1.103       & -0.206   \\
Irish                                    & 0.731*      & -0.118   & 0.723       & -0.116   & 0.723       & -0.115   \\
British                                  & 0.616*      & -0.167   & 0.630*      & -0.17    & 0.637*      & -0.174   \\
Other                                    & 0.612       & -0.145   & 0.603       & -0.144   & 0.602       & -0.143   \\
Sergeant, corporal or officer            & 0.570++     & -0.117   & 0.561++     & -0.113   & 0.557++     & -0.112   \\
Age at captivity                         & 1.042++     & -0.008   & 1.040++     & -0.007   & 1.040++     & -0.007   \\
Height at enlistment                     & 1.014*      & -0.007   & 1.014*      & -0.007   & 1.014*      & -0.007   \\
Observations                             & 3026        &          & 3026        &          & 3026        &          \\
Number of subjects                       & 23174       &          & 23174       &          & 23174       &          \\
Log pseudo likelihood                    & -1307.77    &          & -1291.45    &          & -1290.674   &          \\
\end{tabular}
\end{sidewaystable}

\paragraph{Table 3 with splines}
page 1476, line 6 and footnote 23 ``Our experiments with splines suggested that the marginal effect of a friend on survival was greater for the first two friends than for more."  Footnote 23: "The hazard rate on the marginal effect of fewer than three friends was $0.956$ ($=0.044$) and the hazard rate on the marginal effect of three or more friends was $0.980$ ($=0.011$). Although the first hazard rate was not statistically significantly different from one, the two terms together were jointly significant.''

\begin{table}[ht]
\centering
\caption{Spline at 3}
\begin{tabular}{ll}
\hline
                     & Hazard rate \\
Fewer than 3 friends & 0.956       \\
                     & -0.0443     \\
3 or more friends    & 0.980*      \\
                     & -0.0108     \\
Observations         & 23256       \\
Chi-sq               & 7.789       \\
Prob > chi-sq        & 0.0204      \\
\end{tabular}
\end{table}

\paragraph{Weibull specification}
page 1477, line 12. ``When we use a Weibull rather than an exponential specification, we found no evidence of duration dependence...''

\begin{sidewaystable}
\caption{Weibul}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\begin{tabular}{llllllllll}
\hline
                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
VARIABLES                                & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
Number of friends                        & 0.986                               & -0.009                              & 0.979                               & -0.009 &  &  \\
Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
Ln(number of prisoners in camp)          &                                     &                                     & 1.531++                             & -0.139 & 1.517++ & -0.139 \\
Fraction of company dying before capture & 1.242                               & -0.897                              & 1.008                               & -0.722 & 0.733 & -0.525 \\
Professional or propietor                & 0.566                               & -0.147                              & 0.562                               & -0.144 & 0.554 & -0.142 \\
Artisan                                  & 0.95                                & -0.121                              & 0.952                               & -0.12 & 0.942 & -0.119 \\
Laborer                                  & 1.308                               & -0.157                              & 1.303                               & -0.154 & 1.296 & -0.154 \\
German                                   & 1.198                               & -0.218                              & 1.169                               & -0.212 & 1.153 & -0.209 \\
Irish                                    & 0.771                               & -0.123                              & 0.765*                              & -0.12 & 0.753* & -0.118 \\
British                                  & 0.630*                              & -0.17                               & 0.644                               & -0.174 & 0.646 & -0.176 \\
Other                                    & 0.656*                              & -0.155                              & 0.643*                              & -0.153 & 0.640* & -0.151 \\
Sargeant, corporal or officer            & 0.536++                             & -0.114                              & 0.531++                             & -0.11 & 0.528++ & -0.11 \\
Age at captivity                         & 1.046++                             & -0.008                              & 1.045++                             & -0.008 & 1.045++ & -0.008 \\
Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
Log pseudo likelihood                    & -1322.852                           &                                     & -1306.836                           &  & -1305.627 &  \\
Duration dependence                      & 1.088                               &                                     & 1.08                                &  & 1.084 &  \\
\end{tabular}
\end{sidewaystable}

\paragraph{Month dummies}
page 1477, line 19. ``When we included dummy variables in our specification indicating that an individual had survived 1, 2, 3 or more months, we found that those who had survived one or two months were less likely to die than those still in their first month of captivity, but that the advantage of having survived a third month was small and there was no advantage to having survived a fourth month.''

\begin{sidewaystable}
\caption{controlling for months survived}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\begin{tabular}{lllllll}
\hline
                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
                                         & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
Number of friends                        & 0.989                               & -0.009                              & 0.982*                              & -0.009 &  &  \\
Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
Ln(number of prisoners in camp)          &                                     &                                     & 1.612++                             & -0.146 & 1.604++ & -0.145 \\
Fraction of company dying before capture & 1.368                               & -1.001                              & 1.117                               & -0.811 & 0.832 & -0.603 \\
Professional or propietor                & 0.56                                & -0.145                              & 0.557                               & -0.142 & 0.547 & -0.14 \\
Artisan                                  & 0.946                               & -0.121                              & 0.951                               & -0.121 & 0.939 & -0.12 \\
Laborer                                  & 1.302                               & -0.158                              & 1.302                               & -0.156 & 1.298 & -0.156 \\
German                                   & 1.22                                & -0.223                              & 1.195                               & -0.216 & 1.178 & -0.213 \\
Irish                                    & 0.774                               & -0.125                              & 0.770*                              & -0.122 & 0.756* & -0.12 \\
British                                  & 0.618*                              & -0.168                              & 0.632*                              & -0.172 & 0.634* & -0.174 \\
Other                                    & 0.658*                              & -0.156                              & 0.650*                              & -0.156 & 0.647* & -0.154 \\
Sargeant, corporal or officer            & 0.533++                             & -0.114                              & 0.531++                             & -0.111 & 0.526++ & -0.11 \\
Age at captivity                         & 1.047++                             & -0.008                              & 1.046++                             & -0.008 & 1.045++ & -0.008 \\
Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
Survived 1 month                         & 0.407++                             & -0.08                               & 0.362++                             & -0.072 & 0.352++ & -0.071 \\
Survived 2 months                        & 0.472++                             & -0.092                              & 0.401++                             & -0.08 & 0.393++ & -0.078 \\
Survived 3 months                        & 0.74                                & -0.137                              & 0.64                                & -0.12 & 0.631 & -0.118 \\
Survived 4 or more months                & 0.833                               & -0.134                              & 0.745*                              & -0.12 & 0.740* & -0.119 \\
Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
Log pseudo likelihood                    & -1307.333                           &                                     & -1287.9                             &  & -1285.595 &  \\
\end{tabular}
\end{sidewaystable}

\paragraph{Cox Proportional Hazard Model}
page 1477, line 26 footnote.
``We also investigated the use of a Cox proportional hazard model to allow the baseline hazard to rise or fall in any month. Controlling for camp conditions, we obtained a statistically insignificant hazard ratio on friends of $0.987$ ($=0.009$). We suspect that we are losing power because of our small sample size.''

\begin{sidewaystable}
\caption{Cox proportional models}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\begin{tabular}{lllllll}
\hline
                                         & Hazard rate & Std. err. & Hazard rate & Std. err. & Hazard rate & Std. err. \\
Number of friends                        & 0.992       & -0.009    & 0.987       & -0.009    &             &           \\
Initial number of friends                &             &           &             &           & 0.978       & -0.009    \\
Ln(number of prisoners in camp)          &             &           & 1.593++     & -0.149    & 1.587++     & -0.149    \\
Fraction of company dying before capture & 1.751       & -1.298    & 1.558       & -1.148    & 1.179       & -0.867    \\
Professional or propietor                & 0.557       & -0.144    & 0.556       & -0.142    & 0.546       & -0.139    \\
Artisan                                  & 0.942       & -0.121    & 0.952       & -0.122    & 0.938       & -0.12     \\
Laborer                                  & 1.284       & -0.157    & 1.287       & -0.157    & 1.284       & -0.156    \\
German                                   & 1.241       & -0.228    & 1.218       & -0.223    & 1.2         & -0.22     \\
Irish                                    & 0.765       & -0.126    & 0.763*      & -0.123    & 0.746*      & -0.121    \\
British                                  & 0.613*      & -0.166    & 0.625*      & -0.169    & 0.626*      & -0.171    \\
Other                                    & 0.658*      & -0.159    & 0.652*      & -0.159    & 0.649*      & -0.158    \\
Sargeant, corporal or officer            & 0.538++     & -0.115    & 0.537++     & -0.113    & 0.532++     & -0.112    \\
Age at captivity                         & 1.048++     & -0.008    & 1.046++     & -0.008    & 1.046++     & -0.008    \\
Height at entlistment                    & 1.01        & -0.008    & 1.01        & -0.007    & 1.011       & -0.007    \\
Observations                             & 23256       &           & 23256       &           & 23256       &           \\
Log pseudo likelihood                    & -3102.845   &           & -3086.134   &           & -3083.63    &           \\
\end{tabular}
\end{sidewaystable}

\begin{table}[ht]
\centering
\caption{table 4 net transfer}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\begin{tabular}{lll}
\hline
VARIABLES               & Hazard Rate & Std. err. \\
Net transfer of friends & 0.946**     & -0.024    \\
Observations            & 15998       &           \\
\end{tabular}
\end{table}

\paragraph{On limiting the sample}
page 1480, line 17. ``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged. The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).

\paragraph{On the mortality of privates}
page 1480, line 54. ``The fraction of sergeants or higher rank is not a reflection of own officer mortality. When we restricted the sample to privates, we found that the derivative of this coefficient was 0.115 (sdev=0.054).''

\paragraph{On the role of networks in predicting escape from Andersonville}
page 1482, line 25. ``Also suggestive of friends not always helping survival is that, among the men at Andersonville, we find no evidence that the number of friends predicted whether an individual was one of the 140 escaped.''

See table below for the final three verifications:

\begin{sidewaystable}
\caption{Final three specifications}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
\begin{tabular}{llll}
\hline
                                                 & Dependent variable: Lived & Dependent variable: Lived & Dependent variable: Escaped \\
                                                 & Shorter time period       & Privates only             &                             \\
Number of men in company                         & 0.003++                   & 0.003++                   & 0                           \\
                                                 & -0.001                    & -0.001                    & 0                           \\
Fraction of company with rank sergeant or higher & 0.115                     & 0.139++                   & -0.001                      \\
                                                 & -0.054                    & -0.036                    & -0.002                      \\
Number of men with same last name in regiment    & 0.033++                   & 0.035++                   & 0                           \\
                                                 & -0.007                    & -0.007                    & 0                           \\
Log(number of men in camp from same town)        & -0.003                    & -0.001                    & 0                           \\
                                                 & -0.005                    & -0.005                    & 0                           \\
Pseudo R2                                        & 0.036                     & 0.047                     & 0.015                       \\
Observations                                     & 25880                     & 27923                     & 28190                       \\
\end{tabular}
\end{sidewaystable}

The only in-text claim that we are not able to confirm is their statement that there is no mortality difference between the colored non-officers and the rest of the Andersonville POWs (page 1480, footnote 29) as we don’t have any information on the race of the POWs.

\section{Non-parametric estimation}
The following figures are our replications of the Kaplan-Meier survival estimates which show no differences to the original:

\begin{figure}
\centering
\caption{Kaplan-Meier survival estimate}
\label{kmSurvival}
\includegraphics[scale=0.3]{kaplan1.png}
\end{figure}

\begin{figure}
\centering
\caption{Kaplan-Meier survival estimates by early and late capture date}
\label{kmCapture}
\includegraphics[scale=0.3]{kaplan2.png}
\end{figure}

\begin{figure}
\centering
\caption{Kaplan-Meier survival estimates by camp for late captures}
\label{kmCamp}
\includegraphics[scale=0.3]{kaplan3.png}
\end{figure}

\begin{figure}
\centering
\caption{Kaplan-Meier survival estimates by number of friends for Anderson}
\label{kmNumber}
\includegraphics[scale=0.3]{kaplan4.png}
\end{figure}

\vspace{\stretch{1}}

\printbibliography

\pagebreak

\end{document}

### 2013-11-13 draft.Rnw
minor
add packages, add bibliography
revert to book docu class
add morris shin citation

--- 2013-11-13 draft.Rnw
@@
-\documentclass[a4paper]{report}
+\documentclass[a4paper]{book}
 \usepackage{subfiles}
-\usepackage{hyperref}
+\usepackage{mathtools}
+\usepackage{rotating}
+\usepackage{graphicx}
+\usepackage[authordate,backend=biber]{biblatex-chicago}
+\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
 
@@
 
+\let\oldmarginpar\marginpar
+\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]
+{\raggedright\footnotesize #1}}
+
+\addbibresource{bibliography.bib}
+
+\newbibmacro{string+doiurlisbn}[1]{%
+  \iffieldundef{doi}{%
+    \iffieldundef{url}{%
+      \iffieldundef{isbn}{%
+        \iffieldundef{issn}{%
+          #1%
+        }{%
+          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
+        }%
+      }{%
+        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
+      }%
+    }{%
+      \href{\thefield{url}}{#1}%
+    }%
+  }{%
+    \href{http://dx.doi.org/\thefield{doi}}{#1}%
+  }%
+}
+
+\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
+\DeclareFieldFormat[article,incollection]{title}%
+    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}
+
 \begin{document}
 
+\frontmatter
 \maketitle
-
 \tableofcontents
 
-\chapter*{Introduction}
+\chapter{Introduction}
 jade
 
+\mainmatter
 \chapter{South Africa}
@@
 
-\chapter{Surviving Andersonville}
-article
+\subfile{surviving.tex}
 
@@
 
-\chapter{Morris Shin 1998, Unique equilibrium in a model of self-fulfilling currency attacks}
-\subfile{MorrisShin.tex}
+\subfile{morrisShin.tex}
 
-\chapter*{End notes}
+\backmatter
+\chapter{End notes}
+
+\printbibliography
 

### 2013-11-13 draft.tex
minor
add packages, add bibliography
revert to book docu class
add morris shin citation

--- 2013-11-13 draft.tex
@@
-\documentclass[a4paper]{report}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[a4paper]{book}\usepackage{graphicx, color}
 %% maxwidth is the original width if it is less than linewidth
@@
 
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
+\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
+\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
+\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
+\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
+\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
+\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
+\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
+\newcommand{\hlslot}[1]{\textit{#1}}%
+\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
 
@@
 \usepackage{subfiles}
-\usepackage{hyperref}
+\usepackage{mathtools}
+\usepackage{rotating}
+\usepackage{graphicx}
+\usepackage[authordate,backend=biber]{biblatex-chicago}
+\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
 
@@
 \author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}}
+
+\let\oldmarginpar\marginpar
+\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]
+{\raggedright\footnotesize #1}}
+
+\addbibresource{bibliography.bib}
+
+\newbibmacro{string+doiurlisbn}[1]{%
+  \iffieldundef{doi}{%
+    \iffieldundef{url}{%
+      \iffieldundef{isbn}{%
+        \iffieldundef{issn}{%
+          #1%
+        }{%
+          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
+        }%
+      }{%
+        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
+      }%
+    }{%
+      \href{\thefield{url}}{#1}%
+    }%
+  }{%
+    \href{http://dx.doi.org/\thefield{doi}}{#1}%
+  }%
+}
+
+\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
+\DeclareFieldFormat[article,incollection]{title}%
+    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 
+\frontmatter
 \maketitle
-
 \tableofcontents
 
-\chapter*{Introduction}
+\chapter{Introduction}
 jade
 
+\mainmatter
 \chapter{South Africa}

### 2013-11-13 draft.Rnw
functioning refsections
update frontpage

@@
 
-\title{Preliminary Thesis Defence}
-%\subtitle{
-%\begin{tabular}{rl}
-%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
-%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
-%\end{tabular}
-%}
+\title{Preliminary Thesis Defence\\~\\
+\begin{tabular}{rl}
+Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
+Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
+\end{tabular}
+}
 
@@
 
-\addbibresource{bibliography.bib}
+\addglobalbib{bibliography.bib}
 
@@
 
+\begin{refsection}
 \subfile{surviving.tex}
+\printbibliography
+\end{refsection}
 
@@
 
+\begin{refsection}
 \subfile{morrisShin.tex}
+\parencite{morris1998unique}
+\printbibliography
+\end{refsection}
 

### 2013-11-14 draft.Rnw
correct name lore

@@
 Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
-Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
+Second Reader:&Lore Vandewalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
 \end{tabular}

### 2013-11-14 distributions.tex
included distributions (inc. R code)

\documentclass[draft.tex]{subfiles}

\begin{document}

\section{Modelling probabilistic beliefs for single agents as
distributions, incorporating changes and apparent incommensurability.}

\section{Abstract}

By constructing a distribution of the belief structure of a single
agent, we can mitigate seemingly incommensurable beliefs. This paper
proposes to generalise the concept of a single agents beliefs, from a
point estimate to a distributional approximation. This will allow us to
deal with differing estimates of the probability \emph{p}, as well as
%with estimates of \emph{p} and \emph{¬p} violating unitarity, in
meaningful way. Additionally with a distributional approximation, we can
estimate agents' beliefs, using the state which they are in.

\section{Introduction}

It generally held to be so that people sometimes hold beliefs which are
incommensurable with each other. In technical terms we could say, the
knowledge base is interally inconsistent. This incommensurability
becomes especially apparent when these beliefs are quantified.

As an example consider the following. If we have the probability of some
event \emph{e} occuring with probability \emph{p}. By definition, all
probabilities are exhausted at \emph{1}. Therefore the probability of
that event not occuring (i.e. \emph{¬p} or \emph{not p}) is \emph{1-p}.

\begin{quote}
¬p = 1 - p
\end{quote}

It is often observed, that people hold beliefs that do not meet this
condition, these beliefs can thus be described as:

\begin{quote}
¬p ≠ 1 - p
\end{quote}

In addition to this, we often see that people have different beliefs
about the same thing, often just moments apart (e.g.~beginning and end
of a survey). This could be the case for many (unrelated) reasons, such
as, fatigue, hunger, anchoring, etc. We can express this as:

\begin{quote}
p\_1(e) ≠ p\_2(e)
\end{quote}

We are thus faced with the fact that we get responses from agents

In this paper I describe how we can generalise the idea of perception of
probability -for a single agent- from a point estimate, to a
distributional approximation.

Doing this will allow us to deal with seemingly inconsistent beliefs in
a single framework in a \emph{meaningful} way.

\section{An example}

On a fair die, the chance of throwing 3 eyes is 16, call this \emph{p}.
The chance that you do not throw 3 eyes (i.e. \emph{¬p}) is therefore
\emph{1-p}, or

<<die, eval=TRUE>>=
1 - (1/6)
@

This is a very simple statistical exercise, and most people will be able
to give you the answer that I derived. The reason for this is that
people learn to use dice and how they operate, in e.g.~board games.
Likewise for coin flipping and many other basic statistical trials. In
this context, you would rarely find people accepting a bet that has a
negative expected value. Such as non-equal payout for a fair coin flip.

However, as soon as odds become less transparent, statistical methods
are often applied with less rigour. Especially when dealing with
observed implicit payout structures. As a results bets with negative
expected payouts, such as lotteries, are often accepted.

Let us continue with the idea of a lottery. For a lottery at the local
sports club, 100 tickets were printed, yet only 5 out of every 8 tickets
was sold, therefore tickets will be drawn until a winner is found. The
price of a ticket is 1 apple, and the prize for the winner is 50 apples.

Our victim is called Janus. After Janus buys a ticket for the lottery,
we ask him the following questions.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  What is the chance (in percent) that you will win the lottery?
\item
  What is the chance (as a ratio) that someone else will win the
  lottery?
\item
  What is the chance that nobody wins the lottery?
\item
  You came with one apple, with how many apples do you expect to walked
  away?
\item
  What is the chance (as a ratio) that you will win the lottery?
\end{enumerate}

The first question is not very hard:

% R block

But perhaps it is something you wouldn't always do without a calculator
or at least pen and paper. The second probability is:

Definitely something most people would do on paper. However, since we
are at the sports club, this is something we might not have at hand.

As can be seen, question (1) and (5) are identical. If you go through
the questions without having done the calculations beforehand, you will
likely be inclined to give a lower answer to (5) than you were to (1).
Presumable you would be quite neutral when answering question (1). Yet
the question preceding question (5) is rather negative, since you would
probably expect to walk away with zero apples, this would lead you to be
in a more negative mood when answering (5). Furthermore, you could have
become tired of answering so many questions, which generally diminishes
your perception of your chance of being successful.

Janus acts very much in accordance with our expectations, and gives us
the following responses.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  2\% (has to be more than two)
\item
  19/20
\item
  0
\item
  0
\item
  1/60
\end{enumerate}

Normally we would take either one of the responses, or such some other
way to come to a point estimate, such as averaging.

\section{As a distribution}

Let us assume that question (2) was answered in an slightly optimistic
state, and question 6 in a slightly pessimistic state. Furthermore, let
us assume that beliefs are normally distributed, and that these slightly
pessimistic and slightly optimistic state are each away from the mean,
below and above respectively. Lets express (5) as a number: 0.0167. We
can now construct the standard deviation.

% R block

We can now define our subjects beliefs on winning the lottery as:

\begin{quote}
B\textasciitilde{}N(0.0167,0.00167)
\end{quote}

Let us now suppose that our subject loses his wallet before the winner
is drawn. If we want to predict how is beliefs have changed, we can for
example assume that they are now 2below is mean belief. This would thus
give us:

% R block

If however, Janus there after is in a euphoric state because he find his
wallet again, and on top of this a nice shiny green apple, than his new
belief might change to \emph{3s} above his mean level. Which would give
us:

% R block

\begin{quote}
p anp (1-p)
\end{quote}

How do we match the answers to questions (2) and (3), the chance that
Janus thinks he has of winning, with the chance that somebody else win
(i.e.~that he does not win). Let us write both odds as numbers:

\begin{quote}
p\_1 = 0.02 1 - p\_2 = 0.95 =\textgreater{} p\_2 = 0.05
\end{quote}

Let us suppose that the estimate of \emph{p} was positive by one and
that the estimate of \emph{1-p} was positive by \emph{3s} then we know:

% R Block

\section{An application}

Estimation of a 95\% confidence interval for a belief on probability,
how the lottery profit from this.

\section{Now\ldots{}for something much more important}

\href{http://www.youtube.com/watch?v=FVwtTrlPSSk}{A video of a penguin
being tickled}

\end{document}

### 2013-11-14 draft.Rnw
included distributions (inc. R code)
R code working

@@
 \begin{refsection}
+\chapter{Replication of: ``Surviving Andersonville''}
 \subfile{surviving.tex}
@@
 
-\chapter{Single-Agent Belief Distritutions}
-examples
+\chapter{Single-Agent Belief Distributions}
+
+\section{Modelling probabilistic beliefs for single agents as
+distributions, incorporating changes and apparent incommensurability.}
+
+\section{Abstract}
+
+By constructing a distribution of the belief structure of a single
+agent, we can mitigate seemingly incommensurable beliefs. This paper
+proposes to generalise the concept of a single agents beliefs, from a
+point estimate to a distributional approximation. This will allow us to
+deal with differing estimates of the probability \emph{p}, as well as
+with estimates of \emph{p} and \emph{¬p} violating unitarity, in
+meaningful way. Additionally with a distributional approximation, we can
+estimate agents' beliefs, using the state which they are in.
+
+\section{Introduction}
+
+It generally held to be so that people sometimes hold beliefs which are
+incommensurable with each other. In technical terms we could say, the
+knowledge base is interally inconsistent. This incommensurability
+becomes especially apparent when these beliefs are quantified.
+
+As an example consider the following. If we have the probability of some
+event \emph{e} occuring with probability \emph{p}. By definition, all
+probabilities are exhausted at \emph{1}. Therefore the probability of
+that event not occuring (i.e. \emph{¬p} or \emph{not p}) is \emph{1-p}.
+
+\begin{quote}
+¬p = 1 - p
+\end{quote}
+
+It is often observed, that people hold beliefs that do not meet this
+condition, these beliefs can thus be described as:
+
+\begin{quote}
+¬p ≠ 1 - p
+\end{quote}
+
+In addition to this, we often see that people have different beliefs
+about the same thing, often just moments apart (e.g.~beginning and end
+of a survey). This could be the case for many (unrelated) reasons, such
+as, fatigue, hunger, anchoring, etc. We can express this as:
+
+\begin{quote}
+p\_1(e) ≠ p\_2(e)
+\end{quote}
+
+We are thus faced with the fact that we get responses from agents
+
+In this paper I describe how we can generalise the idea of perception of
+probability -for a single agent- from a point estimate, to a
+distributional approximation.
+
+Doing this will allow us to deal with seemingly inconsistent beliefs in
+a single framework in a \emph{meaningful} way.
+
+\section{An example}
+
+On a fair die, the chance of throwing 3 eyes is 16, call this \emph{p}.
+The chance that you do not throw 3 eyes (i.e. \emph{¬p}) is therefore
+\emph{1-p}, or
+
+<<die, eval=TRUE>>=
+1 - (1/6)
+@
+
+This is a very simple statistical exercise, and most people will be able
+to give you the answer that I derived. The reason for this is that
+people learn to use dice and how they operate, in e.g.~board games.
+Likewise for coin flipping and many other basic statistical trials. In
+this context, you would rarely find people accepting a bet that has a
+negative expected value. Such as non-equal payout for a fair coin flip.
+
+However, as soon as odds become less transparent, statistical methods
+are often applied with less rigour. Especially when dealing with
+observed implicit payout structures. As a results bets with negative
+expected payouts, such as lotteries, are often accepted.
+
+Let us continue with the idea of a lottery. For a lottery at the local
+sports club, 100 tickets were printed, yet only 5 out of every 8 tickets
+was sold, therefore tickets will be drawn until a winner is found. The
+price of a ticket is 1 apple, and the prize for the winner is 50 apples.
+
+Our victim is called Janus. After Janus buys a ticket for the lottery,
+we ask him the following questions.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  What is the chance (in percent) that you will win the lottery?
+\item
+  What is the chance (as a ratio) that someone else will win the
+  lottery?
+\item
+  What is the chance that nobody wins the lottery?
+\item
+  You came with one apple, with how many apples do you expect to walked
+  away?
+\item
+  What is the chance (as a ratio) that you will win the lottery?
+\end{enumerate}
+
+The first question is not very hard:
+
+<<first, eval=TRUE>>=
+1/(100 * (5*8))
+@
+
+But perhaps it is something you wouldn't always do without a calculator
+or at least pen and paper. The second probability is:
+
+Definitely something most people would do on paper. However, since we
+are at the sports club, this is something we might not have at hand.
+
+As can be seen, question (1) and (5) are identical. If you go through
+the questions without having done the calculations beforehand, you will
+likely be inclined to give a lower answer to (5) than you were to (1).
+Presumable you would be quite neutral when answering question (1). Yet
+the question preceding question (5) is rather negative, since you would
+probably expect to walk away with zero apples, this would lead you to be
+in a more negative mood when answering (5). Furthermore, you could have
+become tired of answering so many questions, which generally diminishes
+your perception of your chance of being successful.
+
+Janus acts very much in accordance with our expectations, and gives us
+the following responses.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  2\% (has to be more than two)
+\item
+  19/20
+\item
+  0
+\item
+  0
+\item
+  1/60
+\end{enumerate}
+
+We observe two different estimates of the same \emph{p(e)}.
+
+<<p1, eval=TRUE>>=
+p_1 = 1/100
+p_1
+@
+
+<<p2, eval=TRUE>>=
+p_2 = 1/60
+p_2
+@
+
+Normally we would take either one of the responses, or such some other
+way to come to a point estimate, such as averaging.
+
+\section{As a distribution}
+
+Let us assume that question (2) was answered in an slightly optimistic
+state, and question 6 in a slightly pessimistic state. Furthermore, let
+us assume that beliefs are normally distributed, and that these slightly
+pessimistic and slightly optimistic state are each away from the mean,
+below and above respectively. Lets express (5) as a number: 0.0167. We
+can now construct the standard deviation.
+
+<<mu, eval=TRUE>>=
+mu = p_1
+mu
+@
+
+<<sigma, eval=TRUE>>=
+sigma = p_2 - mu
+sigma
+@
+
+We can now define our subjects beliefs on winning the lottery as:
+
+\begin{quote}
+B\textasciitilde{}N(0.0167,0.00167)
+\end{quote}
+
+Let us now suppose that our subject loses his wallet before the winner
+is drawn. If we want to predict how is beliefs have changed, we can for
+example assume that they are now 2below is mean belief. This would thus
+give us:
+
+<<mu-sigma, eval=TRUE>>=
+mu - sigma
+@
+
+If however, Janus there after is in a euphoric state because he find his
+wallet again, and on top of this a nice shiny green apple, than his new
+belief might change to \emph{3s} above his mean level. Which would give
+us:
+
+<<mu+2sigma, eval=TRUE>>=
+mu + 2 * sigma
+@
+
+\begin{quote}
+p anp (1-p)
+\end{quote}
+
+How do we match the answers to questions (2) and (3), the chance that
+Janus thinks he has of winning, with the chance that somebody else win
+(i.e.~that he does not win). Let us write both odds as numbers:
+
+\begin{quote}
+p\_1 = 0.02 1 - p\_2 = 0.95 =\textgreater{} p\_2 = 0.05
+\end{quote}
+
+Let us suppose that the estimate of \emph{p} was positive by one and
+that the estimate of \emph{1-p} was positive by \emph{3s} then we know:
+
+% R Block
+
+\section{An application}
+
+Estimation of a 95\% confidence interval for a belief on probability,
+how the lottery profit from this.
+
+\section{Now\ldots{}for something much more important}
+
+\href{http://www.youtube.com/watch?v=FVwtTrlPSSk}{A video of a penguin
+being tickled}
 
@@
 
-\printbibliography
-
 \end{document}

### 2013-11-14 draft.tex
included distributions (inc. R code)
R code working

@@
 
-\chapter{Single-Agent Belief Distritutions}
-examples
+\chapter{Single-Agent Belief Distributions}
+
+\section{Modelling probabilistic beliefs for single agents as
+distributions, incorporating changes and apparent incommensurability.}
+
+\section{Abstract}
+
+By constructing a distribution of the belief structure of a single
+agent, we can mitigate seemingly incommensurable beliefs. This paper
+proposes to generalise the concept of a single agents beliefs, from a
+point estimate to a distributional approximation. This will allow us to
+deal with differing estimates of the probability \emph{p}, as well as
+with estimates of \emph{p} and \emph{¬p} violating unitarity, in
+meaningful way. Additionally with a distributional approximation, we can
+estimate agents' beliefs, using the state which they are in.
+
+\section{Introduction}
+
+It generally held to be so that people sometimes hold beliefs which are
+incommensurable with each other. In technical terms we could say, the
+knowledge base is interally inconsistent. This incommensurability
+becomes especially apparent when these beliefs are quantified.
+
+As an example consider the following. If we have the probability of some
+event \emph{e} occuring with probability \emph{p}. By definition, all
+probabilities are exhausted at \emph{1}. Therefore the probability of
+that event not occuring (i.e. \emph{¬p} or \emph{not p}) is \emph{1-p}.
+
+\begin{quote}
+¬p = 1 - p
+\end{quote}
+
+It is often observed, that people hold beliefs that do not meet this
+condition, these beliefs can thus be described as:
+
+\begin{quote}
+¬p ≠ 1 - p
+\end{quote}
+
+In addition to this, we often see that people have different beliefs
+about the same thing, often just moments apart (e.g.~beginning and end
+of a survey). This could be the case for many (unrelated) reasons, such
+as, fatigue, hunger, anchoring, etc. We can express this as:
+
+\begin{quote}
+p\_1(e) ≠ p\_2(e)
+\end{quote}
+
+We are thus faced with the fact that we get responses from agents
+
+In this paper I describe how we can generalise the idea of perception of
+probability -for a single agent- from a point estimate, to a
+distributional approximation.
+
+Doing this will allow us to deal with seemingly inconsistent beliefs in
+a single framework in a \emph{meaningful} way.
+
+\section{An example}
+
+On a fair die, the chance of throwing 3 eyes is 16, call this \emph{p}.
+The chance that you do not throw 3 eyes (i.e. \emph{¬p}) is therefore
+\emph{1-p}, or
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+1 - (1/6)
+\end{alltt}
+\begin{verbatim}
+## [1] 0.8333
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+This is a very simple statistical exercise, and most people will be able
+to give you the answer that I derived. The reason for this is that
+people learn to use dice and how they operate, in e.g.~board games.
+Likewise for coin flipping and many other basic statistical trials. In
+this context, you would rarely find people accepting a bet that has a
+negative expected value. Such as non-equal payout for a fair coin flip.
+
+However, as soon as odds become less transparent, statistical methods
+are often applied with less rigour. Especially when dealing with
+observed implicit payout structures. As a results bets with negative
+expected payouts, such as lotteries, are often accepted.
+
+Let us continue with the idea of a lottery. For a lottery at the local
+sports club, 100 tickets were printed, yet only 5 out of every 8 tickets
+was sold, therefore tickets will be drawn until a winner is found. The
+price of a ticket is 1 apple, and the prize for the winner is 50 apples.
+
+Our victim is called Janus. After Janus buys a ticket for the lottery,
+we ask him the following questions.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  What is the chance (in percent) that you will win the lottery?
+\item
+  What is the chance (as a ratio) that someone else will win the
+  lottery?
+\item
+  What is the chance that nobody wins the lottery?
+\item
+  You came with one apple, with how many apples do you expect to walked
+  away?
+\item
+  What is the chance (as a ratio) that you will win the lottery?
+\end{enumerate}
+
+The first question is not very hard:
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+1/(100 * (5 * 8))
+\end{alltt}
+\begin{verbatim}
+## [1] 0.00025
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+But perhaps it is something you wouldn't always do without a calculator
+or at least pen and paper. The second probability is:
+
+Definitely something most people would do on paper. However, since we
+are at the sports club, this is something we might not have at hand.
+
+As can be seen, question (1) and (5) are identical. If you go through
+the questions without having done the calculations beforehand, you will
+likely be inclined to give a lower answer to (5) than you were to (1).
+Presumable you would be quite neutral when answering question (1). Yet
+the question preceding question (5) is rather negative, since you would
+probably expect to walk away with zero apples, this would lead you to be
+in a more negative mood when answering (5). Furthermore, you could have
+become tired of answering so many questions, which generally diminishes
+your perception of your chance of being successful.
+
+Janus acts very much in accordance with our expectations, and gives us
+the following responses.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\itemsep1pt\parskip0pt\parsep0pt
+\item
+  2\% (has to be more than two)
+\item
+  19/20
+\item
+  0
+\item
+  0
+\item
+  1/60
+\end{enumerate}
+
+We observe two different estimates of the same \emph{p(e)}.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+p_1 = 1/100
+p_1
+\end{alltt}
+\begin{verbatim}
+## [1] 0.01
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+p_2 = 1/60
+p_2
+\end{alltt}
+\begin{verbatim}
+## [1] 0.01667
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+Normally we would take either one of the responses, or such some other
+way to come to a point estimate, such as averaging.
+
+\section{As a distribution}
+
+Let us assume that question (2) was answered in an slightly optimistic
+state, and question 6 in a slightly pessimistic state. Furthermore, let
+us assume that beliefs are normally distributed, and that these slightly
+pessimistic and slightly optimistic state are each away from the mean,
+below and above respectively. Lets express (5) as a number: 0.0167. We
+can now construct the standard deviation.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+mu = p_1
+mu
+\end{alltt}
+\begin{verbatim}
+## [1] 0.01
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+sigma = p_2 - mu
+sigma
+\end{alltt}
+\begin{verbatim}
+## [1] 0.006667
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+We can now define our subjects beliefs on winning the lottery as:
+
+\begin{quote}
+B\textasciitilde{}N(0.0167,0.00167)
+\end{quote}
+
+Let us now suppose that our subject loses his wallet before the winner
+is drawn. If we want to predict how is beliefs have changed, we can for
+example assume that they are now 2below is mean belief. This would thus
+give us:
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+mu - sigma
+\end{alltt}
+\begin{verbatim}
+## [1] 0.003333
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+If however, Janus there after is in a euphoric state because he find his
+wallet again, and on top of this a nice shiny green apple, than his new
+belief might change to \emph{3s} above his mean level. Which would give
+us:
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+mu + 2 * sigma
+\end{alltt}
+\begin{verbatim}
+## [1] 0.02333
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\begin{quote}
+p anp (1-p)
+\end{quote}
+
+How do we match the answers to questions (2) and (3), the chance that
+Janus thinks he has of winning, with the chance that somebody else win
+(i.e.~that he does not win). Let us write both odds as numbers:
+
+\begin{quote}
+p\_1 = 0.02 1 - p\_2 = 0.95 =\textgreater{} p\_2 = 0.05
+\end{quote}
+
+Let us suppose that the estimate of \emph{p} was positive by one and
+that the estimate of \emph{1-p} was positive by \emph{3s} then we know:
+
+% R Block
+
+\section{An application}
+
+Estimation of a 95\% confidence interval for a belief on probability,
+how the lottery profit from this.
+
+\section{Now\ldots{}for something much more important}
+
+\href{http://www.youtube.com/watch?v=FVwtTrlPSSk}{A video of a penguin
+being tickled}
 

### 2013-11-14 South-Africa.Rmd
added south-africa, r code not running

Additional South African Evidence on Pensions and Child Growth
==============================================================
Bastiaan Quast
--------------------------------------------------------------

Abstract
--------------------------------------------------------------
In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.

I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients. This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.

The main preliminary finding is that the household effect was only significant in 2012.

Introduction
--------------------------------------------------------------
This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach is very similar to Duflo ([2000][1],[2003][2]). The deviation from international standards [Child Growth Standards][6] for weight-for-height and length-for-age are computed as z-scores. These are then compared for different pension recipient status.

The anthropometrics are useful for computing z-scores. These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.

The South African pension is a useful variable to measure income because of its criteria. Besides a maximum level of income, the only criterium is the age of a person. Because of this the status as a recipient is quite exogenous and there are few selection bias problems. The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.

Duflo finds evidence in South Africa's 1993 [Integrated Household Survey][3] that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension. This is directly after the significant increase in the pension sum for blacks. The pension-eligibility age at this time was 60 for women and 65 for men.

This study deviates from the Duflo study in several ways. In 2008 and 2012 the first and second wave of the [National Income Dynamics Study][4] have gathered similar data. In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 ([Announcement][5]).

This happened in a few steps. As of July 16th 2008 men aged 63 and 64 were eligible for a pension. Men aged 61 and 62 became eligible in April 2009. Finally in January 2010, pension eligibility age was at 60 for all citizens.

Another deviation is the usage of [Child Growth Standards][6] in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.

The main preliminary result is that the household effect (i.e. having one or more recipients in the household) is very insignificant in the 2008 estimate. But in the 2012 estimate it is very significant.

Data
--------------------------------------------------------------
In this paper I use data from two sources. The first is the South African National Income Dynamics Survey  and the second is the World Health Organization's Child Growth Standards [Child Growth Standards][6].

The main source of data is the NIDS. This survey collects data on a representative set of appproximately 10,000 South African households. The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.

For adults several variables measure the different amounts and sources of income. Among those, a variable if the adult receives a state pension, and if so, how much. This is a numeric variable, the values of which lie very close together. For simplicity I have temporarily used this variable as a dummy.

Children's anthropometrics are taken, these are length/height, weight, and waist. Using these anthropometics and WHO growth standards, z-scores have been calculated. Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published. However, I have computed the length-for-age z-scores manually.

In 2006 the WHO published its standards for child growth [Child Growth Standards][6]. These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle. The standards provide the means and standards deviations used. These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.

```{r, include=FALSE}
load("w1w2.RData")
library(sem)
library(ggplot2)
```

```{r}
p1 <- ggplot(subset(w1_child,w1_woman_60 == 1), aes(w1_c_age_m, w1_zhfa, colour=factor(w1_c_woman)))
p1 + stat_smooth(method="loess")# + geom_point()
```

Results
--------------------------------------------------------------
Basic HAZ (2008).
```{r}
summary(w1_haz0)
```

HAZ 2008, with 2012 eligiblity as an IV
```{r}
summary(tsls_w1w2_haz0)
```

HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
```{r}
summary(tsls_w1w2_haz1)
```

  [1]: http://www.jstor.org/discover/10.2307/117257         "Child Health and Household Resources in South Africa"
  [2]: http://wber.oxfordjournals.org/content/17/1/1        "Grandmothers and Granddaughters"
  [3]: http://microdata.worldbank.org/index.php/catalog/297 "Integrated Household Survey"
  [4]: http://www.nids.uct.ac.za/home/                      "National Income Dynamics Study"
  [5]: http://www.southafrica.info/services/government/pension-160708.htm
  [6]: http://www.who.int/childgrowth/en/                   "Child Growth Standards"
  [7]: http://www.who.int/nutgrowthdb/en/                   "Global Database on Child Growth and Malnutrition"

### 2013-11-14 draft.Rnw
added south-africa, r code not running

@@
 \mainmatter
-\chapter{South Africa}
-a la duflo
+
+\subfile{south-africa.tex}
 
@@
 
-\section{Modelling probabilistic beliefs for single agents as
-distributions, incorporating changes and apparent incommensurability.}
-
-\section{Abstract}
-
+\section*{Abstract}
 By constructing a distribution of the belief structure of a single
@@
 
-\chapter{Police Reform Conkary}
-\subfile{conakry.tex}
-
-\chapter{Bitcoin remitances}
-\subfile{bitcoin.tex}
-
-\chapter{Rare events}
-black swans, dragon king
-
 \begin{refsection}
+\chapter{Morris Shin Currency Attacks}
 \subfile{morrisShin.tex}

### 2013-11-14 south-africa.tex
added south-africa, r code not running

--- 2013-11-14 South-Africa.Rmd
@@
-Additional South African Evidence on Pensions and Child Growth
-==============================================================
-Bastiaan Quast
---------------------------------------------------------------
+\documentclass[draft.tex]{subfiles}
 
-Abstract
---------------------------------------------------------------
-In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.
+\begin{document}
 
-I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.
+\chapter{Additional South African Evidence on Pensions and Child Growth}
 
-The main preliminary finding is that the household effect was only significant in 2012.
+\section{Abstract}
 
-Introduction
---------------------------------------------------------------
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa.
-The approach is very similar to Duflo ([2000][1],[2003][2]).
-The deviation from international standards [Child Growth Standards][6] for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status.
+In this paper I look at the effect of the gender of pension recipients
+on the growth of children in the same households.
 
-The anthropometrics are useful for computing z-scores.
-These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
+I do this by comparing z-scores of anthropometrics of South African
+children living in the same household as state pension recipients. This
+paper exploits the fact that the data set consists of two surveys which
+were done before and after the lowering of the pension eligibility age
+for men to the same age as women.
 
-The South African pension is a useful variable to measure income because of its criteria.
-Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
-The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
+The main preliminary finding is that the household effect was only
+significant in 2012.
 
-Duflo finds evidence in South Africa's 1993 [Integrated Household Survey][3] that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension.
-This is directly after the significant increase in the pension sum for blacks.
-The pension-eligibility age at this time was 60 for women and 65 for men.
+\section{Introduction}
 
-This study deviates from the Duflo study in several ways.
-In 2008 and 2012 the first and second wave of the [National Income Dynamics Study][4] have gathered similar data.
-In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 ([Announcement][5]).
+This paper looks at the effect of the gender of pension recipients on
+the growth of children in their household in South Africa. The approach
+is very similar to Duflo
+(\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}).
+The deviation from international standards
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for
+weight-for-height and length-for-age are computed as z-scores. These are
+then compared for different pension recipient status.
 
-This happened in a few steps.
-As of July 16th 2008 men aged 63 and 64 were eligible for a pension.
-Men aged 61 and 62 became eligible in April 2009.
-Finally in January 2010, pension eligibility age was at 60 for all citizens.
+The anthropometrics are useful for computing z-scores. These z-scores
+are considered a good representation of short-term or long-term
+malnutrition respectively, especially for children between 6 and 60
+months old.
 
-Another deviation is the usage of [Child Growth Standards][6] in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.
+The South African pension is a useful variable to measure income because
+of its criteria. Besides a maximum level of income, the only criterium
+is the age of a person. Because of this the status as a recipient is
+quite exogenous and there are few selection bias problems. The
+problematic difference between the eligibility age of men and women was
+eliminated between the two surveys which creates an interesting natural
+experiment.
 
-The main preliminary result is that the household effect (i.e.
-having one or more recipients in the household) is very insignificant in the 2008 estimate.
-But in the 2012 estimate it is very significant.
+Duflo finds evidence in South Africa's 1993
+\href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated
+Household Survey} that girls' short term nutrition (weight-for-height)
+was positively influence by living with the maternal grandmother if the
+grandmother was eligible for a state pension. This is directly after the
+significant increase in the pension sum for blacks. The
+pension-eligibility age at this time was 60 for women and 65 for men.
 
-Data
---------------------------------------------------------------
-In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey  and the second is the World Health Organization's Child Growth Standards [Child Growth Standards][6].
+This study deviates from the Duflo study in several ways. In 2008 and
+2012 the first and second wave of the
+\href{http://www.nids.uct.ac.za/home/}{National Income Dynamics Study}
+have gathered similar data. In the period 2008-2010, the government
+lowered the eligibility age for men from 65 to 60
+(\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
 
-The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South African households.
-The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
+This happened in a few steps. As of July 16th 2008 men aged 63 and 64
+were eligible for a pension. Men aged 61 and 62 became eligible in April
+2009. Finally in January 2010, pension eligibility age was at 60 for all
+citizens.
 
-For adults several variables measure the different amounts and sources of income.
-Among those, a variable if the adult receives a state pension, and if so, how much.
-This is a numeric variable, the values of which lie very close together.
-For simplicity I have temporarily used this variable as a dummy.
+Another deviation is the usage of
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} in
+stead of CDC's, since these have superseded the CDC charts, however this
+should not be of any consequence.
 
-Children's anthropometrics are taken, these are length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
-However, I have computed the length-for-age z-scores manually.
+The main preliminary result is that the household effect (i.e.~having
+one or more recipients in the household) is very insignificant in the
+2008 estimate. But in the 2012 estimate it is very significant.
 
-In 2006 the WHO published its standards for child growth [Child Growth Standards][6].
-These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
-The standards provide the means and standards deviations used.
-These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
+\section{Data}
 
-```{r, include=FALSE}
-load("w1w2.RData")
-library(sem)
-library(ggplot2)
-```
+In this paper I use data from two sources. The first is the South
+African National Income Dynamics Survey and the second is the World
+Health Organization's Child Growth Standards
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
 
-```{r}
-p1 <- ggplot(subset(w1_child,w1_woman_60 == 1), aes(w1_c_age_m, w1_zhfa, colour=factor(w1_c_woman)))
-p1 + stat_smooth(method="loess")# + geom_point()
-```
+The main source of data is the NIDS. This survey collects data on a
+representative set of appproximately 10,000 South African households.
+The primary information types I use are, the child anthropometrics, the
+age and gender of household members, and the status as state pension
+recipients.
 
-Results
---------------------------------------------------------------
-Basic HAZ (2008).
-```{r}
-summary(w1_haz0)
-```
+For adults several variables measure the different amounts and sources
+of income. Among those, a variable if the adult receives a state
+pension, and if so, how much. This is a numeric variable, the values of
+which lie very close together. For simplicity I have temporarily used
+this variable as a dummy.
+
+Children's anthropometrics are taken, these are length/height, weight,
+and waist. Using these anthropometics and WHO growth standards, z-scores
+have been calculated. Unfortunately wave 2 (2012) accidentally omitted
+the z-scores, so that these cannot be evaluated until an updated version
+is published. However, I have computed the length-for-age z-scores
+manually.
+
+In 2006 the WHO published its standards for child growth
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}. These
+standards are based on the scores of children from different ethnic
+populations in households which observed a healthy lifestyle. The
+standards provide the means and standards deviations used. These are on
+a monthly basis for height-for-age, and on a semi-centimeter level for
+weight-for-height scores.
+
+\texttt{\{r, include=FALSE\} load("w1w2.RData") library(sem) library(ggplot2)}
+
+\texttt{\{r\} p1 \textless{}- ggplot(subset(w1\_child,w1\_woman\_60 == 1), aes(w1\_c\_age\_m, w1\_zhfa, colour=factor(w1\_c\_woman))) p1 + stat\_smooth(method="loess")\# + geom\_point()}
+
+\section{Results}
+
+Basic HAZ (2008). \texttt{\{r\} summary(w1\_haz0)}
 
 HAZ 2008, with 2012 eligiblity as an IV
-```{r}
-summary(tsls_w1w2_haz0)
-```
+\texttt{\{r\} summary(tsls\_w1w2\_haz0)}
 
 HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-```{r}
-summary(tsls_w1w2_haz1)
-```
+\texttt{\{r\} summary(tsls\_w1w2\_haz1)}
 
-  [1]: http://www.jstor.org/discover/10.2307/117257         "Child Health and Household Resources in South Africa"
-  [2]: http://wber.oxfordjournals.org/content/17/1/1        "Grandmothers and Granddaughters"
-  [3]: http://microdata.worldbank.org/index.php/catalog/297 "Integrated Household Survey"
-  [4]: http://www.nids.uct.ac.za/home/                      "National Income Dynamics Study"
-  [5]: http://www.southafrica.info/services/government/pension-160708.htm
-  [6]: http://www.who.int/childgrowth/en/                   "Child Growth Standards"
-  [7]: http://www.who.int/nutgrowthdb/en/                   "Global Database on Child Growth and Malnutrition"
+\end{document}

### 2013-11-14 draft.Rnw
move SAfr to main doc, update title surviving and

@@
 
-\subfile{south-africa.tex}
+\chapter{Additional South African Evidence on Pensions and Child Growth}
+
+\section*{Abstract}
+
+In this paper I look at the effect of the gender of pension recipients
+on the growth of children in the same households.
+
+I do this by comparing z-scores of anthropometrics of South African
+children living in the same household as state pension recipients. This
+paper exploits the fact that the data set consists of two surveys which
+were done before and after the lowering of the pension eligibility age
+for men to the same age as women.
+
+The main preliminary finding is that the household effect was only
+significant in 2012.
+
+\section{Introduction}
+
+This paper looks at the effect of the gender of pension recipients on
+the growth of children in their household in South Africa. The approach
+is very similar to Duflo
+(\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}).
+The deviation from international standards
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for
+weight-for-height and length-for-age are computed as z-scores. These are
+then compared for different pension recipient status.
+
+The anthropometrics are useful for computing z-scores. These z-scores
+are considered a good representation of short-term or long-term
+malnutrition respectively, especially for children between 6 and 60
+months old.
+
+The South African pension is a useful variable to measure income because
+of its criteria. Besides a maximum level of income, the only criterium
+is the age of a person. Because of this the status as a recipient is
+quite exogenous and there are few selection bias problems. The
+problematic difference between the eligibility age of men and women was
+eliminated between the two surveys which creates an interesting natural
+experiment.
+
+Duflo finds evidence in South Africa's 1993
+\href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated
+Household Survey} that girls' short term nutrition (weight-for-height)
+was positively influence by living with the maternal grandmother if the
+grandmother was eligible for a state pension. This is directly after the
+significant increase in the pension sum for blacks. The
+pension-eligibility age at this time was 60 for women and 65 for men.
+
+This study deviates from the Duflo study in several ways. In 2008 and
+2012 the first and second wave of the
+\href{http://www.nids.uct.ac.za/home/}{National Income Dynamics Study}
+have gathered similar data. In the period 2008-2010, the government
+lowered the eligibility age for men from 65 to 60
+(\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
+
+This happened in a few steps. As of July 16th 2008 men aged 63 and 64
+were eligible for a pension. Men aged 61 and 62 became eligible in April
+2009. Finally in January 2010, pension eligibility age was at 60 for all
+citizens.
+
+Another deviation is the usage of
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} in
+stead of CDC's, since these have superseded the CDC charts, however this
+should not be of any consequence.
+
+The main preliminary result is that the household effect (i.e.~having
+one or more recipients in the household) is very insignificant in the
+2008 estimate. But in the 2012 estimate it is very significant.
+
+\section{Data}
+
+In this paper I use data from two sources. The first is the South
+African National Income Dynamics Survey and the second is the World
+Health Organization's Child Growth Standards
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
+
+The main source of data is the NIDS. This survey collects data on a
+representative set of appproximately 10,000 South African households.
+The primary information types I use are, the child anthropometrics, the
+age and gender of household members, and the status as state pension
+recipients.
+
+For adults several variables measure the different amounts and sources
+of income. Among those, a variable if the adult receives a state
+pension, and if so, how much. This is a numeric variable, the values of
+which lie very close together. For simplicity I have temporarily used
+this variable as a dummy.
+
+Children's anthropometrics are taken, these are length/height, weight,
+and waist. Using these anthropometics and WHO growth standards, z-scores
+have been calculated. Unfortunately wave 2 (2012) accidentally omitted
+the z-scores, so that these cannot be evaluated until an updated version
+is published. However, I have computed the length-for-age z-scores
+manually.
+
+In 2006 the WHO published its standards for child growth
+\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}. These
+standards are based on the scores of children from different ethnic
+populations in households which observed a healthy lifestyle. The
+standards provide the means and standards deviations used. These are on
+a monthly basis for height-for-age, and on a semi-centimeter level for
+weight-for-height scores.
+
+\texttt{\{r, include=FALSE\} load("w1w2.RData") library(sem) library(ggplot2)}
+
+\texttt{\{r\} p1 \textless{}- ggplot(subset(w1\_child,w1\_woman\_60 == 1), aes(w1\_c\_age\_m, w1\_zhfa, colour=factor(w1\_c\_woman))) p1 + stat\_smooth(method="loess")\# + geom\_point()}
+
+\section{Results}
+
+Basic HAZ (2008). \texttt{\{r\} summary(w1\_haz0)}
+
+HAZ 2008, with 2012 eligiblity as an IV
+\texttt{\{r\} summary(tsls\_w1w2\_haz0)}
+
+HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
+\texttt{\{r\} summary(tsls\_w1w2\_haz1)}
 
 \begin{refsection}
-\chapter{Replication of: ``Surviving Andersonville''}
+\chapter{Replication of: Surviving Andersonville}
 \subfile{surviving.tex}

### 2013-11-14 draft.Rnw
functioning R code in safr

@@
 
-\texttt{\{r, include=FALSE\} load("w1w2.RData") library(sem) library(ggplot2)}
+<<load, include=FALSE>>=
+load("w1w2.RData")
+library(sem)
+library(ggplot2)
+@
 
-\texttt{\{r\} p1 \textless{}- ggplot(subset(w1\_child,w1\_woman\_60 == 1), aes(w1\_c\_age\_m, w1\_zhfa, colour=factor(w1\_c\_woman))) p1 + stat\_smooth(method="loess")\# + geom\_point()}
+<<r-p1, eval=TRUE>>=
+p1 <- ggplot(subset(w1_child,w1_woman_60 == 1), aes(w1_c_age_m, w1_zhfa, colour=factor(w1_c_woman)))
+p1 + stat_smooth(method="loess") + geom_point()
+@
 
@@
 
-Basic HAZ (2008). \texttt{\{r\} summary(w1\_haz0)}
+Basic HAZ (2008)
+
+<<sum-w1, eval=TRUE>>=
+summary(w1_haz0)
+@
 
 HAZ 2008, with 2012 eligiblity as an IV
-\texttt{\{r\} summary(tsls\_w1w2\_haz0)}
+<<sum-iv, eval=TRUE>>=
+summary(tsls_w1w2_haz0)
+@
 
 HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-\texttt{\{r\} summary(tsls\_w1w2\_haz1)}
+<<sum-iv-men65, eval=TRUE>>=
+summary(tsls_w1w2_haz1)
+@
 

### 2013-11-14 draft.tex
functioning R code in safr

@@
 
-\texttt{\{r, include=FALSE\} load("w1w2.RData") library(sem) library(ggplot2)}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1), \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman)))
+p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
+\end{alltt}
 
-\texttt{\{r\} p1 \textless{}- ggplot(subset(w1\_child,w1\_woman\_60 == 1), aes(w1\_c\_age\_m, w1\_zhfa, colour=factor(w1\_c\_woman))) p1 + stat\_smooth(method="loess")\# + geom\_point()}
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 324 rows containing missing values (stat\_smooth).}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 263 rows containing missing values (stat\_smooth).}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 51 rows containing missing values (stat\_smooth).}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 638 rows containing missing values (geom\_point).}}\end{kframe}
+\includegraphics[width=\maxwidth]{figure/r-p1}
+
+\end{knitrout}
 
@@
 
-Basic HAZ (2008). \texttt{\{r\} summary(w1\_haz0)}
+Basic HAZ (2008)
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlfunctioncall{summary}(w1_haz0)
+\end{alltt}
+\begin{verbatim}
+## 
+## Call:
+## lm(formula = w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + 
+##     w1_best_age_yrs, data = w1_child, subset = w1_c_age_m >= 
+##     6 & w1_c_age_m <= 60)
+## 
+## Residuals:
+##    Min     1Q Median     3Q    Max 
+## -4.779 -1.036 -0.169  0.834  7.060 
+## 
+## Coefficients:
+##                  Estimate Std. Error t value Pr(>|t|)    
+## (Intercept)     -1.43e+00   1.44e-01   -9.87   <2e-16 ***
+## w1_spen_w        2.32e-02   1.15e-01    0.20   0.8402    
+## w1_spen_m        1.36e-01   1.72e-01    0.79   0.4281    
+## w1_h_tinc        3.62e-05   9.99e-06    3.62   0.0003 ***
+## w1_best_edu      1.63e-03   7.84e-03    0.21   0.8355    
+## w1_best_age_yrs  7.61e-03   3.64e-03    2.09   0.0369 *  
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+## 
+## Residual standard error: 1.77 on 1436 degrees of freedom
+##   (1936 observations deleted due to missingness)
+## Multiple R-squared:  0.0134,	Adjusted R-squared:  0.00994 
+## F-statistic: 3.89 on 5 and 1436 DF,  p-value: 0.00164
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
 HAZ 2008, with 2012 eligiblity as an IV
-\texttt{\{r\} summary(tsls\_w1w2\_haz0)}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlfunctioncall{summary}(tsls_w1w2_haz0)
+\end{alltt}
+\begin{verbatim}
+## 
+##  2SLS Estimates
+## 
+## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
+## 
+## Instruments: ~w2_spen_w + w2_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
+## 
+## Residuals:
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+##  -4.990  -0.835  -0.050   0.000   0.788   7.070 
+## 
+##                   Estimate Std. Error t value Pr(>|t|)    
+## (Intercept)     -1.172e+00  7.388e-02 -15.861  < 2e-16 ***
+## w1_spen_w        1.748e-02  9.477e-02   0.184   0.8536    
+## w1_spen_m       -1.374e-01  1.444e-01  -0.952   0.3414    
+## w1_h_tinc        2.995e-05  5.606e-06   5.342 9.69e-08 ***
+## w1_best_edu      2.410e-03  3.532e-03   0.682   0.4951    
+## w1_best_age_yrs  4.127e-03  1.863e-03   2.215   0.0268 *  
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+## 
+## Residual standard error: 1.4889 on 4227 degrees of freedom
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
 HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-\texttt{\{r\} summary(tsls\_w1w2\_haz1)}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlfunctioncall{summary}(tsls_w1w2_haz1)
+\end{alltt}
+\begin{verbatim}
+## 
+##  2SLS Estimates
+## 
+## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
+## 
+## Instruments: ~w2_spen_w + w2_spen_m_65 + w1_h_tinc + w1_best_edu + w1_best_age_yrs
+## 
+## Residuals:
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+##  -4.990  -0.836  -0.050   0.000   0.786   7.040 
+## 
+##                   Estimate Std. Error t value Pr(>|t|)    
+## (Intercept)     -1.173e+00  7.387e-02 -15.880  < 2e-16 ***
+## w1_spen_w        8.576e-03  9.541e-02   0.090   0.9284    
+## w1_spen_m       -9.189e-02  1.348e-01  -0.681   0.4956    
+## w1_h_tinc        2.992e-05  5.605e-06   5.339 9.85e-08 ***
+## w1_best_edu      2.443e-03  3.531e-03   0.692   0.4890    
+## w1_best_age_yrs  4.092e-03  1.860e-03   2.200   0.0278 *  
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+## 
+## Residual standard error: 1.4885 on 4227 degrees of freedom
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 

### 2013-11-14 draft.Rnw
fix line breaks

@@
 Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
-Second Reader:&Lore Vandewalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
+Second Reader:&%Lore Vandewalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
 \end{tabular}
@@
 
-In this paper I look at the effect of the gender of pension recipients
-on the growth of children in the same households.
+In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.
 
-I do this by comparing z-scores of anthropometrics of South African
-children living in the same household as state pension recipients. This
-paper exploits the fact that the data set consists of two surveys which
-were done before and after the lowering of the pension eligibility age
-for men to the same age as women.
+I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
+This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.
 
-The main preliminary finding is that the household effect was only
-significant in 2012.
+The main preliminary finding is that the household effect was only significant in 2012.
 
@@
 
-This paper looks at the effect of the gender of pension recipients on
-the growth of children in their household in South Africa. The approach
-is very similar to Duflo
-(\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}).
-The deviation from international standards
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for
-weight-for-height and length-for-age are computed as z-scores. These are
-then compared for different pension recipient status.
+This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
+is very similar to Duflo (\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}).
+The deviation from international standards \href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for weight-for-height and length-for-age are computed as z-scores.
+These are then compared for different pension recipient status.
 
-The anthropometrics are useful for computing z-scores. These z-scores
-are considered a good representation of short-term or long-term
-malnutrition respectively, especially for children between 6 and 60
-months old.
+The anthropometrics are useful for computing z-scores.
+These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
 
-The South African pension is a useful variable to measure income because
-of its criteria. Besides a maximum level of income, the only criterium
-is the age of a person. Because of this the status as a recipient is
-quite exogenous and there are few selection bias problems. The
-problematic difference between the eligibility age of men and women was
-eliminated between the two surveys which creates an interesting natural
-experiment.
+The South African pension is a useful variable to measure income because of its criteria.
+Besides a maximum level of income, the only criterium is the age of a person.
+Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
+The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
 
-Duflo finds evidence in South Africa's 1993
-\href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated
-Household Survey} that girls' short term nutrition (weight-for-height)
-was positively influence by living with the maternal grandmother if the
-grandmother was eligible for a state pension. This is directly after the
-significant increase in the pension sum for blacks. The
-pension-eligibility age at this time was 60 for women and 65 for men.
+Duflo finds evidence in South Africa's 1993 \href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated Household Survey} that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension.
+This is directly after the significant increase in the pension sum for blacks.
+The pension-eligibility age at this time was 60 for women and 65 for men.
 
-This study deviates from the Duflo study in several ways. In 2008 and
-2012 the first and second wave of the
-\href{http://www.nids.uct.ac.za/home/}{National Income Dynamics Study}
-have gathered similar data. In the period 2008-2010, the government
-lowered the eligibility age for men from 65 to 60
-(\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
+This study deviates from the Duflo study in several ways.
+In 2008 and 2012 the first and second wave of the \href{http://www.nids.uct.ac.za/home/}{National Income Dynamics Study} have gathered similar data.
+In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
 
-This happened in a few steps. As of July 16th 2008 men aged 63 and 64
-were eligible for a pension. Men aged 61 and 62 became eligible in April
-2009. Finally in January 2010, pension eligibility age was at 60 for all
-citizens.
+This happened in a few steps.
+As of July 16th 2008 men aged 63 and 64 were eligible for a pension.
+Men aged 61 and 62 became eligible in April 2009.
+Finally in January 2010, pension eligibility age was at 60 for all citizens.
 
-Another deviation is the usage of
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} in
-stead of CDC's, since these have superseded the CDC charts, however this
-should not be of any consequence.
+Another deviation is the usage of \href{http://www.who.int/childgrowth/en/}{Child Growth Standards} in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.
 
-The main preliminary result is that the household effect (i.e.~having
-one or more recipients in the household) is very insignificant in the
-2008 estimate. But in the 2012 estimate it is very significant.
+The main preliminary result is that the household effect (i.e.~having one or more recipients in the household) is very insignificant in the 2008 estimate.
+But in the 2012 estimate it is very significant.
 
@@
 
-In this paper I use data from two sources. The first is the South
-African National Income Dynamics Survey and the second is the World
-Health Organization's Child Growth Standards
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
+In this paper I use data from two sources.
+The first is the South African National Income Dynamics Survey and the second is the World Health Organization's Child Growth Standards \href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
 
-The main source of data is the NIDS. This survey collects data on a
-representative set of appproximately 10,000 South African households.
-The primary information types I use are, the child anthropometrics, the
-age and gender of household members, and the status as state pension
-recipients.
+The main source of data is the NIDS.
+This survey collects data on a representative set of appproximately 10,000 South African households.
+The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
 
-For adults several variables measure the different amounts and sources
-of income. Among those, a variable if the adult receives a state
-pension, and if so, how much. This is a numeric variable, the values of
-which lie very close together. For simplicity I have temporarily used
-this variable as a dummy.
+For adults several variables measure the different amounts and sources of income.
+Among those, a variable if the adult receives a state pension, and if so, how much.
+This is a numeric variable, the values of which lie very close together.
+For simplicity I have temporarily used this variable as a dummy.
 
-Children's anthropometrics are taken, these are length/height, weight,
-and waist. Using these anthropometics and WHO growth standards, z-scores
-have been calculated. Unfortunately wave 2 (2012) accidentally omitted
-the z-scores, so that these cannot be evaluated until an updated version
-is published. However, I have computed the length-for-age z-scores
-manually.
+Children's anthropometrics are taken, these are length/height, weight, and waist.
+Using these anthropometics and WHO growth standards, z-scores have been calculated.
+Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
+However, I have computed the length-for-age z-scores manually.
 
-In 2006 the WHO published its standards for child growth
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}. These
-standards are based on the scores of children from different ethnic
-populations in households which observed a healthy lifestyle. The
-standards provide the means and standards deviations used. These are on
-a monthly basis for height-for-age, and on a semi-centimeter level for
-weight-for-height scores.
+In 2006 the WHO published its standards for child growth \href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
+These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
+The standards provide the means and standards deviations used.
+These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
 
@@
 \section*{Abstract}
-By constructing a distribution of the belief structure of a single
-agent, we can mitigate seemingly incommensurable beliefs. This paper
-proposes to generalise the concept of a single agents beliefs, from a
-point estimate to a distributional approximation. This will allow us to
-deal with differing estimates of the probability \emph{p}, as well as
-with estimates of \emph{p} and \emph{¬p} violating unitarity, in
-meaningful way. Additionally with a distributional approximation, we can
-estimate agents' beliefs, using the state which they are in.
+By constructing a distribution of the belief structure of a single agent, we can mitigate seemingly incommensurable beliefs.
+This paper proposes to generalise the concept of a single agents beliefs, from a point estimate to a distributional approximation.
+This will allow us to deal with differing estimates of the probability \emph{p}, as well aswith estimates of \emph{p} and \emph{¬p} violating unitarity, in meaningful way.
+Additionally with a distributional approximation, we can estimate agents' beliefs, using the state which they are in.
 
 \section{Introduction}
+It generally held to be so that people sometimes hold beliefs which are incommensurable with each other.
+In technical terms we could say, the knowledge base is interally inconsistent.
+This incommensurability becomes especially apparent when these beliefs are quantified.
 
-It generally held to be so that people sometimes hold beliefs which are
-incommensurable with each other. In technical terms we could say, the
-knowledge base is interally inconsistent. This incommensurability
-becomes especially apparent when these beliefs are quantified.
-
-As an example consider the following. If we have the probability of some
-event \emph{e} occuring with probability \emph{p}. By definition, all
-probabilities are exhausted at \emph{1}. Therefore the probability of
-that event not occuring (i.e. \emph{¬p} or \emph{not p}) is \emph{1-p}.
+As an example consider the following.
+If we have the probability of some event \emph{e} occuring with probability \emph{p}.
+By definition, all probabilities are exhausted at \emph{1}.
+Therefore the probability of that event not occuring (i.e.
+\emph{¬p} or \emph{not p}) is \emph{1-p}.
 
@@
 
-It is often observed, that people hold beliefs that do not meet this
-condition, these beliefs can thus be described as:
+It is often observed, that people hold beliefs that do not meet this condition, these beliefs can thus be described as:
 
@@
 
-In addition to this, we often see that people have different beliefs
-about the same thing, often just moments apart (e.g.~beginning and end
-of a survey). This could be the case for many (unrelated) reasons, such
-as, fatigue, hunger, anchoring, etc. We can express this as:
+In addition to this, we often see that people have different beliefs about the same thing, often just moments apart (e.g.~beginning and end of a survey).
+This could be the case for many (unrelated) reasons, such as, fatigue, hunger, anchoring, etc.
+We can express this as:
 
@@
 
-We are thus faced with the fact that we get responses from agents
+% We are thus faced with the fact that we get responses from agents
 
-In this paper I describe how we can generalise the idea of perception of
-probability -for a single agent- from a point estimate, to a
-distributional approximation.
+In this paper I describe how we can generalise the idea of perception of probability -for a single agent- from a point estimate, to a distributional approximation.
 
-Doing this will allow us to deal with seemingly inconsistent beliefs in
-a single framework in a \emph{meaningful} way.
+Doing this will allow us to deal with seemingly inconsistent beliefs in a single framework in a \emph{meaningful} way.
 
@@
 
-On a fair die, the chance of throwing 3 eyes is 16, call this \emph{p}.
-The chance that you do not throw 3 eyes (i.e. \emph{¬p}) is therefore
-\emph{1-p}, or
+On a fair die, the chance of throwing 3 eyes is 16, call this \emph{p}. The chance that you do not throw 3 eyes (i.e. \emph{¬p}) is therefore \emph{1-p}, or
 
@@
 
-This is a very simple statistical exercise, and most people will be able
-to give you the answer that I derived. The reason for this is that
-people learn to use dice and how they operate, in e.g.~board games.
-Likewise for coin flipping and many other basic statistical trials. In
-this context, you would rarely find people accepting a bet that has a
-negative expected value. Such as non-equal payout for a fair coin flip.
+This is a very simple statistical exercise, and most people will be able to give you the answer that I derived.
+The reason for this is that people learn to use dice and how they operate, in e.g.~board games.
+Likewise for coin flipping and many other basic statistical trials.
+In this context, you would rarely find people accepting a bet that has a negative expected value.
+Such as non-equal payout for a fair coin flip.
 
-However, as soon as odds become less transparent, statistical methods
-are often applied with less rigour. Especially when dealing with
-observed implicit payout structures. As a results bets with negative
-expected payouts, such as lotteries, are often accepted.
+However, as soon as odds become less transparent, statistical methods are often applied with less rigour.
+Especially when dealing with observed implicit payout structures.
+As a results bets with negative expected payouts, such as lotteries, are often accepted.
 
-Let us continue with the idea of a lottery. For a lottery at the local
-sports club, 100 tickets were printed, yet only 5 out of every 8 tickets
-was sold, therefore tickets will be drawn until a winner is found. The
-price of a ticket is 1 apple, and the prize for the winner is 50 apples.
+Let us continue with the idea of a lottery.
+For a lottery at the local sports club, 100 tickets were printed, yet only 5 out of every 8 tickets was sold, therefore tickets will be drawn until a winner is found.
+The price of a ticket is 1 apple, and the prize for the winner is 50 apples.
 
-Our victim is called Janus. After Janus buys a ticket for the lottery,
-we ask him the following questions.
+Our victim is called Janus. After Janus buys a ticket for the lottery, we ask him the following questions.
 
@@
 
-But perhaps it is something you wouldn't always do without a calculator
-or at least pen and paper. The second probability is:
+But perhaps it is something you wouldn't always do without a calculator or at least pen and paper. The second probability is:
 
-Definitely something most people would do on paper. However, since we
-are at the sports club, this is something we might not have at hand.
+Definitely something most people would do on paper. However, since we are at the sports club, this is something we might not have at hand.
 
-As can be seen, question (1) and (5) are identical. If you go through
-the questions without having done the calculations beforehand, you will
-likely be inclined to give a lower answer to (5) than you were to (1).
-Presumable you would be quite neutral when answering question (1). Yet
-the question preceding question (5) is rather negative, since you would
-probably expect to walk away with zero apples, this would lead you to be
-in a more negative mood when answering (5). Furthermore, you could have
-become tired of answering so many questions, which generally diminishes
-your perception of your chance of being successful.
+As can be seen, question (1) and (5) are identical.
+If you go through the questions without having done the calculations beforehand, you will likely be inclined to give a lower answer to (5) than you were to (1).
+Presumable you would be quite neutral when answering question (1).
+Yet the question preceding question (5) is rather negative, since you would probably expect to walk away with zero apples, this would lead you to be in a more negative mood when answering (5).
+Furthermore, you could have become tired of answering so many questions, which generally diminishes your perception of your chance of being successful.
 
-Janus acts very much in accordance with our expectations, and gives us
-the following responses.
+Janus acts very much in accordance with our expectations, and gives us the following responses.
 
@@
 
-Normally we would take either one of the responses, or such some other
-way to come to a point estimate, such as averaging.
+Normally we would take either one of the responses, or such some other way to come to a point estimate, such as averaging.
 
@@
 
-Let us assume that question (2) was answered in an slightly optimistic
-state, and question 6 in a slightly pessimistic state. Furthermore, let
-us assume that beliefs are normally distributed, and that these slightly
-pessimistic and slightly optimistic state are each away from the mean,
-below and above respectively. Lets express (5) as a number: 0.0167. We
-can now construct the standard deviation.
+Let us assume that question (2) was answered in an slightly optimistic state, and question 6 in a slightly pessimistic state.
+Furthermore, let us assume that beliefs are normally distributed, and that these slightly pessimistic and slightly optimistic state are each away from the mean, below and above respectively.
+Lets express (5) as a number: 0.0167.
+We can now construct the standard deviation.
 
@@
 
-Let us now suppose that our subject loses his wallet before the winner
-is drawn. If we want to predict how is beliefs have changed, we can for
-example assume that they are now 2below is mean belief. This would thus
-give us:
+Let us now suppose that our subject loses his wallet before the winner is drawn.
+If we want to predict how is beliefs have changed, we can for example assume that they are now 2below is mean belief.
+This would thus give us:
 
@@
 
-If however, Janus there after is in a euphoric state because he find his
-wallet again, and on top of this a nice shiny green apple, than his new
-belief might change to \emph{3s} above his mean level. Which would give
-us:
+If however, Janus there after is in a euphoric state because he find his wallet again, and on top of this a nice shiny green apple, than his new belief might change to \emph{3s} above his mean level.
+Which would give us:
 
@@
 
-How do we match the answers to questions (2) and (3), the chance that
-Janus thinks he has of winning, with the chance that somebody else win
-(i.e.~that he does not win). Let us write both odds as numbers:
+How do we match the answers to questions (2) and (3), the chance that Janus thinks he has of winning, with the chance that somebody else win (i.e.~that he does not win).
+Let us write both odds as numbers:
 
@@
 
-Let us suppose that the estimate of \emph{p} was positive by one and
-that the estimate of \emph{1-p} was positive by \emph{3s} then we know:
+Let us suppose that the estimate of \emph{p} was positive by one and that the estimate of \emph{1-p} was positive by \emph{3s} then we know:
 
@@
 
-Estimation of a 95\% confidence interval for a belief on probability,
-how the lottery profit from this.
-
-\section{Now\ldots{}for something much more important}
-
-\href{http://www.youtube.com/watch?v=FVwtTrlPSSk}{A video of a penguin
-being tickled}
+Estimation of a 95\% confidence interval for a belief on probability, how the lottery profit from this.
 

### 2013-11-14 draft.Rnw

@@
 \documentclass[a4paper]{book}
-\usepackage{subfiles}
 \usepackage{mathtools}
@@
 \begin{refsection}
+
 \chapter{Replication of: Surviving Andersonville}
-\subfile{surviving.tex}
+
+%\author{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}
+
+\section{Summary of the paper}
+\textcite{costa2007surviving} tries to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps.
+To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.
+
+The empirical specification for the longitudinal data that measures the effect of the size of the network is as follows:
+
+\begin{equation} \label{eq:ht}
+h(t) = \exp ( \beta_1 F + \beta_2 I + \beta_3 M )
+\end{equation}
+
+where $h$ is hazard at time $t$, $F$ is the number of friends (=social network), $I$ are individual characteristics and $M$ macro camp conditions.
+The number of friends is measured as the number of POWs of the same company and varies by month due to deaths or camp transfers.
+As it might capture the lagged mortality of the group, the authors use as second strategy the initial number of friends as a time-invariant proxy.
+In addition, they instrument for the number of friends using the number of net camp transfers combined with a dummy indicating whether the POW was transferred to account for omitted variables.
+The specification for the Andersonville data in turn is a probit model:
+
+\begin{align}
+\label{s1} Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F)\\
+\label{s1b} Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j)
+\end{align}
+
+where \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
+
+The longitudinal data indicates that POWs had special characteristics.
+For instance, they were likely to be volunteers, and from companies with more wounded or dead.
+POWs with more friends were typically US-born and wealthier while Irish and older men had less friends.
+Concerning survival rates, Kaplan-Meier hazard rates show that POWs captured later (after 1963 when the Union and the Confederate Army stopped exchanging POWs) have lower survival rates.
+They also show that survival rates were higher for POWs with 10 or more friends.
+In addition, the rates show that it takes 50 days until there is a divergence in survival between POWs with and without friends.
+The exponential function estimates that an additional friend leads to a 0.98 times lower mortality hazard.
+An increase in the number of friends from 0 to 5 (5 to 10), decreases the predicted probability of death from 0.31 to 0.28 (0.26) while a spline specification provides evidence that the effect is greatest for the first two friends.
+In addition, survival is more likely for POWs that had survived at least one or two months.
+Factors increasing mortality are the number of men in the camp, low rank, high age, and height among others.
+Insignificant variables are for instance wealth and marital status.
+There is no evidence for individual heterogeneity.
+The use of a Weibull specification indicates no duration dependence (toughen up effects).
+Interestingly though, a Cox model gives no significant effect of friends which the authors interpret as a result of their loss of power due to the small sample size.
+Robustness checks, including the IV approach and the effect of friends transferred in, confirms the significant effect of friends.
+Finally, the cross-sectional results provide evidence that having the same last name, being from the same town for smaller towns, ethnic similarity and having a sergeant or a higher rank in one's network are all important factors in raising survival probabilities which in turn shows that the quality of social networks matters.
+
+In summary, Costa and Kahn are able to show that quantity and quality of social networks mattered for survival in civil war POW camps.
+Potential explanations for this are the sharing of scarce resources, moral support and protection from other prisoners.
+
+\section{Data}
+The raw data for the first part of the paper is extracted from the Union Army dataset readily accessible at \url{http://www.cpe.uchicago.edu}.
+This dataset draws information from censuses, medical records and military pension records linking military, socioeconomic and health information for nearly $40,000$ white males that served in the Union Army during the Civil War.
+For the second part, the Andersonville database is available at \url{http://www.itd.nps.gov/cwss} but only as a ``searchable version'', which allows viewing the information for one soldier at a time, and more convenient formats are not readily available.
+
+The datasets provided for the estimations alongside with the publication are already partially processed parts of the raw data available online.
+No clear guidance is given as to what steps were taken to go from the raw data to the files provided, and matching both things proved to be less than straightforward.
+In view of this, we decided to proceed with the replication using the files provided by the authors, pointing out along the way the cases where potential problems in them seemed likely given the raw data we observed.
+Taking those files as starting points, it is possible to reproduce the tables and graphs published in the paper, so in this sense we can say that the data set is complete.
+Originally, some of the data required by the published .do files was not included in the published data files, but the authors provided it promptly upon our request and added it subsequently to the online files of the publishing journal.
+
+The data and .do files provided do not describe or label many of the variables used, nor does the limited variable description in the Appendix cover all of them.
+A very thorough description of the variables in the raw data set can be found at its online source, but the match between this and the variables in the files provided is not straightforward or complete, since some of them are already created by the authors from the raw data.
+The description of the data itself, mainly of the variables that are used most often, is succinct but adequate, with Table 1 and Table 2 presenting some relevant descriptive traits.
+Despite this, some attention should be drawn to the fact that some of the variables have a relevant share of missing values (only the highest number of observations is reported), a point that will be commented in detail later on.
+
+\section{Stata code and interpretation}
+All codes run to their full extent, and produce the estimations presented in the paper, with minor differences that we describe in detail below.
+The codes themselves are not commented at all and include plenty of estimations and specifications not included in the published paper, as well as unexplained data processing steps.
+No exporting commands were set up, or log files kept, which might be the root of some of the rounding and significance discrepancies we have found.
+
+In what follows, all reproduced tables are presented with a comment on the differences found (in bold), whenever there were any.
+
+\subsection{Tables}
+Table 1: This table presents the means of most variables later used for estimation, dividing observations in POWs and NON POWs, to illustrate ex ante differences in observables between them.
+
+\begin{table}[bt]
+\centering
+\caption{Characteristics of Soldiers by POW Status}
+\label{characteristics}
+\begin{tabular}{lllllll}
+\hline
+                           & All   & Obs.  & Never POW & Obs.  & POW   & Obs. \\
+US born                    & 0.745 & 35007 & 0.745     & 31967 & 0.743 & 3040 \\
+US born corrected          & 0.747 & 34941 & 0.745     & 31966 & 0.759 & 2975 \\
+Irish                      & 0.087 & 34941 & 0.086     & 31966 & 0.102 & 2975 \\
+German                     & 0.074 & 34941 & 0.075     & 31966 & 0.062 & 2975 \\
+British                    & 0.039 & 34941 & 0.039     & 31966 & 0.033 & 2975 \\
+Other                      & 0.054 & 34941 & 0.055     & 31966 & 0.043 & 2975 \\
+Artisan                    & 0.2   & 34941 & 0.199     & 31966 & 0.211 & 2975 \\
+Farmer corrected           & 0.505 & 34941 & 0.505     & 31966 & 0.508 & 2975 \\
+Professional or proprietor & 0.075 & 34941 & 0.077     & 31966 & 0.061 & 2975 \\
+Laborer                    & 0.212 & 34941 & 0.212     & 31966 & 0.212 & 2975 \\
+Unknown                    & 0.007 & 34941 & 0.007     & 31966 & 0.008 & 2975 \\
+Enlisted in 1861           & 0.21  & 35007 & 0.205     & 31967 & 0.263 & 3040 \\
+Enlisted in 1861 corrected & 0.21  & 34878 & 0.205     & 31906 & 0.269 & 2972 \\
+Enlisted in 1862                  & 0.344   & 34878 & 0.331   & 31906 & 0.487  & 2972 \\
+Enlisted in 1863                  & 0.068   & 34878 & 0.066   & 31906 & 0.087  & 2972 \\
+Enlisted in 1864                  & 0.256   & 34878 & 0.266   & 31906 & 0.147  & 2972 \\
+Enlisted in 1865                  & 0.122   & 34878 & 0.132   & 31906 & 0.009  & 2972 \\
+Volunteer                         & 0.909   & 34941 & 0.905   & 31966 & 0.951  & 2975 \\
+Height in inches                  & 67.599  & 34941 & 67.589  & 31966 & 67.709 & 2975 \\
+Household property income in 1860 & 534.155 & 13769 & 531.734 & 12509 & 558.2  & 1260 \\
+Company birthplace fragmentation  & 0.642   & 34941 & 0.644   & 31966 & 0.62   & 2975 \\
+Company occupation fragmentation  & 0.559   & 34941 & 0.558   & 31966 & 0.57   & 2975 \\
+Fraction company died as non-POWs & 0.135   & 34941 & 0.131   & 31966 & 0.182  & 2975 \\
+\end{tabular}
+\end{table}
+
+We have added to \autoref{characteristics} the number of observations per variable, not originally included in the paper, in order to highlight the fact that some of them have significant amounts of missing values, something that should be kept in mind later at the estimation stage.
+In this table, the case in point is Household property income in 1860, which is used in most of the specifications proposed, but as will be discussed for later tables, this is a pattern common to all the variables imported from census data.
+Additionally, considering the number of observations for each of the variables leads to the suggestion of a small correction for three of the dummy variables describing categories: US born, farmer and enlisted in 1861.
+The initial data file is missing these variables, which are likely to have been dropped as the basis category for estimation purposes in some other use of the data.
+They were then rebuilt in the .do file from the remaining categories in such a way that generated zeroes for some observations that should have been missing (except for farmer, which is not included at all in the file).
+For example: as provided by the code, US born has $35,007$ observations, whereas other nationality dummies, all built from the same original variable, have $34,941$.
+The correction proposed then, is to set these dummies to missing whenever the other categories of their class are missing, which slightly changes their descriptive statistics (for example the mean of US born goes from $0.745$ to $0.747$ when this correction is implemented).
+
+Remaining discrepancies are minor and could be due to some kind of rounding difference.
+An alternative explanation for these differences is that the table was produced from a slightly different dataset.
+Considering that even the most populous variables present over 500 observations less than the amount declared in the paper, and the fact that one of the variables (farmer) is not included in the data file at all, we consider the second option to be more likely, which would also explain the minor differences in the means of Artisan, British, Height in inches, etc.
+
+A last and minor comment is that the inclusion of the variable volunteer is surprising, since by sample design the Union Army dataset was restricted to white volunteer infantry regiments.
+The inclusion of this variable when comparing POWs and non POWs probably responds to the point raised in the paper about POWs not being representative of all soldiers, for example in ideology (p.1471).
+A variable that reflects that both POWs and non POWs volunteered in similar proportions would suggest homogeneity between POWs and non POWs in this dimension and, hence, increase  external validity.
+The similarities observed in Table 1 between POWs and non POWs in their mean of volunteer do not reflect that, since they are both close to one by construction.
+Any individuals not listed as volunteers, either correspond to the very few drafted men, or are actually soldiers that re-enlisted as commissioned officers, but were originally volunteers, as explained in the codebooks for the source data.
+
+\autoref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.
+It also presents separately their mean and standard errors for the subsamples of POWs with few (less than 3) and many friends (three or more).
+
+\begin{sidewaystable}
+\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity}
+\label{friends}
+\begin{tabular}{llllllllll}
+
+                                  & \multicolumn{3}{l}{All} & \multicolumn{3}{l}{Few friends ($<3$)} & \multicolumn{3}{l}{Many friends ($>=3$)} \\
+                                  & Mean                    & Std.
+err.
+& No.
+obs.
+& Mean & Std.
+err.
+& No.
+obs.
+& Mean & Std.
+err.
+& No.
+obs.
+\\
+US born                           & 0.731                   & 0.444                                & 1976                                   & 0.708 & 0.455 & 990 & 0.754 & 0.431 & 986 \\
+Irish                             & 0.12                    & 0.325                                & 1976                                   & 0.115 & 0.319 & 990 & 0.125 & 0.331 & 986 \\
+German                            & 0.063                   & 0.243                                & 1976                                   & 0.081 & 0.273 & 990 & 0.045 & 0.207 & 986 \\
+British                           & 0.034                   & 0.182                                & 1976                                   & 0.042 & 0.202 & 990 & 0.026 & 0.16 & 986 \\
+Other                             & 0.05                    & 0.217                                & 1976                                   & 0.053 & 0.223 & 990 & 0.047 & 0.211 & 986 \\
+Artisan                           & 0.209                   & 0.407                                & 1976                                   & 0.214 & 0.41 & 990 & 0.204 & 0.403 & 986 \\
+Farmer                            & 0.421                   & 0.494                                & 1976                                   & 0.44 & 0.497 & 990 & 0.401 & 0.49 & 986 \\
+Professional or propietor         & 0.07                    & 0.256                                & 1976                                   & 0.077 & 0.266 & 990 & 0.064 & 0.245 & 986 \\
+Laborer                           & 0.266                   & 0.442                                & 1976                                   & 0.243 & 0.429 & 990 & 0.288 & 0.453 & 986 \\
+Unknown                           & 0.034                   & 0.182                                & 1976                                   & 0.025 & 0.157 & 990 & 0.044 & 0.204 & 986 \\
+Enlisted in big city              & 0.475                   & 0.5                                  & 1976                                   & 0.493 & 0.5 & 990 & 0.457 & 0.498 & 986 \\
+Household property income in 1860 & 576.475                 & 1855.699                             & 817                                    & 483.609 & 1084.987 & 391 & 661.711 & 2348.676 & 426 \\
+Age when captured                 & 25.96                   & 7.056                                & 1966                                   & 26.645 & 7.415 & 990 & 25.265 & 6.604 & 976 \\
+Height when captured                 & 171.576 & 6.612 & 1925 & 171.79 & 6.384 & 974 & 171.356 & 6.833 & 951 \\
+Commisoned or noncommisoned officer  & 0.076   & 0.266 & 1976 & 0.083  & 0.276 & 990 & 0.07    & 0.255 & 986 \\
+Married in 1860                      & 0.257   & 0.437 & 817  & 0.276  & 0.448 & 391 & 0.239   & 0.427 & 426 \\
+Wounded 10 days before capture       & 0.118   & 0.323 & 1976 & 0.148  & 0.356 & 990 & 0.088   & 0.284 & 986 \\
+Fraction company dead before capture & 0.089   & 0.064 & 1976 & 0.093  & 0.07  & 990 & 0.085   & 0.057 & 986 \\
+Company birthplace fragmentation     & 0.542   & 0.2   & 1923 & 0.547  & 0.193 & 985 & 0.536   & 0.206 & 938 \\
+Company occupational fragmentation   & 0.596   & 0.173 & 1923 & 0.586  & 0.173 & 985 & 0.607   & 0.172 & 938 \\
+\end{tabular}
+\end{sidewaystable}
+
+This table is almost exactly reproduced, except for the minor differences set in bold, which appear to be rounding differences (and a typo in the case of Laborer).
+The number of observations stated on the table in the paper (1923) corresponds to the last variable in this case as well, even though, as mentioned for the previous table, it is relevant to keep in mind that some of the other variables of interest show a considerably lower count of observations, as can be seen in the added columns.
+For this table, this is the case of variables Married in 1860 and Household property income in 1860, which are both variables from the 1860 census.
+The main concern regarding this table is the process of organizing the data, particularly one step in which a merge to the file ``transfer.dta'' is conducted.
+This file contains the prisoner identifier variable, month, year, and a dummy variable reflecting whether the prisoner was transferred (transferin).
+This variable is not needed for \autoref{friends}, and we can only speculate that it was incorporated, as some other steps were, in an attempt to exactly reproduce the dataset used in \autoref{corrected}.
+The problem in this case is that the file ``transfer.dta'' contains duplicate observations, which in turn duplicates observations in the main data set via the merge, artificially inflating the number of observations in the data used for \autoref{friends}\footnote{Duplicate observations per month-year-prisoner are natural in the context of \autoref{corrected}, because in there capture time is measured per fortnight.
+Including additional observations because of this in a stage of data description such as this one is hardly appropriate.}.
+
+If these duplicate observations are eliminated from the ``transfer.dta'' file before the merge, the statistics presented do not seem to defer significantly, and certainly neither do the conclusions drawn from them, but the number of observations in the subsample considered is significantly lower.
+This exercise is presented in the table below.
+
+\begin{sidewaystable}
+\centering
+\caption{corrected}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{corrected}
+\begin{tabular}{llllllllll}
+\hline
+                                  & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. \\
+US born                           & 0.732   & 0.443     & 1470     & 0.715   & 0.452     & 727      & 0.748   & 0.434     & 743      \\
+Irish                             & 0.122   & 0.327     & 1470     & 0.113   & 0.317     & 727      & 0.131   & 0.337     & 743      \\
+German                            & 0.06    & 0.237     & 1470     & 0.074   & 0.262     & 727      & 0.046   & 0.209     & 743      \\
+British                           & 0.034   & 0.181     & 1470     & 0.04    & 0.196     & 727      & 0.028   & 0.166     & 743      \\
+Other                             & 0.05    & 0.219     & 1470     & 0.056   & 0.231     & 727      & 0.044   & 0.206     & 743      \\
+Artisan                           & 0.212   & 0.409     & 1470     & 0.217   & 0.413     & 727      & 0.207   & 0.406     & 743      \\
+Farmer                            & 0.427   & 0.495     & 1470     & 0.442   & 0.497     & 727      & 0.413   & 0.493     & 743      \\
+Professional or proprietor        & 0.065   & 0.247     & 1470     & 0.073   & 0.26      & 727      & 0.058   & 0.234     & 743      \\
+Laborer                           & 0.265   & 0.441     & 1470     & 0.242   & 0.429     & 727      & 0.287   & 0.453     & 743      \\
+Unknown                           & 0.031   & 0.172     & 1470     & 0.026   & 0.16      & 727      & 0.035   & 0.184     & 743      \\
+Enlisted in big city              & 0.48    & 0.5       & 1470     & 0.486   & 0.5       & 727      & 0.475   & 0.5       & 743      \\
+Household property income in 1860 & 547.314 & 1637.903  & 615      & 476.274 & 1107.659  & 299      & 614.532 & 2014.738  & 316      \\
+Age when captured                 & 25.834  & 6.931     & 1465     & 26.4    & 7.263     & 727      & 25.276  & 6.544     & 738      \\
+Height when captured              & 171.526 & 6.624     & 1439     & 171.683 & 6.433     & 717      & 171.37  & 6.81      & 722      \\
+Commisioned or noncommisioned officer\footnote{Related to the point about the variable Volunteer made before, the name Commisioned or non commissioned officer may be misleading, since commissioned officers are excluded from the sample by construction.} & 0.074 & 0.262 & 1470 & 0.078 & 0.269 & 727 & 0.07  & 0.255 & 743 \\
+Married in 1860                       & 0.252 & 0.435 & 615  & 0.264 & 0.442 & 299 & 0.241 & 0.428 & 316 \\
+Wounded 10 days before capture        & 0.125 & 0.331 & 1470 & 0.155 & 0.363 & 727 & 0.096 & 0.294 & 743 \\
+Fraction company dead before capture  & 0.091 & 0.063 & 1470 & 0.094 & 0.069 & 727 & 0.089 & 0.056 & 743 \\
+Company birthplace fragmentation      & 0.542 & 0.198 & 1442 & 0.55  & 0.189 & 723 & 0.534 & 0.207 & 719 \\
+Company occupational fragmentation    & 0.593 & 0.175 & 1442 & 0.585 & 0.173 & 723 & 0.601 & 0.178 & 719 \\
+\end{tabular}
+\end{sidewaystable}
+
+Two additional remarks related to this are: a) whenever month was larger than 12, it is set to missing, b) all observations marked as having occurred in 1861 are shifted to 1862.
+Neither month nor year are directly used for this table, but they are the matching points for the merge to the ``transfer.dta'' file discussed above.
+The file “transfer.dta” also contains month>12 and observations for 1861, and they are not replaced in a similar fashion, introducing some additional artificial matching problems into the merge operation.3 Besides the potential distortions in the merge that these asymmetric replacements may cause, the switch of 1861 to 1862 seems particularly surprising given that no explanation for it is offered.
+
+Additionally, if the aim of this table is to have a general impression of the variables used in the main regressions (\autoref{corrected}), the same observations should have been considered in both accounts.
+This is not the case, since the observations with an unknown number of friends are dropped for this table, but not for the next one.
+
+\autoref{corrected}: This table shows the results of the hazard rate analysis using a set of covariates described in the previous tables and alternating two measures of friends: number of friends at the time of the observation and initial number of friends.
+
+\begin{sidewaystable}
+\caption{Social Networks and Individual Characteristics on Mortality}\footnote{Company clustered standard errors are in parentheses.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{social}
+\begin{tabular}{lllllll}
+\hline
+                                         & \multicolumn{2}{l}{specification I} & \multicolumn{2}{l}{specification II} & \multicolumn{2}{l}{specification III} \\
+VARIABLES                                & Hazard rate                         & Std. err.                            & Hazard rate                           & Std. err. & Hazard rate & Std. err. \\
+Current number of friends                & 0.983                               & -0.008                               & 0.977++                               & -0.009 &  &  \\
+Initial number of friends                &                                     &                                      &                                       &  & 0.976++ & -0.009 \\
+Ln(number of prisoners in camp)          &                                     &                                      & 1.536++                               & -0.14 & 1.521++ & -0.139 \\
+Fraction of company dying before capture & 1.091                               & -0.782                               & 0.892                                 & -0.636 & 0.63 & -0.449 \\
+Professional or proprietor               & 0.567                               & -0.146                               & 0.563                                 & -0.143 & 0.556 & -0.141 \\
+Artisan                                  & 0.944                               & -0.119                               & 0.947                                 & -0.119 & 0.937 & -0.117 \\
+Laborer                                  & 1.298                               & -0.154                               & 1.295                                 & -0.152 & 1.287 & -0.152 \\
+German                                   & 1.197                               & -0.215                               & 1.166                                 & -0.209 & 1.149 & -0.206 \\
+Irish                                    & 0.768*                              & -0.121                               & 0.762*                                & -0.118 & 0.750* & -0.117 \\
+British                       & 0.641*    & -0.171 & 0.654     & -0.174 & 0.656    & -0.177 \\
+Other                         & 0.658*    & -0.154 & 0.645*    & -0.153 & 0.642*   & -0.151 \\
+Sergeant, corporal or officer & 0.549++   & -0.115 & 0.543++   & -0.111 & 0.541++  & -0.111 \\
+Age at captivity              & 1.045++   & -0.007 & 1.044++   & -0.007 & 1.044++  & -0.007 \\
+Height at enlistment          & 1.01      & -0.007 & 1.01      & -0.007 & 1.011    & -0.007 \\
+Observations                  & 23256     &        & 23256     &        & 23256    &        \\
+Number of subjects            & 3026      &        & 3026      &        & 3026     &        \\
+Log pseudo likelihood         & -1324.607 &        & -1308.229 &        & -1307.17 &        \\
+\end{tabular}
+\end{sidewaystable}
+
+\autoref{corrected} is reproduced almost completely, except for the results in bold, for which the significance level differs from the one presented in the publication.
+
+In this case, month larger than 12 is replaced by 99, and in this case as well this might generate distortions since an equivalent change was not performed in the file to which this is merged (``Died.dta'').
+The observations for which the number of friends is unknown are not dropped here, but set to zero.
+Whenever the number of deaths in the prisoners' company before capture is unknown, it is set to zero.
+Whenever the number of men in camp is unknown it is set to 40.
+Whenever the variables imported from the 1860 census are missing (i.e.
+there was no match to the census) they are still included in the regression by setting their value to zero in the case of dummy variables (married and illiterate), and by taking log(1+variable) in the case of Household property.
+In all of these cases, dummy variables are included in the regression indicating whether the data is actually missing (e.g.
+a dummy variable that takes value one if the observation was not matched to the 1860 census, link60).
+It is understandable that in order to maintain a healthy sample size, and to use as much of the information as possible, some assumptions are made, but the trade off related to this point is that these assumptions may create artificial noise in the data that would not be fully captured by these control dummies.
+
+\autoref{social}: This table presents an alternative estimation strategy.
+As a benchmark, the effect of the number of friends in the camp is estimated including company fixed effects and the same covariates as before.
+To avoid endogeneity issues that may arise due to the potential correlation between the current number of friends and the prisoner’s own unobservable health (via its correlation to the lagged mortality of the group), an IV-hazard rate strategy is pursued next.
+The instruments chosen are the new number of friends the prisoner has in each period (the newly captured soldiers of his company) and a dummy variable that reflects whether the POW was transferred.
+Both variables clearly affect the number of friends a POW has, and are meant to be uncorrelated with his unobservable health, since transfers and the amount of newly captured men assigned to each camp were determined by camp needs or evolution of war events5.
+In the first stage, the number of friends is regressed on the instruments, as well as the whole set of covariates and fixed effects.
+The predicted residuals of this first stage are then included in the second stage, along with all covariates, fixed effects and the number of friends.
+This procedure is repeated 100 times, preserving the coefficients and standard errors of the number of friends, the number of men in the camp and the residuals, as well as the R-squared of the first stage.
+The final result of this Montecarlo procedure is obtained by computing the mean of those variables among the 100 repetitions.
+
+\begin{sidewaystable}
+\caption{Effect of Social Networks on Mortality, with Company Fixed Effects and Instrumented}\footnote{Company clustered standard errors are in parentheses.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{effect}
+\begin{tabular}{lllll}
+\hline
+                                    & \multicolumn{2}{l}{Original} & \multicolumn{2}{l}{IV} \\
+                                    & Haz. Rate                    & Std. Err.              & Haz. Rate & Std. Err. \\
+Number of friends                   & 0.978*                       & -0.012                 & 0.895 & -0.055 \\
+Ln(total number of men in the camp) & 1.437++                      & -0.122                 & 1.537 & -0.196 \\
+Residual                            &                              &                        & 1.06 & -0.071 \\
+\end{tabular}
+\end{sidewaystable}
+
+Here, the results are replicated entirely.
+
+A concern raised is that it is not clear how the variable that reflects transfers was constructed, since this information is not directly provided in the raw data available online.
+In some cases, the variable that reflects the camp contains multiple entries per individual, and we can only assume that those were used to infer that the POW was transferred between those camps.
+This is most likely an accurate interpretation of the data, the only problem being that there is no information about the date of transfer, which makes the instrument weaker.
+
+In the following section, the authors use The National Park Service's cross-sectional data of the population of Andersonville and estimate probit models of the probability of survival on the number of friends and various demographic characteristics as described in the summary.
+
+\autoref{effect}: This table estimates the effect of social networks on probability of survival controlling for a large of variables that measure existing networks outside of the company.
+
+\begin{sidewaystable}
+\caption{Effect of social networks on probability of survival}\footnote{Like in the paper, the estimations exclude the two outlier companies.
+Company clustered standard errors are in parentheses.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{effectsocial}
+\begin{tabular}{lllllll}
+\hline
+                                                              &         &         &         &         & \multicolumn{2}{l}{From small town} \\
+                                                              & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
+Number of men in regiment÷10                                  & 9.157   & 0.004++ &         &         &                                     &  \\
+                                                              & -10.358 & -0.001  &         &         &                                     &  \\
+Number of men in company                                      & 12.899  &         & 0.003++ & 0.002++ & 0.003++                             & 0.002++ \\
+                                                              & -15.39  &         & -0.001  & -0.001  & -0.001                              & -0.001 \\
+Fraction of company with              rank sergeant or higher & 0.073   & 0.120++ & 0.128++ & 0.079   & 0.152                               & 0.085 \\
+                                                              &         & -0.034  & -0.034  & -0.032  & -0.061                              & -0.056 \\
+Number of men with same last name in regiment                 & 1.19    & 0.033++ & 0.033++ & 0.036++ & 0.018*                              & 0.023++ \\
+                                                              & -0.599  & -0.007  & -0.007  & -0.006  & -0.009                              & -0.009 \\
+Log(number of men in camp from same town)                     & 5.101   & -0.003  & -0.002  & 0       & 0.018*                              & 0.026++ \\
+                                                              & -1.994  & -0.005  & -0.005  & -0.005  & -0.009                              & -0.008 \\
+Dummy=1 if town population<9552                               & 0.423   & 0.037+  & 0.034+  & 0.032+  &                                     &  \\
+                                                              &         & -0.014  & -0.014  & -0.013  &                                     &  \\
+Private                                                       & 0.824   &         &         &         &                                     &  \\
+Officer             & 0.003 & 0.347++ & 0.347++ & 0.354++ & 0.311++ & 0.328++ \\
+                    &       & -0.027  & -0.027  & -0.021  & -0.038  & -0.025  \\
+Sergeant            & 0.068 & 0.080++ & 0.080++ & 0.083++ & 0.084++ & 0.088++ \\
+                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
+Other rank          & 0.01  & 0.028   & 0.034   & 0.03    & 0.067   & 0.046   \\
+                    &       & -0.03   & -0.03   & -0.03   & -0.049  & -0.05   \\
+Corporal            & 0.078 & 0.055++ & 0.055++ & 0.046++ & 0.064++ & 0.054++ \\
+                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
+Irish surname       & 0.023 & 0.02    & 0.022   & 0.017   & 0.069   & 0.059*  \\
+                    &       & -0.019  & -0.019  & -0.019  & -0.03   & -0.03   \\
+German surname      & 0.043 & -0.009  & -0.009  & -0.016  & -0.001  & -0.025  \\
+                    &       & -0.015  & -0.015  & -0.015  & -0.024  & -0.025  \\
+French surname      & 0.028 & 0.028   & 0.028*  & 0.028   & 0.033   & 0.032   \\
+                    &       & -0.017  & -0.017  & -0.017  & -0.027  & -0.028  \\
+Continental surname & 0.029 & 0.006   & 0.007   & -0.004  & -0.021  & -0.029  \\
+                    &       & -0.018  & -0.018  & -0.018  & -0.032  & -0.032  \\
+State fixed effects? &       & N     & N     & Y     & N     & Y     \\
+Pseudo R2            &       & 0.043 & 0.044 & 0.087 & 0.048 & 0.115 \\
+Observations         & 31336 & 31336 & 31336 & 31330 & 12002 & 12002 \\
+\end{tabular}
+\end{sidewaystable}
+
+All figures on the table are replicated perfectly.
+However, the coefficients in bold are estimated with different significance levels (even though the coefficients and their standard errors are the same).
+For example, we find that the coefficient on Dummy=1 if town population $<9,552$ is significant at the 5 percent level whereas the table in the original paper indicates that it is significant at the 1 percent level in specifications 1, 2, and 3.
+It is important to note that the difference is not always in the same direction.
+For instance, we find that the coefficient on French surname in specification 2 is significant at the 10 percent level whereas the original table does not show any significance.
+Thus, we suspect that this discrepancy might be due to rounding error.
+
+\autoref{effectsocial}: Here, the authors estimate the same equation in logs and include the two outlier companies that were excluded in Table 5 to show the resulting nonlinearity.
+In the .do file, the outliers are dropped early on and thus their estimations never include these outliers.
+We save the dataset with the outliers at an early stage so that we can include them in the estimation.
+
+\begin{sidewaystable}
+\caption{Effect of social networks on probability of survival, logarithmic form}\footnote{Like in the paper, the estimations exclude the two outlier companies.
+Company clustered standard errors are in parentheses.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{effectLog}
+\begin{tabular}{lllllll}
+\hline
+                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
+                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
+Log(number of men in regiment)                     & 3.865  & 0.014++ &         &         &                                     &  \\
+                                                   & -1.29  & -0.005  &         &         &                                     &  \\
+Log(number of men in company)                      & 2.052  &         & 0.021++ & 0.012   & 0.029                               & 0.022 \\
+                                                   & -1.18  &         & -0.007  & -0.006  & -0.012                              & -0.009 \\
+Fraction of company with rank sergeant or higher   & 0.072  & 0.134++ & 0.134++ & 0.08    & 0.153                               & 0.084 \\
+                                                   & -0.127 & -0.034  & -0.034  & -0.032  & -0.061                              & -0.057 \\
+Log(number of men with same last name in regiment) & 0.112  & 0.101++ & 0.095++ & 0.096++ & 0.061++                             & 0.063++ \\
+                                                   & -0.305 & -0.012  & -0.012  & -0.011  & -0.018                              & -0.017 \\
+Log(number of men in camp from same town)          & 5.114  & -0.004  & 0       & 0.002   & 0.024                               & 0.030++ \\
+                                                   & -1.991 & -0.004  & -0.005  & -0.005  & -0.009                              & -0.008 \\
+State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
+Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.114 \\
+Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002                               & 12002 \\
+                                                   &        &         &         &         &                                     &  \\
+\end{tabular}
+\end{sidewaystable}
+
+The first thing to notice is that the number of observations is different.
+The original paper shows a total of 31,678 observations for the first three specifications, and a total of 12,025 observations for specifications 4 and 5.
+We have less number of observations mostly due to the 83 observations with missing Fraction of company with rank sergeant or higher variable.
+We don’t know how the authors included these observations in their estimation.
+A minor difference in the first descriptive column is the mean for Log(number of men with same last name in regiment), which is $0.113$ in the paper paper and $0.112$ in our data.
+
+All the coefficients in bold are slightly different from the original table; some are different only in their magnitude but some are also different in their level of significance.
+For example, the coefficient on Log(number of men in regiment) in specification 1 is $0.011$ with $5\%$ significance level in the paper, whereas we find a higher and more significant effect.
+Despite these quantitative differences, the results are not qualitatively different.
+
+\autoref{effectLog}: Here, the authors estimate the effect of ethnic networks on probability of survival to show that the quality of the network matters.
+
+\begin{sidewaystable}
+\caption{Effect of ethnic network on probability of survival}\footnote{Company clustered standard errors.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{ethnic}
+\begin{tabular}{lllllll}
+\hline
+
+                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
+                                          & b                         & se                         & b                          & se & b & se \\
+Number of men in company                  & 0.003*                    & 0.002                      & 0.003                      & 0.001 & 0.002 & 0.002 \\
+Number of men of own ethnicity in company & 0.03                      & 0.036                      & 0.03                       & 0.013 & 0.019 & 0.026 \\
+Dummy = 1 if Private                      & -0.046                    & 0.049                      & -0.078+                    & 0.037 & -0.093+ & 0.043 \\
+From small town                           & 0.1                       & 0.04                       & 0.036                      & 0.031 & 0.054 & 0.036 \\
+Captured 1864 or 1865                     & 0.239++                   & 0.077                      & 0.282++                    & 0.049 & 0.388++ & 0.058 \\
+Pseudo R2                                 & 0.036                     &                            & 0.059                      &  & 0.058 &  \\
+Joint significance test                   & 8.6                       &                            & 22.01                      &  & 3.2 &  \\
+Observations                              & 735                       &                            & 1355                       &  & 869 &  \\
+\end{tabular}
+\end{sidewaystable}
+
+The bold coefficients in \autoref{effectLog} are different in significance levels than what the authors report in their original table (all coefficients and standard errors are the same).
+The most striking one is the Captured 1864 or 1865 variable for French POWs where the authors find no significance at all and we find significance at the 1 percent level.
+Since this is too large of a difference to be a rounding error, we suspect that it is a typo.
+
+\subsection{Robustness check - Logit instead of Probit}
+
+As a robustness check, we estimate tables 5-7 with logit instead of probit and results are qualitatively similar.
+Bold coefficients below show differing levels of significance (only 1-level) when compared to probit.
+
+\begin{sidewaystable}
+\caption{Effect of social networks on probability of survival, logit}\footnote{There is no explanation in the paper as to why probit was preferred to logit.}
+\label{logit}
+\begin{tabular}{lllllll}
+\hline
+                                                 &         &         &         &         & \multicolumn{2}{l}{From small town} \\
+                                                 & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
+Number of men in regiment ÷10                    & 9.157   & 0.018++ &         &         &                                     &  \\
+                                                 & -10.358 & -0.003  &         &         &                                     &  \\
+Number of men in company                         & 12.899  &         & 0.013++ & 0.009++ & 0.014++                             & 0.010++ \\
+                                                 & -15.39  &         & -0.003  & -0.002  & -0.004                              & -0.003 \\
+Fraction of company with rank sergeant or higher & 0.073   & 0.495++ & 0.526++ & 0.336   & 0.647                               & 0.387 \\
+                                                 &         & -0.145  & -0.144  & -0.139  & -0.266                              & -0.251 \\
+Number of men with same last name in regiment    & 1.19    & 0.149++ & 0.147++ & 0.158++ & 0.081*                              & 0.101++ \\
+                                                 & -0.599  & -0.03   & -0.03   & -0.028  & -0.042                              & -0.038 \\
+Log(number of men in camp from same town)        & 5.101   & -0.012  & -0.01   & 0       & 0.075                               & 0.114++ \\
+                                                 & -1.994  & -0.019  & -0.019  & -0.019  & -0.038                              & -0.034 \\
+Dummy=1 if town population<9552                  & 0.423   & 0.154   & 0.145   & 0.133   &                                     &  \\
+                                                 &         & -0.06   & -0.056  & -0.054  &                                     &  \\
+Private                                          & 0.824   &         &         &         &                                     &  \\
+Officer & 0.003 & 2.342++ & 2.339++ & 2.481++ & 2.043++ & 2.342++ \\
+        &       & -0.454  & -0.455  & -0.426  & -0.562  & -0.502  \\
+Sergeant             & 0.068 & 0.344++ & 0.344++ & 0.367++ & 0.377++ & 0.407++ \\
+                     &       & -0.05   & -0.05   & -0.053  & -0.081  & -0.087  \\
+Other rank           & 0.01  & 0.109   & 0.135   & 0.12    & 0.295   & 0.2     \\
+                     &       & -0.128  & -0.128  & -0.132  & -0.232  & -0.231  \\
+Corporal             & 0.078 & 0.236++ & 0.235++ & 0.201++ & 0.283++ & 0.244++ \\
+                     &       & -0.046  & -0.046  & -0.048  & -0.077  & -0.084  \\
+Irish surname        & 0.023 & 0.086   & 0.095   & 0.072   & 0.31    & 0.264*  \\
+                     &       & -0.081  & -0.081  & -0.082  & -0.14   & -0.146  \\
+German surname       & 0.043 & -0.039  & -0.036  & -0.07   & -0.003  & -0.111  \\
+                     &       & -0.061  & -0.06   & -0.061  & -0.103  & -0.106  \\
+French surname       & 0.028 & 0.113   & 0.117   & 0.119   & 0.14    & 0.152   \\
+                     &       & -0.073  & -0.073  & -0.075  & -0.12   & -0.127  \\
+Continental surname  & 0.029 & 0.026   & 0.031   & -0.015  & -0.093  & -0.126  \\
+                     &       & -0.075  & -0.075  & -0.076  & -0.134  & -0.135  \\
+State fixed effects? &       & N       & N       & Y       & N       & Y       \\
+Pseudo R2            &       & 0.043   & 0.044   & 0.086   & 0.047   & 0.114   \\
+Observations         & 31336 & 31336   & 31336   & 31330   & 12002   & 12002   \\
+\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+\caption{Effect of social networks on probability of survival, logarithmic form, logit}\footnote{Company clustered standard errors are in parentheses.
+The number of observations for the Fraction of company with rank sergeant or higher variable in the first column is 31605.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{logLogit}
+\begin{tabular}{llllllllll}
+\hline
+                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
+                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
+Log(number of men in regiment)                     & 3.865  & 0.057   &         &         &                                     &  \\
+                                                   & -1.29  & -0.022  &         &         &                                     &  \\
+Log(number of men in company)                      & 2.052  &         & 0.088++ & 0.047   & 0.124                               & 0.085 \\
+                                                   & -1.18  &         & -0.028  & -0.024  & -0.051                              & -0.04 \\
+Fraction of company with rank sergeant or higher   & 0.072  & 0.559++ & 0.552++ & 0.342   & 0.652                               & 0.383 \\
+                                                   & -0.127 & -0.147  & -0.145  & -0.139  & -0.266                              & -0.251 \\
+Log(number of men with same last name in regiment) & 0.112  & 0.438++ & 0.409++ & 0.416++ & 0.267++                             & 0.277++ \\
+                                                   & -0.305 & -0.052  & -0.052  & -0.049  & -0.078                              & -0.074 \\
+Log(number of men in camp from same town)          & 5.114  & -0.018  & 0       & 0.006   & 0.100++                             & 0.131++ \\
+                                                   & -1.991 & -0.018  & -0.019  & -0.019  & -0.039                              & -0.036 \\
+State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
+Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.113 \\
+Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002 
+\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}
+\caption{Effect of ethnic networks on probability of survival, logit}\footnote{Standard errors are clustered on the company.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\label{ethLogit}
+\begin{tabular}{lllllll}
+\hline
+                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
+                                          & b                         & se                         & b                          & se & b & se \\
+Number of men in company                  & 0.009                     & 0.007                      & 0.011*                     & 0.006 & -0.001 & 0.007 \\
+Number of men of own ethnicity in company & 0.011                     & 0.11                       & 0.139                      & 0.06 & 0.154 & 0.116 \\
+Dummy =1 if Private                       & -0.228                    & 0.214                      & -0.337+                    & 0.162 & -0.445+ & 0.2 \\
+From small town                           & 0.417                     & 0.173                      & 0.154                      & 0.131 & 0.23 & 0.154 \\
+Captured 1864 or 1865                     & 1.082++                   & 0.347                      & 1.223++                    & 0.227 & 1.826++ & 0.307 \\
+Pseudo R2                                 & 0.032                     &                            & 0.058                      &  & 0.055 &  \\
+Joint significance test                   & 3.81                      &                            & 18.22                      &  & 2.16 &  \\
+Observations                              & 752                       &                            & 1357                       &  & 874 &  \\
+\end{tabular}
+\end{sidewaystable}
+
+\section{Conclusion}
+To sum up our replication, our key message is that while we do find small differences between our results and the published results of \textcite{costa2007surviving}, we find no evidence that would call their conclusions into question, either qualitatively or quantitatively.
+
+Furthermore, the interpretation of the results seems convincing to us.
+While they cannot test for how friends ensured survival the mentioned explanations from the supply of food to moral support are very comprehensible.
+In addition, their study is clearly and quite literally made for survival analysis so we do not see space to improve upon the results by applying a different estimation technique.
+\textcite{costa2007surviving} also apply a wide set of survival analysis tools (e.g.
+from non-parametric to parametric estimation) so we did not come up with many ideas for robustifying their paper in this direction.
+Potential future extensions could build on the use of different data sets.
+A weakness of the paper is clearly that external validity is limited because the authors look at a civil war of the 19th century.
+For instance, looking at World War I or II data could prove to be fruitful and lead to further insight.
+While we tried to start with such an extension, we were not able to find a sufficient dataset within this period of time.
+
+To come back to the differences between our replication and the original paper, we consider the most relevant issue the difference in significance levels.
+Interestingly, when looking into this matter in more detail we find that in almost all cases the p-values are at the margin which clearly points in the direction of a rounding error.
+We can only speculate that given the lack of exporting commands the reason for this is a certain degree of carelessness and, therefore, would like to emphasize the need of these very exporting commands.
+Nevertheless, and as mentioned before, the differences do not affect the general message of the paper.
+
+%\appendix
+
+\section{In-text estimation}
+Most in-text estimations are not included in the .do files provided, therefore some of the results to follow do not exactly reproduce the ones published, probably due to differences in specifications.
+They can nonetheless generally be replicated in terms of signs and significance.
+
+\paragraph{Probit statement}
+page 1474, line 21 ``When we run a Probit, in which the dependent variable is POW status and the independent variables are economic and geographic characteristics and the number of men in the company who were ever wounded or who ever died, we find that these two company characteristics were the main predictors of POW status.
+The derivative on the number of men in the company who were ever wounded or who ever died, was $0.257$ (robust $= 0.257$) and the derivative on the number of men who were ever wounded was $0.139$ (robust $= 0.042$).''
+
+\begin{table}[ht]
+\centering
+\caption{Determinants of POW Status}
+\begin{tabular}{lll}
+\hline
+                          & Marginal Effect & Marginal Effect \\
+\% in comp who died        & 0.359***        & 0.430***        \\
+                          & -0.021          & -0.0331         \\
+\% in comp who wounded     & 0.123***        & 0.140***        \\
+                          & -0.0136         & -0.022          \\
+Includes property in 1860 & No              & Yes             \\
+Observations              & 34878           & 13754           \\
+\end{tabular}
+\end{table}
+
+\paragraph{Comment on late capture}
+page 1474, line 77 ``We also found no evidence of group surrender to become a POW - men who were captured in 1864 and 1865 had more friends, even though a group who surrendered during these years would have no hope of a quick exchange.''
+
+\begin{sidewaystable}
+\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity and Late or Early Capture}
+\begin{tabular}{lllllllll}
+\hline
+                     & \multicolumn{4}{c}{Early capture} & \multicolumn{4}{c}{Late capture} \\
+                     & \multicolumn{2}{c}{$< 3$}           & \multicolumn{2}{c}{$>= 3$}         & \multicolumn{2}{c}{$< 3$} & \multicolumn{2}{c}{$>= 3$} \\
+                     & Mean                              & Std. err.                        & Mean & Std. err. & Mean & Std. err. & Mean & Std. err. \\
+US born              & 0.706                             & 0.456                            & 0.77 & 0.421 & 0.709 & 0.455 & 0.738 & 0.44 \\
+Irish                & 0.082                             & 0.275                            & 0.109 & 0.311 & 0.136 & 0.343 & 0.14 & 0.347 \\
+German               & 0.108                             & 0.311                            & 0.046 & 0.21 & 0.064 & 0.244 & 0.043 & 0.204 \\
+British              & 0.053                             & 0.224                            & 0.021 & 0.143 & 0.036 & 0.186 & 0.032 & 0.175 \\
+Other                & 0.048                             & 0.213                            & 0.046 & 0.21 & 0.056 & 0.229 & 0.047 & 0.213 \\
+Artisan              & 0.233                             & 0.423                            & 0.2 & 0.401 & 0.203 & 0.402 & 0.207 & 0.406 \\
+Farmer               & 0.423                             & 0.495                            & 0.355 & 0.479 & 0.451 & 0.498 & 0.444 & 0.497 \\
+Prof. or proprietor  & 0.09                              & 0.286                            & 0.075 & 0.264 & 0.069 & 0.253 & 0.053 & 0.225 \\
+Laborer              & 0.235                             & 0.425                            & 0.288 & 0.453 & 0.248 & 0.432 & 0.288 & 0.453 \\
+Unknown              & 0.019                             & 0.135                            & 0.081 & 0.274 & 0.029 & 0.169 & 0.008 & 0.089 \\
+Enlisted in big city & 0.545                             & 0.499                            & 0.497 & 0.501 & 0.461 & 0.499 & 0.42 & 0.494 \\
+Property inc in 1860 & 444.889                           & 1056.215                         & 703.517 & 2190.478 & 502.019 & 1099.896 & 620.684 & 2498.66 \\
+Age when captured    & 26.079                            & 7.152                            & 24.848 & 6.588 & 26.995 & 7.558 & 25.658 & 6.601 \\
+Height when captured & 171.518                           & 6.2                              & 171.377 & 6.914 & 171.959 & 6.495 & 171.338 & 6.765 \\
+Officer              & 0.111                             & 0.315                            & 0.092 & 0.289 & 0.065 & 0.247 & 0.049 & 0.217 \\
+Married in 1860      & 0.27                              & 0.446                            & 0.246 & 0.432 & 0.279 & 0.449 & 0.233 & 0.423 \\
+Fraction company dead before capture & 0.056 & 0.054 & 0.057 & 0.046 & 0.116 & 0.069 & 0.112 & 0.054 \\
+Company birthplace fragmentation     & 0.554 & 0.183 & 0.516 & 0.238 & 0.543 & 0.199 & 0.553 & 0.173 \\
+Company occupational fragmentation   & 0.587 & 0.173 & 0.614 & 0.177 & 0.586 & 0.173 & 0.601 & 0.168 \\
+\end{tabular}
+\end{sidewaystable}
+
+\paragraph{OLS statement}
+page 1474 line 65 and footnote 22.
+``When we ran an OLS regression of the number of friends on the covariates we later use in our hazard specification, we found that professionals and proprietors, the Irish, older men, and the recently wounded were less likely to have many friends, whereas those from a large city had more friends''...
+``The coefficient on recently wounded was $-0.879$ ($= 0.397$).''
+
+\begin{table}[ht]
+\centering
+\caption{Determinants of number of friends}
+\begin{tabular}{ll}
+\hline
+Professional or proprietor     & -0.913***  \\
+                               & -0.0979    \\
+Irish                          & -0.267***  \\
+                               & -0.0984    \\
+Age at capture                 & -0.0391*** \\
+                               & -0.00504   \\
+Wounded 10 days before capture & -0.831***  \\
+                               & -0.0876    \\
+Large city                     & 0.553***   \\
+                               & -0.0649    \\
+Observations                   & 23256      \\
+R-squared                      & 0.152      \\
+\end{tabular}
+\end{table}
+
+\paragraph{Predicted probability of death}
+page 1475, line 24.
+``As the number of friends increases from 0 to 5, the predicted probability of death, using the second specification in Table 3, decreases from $0.31$ to $0.28$, and as the number of friends increases to $10$, the predicted mortality probability falls to $0.26$.
+(The mean number of friends in each month was $5.6$, with a standard deviation of $9.2$, and the median was $2$.)''
+
+\begin{table}[ht]
+\centering
+\caption{Number of Friends}
+\begin{tabular}{lll}
+\hline
+          & Initial & In estimation \\
+Mean      & 5.58    & 2.87          \\
+Std. Dev. & 9.22    & 5.12          \\
+Median    & 2       & 1             \\
+\end{tabular}
+\end{table}
+
+The summary statistics mentioned for the variable friends match the initial file, but not the data that is actually included in the regression.
+
+\begin{figure}[ht]
+\centering
+\caption{Exponential specification}
+\label{exponential}
+\includegraphics[scale=0.65]{exponential.png}
+\end{figure}
+
+The file ``survival.dta'' contains the predicted survival probability for individuals with 0, 5 and 10 friends (evaluated at means for the other covariates).
+The statement did not specify a point in time, but we find a coincidence with the statement at $t=330.76$ (average days of imprisonment was $131.62$).
+
+\paragraph{Table 3 with regiment fixed effects}
+page 1476, line 2.
+``Even when we included state of regiment fixed effects, the hazard ratio on the number of friends remained virtually unchanged (e.g.
+the hazard ratio on the initial number of friends was $0.976$, $=0.009$).''
+
+\begin{sidewaystable}
+\caption{Table 3 with regiment state effects}\footnote{Company clustered standard errors are in parentheses.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\begin{tabular}{lllllll}
+\hline
+                                         & Hazard rate & Std. err & Hazard rate & Std. err & Hazard rate & Std. err \\
+Number of friends                        & 0.984*      & -0.009   & 0.978       & -0.009   &             &          \\
+Initial number of friends                &             &          &             &          & 0.976++     & -0.009   \\
+Ln(number of prisoners in camp)          &             &          & 1.538++     & -0.141   & 1.525++     & -0.14    \\
+Fraction of company dying before capture & 1.427       & -1.227   & 1.19        & -1.011   & 0.787       & -0.653   \\
+Professional or proprietor               & 0.512       & -0.134   & 0.506++     & -0.131   & 0.502++     & -0.13    \\
+Artisan                                  & 0.862       & -0.114   & 0.862       & -0.114   & 0.851       & -0.112   \\
+Laborer                                  & 1.163       & -0.148   & 1.154       & -0.146   & 1.141       & -0.145   \\
+German                                   & 1.135       & -0.213   & 1.116       & -0.21    & 1.103       & -0.206   \\
+Irish                                    & 0.731*      & -0.118   & 0.723       & -0.116   & 0.723       & -0.115   \\
+British                                  & 0.616*      & -0.167   & 0.630*      & -0.17    & 0.637*      & -0.174   \\
+Other                                    & 0.612       & -0.145   & 0.603       & -0.144   & 0.602       & -0.143   \\
+Sergeant, corporal or officer            & 0.570++     & -0.117   & 0.561++     & -0.113   & 0.557++     & -0.112   \\
+Age at captivity                         & 1.042++     & -0.008   & 1.040++     & -0.007   & 1.040++     & -0.007   \\
+Height at enlistment                     & 1.014*      & -0.007   & 1.014*      & -0.007   & 1.014*      & -0.007   \\
+Observations                             & 3026        &          & 3026        &          & 3026        &          \\
+Number of subjects                       & 23174       &          & 23174       &          & 23174       &          \\
+Log pseudo likelihood                    & -1307.77    &          & -1291.45    &          & -1290.674   &          \\
+\end{tabular}
+\end{sidewaystable}
+
+\paragraph{Table 3 with splines}
+page 1476, line 6 and footnote 23 ``Our experiments with splines suggested that the marginal effect of a friend on survival was greater for the first two friends than for more."  Footnote 23: "The hazard rate on the marginal effect of fewer than three friends was $0.956$ ($=0.044$) and the hazard rate on the marginal effect of three or more friends was $0.980$ ($=0.011$).
+Although the first hazard rate was not statistically significantly different from one, the two terms together were jointly significant.''
+
+\begin{table}[ht]
+\centering
+\caption{Spline at 3}
+\begin{tabular}{ll}
+\hline
+                     & Hazard rate \\
+Fewer than 3 friends & 0.956       \\
+                     & -0.0443     \\
+3 or more friends    & 0.980*      \\
+                     & -0.0108     \\
+Observations         & 23256       \\
+Chi-sq               & 7.789       \\
+Prob > chi-sq        & 0.0204      \\
+\end{tabular}
+\end{table}
+
+\paragraph{Weibull specification}
+page 1477, line 12. ``When we use a Weibull rather than an exponential specification, we found no evidence of duration dependence...''
+
+\begin{sidewaystable}
+\caption{Weibul}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\begin{tabular}{llllllllll}
+\hline
+                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
+VARIABLES                                & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
+Number of friends                        & 0.986                               & -0.009                              & 0.979                               & -0.009 &  &  \\
+Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
+Ln(number of prisoners in camp)          &                                     &                                     & 1.531++                             & -0.139 & 1.517++ & -0.139 \\
+Fraction of company dying before capture & 1.242                               & -0.897                              & 1.008                               & -0.722 & 0.733 & -0.525 \\
+Professional or propietor                & 0.566                               & -0.147                              & 0.562                               & -0.144 & 0.554 & -0.142 \\
+Artisan                                  & 0.95                                & -0.121                              & 0.952                               & -0.12 & 0.942 & -0.119 \\
+Laborer                                  & 1.308                               & -0.157                              & 1.303                               & -0.154 & 1.296 & -0.154 \\
+German                                   & 1.198                               & -0.218                              & 1.169                               & -0.212 & 1.153 & -0.209 \\
+Irish                                    & 0.771                               & -0.123                              & 0.765*                              & -0.12 & 0.753* & -0.118 \\
+British                                  & 0.630*                              & -0.17                               & 0.644                               & -0.174 & 0.646 & -0.176 \\
+Other                                    & 0.656*                              & -0.155                              & 0.643*                              & -0.153 & 0.640* & -0.151 \\
+Sargeant, corporal or officer            & 0.536++                             & -0.114                              & 0.531++                             & -0.11 & 0.528++ & -0.11 \\
+Age at captivity                         & 1.046++                             & -0.008                              & 1.045++                             & -0.008 & 1.045++ & -0.008 \\
+Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
+Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
+Log pseudo likelihood                    & -1322.852                           &                                     & -1306.836                           &  & -1305.627 &  \\
+Duration dependence                      & 1.088                               &                                     & 1.08                                &  & 1.084 &  \\
+\end{tabular}
+\end{sidewaystable}
+
+\paragraph{Month dummies}
+page 1477, line 19.
+``When we included dummy variables in our specification indicating that an individual had survived 1, 2, 3 or more months, we found that those who had survived one or two months were less likely to die than those still in their first month of captivity, but that the advantage of having survived a third month was small and there was no advantage to having survived a fourth month.''
+
+\begin{sidewaystable}
+\caption{controlling for months survived}\footnote{Company clustered standard errors are in parentheses.
+Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\begin{tabular}{lllllll}
+\hline
+                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
+                                         & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
+Number of friends                        & 0.989                               & -0.009                              & 0.982*                              & -0.009 &  &  \\
+Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
+Ln(number of prisoners in camp)          &                                     &                                     & 1.612++                             & -0.146 & 1.604++ & -0.145 \\
+Fraction of company dying before capture & 1.368                               & -1.001                              & 1.117                               & -0.811 & 0.832 & -0.603 \\
+Professional or propietor                & 0.56                                & -0.145                              & 0.557                               & -0.142 & 0.547 & -0.14 \\
+Artisan                                  & 0.946                               & -0.121                              & 0.951                               & -0.121 & 0.939 & -0.12 \\
+Laborer                                  & 1.302                               & -0.158                              & 1.302                               & -0.156 & 1.298 & -0.156 \\
+German                                   & 1.22                                & -0.223                              & 1.195                               & -0.216 & 1.178 & -0.213 \\
+Irish                                    & 0.774                               & -0.125                              & 0.770*                              & -0.122 & 0.756* & -0.12 \\
+British                                  & 0.618*                              & -0.168                              & 0.632*                              & -0.172 & 0.634* & -0.174 \\
+Other                                    & 0.658*                              & -0.156                              & 0.650*                              & -0.156 & 0.647* & -0.154 \\
+Sargeant, corporal or officer            & 0.533++                             & -0.114                              & 0.531++                             & -0.111 & 0.526++ & -0.11 \\
+Age at captivity                         & 1.047++                             & -0.008                              & 1.046++                             & -0.008 & 1.045++ & -0.008 \\
+Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
+Survived 1 month                         & 0.407++                             & -0.08                               & 0.362++                             & -0.072 & 0.352++ & -0.071 \\
+Survived 2 months                        & 0.472++                             & -0.092                              & 0.401++                             & -0.08 & 0.393++ & -0.078 \\
+Survived 3 months                        & 0.74                                & -0.137                              & 0.64                                & -0.12 & 0.631 & -0.118 \\
+Survived 4 or more months                & 0.833                               & -0.134                              & 0.745*                              & -0.12 & 0.740* & -0.119 \\
+Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
+Log pseudo likelihood                    & -1307.333                           &                                     & -1287.9                             &  & -1285.595 &  \\
+\end{tabular}
+\end{sidewaystable}
+
+\paragraph{Cox Proportional Hazard Model}
+page 1477, line 26 footnote.
+``We also investigated the use of a Cox proportional hazard model to allow the baseline hazard to rise or fall in any month.
+Controlling for camp conditions, we obtained a statistically insignificant hazard ratio on friends of $0.987$ ($=0.009$).
+We suspect that we are losing power because of our small sample size.''
+
+\begin{sidewaystable}
+\caption{Cox proportional models}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\begin{tabular}{lllllll}
+\hline
+                                         & Hazard rate & Std. err. & Hazard rate & Std. err. & Hazard rate & Std. err. \\
+Number of friends                        & 0.992       & -0.009    & 0.987       & -0.009    &             &           \\
+Initial number of friends                &             &           &             &           & 0.978       & -0.009    \\
+Ln(number of prisoners in camp)          &             &           & 1.593++     & -0.149    & 1.587++     & -0.149    \\
+Fraction of company dying before capture & 1.751       & -1.298    & 1.558       & -1.148    & 1.179       & -0.867    \\
+Professional or propietor                & 0.557       & -0.144    & 0.556       & -0.142    & 0.546       & -0.139    \\
+Artisan                                  & 0.942       & -0.121    & 0.952       & -0.122    & 0.938       & -0.12     \\
+Laborer                                  & 1.284       & -0.157    & 1.287       & -0.157    & 1.284       & -0.156    \\
+German                                   & 1.241       & -0.228    & 1.218       & -0.223    & 1.2         & -0.22     \\
+Irish                                    & 0.765       & -0.126    & 0.763*      & -0.123    & 0.746*      & -0.121    \\
+British                                  & 0.613*      & -0.166    & 0.625*      & -0.169    & 0.626*      & -0.171    \\
+Other                                    & 0.658*      & -0.159    & 0.652*      & -0.159    & 0.649*      & -0.158    \\
+Sargeant, corporal or officer            & 0.538++     & -0.115    & 0.537++     & -0.113    & 0.532++     & -0.112    \\
+Age at captivity                         & 1.048++     & -0.008    & 1.046++     & -0.008    & 1.046++     & -0.008    \\
+Height at entlistment                    & 1.01        & -0.008    & 1.01        & -0.007    & 1.011       & -0.007    \\
+Observations                             & 23256       &           & 23256       &           & 23256       &           \\
+Log pseudo likelihood                    & -3102.845   &           & -3086.134   &           & -3083.63    &           \\
+\end{tabular}
+\end{sidewaystable}
+
+\begin{table}[ht]
+\centering
+\caption{table 4 net transfer}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\begin{tabular}{lll}
+\hline
+VARIABLES               & Hazard Rate & Std. err. \\
+Net transfer of friends & 0.946**     & -0.024    \\
+Observations            & 15998       &           \\
+\end{tabular}
+\end{table}
+
+\paragraph{On limiting the sample}
+page 1480, line 17.
+``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged.
+The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).
+
+\paragraph{On the mortality of privates}
+page 1480, line 54.
+``The fraction of sergeants or higher rank is not a reflection of own officer mortality.
+When we restricted the sample to privates, we found that the derivative of this coefficient was 0.115 (sdev=0.054).''
+
+\paragraph{On the role of networks in predicting escape from Andersonville}
+page 1482, line 25.
+``Also suggestive of friends not always helping survival is that, among the men at Andersonville, we find no evidence that the number of friends predicted whether an individual was one of the 140 escaped.''
+
+See table below for the final three verifications:
+
+\begin{sidewaystable}
+\caption{Final three specifications}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
+\begin{tabular}{llll}
+\hline
+                                                 & Dependent variable: Lived & Dependent variable: Lived & Dependent variable: Escaped \\
+                                                 & Shorter time period       & Privates only             &                             \\
+Number of men in company                         & 0.003++                   & 0.003++                   & 0                           \\
+                                                 & -0.001                    & -0.001                    & 0                           \\
+Fraction of company with rank sergeant or higher & 0.115                     & 0.139++                   & -0.001                      \\
+                                                 & -0.054                    & -0.036                    & -0.002                      \\
+Number of men with same last name in regiment    & 0.033++                   & 0.035++                   & 0                           \\
+                                                 & -0.007                    & -0.007                    & 0                           \\
+Log(number of men in camp from same town)        & -0.003                    & -0.001                    & 0                           \\
+                                                 & -0.005                    & -0.005                    & 0                           \\
+Pseudo R2                                        & 0.036                     & 0.047                     & 0.015                       \\
+Observations                                     & 25880                     & 27923                     & 28190                       \\
+\end{tabular}
+\end{sidewaystable}
+
+The only in-text claim that we are not able to confirm is their statement that there is no mortality difference between the colored non-officers and the rest of the Andersonville POWs (page 1480, footnote 29) as we don’t have any information on the race of the POWs.
+
+\section{Non-parametric estimation}
+The following figures are our replications of the Kaplan-Meier survival estimates which show no differences to the original:
+
+\begin{figure}
+\centering
+\caption{Kaplan-Meier survival estimate}
+\label{kmSurvival}
+\includegraphics[scale=0.3]{kaplan1.png}
+\end{figure}
+
+\begin{figure}
+\centering
+\caption{Kaplan-Meier survival estimates by early and late capture date}
+\label{kmCapture}
+\includegraphics[scale=0.3]{kaplan2.png}
+\end{figure}
+
+\begin{figure}
+\centering
+\caption{Kaplan-Meier survival estimates by camp for late captures}
+\label{kmCamp}
+\includegraphics[scale=0.3]{kaplan3.png}
+\end{figure}
+
+\begin{figure}
+\centering
+\caption{Kaplan-Meier survival estimates by number of friends for Anderson}
+\label{kmNumber}
+\includegraphics[scale=0.3]{kaplan4.png}
+\end{figure}
+
 \printbibliography
+
 \end{refsection}
@@
 
-Let us suppose that the estimate of \emph{p} was positive by one and that the estimate of \emph{1-p} was positive by \emph{3s} then we know:
-
-% R Block
-
 \section{An application}
@@
 \chapter{Morris Shin Currency Attacks}
-\subfile{morrisShin.tex}
+blafslkfjas;lfkjasfd
 \parencite{morris1998unique}

### 2013-11-14 draft.tex

@@
 \usepackage{alltt}
-\usepackage{subfiles}
 \usepackage{mathtools}

### 2013-11-14 draft.Rnw
text changes

@@
 
+\begin{refsection}
 \chapter{Additional South African Evidence on Pensions and Child Growth}
@@
 The deviation from international standards \href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status.
+These are then compared for different pension recipient status and gender.
 
@@
 
-The South African pension is a useful variable to measure income because of its criteria.
+The South African pension is a interesting variable to measure income because of its criteria.
 Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
+Because of this the status as a recipient is quite exogenous and there are few selection bias issues.
 The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
@@
 @
+
+\printbibliography
+
+\end{refsection}
 
@@
 ``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged.
-The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).
+The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).''
 
@@
 \end{refsection}
+
+\begin{refsection}
 
@@
 
+\printbibliography
+
+\end{refsection}
+
 \begin{refsection}
+
 \chapter{Morris Shin Currency Attacks}
+
 blafslkfjas;lfkjasfd
+
 \parencite{morris1998unique}
+
 \printbibliography
+
 \end{refsection}

### 2013-11-14 draft.tex
text changes

@@
 \end{knitrout}
+
+\printbibliography
+
+\end{refsection}
 

### 2013-11-14 draft.Rnw
citations safr, fix formatting r p1

@@
 \begin{refsection}
-\chapter{Additional South African Evidence on Pensions and Child Growth}
+\chapter{Pensions and Child Growth in South Africa}
 
@@
 This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
-is very similar to Duflo (\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}).
-The deviation from international standards \href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for weight-for-height and length-for-age are computed as z-scores.
+is very similar to \textcite{duflo2000, duflo2003}.
+The deviation from international standards \parencite{who2006child} for weight-for-height and length-for-age are computed as z-scores.
 These are then compared for different pension recipient status and gender.
@@
 This study deviates from the Duflo study in several ways.
-In 2008 and 2012 the first and second wave of the \href{http://www.nids.uct.ac.za/home/}{National Income Dynamics Study} have gathered similar data.
+In 2008 and 2012 the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
 In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
@@
 
-Another deviation is the usage of \href{http://www.who.int/childgrowth/en/}{Child Growth Standards} in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.
+Another deviation is the usage of \textcite{who2006child} in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.
 
@@
 In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey and the second is the World Health Organization's Child Growth Standards \href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
+The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \textcite{who2006child}.
 
@@
 
-In 2006 the WHO published its standards for child growth \href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
+In 2006 the WHO published its standards for child growth \parencite{who2006child}.
 These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
@@
 <<r-p1, eval=TRUE>>=
-p1 <- ggplot(subset(w1_child,w1_woman_60 == 1), aes(w1_c_age_m, w1_zhfa, colour=factor(w1_c_woman)))
-p1 + stat_smooth(method="loess") + geom_point()
+p1 <- ggplot(subset(w1_child,w1_woman_60 == 1))
+p1 <- p1 + aes(w1_c_age_m, w1_zhfa, colour=factor(w1_c_woman))
+p1 <- p1 + stat_smooth(method="loess") + geom_point()
+p1
 @

### 2013-11-14 draft.tex
citations safr, fix formatting r p1

@@
 \begin{alltt}
-p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1), \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman)))
-p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
+p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1))
+p1 <- p1 + \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman))
+p1 <- p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
+p1
 \end{alltt}

### 2013-11-14 draft.Rnw
small fixes

@@
 
-\chapter{Replication of: Surviving Andersonville}
+\chapter{Replication: Surviving Andersonville}
 
@@
 
-\begin{refsection}
-
 \chapter{Single-Agent Belief Distributions}
@@
 Let us now suppose that our subject loses his wallet before the winner is drawn.
-If we want to predict how is beliefs have changed, we can for example assume that they are now 2below is mean belief.
+If we want to predict how is beliefs have changed, we can for example assume that they are now one standard deviation below his mean belief.
 This would thus give us:
@@
 
-If however, Janus there after is in a euphoric state because he find his wallet again, and on top of this a nice shiny green apple, than his new belief might change to \emph{3s} above his mean level.
+If however, Janus there after is in a euphoric state because he find his wallet again, and on top of this a nice shiny green apple, than his new belief might change to 2 standard deviations above his mean level.
 Which would give us:
@@
 
-Estimation of a 95\% confidence interval for a belief on probability, how the lottery profit from this.
-
-\printbibliography
-
-\end{refsection}
+Estimation of a 95\% confidence interval for a belief on probability, how the lottery profits from this.
 

### 2013-11-14 draft.Rnw
add CDC citation

@@
 
-Another deviation is the usage of \textcite{who2006child} in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.
+Another deviation is the usage of \textcite{who2006child} in stead of \textcite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence.
 

### 2013-11-21 draft.Rnw
add ugo as second reader

@@
 Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
-Second Reader:&%Lore Vandewalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
+Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
 \end{tabular}

### 2013-11-21 distributions.Rnw
move distributions out, included MS1998 and Bitcoin

--- 2013-11-21 draft.Rnw
@@
-\documentclass[a4paper]{book}
-\usepackage{mathtools}
-\usepackage{rotating}
-\usepackage{graphicx}
-\usepackage[authordate,backend=biber]{biblatex-chicago}
-\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
-
-\title{Preliminary Thesis Defence\\~\\
-\begin{tabular}{rl}
-Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
-Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
-\end{tabular}
-}
-
-\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}}
-
-\let\oldmarginpar\marginpar
-\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]
-{\raggedright\footnotesize #1}}
-
-\addglobalbib{bibliography.bib}
-
-\newbibmacro{string+doiurlisbn}[1]{%
-  \iffieldundef{doi}{%
-    \iffieldundef{url}{%
-      \iffieldundef{isbn}{%
-        \iffieldundef{issn}{%
-          #1%
-        }{%
-          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
-        }%
-      }{%
-        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
-      }%
-    }{%
-      \href{\thefield{url}}{#1}%
-    }%
-  }{%
-    \href{http://dx.doi.org/\thefield{doi}}{#1}%
-  }%
-}
-
-\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
-\DeclareFieldFormat[article,incollection]{title}%
-    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}
+\documentclass{article}
 
 \begin{document}
-
-\frontmatter
-\maketitle
-\tableofcontents
-
-\chapter{Introduction}
-jade
-
-\mainmatter
-
-\begin{refsection}
-\chapter{Pensions and Child Growth in South Africa}
-
-\section*{Abstract}
-
-In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.
-
-I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.
-
-The main preliminary finding is that the household effect was only significant in 2012.
-
-\section{Introduction}
-
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
-is very similar to \textcite{duflo2000, duflo2003}.
-The deviation from international standards \parencite{who2006child} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status and gender.
-
-The anthropometrics are useful for computing z-scores.
-These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
-
-The South African pension is a interesting variable to measure income because of its criteria.
-Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias issues.
-The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
-
-Duflo finds evidence in South Africa's 1993 \href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated Household Survey} that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension.
-This is directly after the significant increase in the pension sum for blacks.
-The pension-eligibility age at this time was 60 for women and 65 for men.
-
-This study deviates from the Duflo study in several ways.
-In 2008 and 2012 the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
-In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
-
-This happened in a few steps.
-As of July 16th 2008 men aged 63 and 64 were eligible for a pension.
-Men aged 61 and 62 became eligible in April 2009.
-Finally in January 2010, pension eligibility age was at 60 for all citizens.
-
-Another deviation is the usage of \textcite{who2006child} in stead of \textcite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence.
-
-The main preliminary result is that the household effect (i.e.~having one or more recipients in the household) is very insignificant in the 2008 estimate.
-But in the 2012 estimate it is very significant.
-
-\section{Data}
-
-In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \textcite{who2006child}.
-
-The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South African households.
-The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
-
-For adults several variables measure the different amounts and sources of income.
-Among those, a variable if the adult receives a state pension, and if so, how much.
-This is a numeric variable, the values of which lie very close together.
-For simplicity I have temporarily used this variable as a dummy.
-
-Children's anthropometrics are taken, these are length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
-However, I have computed the length-for-age z-scores manually.
-
-In 2006 the WHO published its standards for child growth \parencite{who2006child}.
-These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
-The standards provide the means and standards deviations used.
-These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
-
-<<load, include=FALSE>>=
-load("w1w2.RData")
-library(sem)
-library(ggplot2)
-@
-
-<<r-p1, eval=TRUE>>=
-p1 <- ggplot(subset(w1_child,w1_woman_60 == 1))
-p1 <- p1 + aes(w1_c_age_m, w1_zhfa, colour=factor(w1_c_woman))
-p1 <- p1 + stat_smooth(method="loess") + geom_point()
-p1
-@
-
-\section{Results}
-
-Basic HAZ (2008)
-
-<<sum-w1, eval=TRUE>>=
-summary(w1_haz0)
-@
-
-HAZ 2008, with 2012 eligiblity as an IV
-<<sum-iv, eval=TRUE>>=
-summary(tsls_w1w2_haz0)
-@
-
-HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-<<sum-iv-men65, eval=TRUE>>=
-summary(tsls_w1w2_haz1)
-@
-
-\printbibliography
-
-\end{refsection}
-
-\begin{refsection}
-
-\chapter{Replication: Surviving Andersonville}
-
-%\author{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}
-
-\section{Summary of the paper}
-\textcite{costa2007surviving} tries to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps.
-To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.
-
-The empirical specification for the longitudinal data that measures the effect of the size of the network is as follows:
-
-\begin{equation} \label{eq:ht}
-h(t) = \exp ( \beta_1 F + \beta_2 I + \beta_3 M )
-\end{equation}
-
-where $h$ is hazard at time $t$, $F$ is the number of friends (=social network), $I$ are individual characteristics and $M$ macro camp conditions.
-The number of friends is measured as the number of POWs of the same company and varies by month due to deaths or camp transfers.
-As it might capture the lagged mortality of the group, the authors use as second strategy the initial number of friends as a time-invariant proxy.
-In addition, they instrument for the number of friends using the number of net camp transfers combined with a dummy indicating whether the POW was transferred to account for omitted variables.
-The specification for the Andersonville data in turn is a probit model:
-
-\begin{align}
-\label{s1} Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F)\\
-\label{s1b} Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j)
-\end{align}
-
-where \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
-
-The longitudinal data indicates that POWs had special characteristics.
-For instance, they were likely to be volunteers, and from companies with more wounded or dead.
-POWs with more friends were typically US-born and wealthier while Irish and older men had less friends.
-Concerning survival rates, Kaplan-Meier hazard rates show that POWs captured later (after 1963 when the Union and the Confederate Army stopped exchanging POWs) have lower survival rates.
-They also show that survival rates were higher for POWs with 10 or more friends.
-In addition, the rates show that it takes 50 days until there is a divergence in survival between POWs with and without friends.
-The exponential function estimates that an additional friend leads to a 0.98 times lower mortality hazard.
-An increase in the number of friends from 0 to 5 (5 to 10), decreases the predicted probability of death from 0.31 to 0.28 (0.26) while a spline specification provides evidence that the effect is greatest for the first two friends.
-In addition, survival is more likely for POWs that had survived at least one or two months.
-Factors increasing mortality are the number of men in the camp, low rank, high age, and height among others.
-Insignificant variables are for instance wealth and marital status.
-There is no evidence for individual heterogeneity.
-The use of a Weibull specification indicates no duration dependence (toughen up effects).
-Interestingly though, a Cox model gives no significant effect of friends which the authors interpret as a result of their loss of power due to the small sample size.
-Robustness checks, including the IV approach and the effect of friends transferred in, confirms the significant effect of friends.
-Finally, the cross-sectional results provide evidence that having the same last name, being from the same town for smaller towns, ethnic similarity and having a sergeant or a higher rank in one's network are all important factors in raising survival probabilities which in turn shows that the quality of social networks matters.
-
-In summary, Costa and Kahn are able to show that quantity and quality of social networks mattered for survival in civil war POW camps.
-Potential explanations for this are the sharing of scarce resources, moral support and protection from other prisoners.
-
-\section{Data}
-The raw data for the first part of the paper is extracted from the Union Army dataset readily accessible at \url{http://www.cpe.uchicago.edu}.
-This dataset draws information from censuses, medical records and military pension records linking military, socioeconomic and health information for nearly $40,000$ white males that served in the Union Army during the Civil War.
-For the second part, the Andersonville database is available at \url{http://www.itd.nps.gov/cwss} but only as a ``searchable version'', which allows viewing the information for one soldier at a time, and more convenient formats are not readily available.
-
-The datasets provided for the estimations alongside with the publication are already partially processed parts of the raw data available online.
-No clear guidance is given as to what steps were taken to go from the raw data to the files provided, and matching both things proved to be less than straightforward.
-In view of this, we decided to proceed with the replication using the files provided by the authors, pointing out along the way the cases where potential problems in them seemed likely given the raw data we observed.
-Taking those files as starting points, it is possible to reproduce the tables and graphs published in the paper, so in this sense we can say that the data set is complete.
-Originally, some of the data required by the published .do files was not included in the published data files, but the authors provided it promptly upon our request and added it subsequently to the online files of the publishing journal.
-
-The data and .do files provided do not describe or label many of the variables used, nor does the limited variable description in the Appendix cover all of them.
-A very thorough description of the variables in the raw data set can be found at its online source, but the match between this and the variables in the files provided is not straightforward or complete, since some of them are already created by the authors from the raw data.
-The description of the data itself, mainly of the variables that are used most often, is succinct but adequate, with Table 1 and Table 2 presenting some relevant descriptive traits.
-Despite this, some attention should be drawn to the fact that some of the variables have a relevant share of missing values (only the highest number of observations is reported), a point that will be commented in detail later on.
-
-\section{Stata code and interpretation}
-All codes run to their full extent, and produce the estimations presented in the paper, with minor differences that we describe in detail below.
-The codes themselves are not commented at all and include plenty of estimations and specifications not included in the published paper, as well as unexplained data processing steps.
-No exporting commands were set up, or log files kept, which might be the root of some of the rounding and significance discrepancies we have found.
-
-In what follows, all reproduced tables are presented with a comment on the differences found (in bold), whenever there were any.
-
-\subsection{Tables}
-Table 1: This table presents the means of most variables later used for estimation, dividing observations in POWs and NON POWs, to illustrate ex ante differences in observables between them.
-
-\begin{table}[bt]
-\centering
-\caption{Characteristics of Soldiers by POW Status}
-\label{characteristics}
-\begin{tabular}{lllllll}
-\hline
-                           & All   & Obs.  & Never POW & Obs.  & POW   & Obs. \\
-US born                    & 0.745 & 35007 & 0.745     & 31967 & 0.743 & 3040 \\
-US born corrected          & 0.747 & 34941 & 0.745     & 31966 & 0.759 & 2975 \\
-Irish                      & 0.087 & 34941 & 0.086     & 31966 & 0.102 & 2975 \\
-German                     & 0.074 & 34941 & 0.075     & 31966 & 0.062 & 2975 \\
-British                    & 0.039 & 34941 & 0.039     & 31966 & 0.033 & 2975 \\
-Other                      & 0.054 & 34941 & 0.055     & 31966 & 0.043 & 2975 \\
-Artisan                    & 0.2   & 34941 & 0.199     & 31966 & 0.211 & 2975 \\
-Farmer corrected           & 0.505 & 34941 & 0.505     & 31966 & 0.508 & 2975 \\
-Professional or proprietor & 0.075 & 34941 & 0.077     & 31966 & 0.061 & 2975 \\
-Laborer                    & 0.212 & 34941 & 0.212     & 31966 & 0.212 & 2975 \\
-Unknown                    & 0.007 & 34941 & 0.007     & 31966 & 0.008 & 2975 \\
-Enlisted in 1861           & 0.21  & 35007 & 0.205     & 31967 & 0.263 & 3040 \\
-Enlisted in 1861 corrected & 0.21  & 34878 & 0.205     & 31906 & 0.269 & 2972 \\
-Enlisted in 1862                  & 0.344   & 34878 & 0.331   & 31906 & 0.487  & 2972 \\
-Enlisted in 1863                  & 0.068   & 34878 & 0.066   & 31906 & 0.087  & 2972 \\
-Enlisted in 1864                  & 0.256   & 34878 & 0.266   & 31906 & 0.147  & 2972 \\
-Enlisted in 1865                  & 0.122   & 34878 & 0.132   & 31906 & 0.009  & 2972 \\
-Volunteer                         & 0.909   & 34941 & 0.905   & 31966 & 0.951  & 2975 \\
-Height in inches                  & 67.599  & 34941 & 67.589  & 31966 & 67.709 & 2975 \\
-Household property income in 1860 & 534.155 & 13769 & 531.734 & 12509 & 558.2  & 1260 \\
-Company birthplace fragmentation  & 0.642   & 34941 & 0.644   & 31966 & 0.62   & 2975 \\
-Company occupation fragmentation  & 0.559   & 34941 & 0.558   & 31966 & 0.57   & 2975 \\
-Fraction company died as non-POWs & 0.135   & 34941 & 0.131   & 31966 & 0.182  & 2975 \\
-\end{tabular}
-\end{table}
-
-We have added to \autoref{characteristics} the number of observations per variable, not originally included in the paper, in order to highlight the fact that some of them have significant amounts of missing values, something that should be kept in mind later at the estimation stage.
-In this table, the case in point is Household property income in 1860, which is used in most of the specifications proposed, but as will be discussed for later tables, this is a pattern common to all the variables imported from census data.
-Additionally, considering the number of observations for each of the variables leads to the suggestion of a small correction for three of the dummy variables describing categories: US born, farmer and enlisted in 1861.
-The initial data file is missing these variables, which are likely to have been dropped as the basis category for estimation purposes in some other use of the data.
-They were then rebuilt in the .do file from the remaining categories in such a way that generated zeroes for some observations that should have been missing (except for farmer, which is not included at all in the file).
-For example: as provided by the code, US born has $35,007$ observations, whereas other nationality dummies, all built from the same original variable, have $34,941$.
-The correction proposed then, is to set these dummies to missing whenever the other categories of their class are missing, which slightly changes their descriptive statistics (for example the mean of US born goes from $0.745$ to $0.747$ when this correction is implemented).
-
-Remaining discrepancies are minor and could be due to some kind of rounding difference.
-An alternative explanation for these differences is that the table was produced from a slightly different dataset.
-Considering that even the most populous variables present over 500 observations less than the amount declared in the paper, and the fact that one of the variables (farmer) is not included in the data file at all, we consider the second option to be more likely, which would also explain the minor differences in the means of Artisan, British, Height in inches, etc.
-
-A last and minor comment is that the inclusion of the variable volunteer is surprising, since by sample design the Union Army dataset was restricted to white volunteer infantry regiments.
-The inclusion of this variable when comparing POWs and non POWs probably responds to the point raised in the paper about POWs not being representative of all soldiers, for example in ideology (p.1471).
-A variable that reflects that both POWs and non POWs volunteered in similar proportions would suggest homogeneity between POWs and non POWs in this dimension and, hence, increase  external validity.
-The similarities observed in Table 1 between POWs and non POWs in their mean of volunteer do not reflect that, since they are both close to one by construction.
-Any individuals not listed as volunteers, either correspond to the very few drafted men, or are actually soldiers that re-enlisted as commissioned officers, but were originally volunteers, as explained in the codebooks for the source data.
-
-\autoref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.
-It also presents separately their mean and standard errors for the subsamples of POWs with few (less than 3) and many friends (three or more).
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity}
-\label{friends}
-\begin{tabular}{llllllllll}
-
-                                  & \multicolumn{3}{l}{All} & \multicolumn{3}{l}{Few friends ($<3$)} & \multicolumn{3}{l}{Many friends ($>=3$)} \\
-                                  & Mean                    & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-\\
-US born                           & 0.731                   & 0.444                                & 1976                                   & 0.708 & 0.455 & 990 & 0.754 & 0.431 & 986 \\
-Irish                             & 0.12                    & 0.325                                & 1976                                   & 0.115 & 0.319 & 990 & 0.125 & 0.331 & 986 \\
-German                            & 0.063                   & 0.243                                & 1976                                   & 0.081 & 0.273 & 990 & 0.045 & 0.207 & 986 \\
-British                           & 0.034                   & 0.182                                & 1976                                   & 0.042 & 0.202 & 990 & 0.026 & 0.16 & 986 \\
-Other                             & 0.05                    & 0.217                                & 1976                                   & 0.053 & 0.223 & 990 & 0.047 & 0.211 & 986 \\
-Artisan                           & 0.209                   & 0.407                                & 1976                                   & 0.214 & 0.41 & 990 & 0.204 & 0.403 & 986 \\
-Farmer                            & 0.421                   & 0.494                                & 1976                                   & 0.44 & 0.497 & 990 & 0.401 & 0.49 & 986 \\
-Professional or propietor         & 0.07                    & 0.256                                & 1976                                   & 0.077 & 0.266 & 990 & 0.064 & 0.245 & 986 \\
-Laborer                           & 0.266                   & 0.442                                & 1976                                   & 0.243 & 0.429 & 990 & 0.288 & 0.453 & 986 \\
-Unknown                           & 0.034                   & 0.182                                & 1976                                   & 0.025 & 0.157 & 990 & 0.044 & 0.204 & 986 \\
-Enlisted in big city              & 0.475                   & 0.5                                  & 1976                                   & 0.493 & 0.5 & 990 & 0.457 & 0.498 & 986 \\
-Household property income in 1860 & 576.475                 & 1855.699                             & 817                                    & 483.609 & 1084.987 & 391 & 661.711 & 2348.676 & 426 \\
-Age when captured                 & 25.96                   & 7.056                                & 1966                                   & 26.645 & 7.415 & 990 & 25.265 & 6.604 & 976 \\
-Height when captured                 & 171.576 & 6.612 & 1925 & 171.79 & 6.384 & 974 & 171.356 & 6.833 & 951 \\
-Commisoned or noncommisoned officer  & 0.076   & 0.266 & 1976 & 0.083  & 0.276 & 990 & 0.07    & 0.255 & 986 \\
-Married in 1860                      & 0.257   & 0.437 & 817  & 0.276  & 0.448 & 391 & 0.239   & 0.427 & 426 \\
-Wounded 10 days before capture       & 0.118   & 0.323 & 1976 & 0.148  & 0.356 & 990 & 0.088   & 0.284 & 986 \\
-Fraction company dead before capture & 0.089   & 0.064 & 1976 & 0.093  & 0.07  & 990 & 0.085   & 0.057 & 986 \\
-Company birthplace fragmentation     & 0.542   & 0.2   & 1923 & 0.547  & 0.193 & 985 & 0.536   & 0.206 & 938 \\
-Company occupational fragmentation   & 0.596   & 0.173 & 1923 & 0.586  & 0.173 & 985 & 0.607   & 0.172 & 938 \\
-\end{tabular}
-\end{sidewaystable}
-
-This table is almost exactly reproduced, except for the minor differences set in bold, which appear to be rounding differences (and a typo in the case of Laborer).
-The number of observations stated on the table in the paper (1923) corresponds to the last variable in this case as well, even though, as mentioned for the previous table, it is relevant to keep in mind that some of the other variables of interest show a considerably lower count of observations, as can be seen in the added columns.
-For this table, this is the case of variables Married in 1860 and Household property income in 1860, which are both variables from the 1860 census.
-The main concern regarding this table is the process of organizing the data, particularly one step in which a merge to the file ``transfer.dta'' is conducted.
-This file contains the prisoner identifier variable, month, year, and a dummy variable reflecting whether the prisoner was transferred (transferin).
-This variable is not needed for \autoref{friends}, and we can only speculate that it was incorporated, as some other steps were, in an attempt to exactly reproduce the dataset used in \autoref{corrected}.
-The problem in this case is that the file ``transfer.dta'' contains duplicate observations, which in turn duplicates observations in the main data set via the merge, artificially inflating the number of observations in the data used for \autoref{friends}\footnote{Duplicate observations per month-year-prisoner are natural in the context of \autoref{corrected}, because in there capture time is measured per fortnight.
-Including additional observations because of this in a stage of data description such as this one is hardly appropriate.}.
-
-If these duplicate observations are eliminated from the ``transfer.dta'' file before the merge, the statistics presented do not seem to defer significantly, and certainly neither do the conclusions drawn from them, but the number of observations in the subsample considered is significantly lower.
-This exercise is presented in the table below.
-
-\begin{sidewaystable}
-\centering
-\caption{corrected}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{corrected}
-\begin{tabular}{llllllllll}
-\hline
-                                  & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. \\
-US born                           & 0.732   & 0.443     & 1470     & 0.715   & 0.452     & 727      & 0.748   & 0.434     & 743      \\
-Irish                             & 0.122   & 0.327     & 1470     & 0.113   & 0.317     & 727      & 0.131   & 0.337     & 743      \\
-German                            & 0.06    & 0.237     & 1470     & 0.074   & 0.262     & 727      & 0.046   & 0.209     & 743      \\
-British                           & 0.034   & 0.181     & 1470     & 0.04    & 0.196     & 727      & 0.028   & 0.166     & 743      \\
-Other                             & 0.05    & 0.219     & 1470     & 0.056   & 0.231     & 727      & 0.044   & 0.206     & 743      \\
-Artisan                           & 0.212   & 0.409     & 1470     & 0.217   & 0.413     & 727      & 0.207   & 0.406     & 743      \\
-Farmer                            & 0.427   & 0.495     & 1470     & 0.442   & 0.497     & 727      & 0.413   & 0.493     & 743      \\
-Professional or proprietor        & 0.065   & 0.247     & 1470     & 0.073   & 0.26      & 727      & 0.058   & 0.234     & 743      \\
-Laborer                           & 0.265   & 0.441     & 1470     & 0.242   & 0.429     & 727      & 0.287   & 0.453     & 743      \\
-Unknown                           & 0.031   & 0.172     & 1470     & 0.026   & 0.16      & 727      & 0.035   & 0.184     & 743      \\
-Enlisted in big city              & 0.48    & 0.5       & 1470     & 0.486   & 0.5       & 727      & 0.475   & 0.5       & 743      \\
-Household property income in 1860 & 547.314 & 1637.903  & 615      & 476.274 & 1107.659  & 299      & 614.532 & 2014.738  & 316      \\
-Age when captured                 & 25.834  & 6.931     & 1465     & 26.4    & 7.263     & 727      & 25.276  & 6.544     & 738      \\
-Height when captured              & 171.526 & 6.624     & 1439     & 171.683 & 6.433     & 717      & 171.37  & 6.81      & 722      \\
-Commisioned or noncommisioned officer\footnote{Related to the point about the variable Volunteer made before, the name Commisioned or non commissioned officer may be misleading, since commissioned officers are excluded from the sample by construction.} & 0.074 & 0.262 & 1470 & 0.078 & 0.269 & 727 & 0.07  & 0.255 & 743 \\
-Married in 1860                       & 0.252 & 0.435 & 615  & 0.264 & 0.442 & 299 & 0.241 & 0.428 & 316 \\
-Wounded 10 days before capture        & 0.125 & 0.331 & 1470 & 0.155 & 0.363 & 727 & 0.096 & 0.294 & 743 \\
-Fraction company dead before capture  & 0.091 & 0.063 & 1470 & 0.094 & 0.069 & 727 & 0.089 & 0.056 & 743 \\
-Company birthplace fragmentation      & 0.542 & 0.198 & 1442 & 0.55  & 0.189 & 723 & 0.534 & 0.207 & 719 \\
-Company occupational fragmentation    & 0.593 & 0.175 & 1442 & 0.585 & 0.173 & 723 & 0.601 & 0.178 & 719 \\
-\end{tabular}
-\end{sidewaystable}
-
-Two additional remarks related to this are: a) whenever month was larger than 12, it is set to missing, b) all observations marked as having occurred in 1861 are shifted to 1862.
-Neither month nor year are directly used for this table, but they are the matching points for the merge to the ``transfer.dta'' file discussed above.
-The file “transfer.dta” also contains month>12 and observations for 1861, and they are not replaced in a similar fashion, introducing some additional artificial matching problems into the merge operation.3 Besides the potential distortions in the merge that these asymmetric replacements may cause, the switch of 1861 to 1862 seems particularly surprising given that no explanation for it is offered.
-
-Additionally, if the aim of this table is to have a general impression of the variables used in the main regressions (\autoref{corrected}), the same observations should have been considered in both accounts.
-This is not the case, since the observations with an unknown number of friends are dropped for this table, but not for the next one.
-
-\autoref{corrected}: This table shows the results of the hazard rate analysis using a set of covariates described in the previous tables and alternating two measures of friends: number of friends at the time of the observation and initial number of friends.
-
-\begin{sidewaystable}
-\caption{Social Networks and Individual Characteristics on Mortality}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{social}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{specification I} & \multicolumn{2}{l}{specification II} & \multicolumn{2}{l}{specification III} \\
-VARIABLES                                & Hazard rate                         & Std. err.                            & Hazard rate                           & Std. err. & Hazard rate & Std. err. \\
-Current number of friends                & 0.983                               & -0.008                               & 0.977++                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                      &                                       &  & 0.976++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                      & 1.536++                               & -0.14 & 1.521++ & -0.139 \\
-Fraction of company dying before capture & 1.091                               & -0.782                               & 0.892                                 & -0.636 & 0.63 & -0.449 \\
-Professional or proprietor               & 0.567                               & -0.146                               & 0.563                                 & -0.143 & 0.556 & -0.141 \\
-Artisan                                  & 0.944                               & -0.119                               & 0.947                                 & -0.119 & 0.937 & -0.117 \\
-Laborer                                  & 1.298                               & -0.154                               & 1.295                                 & -0.152 & 1.287 & -0.152 \\
-German                                   & 1.197                               & -0.215                               & 1.166                                 & -0.209 & 1.149 & -0.206 \\
-Irish                                    & 0.768*                              & -0.121                               & 0.762*                                & -0.118 & 0.750* & -0.117 \\
-British                       & 0.641*    & -0.171 & 0.654     & -0.174 & 0.656    & -0.177 \\
-Other                         & 0.658*    & -0.154 & 0.645*    & -0.153 & 0.642*   & -0.151 \\
-Sergeant, corporal or officer & 0.549++   & -0.115 & 0.543++   & -0.111 & 0.541++  & -0.111 \\
-Age at captivity              & 1.045++   & -0.007 & 1.044++   & -0.007 & 1.044++  & -0.007 \\
-Height at enlistment          & 1.01      & -0.007 & 1.01      & -0.007 & 1.011    & -0.007 \\
-Observations                  & 23256     &        & 23256     &        & 23256    &        \\
-Number of subjects            & 3026      &        & 3026      &        & 3026     &        \\
-Log pseudo likelihood         & -1324.607 &        & -1308.229 &        & -1307.17 &        \\
-\end{tabular}
-\end{sidewaystable}
-
-\autoref{corrected} is reproduced almost completely, except for the results in bold, for which the significance level differs from the one presented in the publication.
-
-In this case, month larger than 12 is replaced by 99, and in this case as well this might generate distortions since an equivalent change was not performed in the file to which this is merged (``Died.dta'').
-The observations for which the number of friends is unknown are not dropped here, but set to zero.
-Whenever the number of deaths in the prisoners' company before capture is unknown, it is set to zero.
-Whenever the number of men in camp is unknown it is set to 40.
-Whenever the variables imported from the 1860 census are missing (i.e.
-there was no match to the census) they are still included in the regression by setting their value to zero in the case of dummy variables (married and illiterate), and by taking log(1+variable) in the case of Household property.
-In all of these cases, dummy variables are included in the regression indicating whether the data is actually missing (e.g.
-a dummy variable that takes value one if the observation was not matched to the 1860 census, link60).
-It is understandable that in order to maintain a healthy sample size, and to use as much of the information as possible, some assumptions are made, but the trade off related to this point is that these assumptions may create artificial noise in the data that would not be fully captured by these control dummies.
-
-\autoref{social}: This table presents an alternative estimation strategy.
-As a benchmark, the effect of the number of friends in the camp is estimated including company fixed effects and the same covariates as before.
-To avoid endogeneity issues that may arise due to the potential correlation between the current number of friends and the prisoner’s own unobservable health (via its correlation to the lagged mortality of the group), an IV-hazard rate strategy is pursued next.
-The instruments chosen are the new number of friends the prisoner has in each period (the newly captured soldiers of his company) and a dummy variable that reflects whether the POW was transferred.
-Both variables clearly affect the number of friends a POW has, and are meant to be uncorrelated with his unobservable health, since transfers and the amount of newly captured men assigned to each camp were determined by camp needs or evolution of war events5.
-In the first stage, the number of friends is regressed on the instruments, as well as the whole set of covariates and fixed effects.
-The predicted residuals of this first stage are then included in the second stage, along with all covariates, fixed effects and the number of friends.
-This procedure is repeated 100 times, preserving the coefficients and standard errors of the number of friends, the number of men in the camp and the residuals, as well as the R-squared of the first stage.
-The final result of this Montecarlo procedure is obtained by computing the mean of those variables among the 100 repetitions.
-
-\begin{sidewaystable}
-\caption{Effect of Social Networks on Mortality, with Company Fixed Effects and Instrumented}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effect}
-\begin{tabular}{lllll}
-\hline
-                                    & \multicolumn{2}{l}{Original} & \multicolumn{2}{l}{IV} \\
-                                    & Haz. Rate                    & Std. Err.              & Haz. Rate & Std. Err. \\
-Number of friends                   & 0.978*                       & -0.012                 & 0.895 & -0.055 \\
-Ln(total number of men in the camp) & 1.437++                      & -0.122                 & 1.537 & -0.196 \\
-Residual                            &                              &                        & 1.06 & -0.071 \\
-\end{tabular}
-\end{sidewaystable}
-
-Here, the results are replicated entirely.
-
-A concern raised is that it is not clear how the variable that reflects transfers was constructed, since this information is not directly provided in the raw data available online.
-In some cases, the variable that reflects the camp contains multiple entries per individual, and we can only assume that those were used to infer that the POW was transferred between those camps.
-This is most likely an accurate interpretation of the data, the only problem being that there is no information about the date of transfer, which makes the instrument weaker.
-
-In the following section, the authors use The National Park Service's cross-sectional data of the population of Andersonville and estimate probit models of the probability of survival on the number of friends and various demographic characteristics as described in the summary.
-
-\autoref{effect}: This table estimates the effect of social networks on probability of survival controlling for a large of variables that measure existing networks outside of the company.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectsocial}
-\begin{tabular}{lllllll}
-\hline
-                                                              &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                              & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment÷10                                  & 9.157   & 0.004++ &         &         &                                     &  \\
-                                                              & -10.358 & -0.001  &         &         &                                     &  \\
-Number of men in company                                      & 12.899  &         & 0.003++ & 0.002++ & 0.003++                             & 0.002++ \\
-                                                              & -15.39  &         & -0.001  & -0.001  & -0.001                              & -0.001 \\
-Fraction of company with              rank sergeant or higher & 0.073   & 0.120++ & 0.128++ & 0.079   & 0.152                               & 0.085 \\
-                                                              &         & -0.034  & -0.034  & -0.032  & -0.061                              & -0.056 \\
-Number of men with same last name in regiment                 & 1.19    & 0.033++ & 0.033++ & 0.036++ & 0.018*                              & 0.023++ \\
-                                                              & -0.599  & -0.007  & -0.007  & -0.006  & -0.009                              & -0.009 \\
-Log(number of men in camp from same town)                     & 5.101   & -0.003  & -0.002  & 0       & 0.018*                              & 0.026++ \\
-                                                              & -1.994  & -0.005  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-Dummy=1 if town population<9552                               & 0.423   & 0.037+  & 0.034+  & 0.032+  &                                     &  \\
-                                                              &         & -0.014  & -0.014  & -0.013  &                                     &  \\
-Private                                                       & 0.824   &         &         &         &                                     &  \\
-Officer             & 0.003 & 0.347++ & 0.347++ & 0.354++ & 0.311++ & 0.328++ \\
-                    &       & -0.027  & -0.027  & -0.021  & -0.038  & -0.025  \\
-Sergeant            & 0.068 & 0.080++ & 0.080++ & 0.083++ & 0.084++ & 0.088++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Other rank          & 0.01  & 0.028   & 0.034   & 0.03    & 0.067   & 0.046   \\
-                    &       & -0.03   & -0.03   & -0.03   & -0.049  & -0.05   \\
-Corporal            & 0.078 & 0.055++ & 0.055++ & 0.046++ & 0.064++ & 0.054++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Irish surname       & 0.023 & 0.02    & 0.022   & 0.017   & 0.069   & 0.059*  \\
-                    &       & -0.019  & -0.019  & -0.019  & -0.03   & -0.03   \\
-German surname      & 0.043 & -0.009  & -0.009  & -0.016  & -0.001  & -0.025  \\
-                    &       & -0.015  & -0.015  & -0.015  & -0.024  & -0.025  \\
-French surname      & 0.028 & 0.028   & 0.028*  & 0.028   & 0.033   & 0.032   \\
-                    &       & -0.017  & -0.017  & -0.017  & -0.027  & -0.028  \\
-Continental surname & 0.029 & 0.006   & 0.007   & -0.004  & -0.021  & -0.029  \\
-                    &       & -0.018  & -0.018  & -0.018  & -0.032  & -0.032  \\
-State fixed effects? &       & N     & N     & Y     & N     & Y     \\
-Pseudo R2            &       & 0.043 & 0.044 & 0.087 & 0.048 & 0.115 \\
-Observations         & 31336 & 31336 & 31336 & 31330 & 12002 & 12002 \\
-\end{tabular}
-\end{sidewaystable}
-
-All figures on the table are replicated perfectly.
-However, the coefficients in bold are estimated with different significance levels (even though the coefficients and their standard errors are the same).
-For example, we find that the coefficient on Dummy=1 if town population $<9,552$ is significant at the 5 percent level whereas the table in the original paper indicates that it is significant at the 1 percent level in specifications 1, 2, and 3.
-It is important to note that the difference is not always in the same direction.
-For instance, we find that the coefficient on French surname in specification 2 is significant at the 10 percent level whereas the original table does not show any significance.
-Thus, we suspect that this discrepancy might be due to rounding error.
-
-\autoref{effectsocial}: Here, the authors estimate the same equation in logs and include the two outlier companies that were excluded in Table 5 to show the resulting nonlinearity.
-In the .do file, the outliers are dropped early on and thus their estimations never include these outliers.
-We save the dataset with the outliers at an early stage so that we can include them in the estimation.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectLog}
-\begin{tabular}{lllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.014++ &         &         &                                     &  \\
-                                                   & -1.29  & -0.005  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.021++ & 0.012   & 0.029                               & 0.022 \\
-                                                   & -1.18  &         & -0.007  & -0.006  & -0.012                              & -0.009 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.134++ & 0.134++ & 0.08    & 0.153                               & 0.084 \\
-                                                   & -0.127 & -0.034  & -0.034  & -0.032  & -0.061                              & -0.057 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.101++ & 0.095++ & 0.096++ & 0.061++                             & 0.063++ \\
-                                                   & -0.305 & -0.012  & -0.012  & -0.011  & -0.018                              & -0.017 \\
-Log(number of men in camp from same town)          & 5.114  & -0.004  & 0       & 0.002   & 0.024                               & 0.030++ \\
-                                                   & -1.991 & -0.004  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.114 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002                               & 12002 \\
-                                                   &        &         &         &         &                                     &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The first thing to notice is that the number of observations is different.
-The original paper shows a total of 31,678 observations for the first three specifications, and a total of 12,025 observations for specifications 4 and 5.
-We have less number of observations mostly due to the 83 observations with missing Fraction of company with rank sergeant or higher variable.
-We don’t know how the authors included these observations in their estimation.
-A minor difference in the first descriptive column is the mean for Log(number of men with same last name in regiment), which is $0.113$ in the paper paper and $0.112$ in our data.
-
-All the coefficients in bold are slightly different from the original table; some are different only in their magnitude but some are also different in their level of significance.
-For example, the coefficient on Log(number of men in regiment) in specification 1 is $0.011$ with $5\%$ significance level in the paper, whereas we find a higher and more significant effect.
-Despite these quantitative differences, the results are not qualitatively different.
-
-\autoref{effectLog}: Here, the authors estimate the effect of ethnic networks on probability of survival to show that the quality of the network matters.
-
-\begin{sidewaystable}
-\caption{Effect of ethnic network on probability of survival}\footnote{Company clustered standard errors.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethnic}
-\begin{tabular}{lllllll}
-\hline
-
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.003*                    & 0.002                      & 0.003                      & 0.001 & 0.002 & 0.002 \\
-Number of men of own ethnicity in company & 0.03                      & 0.036                      & 0.03                       & 0.013 & 0.019 & 0.026 \\
-Dummy = 1 if Private                      & -0.046                    & 0.049                      & -0.078+                    & 0.037 & -0.093+ & 0.043 \\
-From small town                           & 0.1                       & 0.04                       & 0.036                      & 0.031 & 0.054 & 0.036 \\
-Captured 1864 or 1865                     & 0.239++                   & 0.077                      & 0.282++                    & 0.049 & 0.388++ & 0.058 \\
-Pseudo R2                                 & 0.036                     &                            & 0.059                      &  & 0.058 &  \\
-Joint significance test                   & 8.6                       &                            & 22.01                      &  & 3.2 &  \\
-Observations                              & 735                       &                            & 1355                       &  & 869 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The bold coefficients in \autoref{effectLog} are different in significance levels than what the authors report in their original table (all coefficients and standard errors are the same).
-The most striking one is the Captured 1864 or 1865 variable for French POWs where the authors find no significance at all and we find significance at the 1 percent level.
-Since this is too large of a difference to be a rounding error, we suspect that it is a typo.
-
-\subsection{Robustness check - Logit instead of Probit}
-
-As a robustness check, we estimate tables 5-7 with logit instead of probit and results are qualitatively similar.
-Bold coefficients below show differing levels of significance (only 1-level) when compared to probit.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logit}\footnote{There is no explanation in the paper as to why probit was preferred to logit.}
-\label{logit}
-\begin{tabular}{lllllll}
-\hline
-                                                 &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                 & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment ÷10                    & 9.157   & 0.018++ &         &         &                                     &  \\
-                                                 & -10.358 & -0.003  &         &         &                                     &  \\
-Number of men in company                         & 12.899  &         & 0.013++ & 0.009++ & 0.014++                             & 0.010++ \\
-                                                 & -15.39  &         & -0.003  & -0.002  & -0.004                              & -0.003 \\
-Fraction of company with rank sergeant or higher & 0.073   & 0.495++ & 0.526++ & 0.336   & 0.647                               & 0.387 \\
-                                                 &         & -0.145  & -0.144  & -0.139  & -0.266                              & -0.251 \\
-Number of men with same last name in regiment    & 1.19    & 0.149++ & 0.147++ & 0.158++ & 0.081*                              & 0.101++ \\
-                                                 & -0.599  & -0.03   & -0.03   & -0.028  & -0.042                              & -0.038 \\
-Log(number of men in camp from same town)        & 5.101   & -0.012  & -0.01   & 0       & 0.075                               & 0.114++ \\
-                                                 & -1.994  & -0.019  & -0.019  & -0.019  & -0.038                              & -0.034 \\
-Dummy=1 if town population<9552                  & 0.423   & 0.154   & 0.145   & 0.133   &                                     &  \\
-                                                 &         & -0.06   & -0.056  & -0.054  &                                     &  \\
-Private                                          & 0.824   &         &         &         &                                     &  \\
-Officer & 0.003 & 2.342++ & 2.339++ & 2.481++ & 2.043++ & 2.342++ \\
-        &       & -0.454  & -0.455  & -0.426  & -0.562  & -0.502  \\
-Sergeant             & 0.068 & 0.344++ & 0.344++ & 0.367++ & 0.377++ & 0.407++ \\
-                     &       & -0.05   & -0.05   & -0.053  & -0.081  & -0.087  \\
-Other rank           & 0.01  & 0.109   & 0.135   & 0.12    & 0.295   & 0.2     \\
-                     &       & -0.128  & -0.128  & -0.132  & -0.232  & -0.231  \\
-Corporal             & 0.078 & 0.236++ & 0.235++ & 0.201++ & 0.283++ & 0.244++ \\
-                     &       & -0.046  & -0.046  & -0.048  & -0.077  & -0.084  \\
-Irish surname        & 0.023 & 0.086   & 0.095   & 0.072   & 0.31    & 0.264*  \\
-                     &       & -0.081  & -0.081  & -0.082  & -0.14   & -0.146  \\
-German surname       & 0.043 & -0.039  & -0.036  & -0.07   & -0.003  & -0.111  \\
-                     &       & -0.061  & -0.06   & -0.061  & -0.103  & -0.106  \\
-French surname       & 0.028 & 0.113   & 0.117   & 0.119   & 0.14    & 0.152   \\
-                     &       & -0.073  & -0.073  & -0.075  & -0.12   & -0.127  \\
-Continental surname  & 0.029 & 0.026   & 0.031   & -0.015  & -0.093  & -0.126  \\
-                     &       & -0.075  & -0.075  & -0.076  & -0.134  & -0.135  \\
-State fixed effects? &       & N       & N       & Y       & N       & Y       \\
-Pseudo R2            &       & 0.043   & 0.044   & 0.086   & 0.047   & 0.114   \\
-Observations         & 31336 & 31336   & 31336   & 31330   & 12002   & 12002   \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form, logit}\footnote{Company clustered standard errors are in parentheses.
-The number of observations for the Fraction of company with rank sergeant or higher variable in the first column is 31605.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{logLogit}
-\begin{tabular}{llllllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.057   &         &         &                                     &  \\
-                                                   & -1.29  & -0.022  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.088++ & 0.047   & 0.124                               & 0.085 \\
-                                                   & -1.18  &         & -0.028  & -0.024  & -0.051                              & -0.04 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.559++ & 0.552++ & 0.342   & 0.652                               & 0.383 \\
-                                                   & -0.127 & -0.147  & -0.145  & -0.139  & -0.266                              & -0.251 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.438++ & 0.409++ & 0.416++ & 0.267++                             & 0.277++ \\
-                                                   & -0.305 & -0.052  & -0.052  & -0.049  & -0.078                              & -0.074 \\
-Log(number of men in camp from same town)          & 5.114  & -0.018  & 0       & 0.006   & 0.100++                             & 0.131++ \\
-                                                   & -1.991 & -0.018  & -0.019  & -0.019  & -0.039                              & -0.036 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.113 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002 
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of ethnic networks on probability of survival, logit}\footnote{Standard errors are clustered on the company.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethLogit}
-\begin{tabular}{lllllll}
-\hline
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.009                     & 0.007                      & 0.011*                     & 0.006 & -0.001 & 0.007 \\
-Number of men of own ethnicity in company & 0.011                     & 0.11                       & 0.139                      & 0.06 & 0.154 & 0.116 \\
-Dummy =1 if Private                       & -0.228                    & 0.214                      & -0.337+                    & 0.162 & -0.445+ & 0.2 \\
-From small town                           & 0.417                     & 0.173                      & 0.154                      & 0.131 & 0.23 & 0.154 \\
-Captured 1864 or 1865                     & 1.082++                   & 0.347                      & 1.223++                    & 0.227 & 1.826++ & 0.307 \\
-Pseudo R2                                 & 0.032                     &                            & 0.058                      &  & 0.055 &  \\
-Joint significance test                   & 3.81                      &                            & 18.22                      &  & 2.16 &  \\
-Observations                              & 752                       &                            & 1357                       &  & 874 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\section{Conclusion}
-To sum up our replication, our key message is that while we do find small differences between our results and the published results of \textcite{costa2007surviving}, we find no evidence that would call their conclusions into question, either qualitatively or quantitatively.
-
-Furthermore, the interpretation of the results seems convincing to us.
-While they cannot test for how friends ensured survival the mentioned explanations from the supply of food to moral support are very comprehensible.
-In addition, their study is clearly and quite literally made for survival analysis so we do not see space to improve upon the results by applying a different estimation technique.
-\textcite{costa2007surviving} also apply a wide set of survival analysis tools (e.g.
-from non-parametric to parametric estimation) so we did not come up with many ideas for robustifying their paper in this direction.
-Potential future extensions could build on the use of different data sets.
-A weakness of the paper is clearly that external validity is limited because the authors look at a civil war of the 19th century.
-For instance, looking at World War I or II data could prove to be fruitful and lead to further insight.
-While we tried to start with such an extension, we were not able to find a sufficient dataset within this period of time.
-
-To come back to the differences between our replication and the original paper, we consider the most relevant issue the difference in significance levels.
-Interestingly, when looking into this matter in more detail we find that in almost all cases the p-values are at the margin which clearly points in the direction of a rounding error.
-We can only speculate that given the lack of exporting commands the reason for this is a certain degree of carelessness and, therefore, would like to emphasize the need of these very exporting commands.
-Nevertheless, and as mentioned before, the differences do not affect the general message of the paper.
-
-%\appendix
-
-\section{In-text estimation}
-Most in-text estimations are not included in the .do files provided, therefore some of the results to follow do not exactly reproduce the ones published, probably due to differences in specifications.
-They can nonetheless generally be replicated in terms of signs and significance.
-
-\paragraph{Probit statement}
-page 1474, line 21 ``When we run a Probit, in which the dependent variable is POW status and the independent variables are economic and geographic characteristics and the number of men in the company who were ever wounded or who ever died, we find that these two company characteristics were the main predictors of POW status.
-The derivative on the number of men in the company who were ever wounded or who ever died, was $0.257$ (robust $= 0.257$) and the derivative on the number of men who were ever wounded was $0.139$ (robust $= 0.042$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of POW Status}
-\begin{tabular}{lll}
-\hline
-                          & Marginal Effect & Marginal Effect \\
-\% in comp who died        & 0.359***        & 0.430***        \\
-                          & -0.021          & -0.0331         \\
-\% in comp who wounded     & 0.123***        & 0.140***        \\
-                          & -0.0136         & -0.022          \\
-Includes property in 1860 & No              & Yes             \\
-Observations              & 34878           & 13754           \\
-\end{tabular}
-\end{table}
-
-\paragraph{Comment on late capture}
-page 1474, line 77 ``We also found no evidence of group surrender to become a POW - men who were captured in 1864 and 1865 had more friends, even though a group who surrendered during these years would have no hope of a quick exchange.''
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity and Late or Early Capture}
-\begin{tabular}{lllllllll}
-\hline
-                     & \multicolumn{4}{c}{Early capture} & \multicolumn{4}{c}{Late capture} \\
-                     & \multicolumn{2}{c}{$< 3$}           & \multicolumn{2}{c}{$>= 3$}         & \multicolumn{2}{c}{$< 3$} & \multicolumn{2}{c}{$>= 3$} \\
-                     & Mean                              & Std. err.                        & Mean & Std. err. & Mean & Std. err. & Mean & Std. err. \\
-US born              & 0.706                             & 0.456                            & 0.77 & 0.421 & 0.709 & 0.455 & 0.738 & 0.44 \\
-Irish                & 0.082                             & 0.275                            & 0.109 & 0.311 & 0.136 & 0.343 & 0.14 & 0.347 \\
-German               & 0.108                             & 0.311                            & 0.046 & 0.21 & 0.064 & 0.244 & 0.043 & 0.204 \\
-British              & 0.053                             & 0.224                            & 0.021 & 0.143 & 0.036 & 0.186 & 0.032 & 0.175 \\
-Other                & 0.048                             & 0.213                            & 0.046 & 0.21 & 0.056 & 0.229 & 0.047 & 0.213 \\
-Artisan              & 0.233                             & 0.423                            & 0.2 & 0.401 & 0.203 & 0.402 & 0.207 & 0.406 \\
-Farmer               & 0.423                             & 0.495                            & 0.355 & 0.479 & 0.451 & 0.498 & 0.444 & 0.497 \\
-Prof. or proprietor  & 0.09                              & 0.286                            & 0.075 & 0.264 & 0.069 & 0.253 & 0.053 & 0.225 \\
-Laborer              & 0.235                             & 0.425                            & 0.288 & 0.453 & 0.248 & 0.432 & 0.288 & 0.453 \\
-Unknown              & 0.019                             & 0.135                            & 0.081 & 0.274 & 0.029 & 0.169 & 0.008 & 0.089 \\
-Enlisted in big city & 0.545                             & 0.499                            & 0.497 & 0.501 & 0.461 & 0.499 & 0.42 & 0.494 \\
-Property inc in 1860 & 444.889                           & 1056.215                         & 703.517 & 2190.478 & 502.019 & 1099.896 & 620.684 & 2498.66 \\
-Age when captured    & 26.079                            & 7.152                            & 24.848 & 6.588 & 26.995 & 7.558 & 25.658 & 6.601 \\
-Height when captured & 171.518                           & 6.2                              & 171.377 & 6.914 & 171.959 & 6.495 & 171.338 & 6.765 \\
-Officer              & 0.111                             & 0.315                            & 0.092 & 0.289 & 0.065 & 0.247 & 0.049 & 0.217 \\
-Married in 1860      & 0.27                              & 0.446                            & 0.246 & 0.432 & 0.279 & 0.449 & 0.233 & 0.423 \\
-Fraction company dead before capture & 0.056 & 0.054 & 0.057 & 0.046 & 0.116 & 0.069 & 0.112 & 0.054 \\
-Company birthplace fragmentation     & 0.554 & 0.183 & 0.516 & 0.238 & 0.543 & 0.199 & 0.553 & 0.173 \\
-Company occupational fragmentation   & 0.587 & 0.173 & 0.614 & 0.177 & 0.586 & 0.173 & 0.601 & 0.168 \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{OLS statement}
-page 1474 line 65 and footnote 22.
-``When we ran an OLS regression of the number of friends on the covariates we later use in our hazard specification, we found that professionals and proprietors, the Irish, older men, and the recently wounded were less likely to have many friends, whereas those from a large city had more friends''...
-``The coefficient on recently wounded was $-0.879$ ($= 0.397$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of number of friends}
-\begin{tabular}{ll}
-\hline
-Professional or proprietor     & -0.913***  \\
-                               & -0.0979    \\
-Irish                          & -0.267***  \\
-                               & -0.0984    \\
-Age at capture                 & -0.0391*** \\
-                               & -0.00504   \\
-Wounded 10 days before capture & -0.831***  \\
-                               & -0.0876    \\
-Large city                     & 0.553***   \\
-                               & -0.0649    \\
-Observations                   & 23256      \\
-R-squared                      & 0.152      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Predicted probability of death}
-page 1475, line 24.
-``As the number of friends increases from 0 to 5, the predicted probability of death, using the second specification in Table 3, decreases from $0.31$ to $0.28$, and as the number of friends increases to $10$, the predicted mortality probability falls to $0.26$.
-(The mean number of friends in each month was $5.6$, with a standard deviation of $9.2$, and the median was $2$.)''
-
-\begin{table}[ht]
-\centering
-\caption{Number of Friends}
-\begin{tabular}{lll}
-\hline
-          & Initial & In estimation \\
-Mean      & 5.58    & 2.87          \\
-Std. Dev. & 9.22    & 5.12          \\
-Median    & 2       & 1             \\
-\end{tabular}
-\end{table}
-
-The summary statistics mentioned for the variable friends match the initial file, but not the data that is actually included in the regression.
-
-\begin{figure}[ht]
-\centering
-\caption{Exponential specification}
-\label{exponential}
-\includegraphics[scale=0.65]{exponential.png}
-\end{figure}
-
-The file ``survival.dta'' contains the predicted survival probability for individuals with 0, 5 and 10 friends (evaluated at means for the other covariates).
-The statement did not specify a point in time, but we find a coincidence with the statement at $t=330.76$ (average days of imprisonment was $131.62$).
-
-\paragraph{Table 3 with regiment fixed effects}
-page 1476, line 2.
-``Even when we included state of regiment fixed effects, the hazard ratio on the number of friends remained virtually unchanged (e.g.
-the hazard ratio on the initial number of friends was $0.976$, $=0.009$).''
-
-\begin{sidewaystable}
-\caption{Table 3 with regiment state effects}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err & Hazard rate & Std. err & Hazard rate & Std. err \\
-Number of friends                        & 0.984*      & -0.009   & 0.978       & -0.009   &             &          \\
-Initial number of friends                &             &          &             &          & 0.976++     & -0.009   \\
-Ln(number of prisoners in camp)          &             &          & 1.538++     & -0.141   & 1.525++     & -0.14    \\
-Fraction of company dying before capture & 1.427       & -1.227   & 1.19        & -1.011   & 0.787       & -0.653   \\
-Professional or proprietor               & 0.512       & -0.134   & 0.506++     & -0.131   & 0.502++     & -0.13    \\
-Artisan                                  & 0.862       & -0.114   & 0.862       & -0.114   & 0.851       & -0.112   \\
-Laborer                                  & 1.163       & -0.148   & 1.154       & -0.146   & 1.141       & -0.145   \\
-German                                   & 1.135       & -0.213   & 1.116       & -0.21    & 1.103       & -0.206   \\
-Irish                                    & 0.731*      & -0.118   & 0.723       & -0.116   & 0.723       & -0.115   \\
-British                                  & 0.616*      & -0.167   & 0.630*      & -0.17    & 0.637*      & -0.174   \\
-Other                                    & 0.612       & -0.145   & 0.603       & -0.144   & 0.602       & -0.143   \\
-Sergeant, corporal or officer            & 0.570++     & -0.117   & 0.561++     & -0.113   & 0.557++     & -0.112   \\
-Age at captivity                         & 1.042++     & -0.008   & 1.040++     & -0.007   & 1.040++     & -0.007   \\
-Height at enlistment                     & 1.014*      & -0.007   & 1.014*      & -0.007   & 1.014*      & -0.007   \\
-Observations                             & 3026        &          & 3026        &          & 3026        &          \\
-Number of subjects                       & 23174       &          & 23174       &          & 23174       &          \\
-Log pseudo likelihood                    & -1307.77    &          & -1291.45    &          & -1290.674   &          \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Table 3 with splines}
-page 1476, line 6 and footnote 23 ``Our experiments with splines suggested that the marginal effect of a friend on survival was greater for the first two friends than for more."  Footnote 23: "The hazard rate on the marginal effect of fewer than three friends was $0.956$ ($=0.044$) and the hazard rate on the marginal effect of three or more friends was $0.980$ ($=0.011$).
-Although the first hazard rate was not statistically significantly different from one, the two terms together were jointly significant.''
-
-\begin{table}[ht]
-\centering
-\caption{Spline at 3}
-\begin{tabular}{ll}
-\hline
-                     & Hazard rate \\
-Fewer than 3 friends & 0.956       \\
-                     & -0.0443     \\
-3 or more friends    & 0.980*      \\
-                     & -0.0108     \\
-Observations         & 23256       \\
-Chi-sq               & 7.789       \\
-Prob > chi-sq        & 0.0204      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Weibull specification}
-page 1477, line 12. ``When we use a Weibull rather than an exponential specification, we found no evidence of duration dependence...''
-
-\begin{sidewaystable}
-\caption{Weibul}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llllllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-VARIABLES                                & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.986                               & -0.009                              & 0.979                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.531++                             & -0.139 & 1.517++ & -0.139 \\
-Fraction of company dying before capture & 1.242                               & -0.897                              & 1.008                               & -0.722 & 0.733 & -0.525 \\
-Professional or propietor                & 0.566                               & -0.147                              & 0.562                               & -0.144 & 0.554 & -0.142 \\
-Artisan                                  & 0.95                                & -0.121                              & 0.952                               & -0.12 & 0.942 & -0.119 \\
-Laborer                                  & 1.308                               & -0.157                              & 1.303                               & -0.154 & 1.296 & -0.154 \\
-German                                   & 1.198                               & -0.218                              & 1.169                               & -0.212 & 1.153 & -0.209 \\
-Irish                                    & 0.771                               & -0.123                              & 0.765*                              & -0.12 & 0.753* & -0.118 \\
-British                                  & 0.630*                              & -0.17                               & 0.644                               & -0.174 & 0.646 & -0.176 \\
-Other                                    & 0.656*                              & -0.155                              & 0.643*                              & -0.153 & 0.640* & -0.151 \\
-Sargeant, corporal or officer            & 0.536++                             & -0.114                              & 0.531++                             & -0.11 & 0.528++ & -0.11 \\
-Age at captivity                         & 1.046++                             & -0.008                              & 1.045++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1322.852                           &                                     & -1306.836                           &  & -1305.627 &  \\
-Duration dependence                      & 1.088                               &                                     & 1.08                                &  & 1.084 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Month dummies}
-page 1477, line 19.
-``When we included dummy variables in our specification indicating that an individual had survived 1, 2, 3 or more months, we found that those who had survived one or two months were less likely to die than those still in their first month of captivity, but that the advantage of having survived a third month was small and there was no advantage to having survived a fourth month.''
-
-\begin{sidewaystable}
-\caption{controlling for months survived}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-                                         & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.989                               & -0.009                              & 0.982*                              & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.612++                             & -0.146 & 1.604++ & -0.145 \\
-Fraction of company dying before capture & 1.368                               & -1.001                              & 1.117                               & -0.811 & 0.832 & -0.603 \\
-Professional or propietor                & 0.56                                & -0.145                              & 0.557                               & -0.142 & 0.547 & -0.14 \\
-Artisan                                  & 0.946                               & -0.121                              & 0.951                               & -0.121 & 0.939 & -0.12 \\
-Laborer                                  & 1.302                               & -0.158                              & 1.302                               & -0.156 & 1.298 & -0.156 \\
-German                                   & 1.22                                & -0.223                              & 1.195                               & -0.216 & 1.178 & -0.213 \\
-Irish                                    & 0.774                               & -0.125                              & 0.770*                              & -0.122 & 0.756* & -0.12 \\
-British                                  & 0.618*                              & -0.168                              & 0.632*                              & -0.172 & 0.634* & -0.174 \\
-Other                                    & 0.658*                              & -0.156                              & 0.650*                              & -0.156 & 0.647* & -0.154 \\
-Sargeant, corporal or officer            & 0.533++                             & -0.114                              & 0.531++                             & -0.111 & 0.526++ & -0.11 \\
-Age at captivity                         & 1.047++                             & -0.008                              & 1.046++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Survived 1 month                         & 0.407++                             & -0.08                               & 0.362++                             & -0.072 & 0.352++ & -0.071 \\
-Survived 2 months                        & 0.472++                             & -0.092                              & 0.401++                             & -0.08 & 0.393++ & -0.078 \\
-Survived 3 months                        & 0.74                                & -0.137                              & 0.64                                & -0.12 & 0.631 & -0.118 \\
-Survived 4 or more months                & 0.833                               & -0.134                              & 0.745*                              & -0.12 & 0.740* & -0.119 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1307.333                           &                                     & -1287.9                             &  & -1285.595 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Cox Proportional Hazard Model}
-page 1477, line 26 footnote.
-``We also investigated the use of a Cox proportional hazard model to allow the baseline hazard to rise or fall in any month.
-Controlling for camp conditions, we obtained a statistically insignificant hazard ratio on friends of $0.987$ ($=0.009$).
-We suspect that we are losing power because of our small sample size.''
-
-\begin{sidewaystable}
-\caption{Cox proportional models}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err. & Hazard rate & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.992       & -0.009    & 0.987       & -0.009    &             &           \\
-Initial number of friends                &             &           &             &           & 0.978       & -0.009    \\
-Ln(number of prisoners in camp)          &             &           & 1.593++     & -0.149    & 1.587++     & -0.149    \\
-Fraction of company dying before capture & 1.751       & -1.298    & 1.558       & -1.148    & 1.179       & -0.867    \\
-Professional or propietor                & 0.557       & -0.144    & 0.556       & -0.142    & 0.546       & -0.139    \\
-Artisan                                  & 0.942       & -0.121    & 0.952       & -0.122    & 0.938       & -0.12     \\
-Laborer                                  & 1.284       & -0.157    & 1.287       & -0.157    & 1.284       & -0.156    \\
-German                                   & 1.241       & -0.228    & 1.218       & -0.223    & 1.2         & -0.22     \\
-Irish                                    & 0.765       & -0.126    & 0.763*      & -0.123    & 0.746*      & -0.121    \\
-British                                  & 0.613*      & -0.166    & 0.625*      & -0.169    & 0.626*      & -0.171    \\
-Other                                    & 0.658*      & -0.159    & 0.652*      & -0.159    & 0.649*      & -0.158    \\
-Sargeant, corporal or officer            & 0.538++     & -0.115    & 0.537++     & -0.113    & 0.532++     & -0.112    \\
-Age at captivity                         & 1.048++     & -0.008    & 1.046++     & -0.008    & 1.046++     & -0.008    \\
-Height at entlistment                    & 1.01        & -0.008    & 1.01        & -0.007    & 1.011       & -0.007    \\
-Observations                             & 23256       &           & 23256       &           & 23256       &           \\
-Log pseudo likelihood                    & -3102.845   &           & -3086.134   &           & -3083.63    &           \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{table}[ht]
-\centering
-\caption{table 4 net transfer}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lll}
-\hline
-VARIABLES               & Hazard Rate & Std. err. \\
-Net transfer of friends & 0.946**     & -0.024    \\
-Observations            & 15998       &           \\
-\end{tabular}
-\end{table}
-
-\paragraph{On limiting the sample}
-page 1480, line 17.
-``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged.
-The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).''
-
-\paragraph{On the mortality of privates}
-page 1480, line 54.
-``The fraction of sergeants or higher rank is not a reflection of own officer mortality.
-When we restricted the sample to privates, we found that the derivative of this coefficient was 0.115 (sdev=0.054).''
-
-\paragraph{On the role of networks in predicting escape from Andersonville}
-page 1482, line 25.
-``Also suggestive of friends not always helping survival is that, among the men at Andersonville, we find no evidence that the number of friends predicted whether an individual was one of the 140 escaped.''
-
-See table below for the final three verifications:
-
-\begin{sidewaystable}
-\caption{Final three specifications}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llll}
-\hline
-                                                 & Dependent variable: Lived & Dependent variable: Lived & Dependent variable: Escaped \\
-                                                 & Shorter time period       & Privates only             &                             \\
-Number of men in company                         & 0.003++                   & 0.003++                   & 0                           \\
-                                                 & -0.001                    & -0.001                    & 0                           \\
-Fraction of company with rank sergeant or higher & 0.115                     & 0.139++                   & -0.001                      \\
-                                                 & -0.054                    & -0.036                    & -0.002                      \\
-Number of men with same last name in regiment    & 0.033++                   & 0.035++                   & 0                           \\
-                                                 & -0.007                    & -0.007                    & 0                           \\
-Log(number of men in camp from same town)        & -0.003                    & -0.001                    & 0                           \\
-                                                 & -0.005                    & -0.005                    & 0                           \\
-Pseudo R2                                        & 0.036                     & 0.047                     & 0.015                       \\
-Observations                                     & 25880                     & 27923                     & 28190                       \\
-\end{tabular}
-\end{sidewaystable}
-
-The only in-text claim that we are not able to confirm is their statement that there is no mortality difference between the colored non-officers and the rest of the Andersonville POWs (page 1480, footnote 29) as we don’t have any information on the race of the POWs.
-
-\section{Non-parametric estimation}
-The following figures are our replications of the Kaplan-Meier survival estimates which show no differences to the original:
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimate}
-\label{kmSurvival}
-\includegraphics[scale=0.3]{kaplan1.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by early and late capture date}
-\label{kmCapture}
-\includegraphics[scale=0.3]{kaplan2.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by camp for late captures}
-\label{kmCamp}
-\includegraphics[scale=0.3]{kaplan3.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by number of friends for Anderson}
-\label{kmNumber}
-\includegraphics[scale=0.3]{kaplan4.png}
-\end{figure}
-
-\printbibliography
-
-\end{refsection}
 
@@
 
-\begin{refsection}
-
-\chapter{Morris Shin Currency Attacks}
-
-blafslkfjas;lfkjasfd
-
-\parencite{morris1998unique}
-
-\printbibliography
-
-\end{refsection}
-
-\backmatter
-\chapter{End notes}
-
 \end{document}

### 2013-11-21 draft.Rnw
move distributions out, included MS1998 and Bitcoin

@@
 
-\chapter{Single-Agent Belief Distributions}
-
-\section*{Abstract}
-By constructing a distribution of the belief structure of a single agent, we can mitigate seemingly incommensurable beliefs.
-This paper proposes to generalise the concept of a single agents beliefs, from a point estimate to a distributional approximation.
-This will allow us to deal with differing estimates of the probability \emph{p}, as well aswith estimates of \emph{p} and \emph{¬p} violating unitarity, in meaningful way.
-Additionally with a distributional approximation, we can estimate agents' beliefs, using the state which they are in.
-
-\section{Introduction}
-It generally held to be so that people sometimes hold beliefs which are incommensurable with each other.
-In technical terms we could say, the knowledge base is interally inconsistent.
-This incommensurability becomes especially apparent when these beliefs are quantified.
-
-As an example consider the following.
-If we have the probability of some event \emph{e} occuring with probability \emph{p}.
-By definition, all probabilities are exhausted at \emph{1}.
-Therefore the probability of that event not occuring (i.e.
-\emph{¬p} or \emph{not p}) is \emph{1-p}.
-
-\begin{quote}
-¬p = 1 - p
-\end{quote}
-
-It is often observed, that people hold beliefs that do not meet this condition, these beliefs can thus be described as:
-
-\begin{quote}
-¬p ≠ 1 - p
-\end{quote}
-
-In addition to this, we often see that people have different beliefs about the same thing, often just moments apart (e.g.~beginning and end of a survey).
-This could be the case for many (unrelated) reasons, such as, fatigue, hunger, anchoring, etc.
-We can express this as:
-
-\begin{quote}
-p\_1(e) ≠ p\_2(e)
-\end{quote}
-
-% We are thus faced with the fact that we get responses from agents
-
-In this paper I describe how we can generalise the idea of perception of probability -for a single agent- from a point estimate, to a distributional approximation.
-
-Doing this will allow us to deal with seemingly inconsistent beliefs in a single framework in a \emph{meaningful} way.
-
-\section{An example}
-
-On a fair die, the chance of throwing 3 eyes is 16, call this \emph{p}. The chance that you do not throw 3 eyes (i.e. \emph{¬p}) is therefore \emph{1-p}, or
-
-<<die, eval=TRUE>>=
-1 - (1/6)
-@
-
-This is a very simple statistical exercise, and most people will be able to give you the answer that I derived.
-The reason for this is that people learn to use dice and how they operate, in e.g.~board games.
-Likewise for coin flipping and many other basic statistical trials.
-In this context, you would rarely find people accepting a bet that has a negative expected value.
-Such as non-equal payout for a fair coin flip.
-
-However, as soon as odds become less transparent, statistical methods are often applied with less rigour.
-Especially when dealing with observed implicit payout structures.
-As a results bets with negative expected payouts, such as lotteries, are often accepted.
-
-Let us continue with the idea of a lottery.
-For a lottery at the local sports club, 100 tickets were printed, yet only 5 out of every 8 tickets was sold, therefore tickets will be drawn until a winner is found.
-The price of a ticket is 1 apple, and the prize for the winner is 50 apples.
-
-Our victim is called Janus. After Janus buys a ticket for the lottery, we ask him the following questions.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  What is the chance (in percent) that you will win the lottery?
-\item
-  What is the chance (as a ratio) that someone else will win the
-  lottery?
-\item
-  What is the chance that nobody wins the lottery?
-\item
-  You came with one apple, with how many apples do you expect to walked
-  away?
-\item
-  What is the chance (as a ratio) that you will win the lottery?
-\end{enumerate}
-
-The first question is not very hard:
-
-<<first, eval=TRUE>>=
-1/(100 * (5*8))
-@
-
-But perhaps it is something you wouldn't always do without a calculator or at least pen and paper. The second probability is:
-
-Definitely something most people would do on paper. However, since we are at the sports club, this is something we might not have at hand.
-
-As can be seen, question (1) and (5) are identical.
-If you go through the questions without having done the calculations beforehand, you will likely be inclined to give a lower answer to (5) than you were to (1).
-Presumable you would be quite neutral when answering question (1).
-Yet the question preceding question (5) is rather negative, since you would probably expect to walk away with zero apples, this would lead you to be in a more negative mood when answering (5).
-Furthermore, you could have become tired of answering so many questions, which generally diminishes your perception of your chance of being successful.
-
-Janus acts very much in accordance with our expectations, and gives us the following responses.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  2\% (has to be more than two)
-\item
-  19/20
-\item
-  0
-\item
-  0
-\item
-  1/60
-\end{enumerate}
-
-We observe two different estimates of the same \emph{p(e)}.
-
-<<p1, eval=TRUE>>=
-p_1 = 1/100
-p_1
-@
-
-<<p2, eval=TRUE>>=
-p_2 = 1/60
-p_2
-@
-
-Normally we would take either one of the responses, or such some other way to come to a point estimate, such as averaging.
-
-\section{As a distribution}
-
-Let us assume that question (2) was answered in an slightly optimistic state, and question 6 in a slightly pessimistic state.
-Furthermore, let us assume that beliefs are normally distributed, and that these slightly pessimistic and slightly optimistic state are each away from the mean, below and above respectively.
-Lets express (5) as a number: 0.0167.
-We can now construct the standard deviation.
-
-<<mu, eval=TRUE>>=
-mu = p_1
-mu
-@
-
-<<sigma, eval=TRUE>>=
-sigma = p_2 - mu
-sigma
-@
-
-We can now define our subjects beliefs on winning the lottery as:
-
-\begin{quote}
-B\textasciitilde{}N(0.0167,0.00167)
-\end{quote}
-
-Let us now suppose that our subject loses his wallet before the winner is drawn.
-If we want to predict how is beliefs have changed, we can for example assume that they are now one standard deviation below his mean belief.
-This would thus give us:
-
-<<mu-sigma, eval=TRUE>>=
-mu - sigma
-@
-
-If however, Janus there after is in a euphoric state because he find his wallet again, and on top of this a nice shiny green apple, than his new belief might change to 2 standard deviations above his mean level.
-Which would give us:
-
-<<mu+2sigma, eval=TRUE>>=
-mu + 2 * sigma
-@
-
-\begin{quote}
-p anp (1-p)
-\end{quote}
-
-How do we match the answers to questions (2) and (3), the chance that Janus thinks he has of winning, with the chance that somebody else win (i.e.~that he does not win).
-Let us write both odds as numbers:
-
-\begin{quote}
-p\_1 = 0.02 1 - p\_2 = 0.95 =\textgreater{} p\_2 = 0.05
-\end{quote}
-
-\section{An application}
-
-Estimation of a 95\% confidence interval for a belief on probability, how the lottery profits from this.
-
 \begin{refsection}
@@
 \chapter{Morris Shin Currency Attacks}
-
-blafslkfjas;lfkjasfd
-
-\parencite{morris1998unique}
+\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
+In my understanding of all the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor is the result of the fact that this risk factor eliminates the previously existing uncertainty.
+In other words, the unique equilibrium is not a surprising result, since knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
+This view is enforced by the fact that the equilibrium is most relevant when the risk factor (epsilon) is minimised, as the authors also state themselve.
+Furthermore, I have doubts about the authors claim that the domain which leads is solved by the equilibrium is in fact the entire 'ripe for attack' domain.
+
+\printbibliography
+
+\end{refsection}
+
+\begin{refsection}
+
+\chapter{Bitcoin and Remitances}
+In the 2008 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
+This currency (the first of a group called cryptocurrencies) has the following economics features:
+
+\begin{itemize}
+\item public transactions
+\item anonymous addresses
+\item fixed amount of units
+\item high granularity (1 Bitcoin can be broken into 100,000,000 Satoshi)
+\item no or low transaction costs
+\end{itemize}
+
+An addition to these economic features, the key feature of Bitcoin is decentralisation.
+All transactions are kept in a public ledger called the blockchain.
+An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
+Conflict resolution is done through majority voting by blockchain copy holders.
+
+There are a number of features which make Bitcoin attractive for remittances.
+Firstly, the low transaction costs are a huge step up from the current facilitators, which charge high percentages.
+Secondly, government intervention (especially in the recipient country) is prevented by the anonymity.
+Thirdly, recipients can choose to keep their remittance in a currency which is not controlled by their government.
+Fourthly, the granularity ensures very small transactions can be conducted.
+
+Bitcoin initially because popular in advanced economies such as those in Europe and North America.
+However, since mid 2013 there has been a large shift towards developing economies, in which comparative advantages of Bitcoin are more pronounced.
+For example, since its inception, Mt.Gox (located in Japan) was the largest Bitcoin exchange (marketplace), however in October 2013, Mt.Gox was overtaken by a Chinese exchange.
+
+Bitcoin transactions are conducted by the electronic 'signing' of a transaction.
+This is a very simple electronic process.
+Currently many smartphone applications are available to this purpose.
+However, in the targeted developing economies, many phones are not smartphones.
+The vast majority using Nokia Operating System.
+These phone can also run applications, of the kind Java Mobile App.
+Currently there are no Bitcoin apps available for this platform.
+
+I propose to participate in the development of open-source applications which would enable the users of stupid phones.
+We can then exploit the temporal difference when releasing the applications in different languages at different times, as well the downloads from traceable IP addresses.
 

### 2013-11-21 draft.tex
move distributions out, included MS1998 and Bitcoin

@@
 
-\chapter{Single-Agent Belief Distributions}
-
-\section*{Abstract}
-By constructing a distribution of the belief structure of a single agent, we can mitigate seemingly incommensurable beliefs.
-This paper proposes to generalise the concept of a single agents beliefs, from a point estimate to a distributional approximation.
-This will allow us to deal with differing estimates of the probability \emph{p}, as well aswith estimates of \emph{p} and \emph{¬p} violating unitarity, in meaningful way.
-Additionally with a distributional approximation, we can estimate agents' beliefs, using the state which they are in.
-
-\section{Introduction}
-It generally held to be so that people sometimes hold beliefs which are incommensurable with each other.
-In technical terms we could say, the knowledge base is interally inconsistent.
-This incommensurability becomes especially apparent when these beliefs are quantified.
-
-As an example consider the following.
-If we have the probability of some event \emph{e} occuring with probability \emph{p}.
-By definition, all probabilities are exhausted at \emph{1}.
-Therefore the probability of that event not occuring (i.e.
-\emph{¬p} or \emph{not p}) is \emph{1-p}.
-
-\begin{quote}
-¬p = 1 - p
-\end{quote}
-
-It is often observed, that people hold beliefs that do not meet this condition, these beliefs can thus be described as:
-
-\begin{quote}
-¬p ≠ 1 - p
-\end{quote}
-
-In addition to this, we often see that people have different beliefs about the same thing, often just moments apart (e.g.~beginning and end of a survey).
-This could be the case for many (unrelated) reasons, such as, fatigue, hunger, anchoring, etc.
-We can express this as:
-
-\begin{quote}
-p\_1(e) ≠ p\_2(e)
-\end{quote}
-
-% We are thus faced with the fact that we get responses from agents
-
-In this paper I describe how we can generalise the idea of perception of probability -for a single agent- from a point estimate, to a distributional approximation.
-
-Doing this will allow us to deal with seemingly inconsistent beliefs in a single framework in a \emph{meaningful} way.
-
-\section{An example}
-
-On a fair die, the chance of throwing 3 eyes is 16, call this \emph{p}. The chance that you do not throw 3 eyes (i.e. \emph{¬p}) is therefore \emph{1-p}, or
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-1 - (1/6)
-\end{alltt}
-\begin{verbatim}
-## [1] 0.8333
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-This is a very simple statistical exercise, and most people will be able to give you the answer that I derived.
-The reason for this is that people learn to use dice and how they operate, in e.g.~board games.
-Likewise for coin flipping and many other basic statistical trials.
-In this context, you would rarely find people accepting a bet that has a negative expected value.
-Such as non-equal payout for a fair coin flip.
-
-However, as soon as odds become less transparent, statistical methods are often applied with less rigour.
-Especially when dealing with observed implicit payout structures.
-As a results bets with negative expected payouts, such as lotteries, are often accepted.
-
-Let us continue with the idea of a lottery.
-For a lottery at the local sports club, 100 tickets were printed, yet only 5 out of every 8 tickets was sold, therefore tickets will be drawn until a winner is found.
-The price of a ticket is 1 apple, and the prize for the winner is 50 apples.
-
-Our victim is called Janus. After Janus buys a ticket for the lottery, we ask him the following questions.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  What is the chance (in percent) that you will win the lottery?
-\item
-  What is the chance (as a ratio) that someone else will win the
-  lottery?
-\item
-  What is the chance that nobody wins the lottery?
-\item
-  You came with one apple, with how many apples do you expect to walked
-  away?
-\item
-  What is the chance (as a ratio) that you will win the lottery?
-\end{enumerate}
-
-The first question is not very hard:
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-1/(100 * (5 * 8))
-\end{alltt}
-\begin{verbatim}
-## [1] 0.00025
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-But perhaps it is something you wouldn't always do without a calculator or at least pen and paper. The second probability is:
-
-Definitely something most people would do on paper. However, since we are at the sports club, this is something we might not have at hand.
-
-As can be seen, question (1) and (5) are identical.
-If you go through the questions without having done the calculations beforehand, you will likely be inclined to give a lower answer to (5) than you were to (1).
-Presumable you would be quite neutral when answering question (1).
-Yet the question preceding question (5) is rather negative, since you would probably expect to walk away with zero apples, this would lead you to be in a more negative mood when answering (5).
-Furthermore, you could have become tired of answering so many questions, which generally diminishes your perception of your chance of being successful.
-
-Janus acts very much in accordance with our expectations, and gives us the following responses.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\itemsep1pt\parskip0pt\parsep0pt
-\item
-  2\% (has to be more than two)
-\item
-  19/20
-\item
-  0
-\item
-  0
-\item
-  1/60
-\end{enumerate}
-
-We observe two different estimates of the same \emph{p(e)}.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-p_1 = 1/100
-p_1
-\end{alltt}
-\begin{verbatim}
-## [1] 0.01
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-p_2 = 1/60
-p_2
-\end{alltt}
-\begin{verbatim}
-## [1] 0.01667
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-Normally we would take either one of the responses, or such some other way to come to a point estimate, such as averaging.
-
-\section{As a distribution}
-
-Let us assume that question (2) was answered in an slightly optimistic state, and question 6 in a slightly pessimistic state.
-Furthermore, let us assume that beliefs are normally distributed, and that these slightly pessimistic and slightly optimistic state are each away from the mean, below and above respectively.
-Lets express (5) as a number: 0.0167.
-We can now construct the standard deviation.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-mu = p_1
-mu
-\end{alltt}
-\begin{verbatim}
-## [1] 0.01
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-sigma = p_2 - mu
-sigma
-\end{alltt}
-\begin{verbatim}
-## [1] 0.006667
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-We can now define our subjects beliefs on winning the lottery as:
-
-\begin{quote}
-B\textasciitilde{}N(0.0167,0.00167)
-\end{quote}
-
-Let us now suppose that our subject loses his wallet before the winner is drawn.
-If we want to predict how is beliefs have changed, we can for example assume that they are now one standard deviation below his mean belief.
-This would thus give us:
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-mu - sigma
-\end{alltt}
-\begin{verbatim}
-## [1] 0.003333
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-If however, Janus there after is in a euphoric state because he find his wallet again, and on top of this a nice shiny green apple, than his new belief might change to 2 standard deviations above his mean level.
-Which would give us:
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-mu + 2 * sigma
-\end{alltt}
-\begin{verbatim}
-## [1] 0.02333
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\begin{quote}
-p anp (1-p)
-\end{quote}
-
-How do we match the answers to questions (2) and (3), the chance that Janus thinks he has of winning, with the chance that somebody else win (i.e.~that he does not win).
-Let us write both odds as numbers:
-
-\begin{quote}
-p\_1 = 0.02 1 - p\_2 = 0.95 =\textgreater{} p\_2 = 0.05
-\end{quote}
-
-\section{An application}
-
-Estimation of a 95\% confidence interval for a belief on probability, how the lottery profits from this.
-
 \begin{refsection}

### 2013-11-21 draft.Rnw
change to report, from book
add GI, G to title page
add introduction

@@
-\documentclass[a4paper]{book}
+\documentclass[a4paper]{report}
 \usepackage{mathtools}
@@
 
-\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}}
+\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}\\~\\
+The Graduate Institute, Geneva}
 
@@
 
-\frontmatter
 \maketitle
@@
 \chapter{Introduction}
-jade
-
-\mainmatter
+In this Preliminary Thesis Defence I present the research projects which I would like to use for my PhD dissertation. These projects are titled:
+
+\begin{itemize}
+\item Additional South African Evidence on Pensions and Child Growth
+\item Replication: Surviving Andersonville
+\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (MS1998)
+\item Bitcoin and Remittances: The Potential of Stupid Phones
+\item Blacks-Swan and Dragon-King Events in Microeconomics
+\end{itemize}
+
+These project are in various stages of completion, though none of them are actually near completion.
+Below I will briefly describe the research idea, the current state, and the potential for each project.
+
+Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}.
+Duflo looks at the effect of the gender of grandparents on the growth metrics of their grandchildren.
+A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
+This paper makes use of a Household Survey from 2008, 2012 and 2013.
+The survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
+As it stand now I have analysed the data from 2008 and 2012.
+As the 2013 data was released several weeks ago I will incorporate these data as well.
+
+Together with several other PhD students we have replicated the paper Surviving Andersonville by \textcite{costa2007surviving}.
+We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors.
+However, replicating this numbers required us to take a number of steps and questionable steps in our analysis.
+When we replace these steps with more obvious alternatives, we find that we cannot quantitatively and qualitatively replicate the main results from the paper.
+As an example, we find that the dataset distinguishes between two different POW camps both located in Andersonville, whereas the authors do not.
+This leads to overstated magnitudes of the social ties of POW.
+This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
+At this point our replication is quite complete.
+Before rewriting this paper, I will redo the analysis in R (the original and our current replication are in Stata).
+
+\textcite{morris1998unique} claim that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
+It thus solves the previous multiple-equilibrium zone called 'ripe for attack' for a unique equilibrium.
+I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainy.
+We thus gain information.
+I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
+
+Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies.
+The transactions are conducted using an electronic process called signing.
+I would like to study the role of Bitcoin in remittances.
+For this I would like to participate in building bitcoin applications for phones common in developing economies (stupid phones).
+We could study the spread of bitcoin by looking at the downloads of the apps from regions, as well looking at how releasing the app in different languages evolves.
+
+After this the papers follow, in the order listed above. In the end notes I present a brief discussion of my dissertation, as it stands now, a whole.
 
@@
 \chapter{Pensions and Child Growth in South Africa}
-
+\label{south-africa}
 \section*{Abstract}
@@
 \textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
+
 In my understanding of all the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor is the result of the fact that this risk factor eliminates the previously existing uncertainty.
@@
 
-\backmatter
 \chapter{End notes}
+\label{end-notes}
 

### 2013-11-21 draft.tex
change to report, from book
add GI, G to title page
add introduction

@@
-\documentclass[a4paper]{book}\usepackage{graphicx, color}
+\documentclass[a4paper]{report}\usepackage{graphicx, color}
 %% maxwidth is the original width if it is less than linewidth

### 2013-11-21 draft.Rnw
ref intro

@@
 
+\begin{refsection}
+
 \chapter{Introduction}
@@
 \item Replication: Surviving Andersonville
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (MS1998)
+\item Risk and Uncertainty in Unique Equilibria in Currency Attacks
 \item Bitcoin and Remittances: The Potential of Stupid Phones
@@
 
-After this the papers follow, in the order listed above. In the end notes I present a brief discussion of my dissertation, as it stands now, a whole.
+After this the papers follow, in the order listed above. In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
+
+\printbibliography
+\end{refsection}
 

### 2013-11-22 draft.Rnw
end notes, corrections

@@
 \usepackage{graphicx}
+\usepackage{cleveref}
 \usepackage[authordate,backend=biber]{biblatex-chicago}
@@
 \begin{tabular}{rl}
-Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
+Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
 Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
@@
 \tableofcontents
+\listoftables
+\listoffigures
 
 \begin{refsection}
-
 \chapter{Introduction}
@@
 \begin{itemize}
-\item Additional South African Evidence on Pensions and Child Growth
-\item Replication: Surviving Andersonville
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks
-\item Bitcoin and Remittances: The Potential of Stupid Phones
-\item Blacks-Swan and Dragon-King Events in Microeconomics
+\item Additional South African Evidence on Pensions and Child Growth (\ref{south-africa})
+\item Replication: Surviving Andersonville (\ref{andersonville})
+\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\ref{currency})
+\item Bitcoin and Remittances: The Potential of Stupid Phones (\ref{bitcoin})
 \end{itemize}
@@
 
-Together with several other PhD students we have replicated the paper Surviving Andersonville by \textcite{costa2007surviving}.
+Together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
 We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors.
@@
 
-After this the papers follow, in the order listed above. In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
+After this the papers follow, in the order listed above.
+A separate citations section is included for each chapter.
+For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
+In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
+I also mention some very premature ideas.
 
@@
 \begin{refsection}
-
 \chapter{Replication: Surviving Andersonville}
-
-%\author{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}
+\label{andersonville}
+\textbf{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}
+
+\section*{Abstract}
+We replicate \textcite{costa2007surviving}.
+We are able to replicate all the result from the paper.
+The authors make a number of choices in order to arrive to the results published.
+We raise some concerns regarding some of these choices.
+For example, the authors treat the POWs of the two Andersonville camps as if they were in the same camp.
+This inflates size of the POWs social network, which is used as the explanatory variable.
+When we make choices which to us seem more defendable, we cannot, quantitatively and qualitatively, replicate the authors' results.
 
 \section{Summary of the paper}
-\textcite{costa2007surviving} tries to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps.
+\textcite{costa2007surviving} try to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps.
 To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.
@@
 
-\chapter{Morris Shin Currency Attacks}
+\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
+\label{currency}
 \textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
@@
 In my understanding of all the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor is the result of the fact that this risk factor eliminates the previously existing uncertainty.
-In other words, the unique equilibrium is not a surprising result, since knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
-This view is enforced by the fact that the equilibrium is most relevant when the risk factor (epsilon) is minimised, as the authors also state themselve.
-Furthermore, I have doubts about the authors claim that the domain which leads is solved by the equilibrium is in fact the entire 'ripe for attack' domain.
-
+In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
+This view is enforced by the fact that the equilibrium is most pronounced when the risk factor (epsilon) is minimised (i.e.~set equal to zero), as the authors also state themselve.
+Furthermore, I have doubts about the authors claim that the domain which leads is solved by the equilibrium is in fact the entire `ripe for attack' domain.
+
+\nocite{taleb2010black}
 \printbibliography
-
 \end{refsection}
@@
 \begin{refsection}
-
 \chapter{Bitcoin and Remitances}
-In the 2008 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
+\label{bitcoin}
+In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
 This currency (the first of a group called cryptocurrencies) has the following economics features:
@@
 \item fixed amount of units
-\item high granularity (1 Bitcoin can be broken into 100,000,000 Satoshi)
+\item high granularity (1 Bitcoin = 100,000,000 Satoshi)
 \item no or low transaction costs
@@
 
-Bitcoin transactions are conducted by the electronic 'signing' of a transaction.
+Bitcoin transactions are conducted by the electronic `signing' of a transaction.
 This is a very simple electronic process.
@@
 
+\begin{refsection}
 \chapter{End notes}
 \label{end-notes}
+In the previous chapters I have presented my current research projects. These projects are in various stages of completions.
+
+The replication of Surviving Andersonville is already completed in term of replication in Stata.
+We would like to redo the analysis in R \parencite{R}.
+That this can be relevant for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
+The findings of this replication can summarised as:
+
+\begin{quote}
+We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
+It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
+This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.
+\end{quote}
+
+We do not expect to find anything similar to Bell and Miller, but think that it can nevertheless be interesting to replicate findings using a different software package.
+In R we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
+In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
+
+The South-Africa paper, I think, provides an interesting opportunity to exploit the data from the household survey done before and after a highly relevant policy change.
+Especially since the methodology and location are as in \textcite{duflo2000, duflo2003} In addition to this there is now a third data wave which has become available.
+In addition to this, the text of the paper still has to be written.
+
+The discussion of \textcite{morris1998unique} is in a very early stage.
+I have looked at the paper in detail.
+I have also done a brief analysis of my main critique, namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
+However, I would like to present a worked out example which demonstrates how this convolution leads to the main result of the paper.
+In addition to this, this example shoul demonstrate how not the entire `ripe for attack' region is solved for the unique equilibrium.
+
+Relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin.
+I would like to analyse the spread of this.
+I propose to follow the spread of applications for platforms which are popular in developing economies.
+
+I realise that almost of all the previously discussed research projects are some form of a replication of a prior work.
+As replications they are mostly critiques of others' work, rather than constructive idea.
+This is mostly a results of the fact that it is easier to progress when building upon the works of others.
+For this reason, these research projects have progressed more then the projects which are primarily based on my own ideas.
+However, it is my attention to shift the focus of my thesis to include more original work.
+Here I present two more ideas which are to premature to include in the main body of the text, but are based on my own work.
+
+Firstly, I was in charge of setting up a baseline diagnostic into security perceptions in Conakry, Guinea.
+This diagnostic will be used to analyse the impact of a police reform conducted here.
+The reform constitutes of the implementation of a model of `police de proximitee'.
+The baseline consist of 4500 interviews using smartphones in the comune of Conkary as well a large number of interviews in N'Zerekore (east Guinea).
+Some time after the implementation of the police reform as follow up study will be conducted.
+I propose to conduct an impact evaluation using the results from the studies in which I have taken and will take part.
+
+Also, \parencite{taleb2010black, sornette2009dragon}
+
+\printbibliography
+\end{refsection}
 

### 2013-11-22 draft.Rnw
corrections endnotes

@@
 
-I realise that almost of all the previously discussed research projects are some form of a replication of a prior work.
+I realise that almost of all the previously discussed research projects are some form of a replication of prior work.
 As replications they are mostly critiques of others' work, rather than constructive idea.
@@
 
-Also, \parencite{taleb2010black, sornette2009dragon}
+Lastly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy.
+I would like to write one paper about an issue relating to this.
+In particular I would like to at the effect of outliers.
+The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}.
+I would like to see how these principles affect research in development microeconomics.
 

### 2013-11-22 draft.Rnw
finish end notes

@@
 
+In this document I have tried to give a description of my research projects.
+None of these projects are near completion and many are in fact in a very early stage.
+The purpose of this has been to describe the direction I am taking with my thesis, and to receive feedback on this.
+As a result of this being work in progress, the articles are still incomplete, this includes lacking the proper attribution of ideas using citations.
+
 \printbibliography

### 2013-11-22 draft.Rnw
updates aditi's corrections

@@
 \chapter{Introduction}
-In this Preliminary Thesis Defence I present the research projects which I would like to use for my PhD dissertation. These projects are titled:
+In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
 
@@
 \item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\ref{currency})
-\item Bitcoin and Remittances: The Potential of Stupid Phones (\ref{bitcoin})
+\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\ref{bitcoin})
 \end{itemize}
 
-These project are in various stages of completion, though none of them are actually near completion.
-Below I will briefly describe the research idea, the current state, and the potential for each project.
-
-Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}.
-Duflo looks at the effect of the gender of grandparents on the growth metrics of their grandchildren.
+These project are in various stages of completion. Below I will briefly describe the research idea, the current state, and the potential for each project.
+
+Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}.
+These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
 A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
@@
 The survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
-As it stand now I have analysed the data from 2008 and 2012.
-As the 2013 data was released several weeks ago I will incorporate these data as well.
-
-Together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
+As it stands now I have analysed the data from 2008 and 2012.
+The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
+
+Secondly, together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
 We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors.
-However, replicating this numbers required us to take a number of steps and questionable steps in our analysis.
-When we replace these steps with more obvious alternatives, we find that we cannot quantitatively and qualitatively replicate the main results from the paper.
-As an example, we find that the dataset distinguishes between two different POW camps both located in Andersonville, whereas the authors do not.
-This leads to overstated magnitudes of the social ties of POW.
+However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
+When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
+As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
+The authors however, aggregate these two.
+This leads to overstated magnitudes of the social ties of POWs.
 This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
 At this point our replication is quite complete.
-Before rewriting this paper, I will redo the analysis in R (the original and our current replication are in Stata).
-
-\textcite{morris1998unique} claim that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
-It thus solves the previous multiple-equilibrium zone called 'ripe for attack' for a unique equilibrium.
-I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainy.
+Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
+
+Thirdly, \textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
+It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
+I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty.
 We thus gain information.
@@
 
-Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies.
-The transactions are conducted using an electronic process called signing.
+Fourthly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies.
+Bitcoin transactions are conducted using an electronic process called signing.
 I would like to study the role of Bitcoin in remittances.
-For this I would like to participate in building bitcoin applications for phones common in developing economies (stupid phones).
+For this I would like to participate in building Bitcoin applications for the simple type of phones common in developing economies (sometimes referred to stupid phones).
 We could study the spread of bitcoin by looking at the downloads of the apps from regions, as well looking at how releasing the app in different languages evolves.
@@
 In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
-I also mention some very premature ideas.
+I also mention some very preliminary ideas.
 
@@
 This study deviates from the Duflo study in several ways.
-In 2008 and 2012 the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
+In 2008 and 2012, the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
 In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
@@
 
-Another deviation is the usage of \textcite{who2006child} in stead of \textcite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence.
+Another deviation is the usage of WHO z-scores \parencite{who2006child} in stead of CDC z-scores \parencite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence, as long as we use the same standards consistently.
 
@@
 In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \textcite{who2006child}.
+The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \parencite{who2006child}.
 
@@
 This survey collects data on a representative set of appproximately 10,000 South African households.
-The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
-
-For adults several variables measure the different amounts and sources of income.
-Among those, a variable if the adult receives a state pension, and if so, how much.
+The primary information variables that I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
+
+For adults, several variables measure the different amounts and sources of income.
+Among those, a variable for the adult receiving a state pension, and if so, how much.
 This is a numeric variable, the values of which lie very close together.
@@
 
-Children's anthropometrics are taken, these are length/height, weight, and waist.
+The children's anthropometrics taken are, length/height, weight, and waist.
 Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
+Unfortunately, the latest version of wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
 However, I have computed the length-for-age z-scores manually.
 
-In 2006 the WHO published its standards for child growth \parencite{who2006child}.
-These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
+In 2006 the WHO published its standards for child growth.
+These standards are based on the scores of children from different ethnic populations in households which maintained a healthy lifestyle.
 The standards provide the means and standards deviations used.
@@
 \begin{align}
-\label{s1} Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F)\\
-\label{s1b} Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j)
+Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F) \label{s1} \\
+Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j) \label{s1b} 
 \end{align}
 
-where \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
+where equation (3.2) examines quantity and equation (3.3) quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
 
@@
 
-\autoref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.
+\ref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.
 It also presents separately their mean and standard errors for the subsamples of POWs with few (less than 3) and many friends (three or more).
@@
 
-\section{In-text estimation}
+\section*{Appendix: In-text estimation}
 Most in-text estimations are not included in the .do files provided, therefore some of the results to follow do not exactly reproduce the ones published, probably due to differences in specifications.
@@
 
-\section{Non-parametric estimation}
+\section*{Appendix: Non-parametric estimation}
 The following figures are our replications of the Kaplan-Meier survival estimates which show no differences to the original:
@@
 
-In my understanding of all the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor is the result of the fact that this risk factor eliminates the previously existing uncertainty.
+In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor, is the result of the fact that this risk factor eliminates the previously existing uncertainty.
 In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
-This view is enforced by the fact that the equilibrium is most pronounced when the risk factor (epsilon) is minimised (i.e.~set equal to zero), as the authors also state themselve.
-Furthermore, I have doubts about the authors claim that the domain which leads is solved by the equilibrium is in fact the entire `ripe for attack' domain.
+This view is enforced by the fact that the equilibrium is most pronounced when the risk factor (epsilon) is minimised (i.e.~set equal to zero), as the authors state themselves.
+Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium is in fact the entire `ripe for attack' domain.
 
@@
 \begin{refsection}
-\chapter{Bitcoin and Remitances}
+\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
 \label{bitcoin}
 In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
-This currency (the first of a group called cryptocurrencies) has the following economics features:
+This currency -the first of a group called cryptocurrencies- has the following economics features:
 
@@
 An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
-Conflict resolution is done through majority voting by blockchain copy holders.
+Conflict resolution, in this system, is done through majority consensus of blockchain copy holders.
 
@@
 This is a very simple electronic process.
-Currently many smartphone applications are available to this purpose.
-However, in the targeted developing economies, many phones are not smartphones.
-The vast majority using Nokia Operating System.
-These phone can also run applications, of the kind Java Mobile App.
+Currently many smartphone apps are available to this purpose.
+However, in the targeted developing economies, many phones are not smartphones, the vast majority using Nokia Operating System (Nokia OS).
+These phone can also run applications, using the Java Mobile App platform.
 Currently there are no Bitcoin apps available for this platform.
@@
 
-The replication of Surviving Andersonville is already completed in term of replication in Stata.
+I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey done before and after a highly relevant policy change.
+Especially since the methodology and location are the same as in \textcite{duflo2000, duflo2003} In addition to this there is now a third data wave which has become available.
+This provides us with more data, and mostly the opportunity to use more interesting methodology.
+The text of the paper still has to be written.
+
+The replication of Surviving Andersonville is already completed in term of the replication in Stata.
 We would like to redo the analysis in R \parencite{R}.
-That this can be relevant for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
+The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
 The findings of this replication can summarised as:
@@
 \begin{quote}
-We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
+``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
 It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
-This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.
+This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
 \end{quote}
@@
 We do not expect to find anything similar to Bell and Miller, but think that it can nevertheless be interesting to replicate findings using a different software package.
-In R we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
+In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
 In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
 
-The South-Africa paper, I think, provides an interesting opportunity to exploit the data from the household survey done before and after a highly relevant policy change.
-Especially since the methodology and location are as in \textcite{duflo2000, duflo2003} In addition to this there is now a third data wave which has become available.
-In addition to this, the text of the paper still has to be written.
-
 The discussion of \textcite{morris1998unique} is in a very early stage.
-I have looked at the paper in detail.
-I have also done a brief analysis of my main critique, namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
-However, I would like to present a worked out example which demonstrates how this convolution leads to the main result of the paper.
-In addition to this, this example shoul demonstrate how not the entire `ripe for attack' region is solved for the unique equilibrium.
-
-Relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin.
+I have looked at the paper in detail, I have also done a brief analysis of my main critique, namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
+However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
+In addition to this, this example should demonstrate how the entire `ripe for attack' region is not solved for the unique equilibrium.
+
+Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin.
 I would like to analyse the spread of this.
@@
 
-I realise that almost of all the previously discussed research projects are some form of a replication of prior work.
-As replications they are mostly critiques of others' work, rather than constructive idea.
-This is mostly a results of the fact that it is easier to progress when building upon the works of others.
-For this reason, these research projects have progressed more then the projects which are primarily based on my own ideas.
+At this point, three out of four of the previously discussed research projects are some form of a replication of prior work.
+As replications they are mostly critiques of others' work, rather than constructive ideas.
+This is mostly a result of the fact that these projects progress faster.
+For this reason, these research projects have progressed more than the projects which are primarily based on my own ideas.
 However, it is my attention to shift the focus of my thesis to include more original work.
-Here I present two more ideas which are to premature to include in the main body of the text, but are based on my own work.
+Here I present two more ideas which are too preliminary to include in the main body of the text, but are based on my own work.
 
@@
 
-Lastly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy.
+Secondly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy.
 I would like to write one paper about an issue relating to this.

### 2013-11-22 draft.Rnw
fix autoref for equations by removing cleveref
twopage
change defence to defense

@@
-\documentclass[a4paper]{report}
+\documentclass[a4paper,twopage]{report}
 \usepackage{mathtools}
@@
 \usepackage{graphicx}
-\usepackage{cleveref}
 \usepackage[authordate,backend=biber]{biblatex-chicago}
@@
 
-\title{Preliminary Thesis Defence\\~\\
+\title{Preliminary Thesis Defense\\~\\
 \begin{tabular}{rl}
@@
 \chapter{Introduction}
-In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
+In this Preliminary Thesis Defense I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
 
@@
 
-where equation (3.2) examines quantity and equation (3.3) quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
+where equation \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
 

### 2013-12-09 presentationPTD.tex
add presentation, remove old .Rproj

% GRADUATE INSTITUTE, GENEVA
% Bastiaan Quast
% bastiaan.quast@graduateinstitute.ch

\documentclass{beamer}

\mode<presentation>
{
  \usetheme{Berkeley}  
  \setbeamercovered{transparent}
}

\usecolortheme[colortext]{geneva}

\usenavigationsymbolstemplate{}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}

\title[]{Preliminary Thesis Defence}
\subtitle{December 18, 2013}

% Supervisor:&\footnote{Professor of Economics, The Graduate Institute, Geneva; }\\
% Second Reader:&\footnote{Professor of Economics, The Graduate Institute, Geneva; }

\author[Bastiaan Quast]{
  Jean-Louis Arcand\inst{1,4}
    \and
  Ugo Panizza\inst{2,4}
    \and
  \\Bastiaan Quast\inst{3,4}
  }

\institute[The Graduate Institute, Geneva] % (optional, but mostly needed)
{
  \inst{1}
  Professor of Economics,\\
  Supervisor
    \and
  \inst{2}
  Professor of Economics,\\
  Second Reader
    \and
  \inst{3}
  PhD Student,\\
  bastiaan.quast@graduateinstitute.ch
    \and
  \inst{4}
  The Graduate Institute, Geneva
}

\date[18-12-2013]%{December 18, 2013}

\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

\begin{document}

\begin{frame}{PhD Development Economics}
  \titlepage
\end{frame}

\section{Introduction}

\begin{frame}{Introduction}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

\section[Pensions, Child Growth]{Pensions and Child Growth: Additional Evidence from South-Africa}

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa}
using the new data
\end{frame}

\section[Surviving Andersonville]{Replication: Surviving Andersonville}

\begin{frame}{Replication: Surviving Andersonville}
these guys mislabeled everything
\end{frame}

\section[Uncertainty, Currency Attacks]{Uncertainty and Risk in Currency Attacks}

\begin{frame}{Uncertainty and Risk in Currency Attacks}{Knightian Uncertainty in Morris and Shin (1998)}
This paper makes no sense!!
\end{frame}

\section[Bitcoin, Stupid Phones]{Bitcoin and Remittances: Stupid Phone Potential}

\begin{frame}{Bitcoin and Remittances}{Stupid Phone Potential}
stupid phones rock!!
\end{frame}

\section{End Notes}

\begin{frame}{End Notes}
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}

  % The following outlook is optional.
  \vskip0pt plus.5fill
  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}

\end{document}

### 2013-12-09 PTD.tex
rename draft to PTD, remove redundant draft files, accidentally added redundant presentation files

--- 2013-11-22 draft.tex
@@
-\documentclass[a4paper]{report}\usepackage{graphicx, color}
+\documentclass[a4paper,twopage]{report}\usepackage{graphicx, color}
 %% maxwidth is the original width if it is less than linewidth

### 2013-12-14 PTD.tex
clean for resubmission

@@
-\documentclass[a4paper,twopage]{report}\usepackage{graphicx, color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
-\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
-\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
-\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
-\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
-\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
-\newcommand{\hlslot}[1]{\textit{#1}}%
-\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
+\documentclass[a4paper]{report}
+\usepackage{graphicx}
+\usepackage{color}
 \usepackage{mathtools}
@@
 \begin{itemize}
-\item Additional South African Evidence on Pensions and Child Growth (\ref{south-africa})
-\item Replication: Surviving Andersonville (\ref{andersonville})
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\ref{currency})
-\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\ref{bitcoin})
+\item Additional South African Evidence on Pensions and Child Growth (\autoref{south-africa})
+% \item Replication: Surviving Andersonville (\ref{andersonville})
+\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{uncertainty})
+\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{bitcoin})
 \end{itemize}
 
-These project are in various stages of completion. Below I will briefly describe the research idea, the current state, and the potential for each project.
+These project are in various stages of completion.
+Below I will briefly describe the research idea, the current state, and the potential for each project.
 
-Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}.
+Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000child, duflo2003grandmothers}.
 These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
 A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
-This paper makes use of a Household Survey from 2008, 2012 and 2013.
-The survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
+This paper makes use of a Household Survey from 2008, 2012 and 2013. The 
+urvey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
 As it stands now I have analysed the data from 2008 and 2012.
 The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
+I will discuss this in \autoref{south-africa}.
 
-Secondly, together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
-We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors.
-However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
-When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
-As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
-The authors however, aggregate these two.
-This leads to overstated magnitudes of the social ties of POWs.
-This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
-At this point our replication is quite complete.
-Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
+% Furthermore, in \autoref{andersonville},
+% together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
+% We were able to replicate all results from the paper, save for a few decimal numbers,
+% which we have taken to be the result of rounding errors.
 
-Thirdly, \textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
+% However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
+% When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
+% As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
+% The authors however, aggregate these two.
+% This leads to overstated magnitudes of the social ties of POWs.
+% This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
+% At this point our replication is quite complete.
+% Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
+
+\textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
 It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
@@
 I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
+This is done in \autoref{uncertainty}.
 
-Fourthly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies.
+Lastly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
 Bitcoin transactions are conducted using an electronic process called signing.
 I would like to study the role of Bitcoin in remittances.
-For this I would like to participate in building Bitcoin applications for the simple type of phones common in developing economies (sometimes referred to stupid phones).
-We could study the spread of bitcoin by looking at the downloads of the apps from regions, as well looking at how releasing the app in different languages evolves.
+For this I would like to participate in building Bitcoin applications for the type of simple phones common in developing economies (sometimes referred to a stupid phones).
+We could study the spread of bitcoin by looking at the downloads of the apps from regions,
+as well looking at how releasing the app in different languages evolves.
 
@@
 For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
-In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
+In the end notes (\autoref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
 I also mention some very preliminary ideas.
@@
 \section*{Abstract}
-
-In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.
+In this paper I look at differences in child malnutrition levels depending on the gender of the recipient of income.
 
 I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.
+This paper exploits the fact that the data set consists of two surveys,
+which were done before and after the lowering of the pension eligibility age for men to the same age as women.
 
@@
 \section{Introduction}
-
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
-is very similar to \textcite{duflo2000, duflo2003}.
-The deviation from international standards \parencite{who2006child} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status and gender.
+This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa.
+The approach is very similar to \textcite{duflo2000child,duflo2003grandmothers}.
+The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for weight-for-height and length-for-age are computed as z-scores.
+These are then compared for different pension recipient status.
 
@@
 
-The South African pension is a interesting variable to measure income because of its criteria.
+The South African pension is a useful variable to measure income because of its criteria.
 Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias issues.
+Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
 The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
 
-Duflo finds evidence in South Africa's 1993 \href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated Household Survey} that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension.
-This is directly after the significant increase in the pension sum for blacks.
-The pension-eligibility age at this time was 60 for women and 65 for men.
+This study deviates from the Duflo study in several ways.
+First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income, including pension recipient status.
+Whereas Duflo uses age as a proxy for recipient status.
+Secondly, between mid 2008 and the end of 2009 the pension age for men was gradualy lowered to sixty, which is at par with women.
+Another deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child} in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}.
+Since these have superseded the CDC charts, however this should not be of any consequence.
 
-This study deviates from the Duflo study in several ways.
-In 2008 and 2012, the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
-In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
-
-This happened in a few steps.
-As of July 16th 2008 men aged 63 and 64 were eligible for a pension.
-Men aged 61 and 62 became eligible in April 2009.
-Finally in January 2010, pension eligibility age was at 60 for all citizens.
-
-Another deviation is the usage of WHO z-scores \parencite{who2006child} in stead of CDC z-scores \parencite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence, as long as we use the same standards consistently.
-
-The main preliminary result is that the household effect (i.e.~having one or more recipients in the household) is very insignificant in the 2008 estimate.
+The main preliminary result is that the household effect (i.e. having one or more recipients in the household),
+is very insignificant in the 2008 estimate.
 But in the 2012 estimate it is very significant.
@@
 \section{Data}
-
 In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \parencite{who2006child}.
+The first is the South African National Income Dynamics Survey \parencite[NIDS]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.
 
 The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South African households.
-The primary information variables that I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
+This survey collects data on a representative set of appproximately 10,000 South-African households.
+The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
 
-For adults, several variables measure the different amounts and sources of income.
-Among those, a variable for the adult receiving a state pension, and if so, how much.
+For adults several variables measure the different amounts and sources of income.
+Among those, a variable if the adult receives a state pension, and if so, how much.
 This is a numeric variable, the values of which lie very close together.
@@
 
-The children's anthropometrics taken are, length/height, weight, and waist.
+Children's anthropometrics are taken, these are length/height, weight, and waist.
 Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately, the latest version of wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
+Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
 However, I have computed the length-for-age z-scores manually.
 
-In 2006 the WHO published its standards for child growth.
-These standards are based on the scores of children from different ethnic populations in households which maintained a healthy lifestyle.
+In 2006 the WHO published its standards for child growth \parencite{who2006child}.
+These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
 The standards provide the means and standards deviations used. 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1))
-p1 <- p1 + \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman))
-p1 <- p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
-p1
-\end{alltt}
+\section{Analysis}
+\label{analysis}
+I perform three types of analysis.
+The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence) and then compare based on living in the household with an of-pension-eligible adult.
+Secondly, I use my computed z-scores and the data set provided variable which describes the actual pension received (or lack thereof).
+Lastly, I use this state pension variable to evaluate the z-scores provided in the dataset.
 
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 324 rows containing missing values (stat\_smooth).}}
+The first type of analysis is almost identical to Duflo.
+Using an internation set of standard anthropometrics for healthy children between 6 and 60 months old, I standarize observed anthropometrics.
+I then construct a number of dummies of different ages and gender of the pension recipients.
 
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 263 rows containing missing values (stat\_smooth).}}
+In the second analysis, I use the same z-scores I calculated for the Duflo method.
+However, here I use the state pension recipient variable provided by the NIDS data set.
+For simplicity I change the numerical variable to a dummy variable (as the benefits are virtually identical this is without much loss of information).
 
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 51 rows containing missing values (stat\_smooth).}}
+This method uses the pre calculated z-scores from the data set and the state pension dummy.
+Unfortunately the 2012 z-scores are missing except for height-for-age.
+I therefore use only the height-for-age z-scores for the 2012 estimates.
 
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 638 rows containing missing values (geom\_point).}}\end{kframe}
-\includegraphics[width=\maxwidth]{figure/r-p1}
-
-\end{knitrout}
-
-\section{Results}
-
-Basic HAZ (2008)
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(w1_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-## Call:
-## lm(formula = w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + 
-##     w1_best_age_yrs, data = w1_child, subset = w1_c_age_m >= 
-##     6 & w1_c_age_m <= 60)
-## 
-## Residuals:
-##    Min     1Q Median     3Q    Max 
-## -4.779 -1.036 -0.169  0.834  7.060 
-## 
-## Coefficients:
-##                  Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.43e+00   1.44e-01   -9.87   <2e-16 ***
-## w1_spen_w        2.32e-02   1.15e-01    0.20   0.8402    
-## w1_spen_m        1.36e-01   1.72e-01    0.79   0.4281    
-## w1_h_tinc        3.62e-05   9.99e-06    3.62   0.0003 ***
-## w1_best_edu      1.63e-03   7.84e-03    0.21   0.8355    
-## w1_best_age_yrs  7.61e-03   3.64e-03    2.09   0.0369 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.77 on 1436 degrees of freedom
-##   (1936 observations deleted due to missingness)
-## Multiple R-squared:  0.0134,	Adjusted R-squared:  0.00994 
-## F-statistic: 3.89 on 5 and 1436 DF,  p-value: 0.00164
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.835  -0.050   0.000   0.788   7.070 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.172e+00  7.388e-02 -15.861  < 2e-16 ***
-## w1_spen_w        1.748e-02  9.477e-02   0.184   0.8536    
-## w1_spen_m       -1.374e-01  1.444e-01  -0.952   0.3414    
-## w1_h_tinc        2.995e-05  5.606e-06   5.342 9.69e-08 ***
-## w1_best_edu      2.410e-03  3.532e-03   0.682   0.4951    
-## w1_best_age_yrs  4.127e-03  1.863e-03   2.215   0.0268 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4889 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz1)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m_65 + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.836  -0.050   0.000   0.786   7.040 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.173e+00  7.387e-02 -15.880  < 2e-16 ***
-## w1_spen_w        8.576e-03  9.541e-02   0.090   0.9284    
-## w1_spen_m       -9.189e-02  1.348e-01  -0.681   0.4956    
-## w1_h_tinc        2.992e-05  5.605e-06   5.339 9.85e-08 ***
-## w1_best_edu      2.443e-03  3.531e-03   0.692   0.4890    
-## w1_best_age_yrs  4.092e-03  1.860e-03   2.200   0.0278 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4885 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
+In all of these methods the z-scores can be compared on a number of properties.
+Firstly, the status of living in the same household as a state pension recipient or not is the first property to compare.
+Secondly, when living with a recipient,the effects of male and female recipients can be compared.
+Thirdly, the effects based on the gender of the child can be compared.
 
 \printbibliography
-
 \end{refsection}
 
-\begin{refsection}
-\chapter{Replication: Surviving Andersonville}
-\label{andersonville}
-\textbf{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}
-
-\section*{Abstract}
-We replicate \textcite{costa2007surviving}.
-We are able to replicate all the result from the paper.
-The authors make a number of choices in order to arrive to the results published.
-We raise some concerns regarding some of these choices.
-For example, the authors treat the POWs of the two Andersonville camps as if they were in the same camp.
-This inflates size of the POWs social network, which is used as the explanatory variable.
-When we make choices which to us seem more defendable, we cannot, quantitatively and qualitatively, replicate the authors' results.
-
-\section{Summary of the paper}
-\textcite{costa2007surviving} try to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps.
-To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.
-
-The empirical specification for the longitudinal data that measures the effect of the size of the network is as follows:
-
-\begin{equation} \label{eq:ht}
-h(t) = \exp ( \beta_1 F + \beta_2 I + \beta_3 M )
-\end{equation}
-
-where $h$ is hazard at time $t$, $F$ is the number of friends (=social network), $I$ are individual characteristics and $M$ macro camp conditions.
-The number of friends is measured as the number of POWs of the same company and varies by month due to deaths or camp transfers.
-As it might capture the lagged mortality of the group, the authors use as second strategy the initial number of friends as a time-invariant proxy.
-In addition, they instrument for the number of friends using the number of net camp transfers combined with a dummy indicating whether the POW was transferred to account for omitted variables.
-The specification for the Andersonville data in turn is a probit model:
-
-\begin{align}
-Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F) \label{s1} \\
-Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j) \label{s1b} 
-\end{align}
-
-where equation \autoref{s1} examines quantity and \autoref{s1b} quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
-
-The longitudinal data indicates that POWs had special characteristics.
-For instance, they were likely to be volunteers, and from companies with more wounded or dead.
-POWs with more friends were typically US-born and wealthier while Irish and older men had less friends.
-Concerning survival rates, Kaplan-Meier hazard rates show that POWs captured later (after 1963 when the Union and the Confederate Army stopped exchanging POWs) have lower survival rates.
-They also show that survival rates were higher for POWs with 10 or more friends.
-In addition, the rates show that it takes 50 days until there is a divergence in survival between POWs with and without friends.
-The exponential function estimates that an additional friend leads to a 0.98 times lower mortality hazard.
-An increase in the number of friends from 0 to 5 (5 to 10), decreases the predicted probability of death from 0.31 to 0.28 (0.26) while a spline specification provides evidence that the effect is greatest for the first two friends.
-In addition, survival is more likely for POWs that had survived at least one or two months.
-Factors increasing mortality are the number of men in the camp, low rank, high age, and height among others.
-Insignificant variables are for instance wealth and marital status.
-There is no evidence for individual heterogeneity.
-The use of a Weibull specification indicates no duration dependence (toughen up effects).
-Interestingly though, a Cox model gives no significant effect of friends which the authors interpret as a result of their loss of power due to the small sample size.
-Robustness checks, including the IV approach and the effect of friends transferred in, confirms the significant effect of friends.
-Finally, the cross-sectional results provide evidence that having the same last name, being from the same town for smaller towns, ethnic similarity and having a sergeant or a higher rank in one's network are all important factors in raising survival probabilities which in turn shows that the quality of social networks matters.
-
-In summary, Costa and Kahn are able to show that quantity and quality of social networks mattered for survival in civil war POW camps.
-Potential explanations for this are the sharing of scarce resources, moral support and protection from other prisoners.
-
-\section{Data}
-The raw data for the first part of the paper is extracted from the Union Army dataset readily accessible at \url{http://www.cpe.uchicago.edu}.
-This dataset draws information from censuses, medical records and military pension records linking military, socioeconomic and health information for nearly $40,000$ white males that served in the Union Army during the Civil War.
-For the second part, the Andersonville database is available at \url{http://www.itd.nps.gov/cwss} but only as a ``searchable version'', which allows viewing the information for one soldier at a time, and more convenient formats are not readily available.
-
-The datasets provided for the estimations alongside with the publication are already partially processed parts of the raw data available online.
-No clear guidance is given as to what steps were taken to go from the raw data to the files provided, and matching both things proved to be less than straightforward.
-In view of this, we decided to proceed with the replication using the files provided by the authors, pointing out along the way the cases where potential problems in them seemed likely given the raw data we observed.
-Taking those files as starting points, it is possible to reproduce the tables and graphs published in the paper, so in this sense we can say that the data set is complete.
-Originally, some of the data required by the published .do files was not included in the published data files, but the authors provided it promptly upon our request and added it subsequently to the online files of the publishing journal.
-
-The data and .do files provided do not describe or label many of the variables used, nor does the limited variable description in the Appendix cover all of them.
-A very thorough description of the variables in the raw data set can be found at its online source, but the match between this and the variables in the files provided is not straightforward or complete, since some of them are already created by the authors from the raw data.
-The description of the data itself, mainly of the variables that are used most often, is succinct but adequate, with Table 1 and Table 2 presenting some relevant descriptive traits.
-Despite this, some attention should be drawn to the fact that some of the variables have a relevant share of missing values (only the highest number of observations is reported), a point that will be commented in detail later on.
-
-\section{Stata code and interpretation}
-All codes run to their full extent, and produce the estimations presented in the paper, with minor differences that we describe in detail below.
-The codes themselves are not commented at all and include plenty of estimations and specifications not included in the published paper, as well as unexplained data processing steps.
-No exporting commands were set up, or log files kept, which might be the root of some of the rounding and significance discrepancies we have found.
-
-In what follows, all reproduced tables are presented with a comment on the differences found (in bold), whenever there were any.
-
-\subsection{Tables}
-Table 1: This table presents the means of most variables later used for estimation, dividing observations in POWs and NON POWs, to illustrate ex ante differences in observables between them.
-
-\begin{table}[bt]
-\centering
-\caption{Characteristics of Soldiers by POW Status}
-\label{characteristics}
-\begin{tabular}{lllllll}
-\hline
-                           & All   & Obs.  & Never POW & Obs.  & POW   & Obs. \\
-US born                    & 0.745 & 35007 & 0.745     & 31967 & 0.743 & 3040 \\
-US born corrected          & 0.747 & 34941 & 0.745     & 31966 & 0.759 & 2975 \\
-Irish                      & 0.087 & 34941 & 0.086     & 31966 & 0.102 & 2975 \\
-German                     & 0.074 & 34941 & 0.075     & 31966 & 0.062 & 2975 \\
-British                    & 0.039 & 34941 & 0.039     & 31966 & 0.033 & 2975 \\
-Other                      & 0.054 & 34941 & 0.055     & 31966 & 0.043 & 2975 \\
-Artisan                    & 0.2   & 34941 & 0.199     & 31966 & 0.211 & 2975 \\
-Farmer corrected           & 0.505 & 34941 & 0.505     & 31966 & 0.508 & 2975 \\
-Professional or proprietor & 0.075 & 34941 & 0.077     & 31966 & 0.061 & 2975 \\
-Laborer                    & 0.212 & 34941 & 0.212     & 31966 & 0.212 & 2975 \\
-Unknown                    & 0.007 & 34941 & 0.007     & 31966 & 0.008 & 2975 \\
-Enlisted in 1861           & 0.21  & 35007 & 0.205     & 31967 & 0.263 & 3040 \\
-Enlisted in 1861 corrected & 0.21  & 34878 & 0.205     & 31906 & 0.269 & 2972 \\
-Enlisted in 1862                  & 0.344   & 34878 & 0.331   & 31906 & 0.487  & 2972 \\
-Enlisted in 1863                  & 0.068   & 34878 & 0.066   & 31906 & 0.087  & 2972 \\
-Enlisted in 1864                  & 0.256   & 34878 & 0.266   & 31906 & 0.147  & 2972 \\
-Enlisted in 1865                  & 0.122   & 34878 & 0.132   & 31906 & 0.009  & 2972 \\
-Volunteer                         & 0.909   & 34941 & 0.905   & 31966 & 0.951  & 2975 \\
-Height in inches                  & 67.599  & 34941 & 67.589  & 31966 & 67.709 & 2975 \\
-Household property income in 1860 & 534.155 & 13769 & 531.734 & 12509 & 558.2  & 1260 \\
-Company birthplace fragmentation  & 0.642   & 34941 & 0.644   & 31966 & 0.62   & 2975 \\
-Company occupation fragmentation  & 0.559   & 34941 & 0.558   & 31966 & 0.57   & 2975 \\
-Fraction company died as non-POWs & 0.135   & 34941 & 0.131   & 31966 & 0.182  & 2975 \\
-\end{tabular}
-\end{table}
-
-We have added to \autoref{characteristics} the number of observations per variable, not originally included in the paper, in order to highlight the fact that some of them have significant amounts of missing values, something that should be kept in mind later at the estimation stage.
-In this table, the case in point is Household property income in 1860, which is used in most of the specifications proposed, but as will be discussed for later tables, this is a pattern common to all the variables imported from census data.
-Additionally, considering the number of observations for each of the variables leads to the suggestion of a small correction for three of the dummy variables describing categories: US born, farmer and enlisted in 1861.
-The initial data file is missing these variables, which are likely to have been dropped as the basis category for estimation purposes in some other use of the data.
-They were then rebuilt in the .do file from the remaining categories in such a way that generated zeroes for some observations that should have been missing (except for farmer, which is not included at all in the file).
-For example: as provided by the code, US born has $35,007$ observations, whereas other nationality dummies, all built from the same original variable, have $34,941$.
-The correction proposed then, is to set these dummies to missing whenever the other categories of their class are missing, which slightly changes their descriptive statistics (for example the mean of US born goes from $0.745$ to $0.747$ when this correction is implemented).
-
-Remaining discrepancies are minor and could be due to some kind of rounding difference.
-An alternative explanation for these differences is that the table was produced from a slightly different dataset.
-Considering that even the most populous variables present over 500 observations less than the amount declared in the paper, and the fact that one of the variables (farmer) is not included in the data file at all, we consider the second option to be more likely, which would also explain the minor differences in the means of Artisan, British, Height in inches, etc.
-
-A last and minor comment is that the inclusion of the variable volunteer is surprising, since by sample design the Union Army dataset was restricted to white volunteer infantry regiments.
-The inclusion of this variable when comparing POWs and non POWs probably responds to the point raised in the paper about POWs not being representative of all soldiers, for example in ideology (p.1471).
-A variable that reflects that both POWs and non POWs volunteered in similar proportions would suggest homogeneity between POWs and non POWs in this dimension and, hence, increase  external validity.
-The similarities observed in Table 1 between POWs and non POWs in their mean of volunteer do not reflect that, since they are both close to one by construction.
-Any individuals not listed as volunteers, either correspond to the very few drafted men, or are actually soldiers that re-enlisted as commissioned officers, but were originally volunteers, as explained in the codebooks for the source data.
-
-\ref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.
-It also presents separately their mean and standard errors for the subsamples of POWs with few (less than 3) and many friends (three or more).
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity}
-\label{friends}
-\begin{tabular}{llllllllll}
-
-                                  & \multicolumn{3}{l}{All} & \multicolumn{3}{l}{Few friends ($<3$)} & \multicolumn{3}{l}{Many friends ($>=3$)} \\
-                                  & Mean                    & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-\\
-US born                           & 0.731                   & 0.444                                & 1976                                   & 0.708 & 0.455 & 990 & 0.754 & 0.431 & 986 \\
-Irish                             & 0.12                    & 0.325                                & 1976                                   & 0.115 & 0.319 & 990 & 0.125 & 0.331 & 986 \\
-German                            & 0.063                   & 0.243                                & 1976                                   & 0.081 & 0.273 & 990 & 0.045 & 0.207 & 986 \\
-British                           & 0.034                   & 0.182                                & 1976                                   & 0.042 & 0.202 & 990 & 0.026 & 0.16 & 986 \\
-Other                             & 0.05                    & 0.217                                & 1976                                   & 0.053 & 0.223 & 990 & 0.047 & 0.211 & 986 \\
-Artisan                           & 0.209                   & 0.407                                & 1976                                   & 0.214 & 0.41 & 990 & 0.204 & 0.403 & 986 \\
-Farmer                            & 0.421                   & 0.494                                & 1976                                   & 0.44 & 0.497 & 990 & 0.401 & 0.49 & 986 \\
-Professional or propietor         & 0.07                    & 0.256                                & 1976                                   & 0.077 & 0.266 & 990 & 0.064 & 0.245 & 986 \\
-Laborer                           & 0.266                   & 0.442                                & 1976                                   & 0.243 & 0.429 & 990 & 0.288 & 0.453 & 986 \\
-Unknown                           & 0.034                   & 0.182                                & 1976                                   & 0.025 & 0.157 & 990 & 0.044 & 0.204 & 986 \\
-Enlisted in big city              & 0.475                   & 0.5                                  & 1976                                   & 0.493 & 0.5 & 990 & 0.457 & 0.498 & 986 \\
-Household property income in 1860 & 576.475                 & 1855.699                             & 817                                    & 483.609 & 1084.987 & 391 & 661.711 & 2348.676 & 426 \\
-Age when captured                 & 25.96                   & 7.056                                & 1966                                   & 26.645 & 7.415 & 990 & 25.265 & 6.604 & 976 \\
-Height when captured                 & 171.576 & 6.612 & 1925 & 171.79 & 6.384 & 974 & 171.356 & 6.833 & 951 \\
-Commisoned or noncommisoned officer  & 0.076   & 0.266 & 1976 & 0.083  & 0.276 & 990 & 0.07    & 0.255 & 986 \\
-Married in 1860                      & 0.257   & 0.437 & 817  & 0.276  & 0.448 & 391 & 0.239   & 0.427 & 426 \\
-Wounded 10 days before capture       & 0.118   & 0.323 & 1976 & 0.148  & 0.356 & 990 & 0.088   & 0.284 & 986 \\
-Fraction company dead before capture & 0.089   & 0.064 & 1976 & 0.093  & 0.07  & 990 & 0.085   & 0.057 & 986 \\
-Company birthplace fragmentation     & 0.542   & 0.2   & 1923 & 0.547  & 0.193 & 985 & 0.536   & 0.206 & 938 \\
-Company occupational fragmentation   & 0.596   & 0.173 & 1923 & 0.586  & 0.173 & 985 & 0.607   & 0.172 & 938 \\
-\end{tabular}
-\end{sidewaystable}
-
-This table is almost exactly reproduced, except for the minor differences set in bold, which appear to be rounding differences (and a typo in the case of Laborer).
-The number of observations stated on the table in the paper (1923) corresponds to the last variable in this case as well, even though, as mentioned for the previous table, it is relevant to keep in mind that some of the other variables of interest show a considerably lower count of observations, as can be seen in the added columns.
-For this table, this is the case of variables Married in 1860 and Household property income in 1860, which are both variables from the 1860 census.
-The main concern regarding this table is the process of organizing the data, particularly one step in which a merge to the file ``transfer.dta'' is conducted.
-This file contains the prisoner identifier variable, month, year, and a dummy variable reflecting whether the prisoner was transferred (transferin).
-This variable is not needed for \autoref{friends}, and we can only speculate that it was incorporated, as some other steps were, in an attempt to exactly reproduce the dataset used in \autoref{corrected}.
-The problem in this case is that the file ``transfer.dta'' contains duplicate observations, which in turn duplicates observations in the main data set via the merge, artificially inflating the number of observations in the data used for \autoref{friends}\footnote{Duplicate observations per month-year-prisoner are natural in the context of \autoref{corrected}, because in there capture time is measured per fortnight.
-Including additional observations because of this in a stage of data description such as this one is hardly appropriate.}.
-
-If these duplicate observations are eliminated from the ``transfer.dta'' file before the merge, the statistics presented do not seem to defer significantly, and certainly neither do the conclusions drawn from them, but the number of observations in the subsample considered is significantly lower.
-This exercise is presented in the table below.
-
-\begin{sidewaystable}
-\centering
-\caption{corrected}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{corrected}
-\begin{tabular}{llllllllll}
-\hline
-                                  & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. \\
-US born                           & 0.732   & 0.443     & 1470     & 0.715   & 0.452     & 727      & 0.748   & 0.434     & 743      \\
-Irish                             & 0.122   & 0.327     & 1470     & 0.113   & 0.317     & 727      & 0.131   & 0.337     & 743      \\
-German                            & 0.06    & 0.237     & 1470     & 0.074   & 0.262     & 727      & 0.046   & 0.209     & 743      \\
-British                           & 0.034   & 0.181     & 1470     & 0.04    & 0.196     & 727      & 0.028   & 0.166     & 743      \\
-Other                             & 0.05    & 0.219     & 1470     & 0.056   & 0.231     & 727      & 0.044   & 0.206     & 743      \\
-Artisan                           & 0.212   & 0.409     & 1470     & 0.217   & 0.413     & 727      & 0.207   & 0.406     & 743      \\
-Farmer                            & 0.427   & 0.495     & 1470     & 0.442   & 0.497     & 727      & 0.413   & 0.493     & 743      \\
-Professional or proprietor        & 0.065   & 0.247     & 1470     & 0.073   & 0.26      & 727      & 0.058   & 0.234     & 743      \\
-Laborer                           & 0.265   & 0.441     & 1470     & 0.242   & 0.429     & 727      & 0.287   & 0.453     & 743      \\
-Unknown                           & 0.031   & 0.172     & 1470     & 0.026   & 0.16      & 727      & 0.035   & 0.184     & 743      \\
-Enlisted in big city              & 0.48    & 0.5       & 1470     & 0.486   & 0.5       & 727      & 0.475   & 0.5       & 743      \\
-Household property income in 1860 & 547.314 & 1637.903  & 615      & 476.274 & 1107.659  & 299      & 614.532 & 2014.738  & 316      \\
-Age when captured                 & 25.834  & 6.931     & 1465     & 26.4    & 7.263     & 727      & 25.276  & 6.544     & 738      \\
-Height when captured              & 171.526 & 6.624     & 1439     & 171.683 & 6.433     & 717      & 171.37  & 6.81      & 722      \\
-Commisioned or noncommisioned officer\footnote{Related to the point about the variable Volunteer made before, the name Commisioned or non commissioned officer may be misleading, since commissioned officers are excluded from the sample by construction.} & 0.074 & 0.262 & 1470 & 0.078 & 0.269 & 727 & 0.07  & 0.255 & 743 \\
-Married in 1860                       & 0.252 & 0.435 & 615  & 0.264 & 0.442 & 299 & 0.241 & 0.428 & 316 \\
-Wounded 10 days before capture        & 0.125 & 0.331 & 1470 & 0.155 & 0.363 & 727 & 0.096 & 0.294 & 743 \\
-Fraction company dead before capture  & 0.091 & 0.063 & 1470 & 0.094 & 0.069 & 727 & 0.089 & 0.056 & 743 \\
-Company birthplace fragmentation      & 0.542 & 0.198 & 1442 & 0.55  & 0.189 & 723 & 0.534 & 0.207 & 719 \\
-Company occupational fragmentation    & 0.593 & 0.175 & 1442 & 0.585 & 0.173 & 723 & 0.601 & 0.178 & 719 \\
-\end{tabular}
-\end{sidewaystable}
-
-Two additional remarks related to this are: a) whenever month was larger than 12, it is set to missing, b) all observations marked as having occurred in 1861 are shifted to 1862.
-Neither month nor year are directly used for this table, but they are the matching points for the merge to the ``transfer.dta'' file discussed above.
-The file “transfer.dta” also contains month>12 and observations for 1861, and they are not replaced in a similar fashion, introducing some additional artificial matching problems into the merge operation.3 Besides the potential distortions in the merge that these asymmetric replacements may cause, the switch of 1861 to 1862 seems particularly surprising given that no explanation for it is offered.
-
-Additionally, if the aim of this table is to have a general impression of the variables used in the main regressions (\autoref{corrected}), the same observations should have been considered in both accounts.
-This is not the case, since the observations with an unknown number of friends are dropped for this table, but not for the next one.
-
-\autoref{corrected}: This table shows the results of the hazard rate analysis using a set of covariates described in the previous tables and alternating two measures of friends: number of friends at the time of the observation and initial number of friends.
-
-\begin{sidewaystable}
-\caption{Social Networks and Individual Characteristics on Mortality}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{social}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{specification I} & \multicolumn{2}{l}{specification II} & \multicolumn{2}{l}{specification III} \\
-VARIABLES                                & Hazard rate                         & Std. err.                            & Hazard rate                           & Std. err. & Hazard rate & Std. err. \\
-Current number of friends                & 0.983                               & -0.008                               & 0.977++                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                      &                                       &  & 0.976++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                      & 1.536++                               & -0.14 & 1.521++ & -0.139 \\
-Fraction of company dying before capture & 1.091                               & -0.782                               & 0.892                                 & -0.636 & 0.63 & -0.449 \\
-Professional or proprietor               & 0.567                               & -0.146                               & 0.563                                 & -0.143 & 0.556 & -0.141 \\
-Artisan                                  & 0.944                               & -0.119                               & 0.947                                 & -0.119 & 0.937 & -0.117 \\
-Laborer                                  & 1.298                               & -0.154                               & 1.295                                 & -0.152 & 1.287 & -0.152 \\
-German                                   & 1.197                               & -0.215                               & 1.166                                 & -0.209 & 1.149 & -0.206 \\
-Irish                                    & 0.768*                              & -0.121                               & 0.762*                                & -0.118 & 0.750* & -0.117 \\
-British                       & 0.641*    & -0.171 & 0.654     & -0.174 & 0.656    & -0.177 \\
-Other                         & 0.658*    & -0.154 & 0.645*    & -0.153 & 0.642*   & -0.151 \\
-Sergeant, corporal or officer & 0.549++   & -0.115 & 0.543++   & -0.111 & 0.541++  & -0.111 \\
-Age at captivity              & 1.045++   & -0.007 & 1.044++   & -0.007 & 1.044++  & -0.007 \\
-Height at enlistment          & 1.01      & -0.007 & 1.01      & -0.007 & 1.011    & -0.007 \\
-Observations                  & 23256     &        & 23256     &        & 23256    &        \\
-Number of subjects            & 3026      &        & 3026      &        & 3026     &        \\
-Log pseudo likelihood         & -1324.607 &        & -1308.229 &        & -1307.17 &        \\
-\end{tabular}
-\end{sidewaystable}
-
-\autoref{corrected} is reproduced almost completely, except for the results in bold, for which the significance level differs from the one presented in the publication.
-
-In this case, month larger than 12 is replaced by 99, and in this case as well this might generate distortions since an equivalent change was not performed in the file to which this is merged (``Died.dta'').
-The observations for which the number of friends is unknown are not dropped here, but set to zero.
-Whenever the number of deaths in the prisoners' company before capture is unknown, it is set to zero.
-Whenever the number of men in camp is unknown it is set to 40.
-Whenever the variables imported from the 1860 census are missing (i.e.
-there was no match to the census) they are still included in the regression by setting their value to zero in the case of dummy variables (married and illiterate), and by taking log(1+variable) in the case of Household property.
-In all of these cases, dummy variables are included in the regression indicating whether the data is actually missing (e.g.
-a dummy variable that takes value one if the observation was not matched to the 1860 census, link60).
-It is understandable that in order to maintain a healthy sample size, and to use as much of the information as possible, some assumptions are made, but the trade off related to this point is that these assumptions may create artificial noise in the data that would not be fully captured by these control dummies.
-
-\autoref{social}: This table presents an alternative estimation strategy.
-As a benchmark, the effect of the number of friends in the camp is estimated including company fixed effects and the same covariates as before.
-To avoid endogeneity issues that may arise due to the potential correlation between the current number of friends and the prisoner’s own unobservable health (via its correlation to the lagged mortality of the group), an IV-hazard rate strategy is pursued next.
-The instruments chosen are the new number of friends the prisoner has in each period (the newly captured soldiers of his company) and a dummy variable that reflects whether the POW was transferred.
-Both variables clearly affect the number of friends a POW has, and are meant to be uncorrelated with his unobservable health, since transfers and the amount of newly captured men assigned to each camp were determined by camp needs or evolution of war events5.
-In the first stage, the number of friends is regressed on the instruments, as well as the whole set of covariates and fixed effects.
-The predicted residuals of this first stage are then included in the second stage, along with all covariates, fixed effects and the number of friends.
-This procedure is repeated 100 times, preserving the coefficients and standard errors of the number of friends, the number of men in the camp and the residuals, as well as the R-squared of the first stage.
-The final result of this Montecarlo procedure is obtained by computing the mean of those variables among the 100 repetitions.
-
-\begin{sidewaystable}
-\caption{Effect of Social Networks on Mortality, with Company Fixed Effects and Instrumented}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effect}
-\begin{tabular}{lllll}
-\hline
-                                    & \multicolumn{2}{l}{Original} & \multicolumn{2}{l}{IV} \\
-                                    & Haz. Rate                    & Std. Err.              & Haz. Rate & Std. Err. \\
-Number of friends                   & 0.978*                       & -0.012                 & 0.895 & -0.055 \\
-Ln(total number of men in the camp) & 1.437++                      & -0.122                 & 1.537 & -0.196 \\
-Residual                            &                              &                        & 1.06 & -0.071 \\
-\end{tabular}
-\end{sidewaystable}
-
-Here, the results are replicated entirely.
-
-A concern raised is that it is not clear how the variable that reflects transfers was constructed, since this information is not directly provided in the raw data available online.
-In some cases, the variable that reflects the camp contains multiple entries per individual, and we can only assume that those were used to infer that the POW was transferred between those camps.
-This is most likely an accurate interpretation of the data, the only problem being that there is no information about the date of transfer, which makes the instrument weaker.
-
-In the following section, the authors use The National Park Service's cross-sectional data of the population of Andersonville and estimate probit models of the probability of survival on the number of friends and various demographic characteristics as described in the summary.
-
-\autoref{effect}: This table estimates the effect of social networks on probability of survival controlling for a large of variables that measure existing networks outside of the company.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectsocial}
-\begin{tabular}{lllllll}
-\hline
-                                                              &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                              & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment÷10                                  & 9.157   & 0.004++ &         &         &                                     &  \\
-                                                              & -10.358 & -0.001  &         &         &                                     &  \\
-Number of men in company                                      & 12.899  &         & 0.003++ & 0.002++ & 0.003++                             & 0.002++ \\
-                                                              & -15.39  &         & -0.001  & -0.001  & -0.001                              & -0.001 \\
-Fraction of company with              rank sergeant or higher & 0.073   & 0.120++ & 0.128++ & 0.079   & 0.152                               & 0.085 \\
-                                                              &         & -0.034  & -0.034  & -0.032  & -0.061                              & -0.056 \\
-Number of men with same last name in regiment                 & 1.19    & 0.033++ & 0.033++ & 0.036++ & 0.018*                              & 0.023++ \\
-                                                              & -0.599  & -0.007  & -0.007  & -0.006  & -0.009                              & -0.009 \\
-Log(number of men in camp from same town)                     & 5.101   & -0.003  & -0.002  & 0       & 0.018*                              & 0.026++ \\
-                                                              & -1.994  & -0.005  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-Dummy=1 if town population<9552                               & 0.423   & 0.037+  & 0.034+  & 0.032+  &                                     &  \\
-                                                              &         & -0.014  & -0.014  & -0.013  &                                     &  \\
-Private                                                       & 0.824   &         &         &         &                                     &  \\
-Officer             & 0.003 & 0.347++ & 0.347++ & 0.354++ & 0.311++ & 0.328++ \\
-                    &       & -0.027  & -0.027  & -0.021  & -0.038  & -0.025  \\
-Sergeant            & 0.068 & 0.080++ & 0.080++ & 0.083++ & 0.084++ & 0.088++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Other rank          & 0.01  & 0.028   & 0.034   & 0.03    & 0.067   & 0.046   \\
-                    &       & -0.03   & -0.03   & -0.03   & -0.049  & -0.05   \\
-Corporal            & 0.078 & 0.055++ & 0.055++ & 0.046++ & 0.064++ & 0.054++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Irish surname       & 0.023 & 0.02    & 0.022   & 0.017   & 0.069   & 0.059*  \\
-                    &       & -0.019  & -0.019  & -0.019  & -0.03   & -0.03   \\
-German surname      & 0.043 & -0.009  & -0.009  & -0.016  & -0.001  & -0.025  \\
-                    &       & -0.015  & -0.015  & -0.015  & -0.024  & -0.025  \\
-French surname      & 0.028 & 0.028   & 0.028*  & 0.028   & 0.033   & 0.032   \\
-                    &       & -0.017  & -0.017  & -0.017  & -0.027  & -0.028  \\
-Continental surname & 0.029 & 0.006   & 0.007   & -0.004  & -0.021  & -0.029  \\
-                    &       & -0.018  & -0.018  & -0.018  & -0.032  & -0.032  \\
-State fixed effects? &       & N     & N     & Y     & N     & Y     \\
-Pseudo R2            &       & 0.043 & 0.044 & 0.087 & 0.048 & 0.115 \\
-Observations         & 31336 & 31336 & 31336 & 31330 & 12002 & 12002 \\
-\end{tabular}
-\end{sidewaystable}
-
-All figures on the table are replicated perfectly.
-However, the coefficients in bold are estimated with different significance levels (even though the coefficients and their standard errors are the same).
-For example, we find that the coefficient on Dummy=1 if town population $<9,552$ is significant at the 5 percent level whereas the table in the original paper indicates that it is significant at the 1 percent level in specifications 1, 2, and 3.
-It is important to note that the difference is not always in the same direction.
-For instance, we find that the coefficient on French surname in specification 2 is significant at the 10 percent level whereas the original table does not show any significance.
-Thus, we suspect that this discrepancy might be due to rounding error.
-
-\autoref{effectsocial}: Here, the authors estimate the same equation in logs and include the two outlier companies that were excluded in Table 5 to show the resulting nonlinearity.
-In the .do file, the outliers are dropped early on and thus their estimations never include these outliers.
-We save the dataset with the outliers at an early stage so that we can include them in the estimation.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectLog}
-\begin{tabular}{lllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.014++ &         &         &                                     &  \\
-                                                   & -1.29  & -0.005  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.021++ & 0.012   & 0.029                               & 0.022 \\
-                                                   & -1.18  &         & -0.007  & -0.006  & -0.012                              & -0.009 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.134++ & 0.134++ & 0.08    & 0.153                               & 0.084 \\
-                                                   & -0.127 & -0.034  & -0.034  & -0.032  & -0.061                              & -0.057 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.101++ & 0.095++ & 0.096++ & 0.061++                             & 0.063++ \\
-                                                   & -0.305 & -0.012  & -0.012  & -0.011  & -0.018                              & -0.017 \\
-Log(number of men in camp from same town)          & 5.114  & -0.004  & 0       & 0.002   & 0.024                               & 0.030++ \\
-                                                   & -1.991 & -0.004  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.114 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002                               & 12002 \\
-                                                   &        &         &         &         &                                     &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The first thing to notice is that the number of observations is different.
-The original paper shows a total of 31,678 observations for the first three specifications, and a total of 12,025 observations for specifications 4 and 5.
-We have less number of observations mostly due to the 83 observations with missing Fraction of company with rank sergeant or higher variable.
-We don’t know how the authors included these observations in their estimation.
-A minor difference in the first descriptive column is the mean for Log(number of men with same last name in regiment), which is $0.113$ in the paper paper and $0.112$ in our data.
-
-All the coefficients in bold are slightly different from the original table; some are different only in their magnitude but some are also different in their level of significance.
-For example, the coefficient on Log(number of men in regiment) in specification 1 is $0.011$ with $5\%$ significance level in the paper, whereas we find a higher and more significant effect.
-Despite these quantitative differences, the results are not qualitatively different.
-
-\autoref{effectLog}: Here, the authors estimate the effect of ethnic networks on probability of survival to show that the quality of the network matters.
-
-\begin{sidewaystable}
-\caption{Effect of ethnic network on probability of survival}\footnote{Company clustered standard errors.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethnic}
-\begin{tabular}{lllllll}
-\hline
-
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.003*                    & 0.002                      & 0.003                      & 0.001 & 0.002 & 0.002 \\
-Number of men of own ethnicity in company & 0.03                      & 0.036                      & 0.03                       & 0.013 & 0.019 & 0.026 \\
-Dummy = 1 if Private                      & -0.046                    & 0.049                      & -0.078+                    & 0.037 & -0.093+ & 0.043 \\
-From small town                           & 0.1                       & 0.04                       & 0.036                      & 0.031 & 0.054 & 0.036 \\
-Captured 1864 or 1865                     & 0.239++                   & 0.077                      & 0.282++                    & 0.049 & 0.388++ & 0.058 \\
-Pseudo R2                                 & 0.036                     &                            & 0.059                      &  & 0.058 &  \\
-Joint significance test                   & 8.6                       &                            & 22.01                      &  & 3.2 &  \\
-Observations                              & 735                       &                            & 1355                       &  & 869 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The bold coefficients in \autoref{effectLog} are different in significance levels than what the authors report in their original table (all coefficients and standard errors are the same).
-The most striking one is the Captured 1864 or 1865 variable for French POWs where the authors find no significance at all and we find significance at the 1 percent level.
-Since this is too large of a difference to be a rounding error, we suspect that it is a typo.
-
-\subsection{Robustness check - Logit instead of Probit}
-
-As a robustness check, we estimate tables 5-7 with logit instead of probit and results are qualitatively similar.
-Bold coefficients below show differing levels of significance (only 1-level) when compared to probit.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logit}\footnote{There is no explanation in the paper as to why probit was preferred to logit.}
-\label{logit}
-\begin{tabular}{lllllll}
-\hline
-                                                 &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                 & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment ÷10                    & 9.157   & 0.018++ &         &         &                                     &  \\
-                                                 & -10.358 & -0.003  &         &         &                                     &  \\
-Number of men in company                         & 12.899  &         & 0.013++ & 0.009++ & 0.014++                             & 0.010++ \\
-                                                 & -15.39  &         & -0.003  & -0.002  & -0.004                              & -0.003 \\
-Fraction of company with rank sergeant or higher & 0.073   & 0.495++ & 0.526++ & 0.336   & 0.647                               & 0.387 \\
-                                                 &         & -0.145  & -0.144  & -0.139  & -0.266                              & -0.251 \\
-Number of men with same last name in regiment    & 1.19    & 0.149++ & 0.147++ & 0.158++ & 0.081*                              & 0.101++ \\
-                                                 & -0.599  & -0.03   & -0.03   & -0.028  & -0.042                              & -0.038 \\
-Log(number of men in camp from same town)        & 5.101   & -0.012  & -0.01   & 0       & 0.075                               & 0.114++ \\
-                                                 & -1.994  & -0.019  & -0.019  & -0.019  & -0.038                              & -0.034 \\
-Dummy=1 if town population<9552                  & 0.423   & 0.154   & 0.145   & 0.133   &                                     &  \\
-                                                 &         & -0.06   & -0.056  & -0.054  &                                     &  \\
-Private                                          & 0.824   &         &         &         &                                     &  \\
-Officer & 0.003 & 2.342++ & 2.339++ & 2.481++ & 2.043++ & 2.342++ \\
-        &       & -0.454  & -0.455  & -0.426  & -0.562  & -0.502  \\
-Sergeant             & 0.068 & 0.344++ & 0.344++ & 0.367++ & 0.377++ & 0.407++ \\
-                     &       & -0.05   & -0.05   & -0.053  & -0.081  & -0.087  \\
-Other rank           & 0.01  & 0.109   & 0.135   & 0.12    & 0.295   & 0.2     \\
-                     &       & -0.128  & -0.128  & -0.132  & -0.232  & -0.231  \\
-Corporal             & 0.078 & 0.236++ & 0.235++ & 0.201++ & 0.283++ & 0.244++ \\
-                     &       & -0.046  & -0.046  & -0.048  & -0.077  & -0.084  \\
-Irish surname        & 0.023 & 0.086   & 0.095   & 0.072   & 0.31    & 0.264*  \\
-                     &       & -0.081  & -0.081  & -0.082  & -0.14   & -0.146  \\
-German surname       & 0.043 & -0.039  & -0.036  & -0.07   & -0.003  & -0.111  \\
-                     &       & -0.061  & -0.06   & -0.061  & -0.103  & -0.106  \\
-French surname       & 0.028 & 0.113   & 0.117   & 0.119   & 0.14    & 0.152   \\
-                     &       & -0.073  & -0.073  & -0.075  & -0.12   & -0.127  \\
-Continental surname  & 0.029 & 0.026   & 0.031   & -0.015  & -0.093  & -0.126  \\
-                     &       & -0.075  & -0.075  & -0.076  & -0.134  & -0.135  \\
-State fixed effects? &       & N       & N       & Y       & N       & Y       \\
-Pseudo R2            &       & 0.043   & 0.044   & 0.086   & 0.047   & 0.114   \\
-Observations         & 31336 & 31336   & 31336   & 31330   & 12002   & 12002   \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form, logit}\footnote{Company clustered standard errors are in parentheses.
-The number of observations for the Fraction of company with rank sergeant or higher variable in the first column is 31605.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{logLogit}
-\begin{tabular}{llllllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.057   &         &         &                                     &  \\
-                                                   & -1.29  & -0.022  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.088++ & 0.047   & 0.124                               & 0.085 \\
-                                                   & -1.18  &         & -0.028  & -0.024  & -0.051                              & -0.04 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.559++ & 0.552++ & 0.342   & 0.652                               & 0.383 \\
-                                                   & -0.127 & -0.147  & -0.145  & -0.139  & -0.266                              & -0.251 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.438++ & 0.409++ & 0.416++ & 0.267++                             & 0.277++ \\
-                                                   & -0.305 & -0.052  & -0.052  & -0.049  & -0.078                              & -0.074 \\
-Log(number of men in camp from same town)          & 5.114  & -0.018  & 0       & 0.006   & 0.100++                             & 0.131++ \\
-                                                   & -1.991 & -0.018  & -0.019  & -0.019  & -0.039                              & -0.036 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.113 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002 
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of ethnic networks on probability of survival, logit}\footnote{Standard errors are clustered on the company.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethLogit}
-\begin{tabular}{lllllll}
-\hline
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.009                     & 0.007                      & 0.011*                     & 0.006 & -0.001 & 0.007 \\
-Number of men of own ethnicity in company & 0.011                     & 0.11                       & 0.139                      & 0.06 & 0.154 & 0.116 \\
-Dummy =1 if Private                       & -0.228                    & 0.214                      & -0.337+                    & 0.162 & -0.445+ & 0.2 \\
-From small town                           & 0.417                     & 0.173                      & 0.154                      & 0.131 & 0.23 & 0.154 \\
-Captured 1864 or 1865                     & 1.082++                   & 0.347                      & 1.223++                    & 0.227 & 1.826++ & 0.307 \\
-Pseudo R2                                 & 0.032                     &                            & 0.058                      &  & 0.055 &  \\
-Joint significance test                   & 3.81                      &                            & 18.22                      &  & 2.16 &  \\
-Observations                              & 752                       &                            & 1357                       &  & 874 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\section{Conclusion}
-To sum up our replication, our key message is that while we do find small differences between our results and the published results of \textcite{costa2007surviving}, we find no evidence that would call their conclusions into question, either qualitatively or quantitatively.
-
-Furthermore, the interpretation of the results seems convincing to us.
-While they cannot test for how friends ensured survival the mentioned explanations from the supply of food to moral support are very comprehensible.
-In addition, their study is clearly and quite literally made for survival analysis so we do not see space to improve upon the results by applying a different estimation technique.
-\textcite{costa2007surviving} also apply a wide set of survival analysis tools (e.g.
-from non-parametric to parametric estimation) so we did not come up with many ideas for robustifying their paper in this direction.
-Potential future extensions could build on the use of different data sets.
-A weakness of the paper is clearly that external validity is limited because the authors look at a civil war of the 19th century.
-For instance, looking at World War I or II data could prove to be fruitful and lead to further insight.
-While we tried to start with such an extension, we were not able to find a sufficient dataset within this period of time.
-
-To come back to the differences between our replication and the original paper, we consider the most relevant issue the difference in significance levels.
-Interestingly, when looking into this matter in more detail we find that in almost all cases the p-values are at the margin which clearly points in the direction of a rounding error.
-We can only speculate that given the lack of exporting commands the reason for this is a certain degree of carelessness and, therefore, would like to emphasize the need of these very exporting commands.
-Nevertheless, and as mentioned before, the differences do not affect the general message of the paper.
-
-%\appendix
-
-\section*{Appendix: In-text estimation}
-Most in-text estimations are not included in the .do files provided, therefore some of the results to follow do not exactly reproduce the ones published, probably due to differences in specifications.
-They can nonetheless generally be replicated in terms of signs and significance.
-
-\paragraph{Probit statement}
-page 1474, line 21 ``When we run a Probit, in which the dependent variable is POW status and the independent variables are economic and geographic characteristics and the number of men in the company who were ever wounded or who ever died, we find that these two company characteristics were the main predictors of POW status.
-The derivative on the number of men in the company who were ever wounded or who ever died, was $0.257$ (robust $= 0.257$) and the derivative on the number of men who were ever wounded was $0.139$ (robust $= 0.042$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of POW Status}
-\begin{tabular}{lll}
-\hline
-                          & Marginal Effect & Marginal Effect \\
-\% in comp who died        & 0.359***        & 0.430***        \\
-                          & -0.021          & -0.0331         \\
-\% in comp who wounded     & 0.123***        & 0.140***        \\
-                          & -0.0136         & -0.022          \\
-Includes property in 1860 & No              & Yes             \\
-Observations              & 34878           & 13754           \\
-\end{tabular}
-\end{table}
-
-\paragraph{Comment on late capture}
-page 1474, line 77 ``We also found no evidence of group surrender to become a POW - men who were captured in 1864 and 1865 had more friends, even though a group who surrendered during these years would have no hope of a quick exchange.''
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity and Late or Early Capture}
-\begin{tabular}{lllllllll}
-\hline
-                     & \multicolumn{4}{c}{Early capture} & \multicolumn{4}{c}{Late capture} \\
-                     & \multicolumn{2}{c}{$< 3$}           & \multicolumn{2}{c}{$>= 3$}         & \multicolumn{2}{c}{$< 3$} & \multicolumn{2}{c}{$>= 3$} \\
-                     & Mean                              & Std. err.                        & Mean & Std. err. & Mean & Std. err. & Mean & Std. err. \\
-US born              & 0.706                             & 0.456                            & 0.77 & 0.421 & 0.709 & 0.455 & 0.738 & 0.44 \\
-Irish                & 0.082                             & 0.275                            & 0.109 & 0.311 & 0.136 & 0.343 & 0.14 & 0.347 \\
-German               & 0.108                             & 0.311                            & 0.046 & 0.21 & 0.064 & 0.244 & 0.043 & 0.204 \\
-British              & 0.053                             & 0.224                            & 0.021 & 0.143 & 0.036 & 0.186 & 0.032 & 0.175 \\
-Other                & 0.048                             & 0.213                            & 0.046 & 0.21 & 0.056 & 0.229 & 0.047 & 0.213 \\
-Artisan              & 0.233                             & 0.423                            & 0.2 & 0.401 & 0.203 & 0.402 & 0.207 & 0.406 \\
-Farmer               & 0.423                             & 0.495                            & 0.355 & 0.479 & 0.451 & 0.498 & 0.444 & 0.497 \\
-Prof. or proprietor  & 0.09                              & 0.286                            & 0.075 & 0.264 & 0.069 & 0.253 & 0.053 & 0.225 \\
-Laborer              & 0.235                             & 0.425                            & 0.288 & 0.453 & 0.248 & 0.432 & 0.288 & 0.453 \\
-Unknown              & 0.019                             & 0.135                            & 0.081 & 0.274 & 0.029 & 0.169 & 0.008 & 0.089 \\
-Enlisted in big city & 0.545                             & 0.499                            & 0.497 & 0.501 & 0.461 & 0.499 & 0.42 & 0.494 \\
-Property inc in 1860 & 444.889                           & 1056.215                         & 703.517 & 2190.478 & 502.019 & 1099.896 & 620.684 & 2498.66 \\
-Age when captured    & 26.079                            & 7.152                            & 24.848 & 6.588 & 26.995 & 7.558 & 25.658 & 6.601 \\
-Height when captured & 171.518                           & 6.2                              & 171.377 & 6.914 & 171.959 & 6.495 & 171.338 & 6.765 \\
-Officer              & 0.111                             & 0.315                            & 0.092 & 0.289 & 0.065 & 0.247 & 0.049 & 0.217 \\
-Married in 1860      & 0.27                              & 0.446                            & 0.246 & 0.432 & 0.279 & 0.449 & 0.233 & 0.423 \\
-Fraction company dead before capture & 0.056 & 0.054 & 0.057 & 0.046 & 0.116 & 0.069 & 0.112 & 0.054 \\
-Company birthplace fragmentation     & 0.554 & 0.183 & 0.516 & 0.238 & 0.543 & 0.199 & 0.553 & 0.173 \\
-Company occupational fragmentation   & 0.587 & 0.173 & 0.614 & 0.177 & 0.586 & 0.173 & 0.601 & 0.168 \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{OLS statement}
-page 1474 line 65 and footnote 22.
-``When we ran an OLS regression of the number of friends on the covariates we later use in our hazard specification, we found that professionals and proprietors, the Irish, older men, and the recently wounded were less likely to have many friends, whereas those from a large city had more friends''...
-``The coefficient on recently wounded was $-0.879$ ($= 0.397$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of number of friends}
-\begin{tabular}{ll}
-\hline
-Professional or proprietor     & -0.913***  \\
-                               & -0.0979    \\
-Irish                          & -0.267***  \\
-                               & -0.0984    \\
-Age at capture                 & -0.0391*** \\
-                               & -0.00504   \\
-Wounded 10 days before capture & -0.831***  \\
-                               & -0.0876    \\
-Large city                     & 0.553***   \\
-                               & -0.0649    \\
-Observations                   & 23256      \\
-R-squared                      & 0.152      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Predicted probability of death}
-page 1475, line 24.
-``As the number of friends increases from 0 to 5, the predicted probability of death, using the second specification in Table 3, decreases from $0.31$ to $0.28$, and as the number of friends increases to $10$, the predicted mortality probability falls to $0.26$.
-(The mean number of friends in each month was $5.6$, with a standard deviation of $9.2$, and the median was $2$.)''
-
-\begin{table}[ht]
-\centering
-\caption{Number of Friends}
-\begin{tabular}{lll}
-\hline
-          & Initial & In estimation \\
-Mean      & 5.58    & 2.87          \\
-Std. Dev. & 9.22    & 5.12          \\
-Median    & 2       & 1             \\
-\end{tabular}
-\end{table}
-
-The summary statistics mentioned for the variable friends match the initial file, but not the data that is actually included in the regression.
-
-\begin{figure}[ht]
-\centering
-\caption{Exponential specification}
-\label{exponential}
-\includegraphics[scale=0.65]{exponential.png}
-\end{figure}
-
-The file ``survival.dta'' contains the predicted survival probability for individuals with 0, 5 and 10 friends (evaluated at means for the other covariates).
-The statement did not specify a point in time, but we find a coincidence with the statement at $t=330.76$ (average days of imprisonment was $131.62$).
-
-\paragraph{Table 3 with regiment fixed effects}
-page 1476, line 2.
-``Even when we included state of regiment fixed effects, the hazard ratio on the number of friends remained virtually unchanged (e.g.
-the hazard ratio on the initial number of friends was $0.976$, $=0.009$).''
-
-\begin{sidewaystable}
-\caption{Table 3 with regiment state effects}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err & Hazard rate & Std. err & Hazard rate & Std. err \\
-Number of friends                        & 0.984*      & -0.009   & 0.978       & -0.009   &             &          \\
-Initial number of friends                &             &          &             &          & 0.976++     & -0.009   \\
-Ln(number of prisoners in camp)          &             &          & 1.538++     & -0.141   & 1.525++     & -0.14    \\
-Fraction of company dying before capture & 1.427       & -1.227   & 1.19        & -1.011   & 0.787       & -0.653   \\
-Professional or proprietor               & 0.512       & -0.134   & 0.506++     & -0.131   & 0.502++     & -0.13    \\
-Artisan                                  & 0.862       & -0.114   & 0.862       & -0.114   & 0.851       & -0.112   \\
-Laborer                                  & 1.163       & -0.148   & 1.154       & -0.146   & 1.141       & -0.145   \\
-German                                   & 1.135       & -0.213   & 1.116       & -0.21    & 1.103       & -0.206   \\
-Irish                                    & 0.731*      & -0.118   & 0.723       & -0.116   & 0.723       & -0.115   \\
-British                                  & 0.616*      & -0.167   & 0.630*      & -0.17    & 0.637*      & -0.174   \\
-Other                                    & 0.612       & -0.145   & 0.603       & -0.144   & 0.602       & -0.143   \\
-Sergeant, corporal or officer            & 0.570++     & -0.117   & 0.561++     & -0.113   & 0.557++     & -0.112   \\
-Age at captivity                         & 1.042++     & -0.008   & 1.040++     & -0.007   & 1.040++     & -0.007   \\
-Height at enlistment                     & 1.014*      & -0.007   & 1.014*      & -0.007   & 1.014*      & -0.007   \\
-Observations                             & 3026        &          & 3026        &          & 3026        &          \\
-Number of subjects                       & 23174       &          & 23174       &          & 23174       &          \\
-Log pseudo likelihood                    & -1307.77    &          & -1291.45    &          & -1290.674   &          \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Table 3 with splines}
-page 1476, line 6 and footnote 23 ``Our experiments with splines suggested that the marginal effect of a friend on survival was greater for the first two friends than for more."  Footnote 23: "The hazard rate on the marginal effect of fewer than three friends was $0.956$ ($=0.044$) and the hazard rate on the marginal effect of three or more friends was $0.980$ ($=0.011$).
-Although the first hazard rate was not statistically significantly different from one, the two terms together were jointly significant.''
-
-\begin{table}[ht]
-\centering
-\caption{Spline at 3}
-\begin{tabular}{ll}
-\hline
-                     & Hazard rate \\
-Fewer than 3 friends & 0.956       \\
-                     & -0.0443     \\
-3 or more friends    & 0.980*      \\
-                     & -0.0108     \\
-Observations         & 23256       \\
-Chi-sq               & 7.789       \\
-Prob > chi-sq        & 0.0204      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Weibull specification}
-page 1477, line 12. ``When we use a Weibull rather than an exponential specification, we found no evidence of duration dependence...''
-
-\begin{sidewaystable}
-\caption{Weibul}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llllllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-VARIABLES                                & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.986                               & -0.009                              & 0.979                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.531++                             & -0.139 & 1.517++ & -0.139 \\
-Fraction of company dying before capture & 1.242                               & -0.897                              & 1.008                               & -0.722 & 0.733 & -0.525 \\
-Professional or propietor                & 0.566                               & -0.147                              & 0.562                               & -0.144 & 0.554 & -0.142 \\
-Artisan                                  & 0.95                                & -0.121                              & 0.952                               & -0.12 & 0.942 & -0.119 \\
-Laborer                                  & 1.308                               & -0.157                              & 1.303                               & -0.154 & 1.296 & -0.154 \\
-German                                   & 1.198                               & -0.218                              & 1.169                               & -0.212 & 1.153 & -0.209 \\
-Irish                                    & 0.771                               & -0.123                              & 0.765*                              & -0.12 & 0.753* & -0.118 \\
-British                                  & 0.630*                              & -0.17                               & 0.644                               & -0.174 & 0.646 & -0.176 \\
-Other                                    & 0.656*                              & -0.155                              & 0.643*                              & -0.153 & 0.640* & -0.151 \\
-Sargeant, corporal or officer            & 0.536++                             & -0.114                              & 0.531++                             & -0.11 & 0.528++ & -0.11 \\
-Age at captivity                         & 1.046++                             & -0.008                              & 1.045++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1322.852                           &                                     & -1306.836                           &  & -1305.627 &  \\
-Duration dependence                      & 1.088                               &                                     & 1.08                                &  & 1.084 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Month dummies}
-page 1477, line 19.
-``When we included dummy variables in our specification indicating that an individual had survived 1, 2, 3 or more months, we found that those who had survived one or two months were less likely to die than those still in their first month of captivity, but that the advantage of having survived a third month was small and there was no advantage to having survived a fourth month.''
-
-\begin{sidewaystable}
-\caption{controlling for months survived}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-                                         & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.989                               & -0.009                              & 0.982*                              & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.612++                             & -0.146 & 1.604++ & -0.145 \\
-Fraction of company dying before capture & 1.368                               & -1.001                              & 1.117                               & -0.811 & 0.832 & -0.603 \\
-Professional or propietor                & 0.56                                & -0.145                              & 0.557                               & -0.142 & 0.547 & -0.14 \\
-Artisan                                  & 0.946                               & -0.121                              & 0.951                               & -0.121 & 0.939 & -0.12 \\
-Laborer                                  & 1.302                               & -0.158                              & 1.302                               & -0.156 & 1.298 & -0.156 \\
-German                                   & 1.22                                & -0.223                              & 1.195                               & -0.216 & 1.178 & -0.213 \\
-Irish                                    & 0.774                               & -0.125                              & 0.770*                              & -0.122 & 0.756* & -0.12 \\
-British                                  & 0.618*                              & -0.168                              & 0.632*                              & -0.172 & 0.634* & -0.174 \\
-Other                                    & 0.658*                              & -0.156                              & 0.650*                              & -0.156 & 0.647* & -0.154 \\
-Sargeant, corporal or officer            & 0.533++                             & -0.114                              & 0.531++                             & -0.111 & 0.526++ & -0.11 \\
-Age at captivity                         & 1.047++                             & -0.008                              & 1.046++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Survived 1 month                         & 0.407++                             & -0.08                               & 0.362++                             & -0.072 & 0.352++ & -0.071 \\
-Survived 2 months                        & 0.472++                             & -0.092                              & 0.401++                             & -0.08 & 0.393++ & -0.078 \\
-Survived 3 months                        & 0.74                                & -0.137                              & 0.64                                & -0.12 & 0.631 & -0.118 \\
-Survived 4 or more months                & 0.833                               & -0.134                              & 0.745*                              & -0.12 & 0.740* & -0.119 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1307.333                           &                                     & -1287.9                             &  & -1285.595 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Cox Proportional Hazard Model}
-page 1477, line 26 footnote.
-``We also investigated the use of a Cox proportional hazard model to allow the baseline hazard to rise or fall in any month.
-Controlling for camp conditions, we obtained a statistically insignificant hazard ratio on friends of $0.987$ ($=0.009$).
-We suspect that we are losing power because of our small sample size.''
-
-\begin{sidewaystable}
-\caption{Cox proportional models}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err. & Hazard rate & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.992       & -0.009    & 0.987       & -0.009    &             &           \\
-Initial number of friends                &             &           &             &           & 0.978       & -0.009    \\
-Ln(number of prisoners in camp)          &             &           & 1.593++     & -0.149    & 1.587++     & -0.149    \\
-Fraction of company dying before capture & 1.751       & -1.298    & 1.558       & -1.148    & 1.179       & -0.867    \\
-Professional or propietor                & 0.557       & -0.144    & 0.556       & -0.142    & 0.546       & -0.139    \\
-Artisan                                  & 0.942       & -0.121    & 0.952       & -0.122    & 0.938       & -0.12     \\
-Laborer                                  & 1.284       & -0.157    & 1.287       & -0.157    & 1.284       & -0.156    \\
-German                                   & 1.241       & -0.228    & 1.218       & -0.223    & 1.2         & -0.22     \\
-Irish                                    & 0.765       & -0.126    & 0.763*      & -0.123    & 0.746*      & -0.121    \\
-British                                  & 0.613*      & -0.166    & 0.625*      & -0.169    & 0.626*      & -0.171    \\
-Other                                    & 0.658*      & -0.159    & 0.652*      & -0.159    & 0.649*      & -0.158    \\
-Sargeant, corporal or officer            & 0.538++     & -0.115    & 0.537++     & -0.113    & 0.532++     & -0.112    \\
-Age at captivity                         & 1.048++     & -0.008    & 1.046++     & -0.008    & 1.046++     & -0.008    \\
-Height at entlistment                    & 1.01        & -0.008    & 1.01        & -0.007    & 1.011       & -0.007    \\
-Observations                             & 23256       &           & 23256       &           & 23256       &           \\
-Log pseudo likelihood                    & -3102.845   &           & -3086.134   &           & -3083.63    &           \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{table}[ht]
-\centering
-\caption{table 4 net transfer}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lll}
-\hline
-VARIABLES               & Hazard Rate & Std. err. \\
-Net transfer of friends & 0.946**     & -0.024    \\
-Observations            & 15998       &           \\
-\end{tabular}
-\end{table}
-
-\paragraph{On limiting the sample}
-page 1480, line 17.
-``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged.
-The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).''
-
-\paragraph{On the mortality of privates}
-page 1480, line 54.
-``The fraction of sergeants or higher rank is not a reflection of own officer mortality.
-When we restricted the sample to privates, we found that the derivative of this coefficient was 0.115 (sdev=0.054).''
-
-\paragraph{On the role of networks in predicting escape from Andersonville}
-page 1482, line 25.
-``Also suggestive of friends not always helping survival is that, among the men at Andersonville, we find no evidence that the number of friends predicted whether an individual was one of the 140 escaped.''
-
-See table below for the final three verifications:
-
-\begin{sidewaystable}
-\caption{Final three specifications}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llll}
-\hline
-                                                 & Dependent variable: Lived & Dependent variable: Lived & Dependent variable: Escaped \\
-                                                 & Shorter time period       & Privates only             &                             \\
-Number of men in company                         & 0.003++                   & 0.003++                   & 0                           \\
-                                                 & -0.001                    & -0.001                    & 0                           \\
-Fraction of company with rank sergeant or higher & 0.115                     & 0.139++                   & -0.001                      \\
-                                                 & -0.054                    & -0.036                    & -0.002                      \\
-Number of men with same last name in regiment    & 0.033++                   & 0.035++                   & 0                           \\
-                                                 & -0.007                    & -0.007                    & 0                           \\
-Log(number of men in camp from same town)        & -0.003                    & -0.001                    & 0                           \\
-                                                 & -0.005                    & -0.005                    & 0                           \\
-Pseudo R2                                        & 0.036                     & 0.047                     & 0.015                       \\
-Observations                                     & 25880                     & 27923                     & 28190                       \\
-\end{tabular}
-\end{sidewaystable}
-
-The only in-text claim that we are not able to confirm is their statement that there is no mortality difference between the colored non-officers and the rest of the Andersonville POWs (page 1480, footnote 29) as we don’t have any information on the race of the POWs.
-
-\section*{Appendix: Non-parametric estimation}
-The following figures are our replications of the Kaplan-Meier survival estimates which show no differences to the original:
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimate}
-\label{kmSurvival}
-\includegraphics[scale=0.3]{kaplan1.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by early and late capture date}
-\label{kmCapture}
-\includegraphics[scale=0.3]{kaplan2.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by camp for late captures}
-\label{kmCamp}
-\includegraphics[scale=0.3]{kaplan3.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by number of friends for Anderson}
-\label{kmNumber}
-\includegraphics[scale=0.3]{kaplan4.png}
-\end{figure}
-
-\printbibliography
-
-\end{refsection}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% UNCOMMENT TO INCLUDE THE ANDERSONVILLE CHAPTER!!!!!
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \input{andersonville.tex}
 
 \begin{refsection}
+\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
+\label{uncertainty}
+\section*{Abstract}
+\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
+The self-fullfilling currency attack model which they propose thus has the suprising feature,
+that with the introduction of risk perceptions, the multiple equilibria region, thus seems to solve to a single equilibrium.
+It is my contention that this is not a surpising result, since the risk factor, replaces a previous existant, Knightian uncertainty, effectively increasing the body of knowledge.
+Furthermore, the quantifiable risk only solves a certain part of the multiple equilibria region.
+Lastly, if we replace the somewhat stange assumption of a bounded uniform distribution of risk perceptions,
+with the more orthodox, normaly distribution, we cannot come to the same results.
 
-\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
-\label{currency}
-\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
+\section{The Idea}
+This paper addresses the issue multiple equilibria in models of currency attacks.
+In situations of a currency peg, there is the possibility of a currency attack.
+Investors will short the pegged currency, hoping the government will release the peg.
+If a sufficiently large proportion of the market participates in this,
+the cost of maintaining the peg for the government becomes too high,
+which will lead to the government releasing the peg.
+Currency attacks thus have a self-fulling nature,
+which leads to a situation of multiple equilibria,
+as described in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}.
 
-In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor, is the result of the fact that this risk factor eliminates the previously existing uncertainty.
-In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
-This view is enforced by the fact that the equilibrium is most pronounced when the risk factor (epsilon) is minimised (i.e.~set equal to zero), as the authors state themselves.
-Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium is in fact the entire `ripe for attack' domain.
+In \textcite{morris1998unique} the authors describe such a model
+and expand on it by introducting a second-order mechanism.
+Hereby investors do not only look at the economics fundamentals of a currency,
+but also at other investors' perceptions of these fundamentals.
+This leads to a standard situation where there is a stable, unstable, and `ripe for attack' region (based on the economic fundamentals.
+
+However, the authors then proceed to introduce a measure of risk around perceptions by investors.
+Investors thus do not now the actual state of the fundamentals, but rather a distored form of it.
+As a result, the investors' perception of other investors' perceptions are even more distorted.
+Paradoxically, the leads to model being solvable to a unique equilibrium.
+
+\section{The Model}
+
+\section{The Results}
+
+\section{The Issues}
+By introduction the idea of perceptions of other investors' perceptions, the authors give a more complete picture of such a currency attack.
+It is thus very surprising that the outcome of their more realistic model, correspond less to reality and the more incomplete models.
+That is to say, the nature of currency attacks does seem to be characterised by multiple equilibria.
+This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.
+
+In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor,
+is the result of the fact that this risk factor eliminates the previously existing uncertainty.
+In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk,
+which is completer body of knowledge.
+This view is enforced by the fact that,
+the equilibrium is most pronounced when the risk factor ($\epsilon$) is minimised (i.e.~set equal to zero),
+as the authors state themselves.
+Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium,
+is in fact the entire `ripe for attack' domain.
+
+Also, the authors assume that the investors perception of other investors perception takes the form of a bounded uniform distribution.
+It is unlikely that perceptions would best be described by a uniform distribution.
+More importantly, it is unlikely that this distribution would be bounded, such as is assumed by the authors.
+If we replace the bounded uniform distribution, with a normal distribution (which is unbounded),
+then we cannot derive the same results.
 
@@
 An addition to these economic features, the key feature of Bitcoin is decentralisation.
-All transactions are kept in a public ledger called the blockchain.
-An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
+All transactions are kept in a public ledger called the blockchain. An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
 Conflict resolution, in this system, is done through majority consensus of blockchain copy holders.
@@
 Bitcoin initially because popular in advanced economies such as those in Europe and North America.
-However, since mid 2013 there has been a large shift towards developing economies, in which comparative advantages of Bitcoin are more pronounced.
+However, since mid 2013 there has been a large shift towards developing economies,
+in which comparative advantages of Bitcoin are more pronounced.
 For example, since its inception, Mt.Gox (located in Japan) was the largest Bitcoin exchange (marketplace), however in October 2013, Mt.Gox was overtaken by a Chinese exchange.
@@
 However, in the targeted developing economies, many phones are not smartphones, the vast majority using Nokia Operating System (Nokia OS).
-These phone can also run applications, using the Java Mobile App platform.
-Currently there are no Bitcoin apps available for this platform.
+ These phone can also run applications, using the Java Mobile App platform. Currently there are no Bitcoin apps available for this platform.
 
 I propose to participate in the development of open-source applications which would enable the users of stupid phones.
-We can then exploit the temporal difference when releasing the applications in different languages at different times, as well the downloads from traceable IP addresses.
+We can then exploit the temporal difference when releasing the applications in different languages at different times,
+as well the downloads from traceable IP addresses.
 
@@
 \label{end-notes}
-In the previous chapters I have presented my current research projects. These projects are in various stages of completions.
+In the previous chapters I have presented my current research projects.
+These projects are in various stages of completions.
 
-I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey done before and after a highly relevant policy change.
-Especially since the methodology and location are the same as in \textcite{duflo2000, duflo2003} In addition to this there is now a third data wave which has become available.
+I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey,
+done before and after a highly relevant policy change.
+Especially since the methodology and location are the same as in \textcite{duflo2000child, duflo2003grandmothers}.
+In addition to this there is now a third data wave which has become available.
 This provides us with more data, and mostly the opportunity to use more interesting methodology.
@@
 
-The replication of Surviving Andersonville is already completed in term of the replication in Stata.
-We would like to redo the analysis in R \parencite{R}.
-The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
-The findings of this replication can summarised as:
+% The replication of Surviving Andersonville is already completed in term of the replication in Stata.
+% We would like to redo the analysis in R \parencite{R}.
+% The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
+% The findings of this replication can summarised as:
 
-\begin{quote}
-``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
+%\begin{quote}
+%``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
 It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
 This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
-\end{quote}
+%\end{quote}
 
-We do not expect to find anything similar to Bell and Miller, but think that it can nevertheless be interesting to replicate findings using a different software package.
-In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
-In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
+% We do not expect to find anything similar to Bell and Miller,
+% but think that it can nevertheless be interesting to replicate findings using a different software package.
+% In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
+% In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
 

### 2013-12-14 andersonville.tex
clean for resubmission

--- 2013-11-22 draft.tex
@@
-\documentclass[a4paper]{report}\usepackage{graphicx, color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
-\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
-\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
-\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
-\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
-\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
-\newcommand{\hlslot}[1]{\textit{#1}}%
-\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\usepackage{mathtools}
-\usepackage{rotating}
-\usepackage{graphicx}
-\usepackage{cleveref}
-\usepackage[authordate,backend=biber]{biblatex-chicago}
-\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
-
-\title{Preliminary Thesis Defence\\~\\
-\begin{tabular}{rl}
-Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
-Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
-\end{tabular}
-}
-
-\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}\\~\\
-The Graduate Institute, Geneva}
-
-\let\oldmarginpar\marginpar
-\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]
-{\raggedright\footnotesize #1}}
-
-\addglobalbib{bibliography.bib}
-
-\newbibmacro{string+doiurlisbn}[1]{%
-  \iffieldundef{doi}{%
-    \iffieldundef{url}{%
-      \iffieldundef{isbn}{%
-        \iffieldundef{issn}{%
-          #1%
-        }{%
-          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
-        }%
-      }{%
-        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
-      }%
-    }{%
-      \href{\thefield{url}}{#1}%
-    }%
-  }{%
-    \href{http://dx.doi.org/\thefield{doi}}{#1}%
-  }%
-}
-
-\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
-\DeclareFieldFormat[article,incollection]{title}%
-    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
-\begin{document}
-
-\maketitle
-\tableofcontents
-\listoftables
-\listoffigures
-
-\begin{refsection}
-\chapter{Introduction}
-In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
-
-\begin{itemize}
-\item Additional South African Evidence on Pensions and Child Growth (\ref{south-africa})
-\item Replication: Surviving Andersonville (\ref{andersonville})
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\ref{currency})
-\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\ref{bitcoin})
-\end{itemize}
-
-These project are in various stages of completion. Below I will briefly describe the research idea, the current state, and the potential for each project.
-
-Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}.
-These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
-A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
-This paper makes use of a Household Survey from 2008, 2012 and 2013.
-The survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
-As it stands now I have analysed the data from 2008 and 2012.
-The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
-
-Secondly, together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
-We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors.
-However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
-When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
-As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
-The authors however, aggregate these two.
-This leads to overstated magnitudes of the social ties of POWs.
-This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
-At this point our replication is quite complete.
-Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
-
-Thirdly, \textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
-It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
-I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty.
-We thus gain information.
-I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
-
-Fourthly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies.
-Bitcoin transactions are conducted using an electronic process called signing.
-I would like to study the role of Bitcoin in remittances.
-For this I would like to participate in building Bitcoin applications for the simple type of phones common in developing economies (sometimes referred to stupid phones).
-We could study the spread of bitcoin by looking at the downloads of the apps from regions, as well looking at how releasing the app in different languages evolves.
-
-After this the papers follow, in the order listed above.
-A separate citations section is included for each chapter.
-For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
-In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
-I also mention some very preliminary ideas.
-
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{Pensions and Child Growth in South Africa}
-\label{south-africa}
-\section*{Abstract}
-
-In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.
-
-I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.
-
-The main preliminary finding is that the household effect was only significant in 2012.
-
-\section{Introduction}
-
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
-is very similar to \textcite{duflo2000, duflo2003}.
-The deviation from international standards \parencite{who2006child} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status and gender.
-
-The anthropometrics are useful for computing z-scores.
-These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
-
-The South African pension is a interesting variable to measure income because of its criteria.
-Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias issues.
-The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
-
-Duflo finds evidence in South Africa's 1993 \href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated Household Survey} that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension.
-This is directly after the significant increase in the pension sum for blacks.
-The pension-eligibility age at this time was 60 for women and 65 for men.
-
-This study deviates from the Duflo study in several ways.
-In 2008 and 2012, the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
-In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
-
-This happened in a few steps.
-As of July 16th 2008 men aged 63 and 64 were eligible for a pension.
-Men aged 61 and 62 became eligible in April 2009.
-Finally in January 2010, pension eligibility age was at 60 for all citizens.
-
-Another deviation is the usage of WHO z-scores \parencite{who2006child} in stead of CDC z-scores \parencite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence, as long as we use the same standards consistently.
-
-The main preliminary result is that the household effect (i.e.~having one or more recipients in the household) is very insignificant in the 2008 estimate.
-But in the 2012 estimate it is very significant.
-
-\section{Data}
-
-In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \parencite{who2006child}.
-
-The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South African households.
-The primary information variables that I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
-
-For adults, several variables measure the different amounts and sources of income.
-Among those, a variable for the adult receiving a state pension, and if so, how much.
-This is a numeric variable, the values of which lie very close together.
-For simplicity I have temporarily used this variable as a dummy.
-
-The children's anthropometrics taken are, length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately, the latest version of wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
-However, I have computed the length-for-age z-scores manually.
-
-In 2006 the WHO published its standards for child growth.
-These standards are based on the scores of children from different ethnic populations in households which maintained a healthy lifestyle.
-The standards provide the means and standards deviations used.
-These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1))
-p1 <- p1 + \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman))
-p1 <- p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
-p1
-\end{alltt}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 324 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 263 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 51 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 638 rows containing missing values (geom\_point).}}\end{kframe}
-\includegraphics[width=\maxwidth]{figure/r-p1}
-
-\end{knitrout}
-
-\section{Results}
-
-Basic HAZ (2008)
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(w1_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-## Call:
-## lm(formula = w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + 
-##     w1_best_age_yrs, data = w1_child, subset = w1_c_age_m >= 
-##     6 & w1_c_age_m <= 60)
-## 
-## Residuals:
-##    Min     1Q Median     3Q    Max 
-## -4.779 -1.036 -0.169  0.834  7.060 
-## 
-## Coefficients:
-##                  Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.43e+00   1.44e-01   -9.87   <2e-16 ***
-## w1_spen_w        2.32e-02   1.15e-01    0.20   0.8402    
-## w1_spen_m        1.36e-01   1.72e-01    0.79   0.4281    
-## w1_h_tinc        3.62e-05   9.99e-06    3.62   0.0003 ***
-## w1_best_edu      1.63e-03   7.84e-03    0.21   0.8355    
-## w1_best_age_yrs  7.61e-03   3.64e-03    2.09   0.0369 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.77 on 1436 degrees of freedom
-##   (1936 observations deleted due to missingness)
-## Multiple R-squared:  0.0134,	Adjusted R-squared:  0.00994 
-## F-statistic: 3.89 on 5 and 1436 DF,  p-value: 0.00164
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.835  -0.050   0.000   0.788   7.070 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.172e+00  7.388e-02 -15.861  < 2e-16 ***
-## w1_spen_w        1.748e-02  9.477e-02   0.184   0.8536    
-## w1_spen_m       -1.374e-01  1.444e-01  -0.952   0.3414    
-## w1_h_tinc        2.995e-05  5.606e-06   5.342 9.69e-08 ***
-## w1_best_edu      2.410e-03  3.532e-03   0.682   0.4951    
-## w1_best_age_yrs  4.127e-03  1.863e-03   2.215   0.0268 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4889 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz1)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m_65 + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.836  -0.050   0.000   0.786   7.040 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.173e+00  7.387e-02 -15.880  < 2e-16 ***
-## w1_spen_w        8.576e-03  9.541e-02   0.090   0.9284    
-## w1_spen_m       -9.189e-02  1.348e-01  -0.681   0.4956    
-## w1_h_tinc        2.992e-05  5.605e-06   5.339 9.85e-08 ***
-## w1_best_edu      2.443e-03  3.531e-03   0.692   0.4890    
-## w1_best_age_yrs  4.092e-03  1.860e-03   2.200   0.0278 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4885 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\printbibliography
-
-\end{refsection}
-
 \begin{refsection}
@@
 \end{refsection}
-
-\begin{refsection}
-
-\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
-\label{currency}
-\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
-
-In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor, is the result of the fact that this risk factor eliminates the previously existing uncertainty.
-In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
-This view is enforced by the fact that the equilibrium is most pronounced when the risk factor (epsilon) is minimised (i.e.~set equal to zero), as the authors state themselves.
-Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium is in fact the entire `ripe for attack' domain.
-
-\nocite{taleb2010black}
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
-\label{bitcoin}
-In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
-This currency -the first of a group called cryptocurrencies- has the following economics features:
-
-\begin{itemize}
-\item public transactions
-\item anonymous addresses
-\item fixed amount of units
-\item high granularity (1 Bitcoin = 100,000,000 Satoshi)
-\item no or low transaction costs
-\end{itemize}
-
-An addition to these economic features, the key feature of Bitcoin is decentralisation.
-All transactions are kept in a public ledger called the blockchain.
-An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
-Conflict resolution, in this system, is done through majority consensus of blockchain copy holders.
-
-There are a number of features which make Bitcoin attractive for remittances.
-Firstly, the low transaction costs are a huge step up from the current facilitators, which charge high percentages.
-Secondly, government intervention (especially in the recipient country) is prevented by the anonymity.
-Thirdly, recipients can choose to keep their remittance in a currency which is not controlled by their government.
-Fourthly, the granularity ensures very small transactions can be conducted.
-
-Bitcoin initially because popular in advanced economies such as those in Europe and North America.
-However, since mid 2013 there has been a large shift towards developing economies, in which comparative advantages of Bitcoin are more pronounced.
-For example, since its inception, Mt.Gox (located in Japan) was the largest Bitcoin exchange (marketplace), however in October 2013, Mt.Gox was overtaken by a Chinese exchange.
-
-Bitcoin transactions are conducted by the electronic `signing' of a transaction.
-This is a very simple electronic process.
-Currently many smartphone apps are available to this purpose.
-However, in the targeted developing economies, many phones are not smartphones, the vast majority using Nokia Operating System (Nokia OS).
-These phone can also run applications, using the Java Mobile App platform.
-Currently there are no Bitcoin apps available for this platform.
-
-I propose to participate in the development of open-source applications which would enable the users of stupid phones.
-We can then exploit the temporal difference when releasing the applications in different languages at different times, as well the downloads from traceable IP addresses.
-
-\printbibliography
-
-\end{refsection}
-
-\begin{refsection}
-\chapter{End notes}
-\label{end-notes}
-In the previous chapters I have presented my current research projects. These projects are in various stages of completions.
-
-I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey done before and after a highly relevant policy change.
-Especially since the methodology and location are the same as in \textcite{duflo2000, duflo2003} In addition to this there is now a third data wave which has become available.
-This provides us with more data, and mostly the opportunity to use more interesting methodology.
-The text of the paper still has to be written.
-
-The replication of Surviving Andersonville is already completed in term of the replication in Stata.
-We would like to redo the analysis in R \parencite{R}.
-The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
-The findings of this replication can summarised as:
-
-\begin{quote}
-``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
-It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
-This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
-\end{quote}
-
-We do not expect to find anything similar to Bell and Miller, but think that it can nevertheless be interesting to replicate findings using a different software package.
-In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
-In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
-
-The discussion of \textcite{morris1998unique} is in a very early stage.
-I have looked at the paper in detail, I have also done a brief analysis of my main critique, namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
-However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
-In addition to this, this example should demonstrate how the entire `ripe for attack' region is not solved for the unique equilibrium.
-
-Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin.
-I would like to analyse the spread of this.
-I propose to follow the spread of applications for platforms which are popular in developing economies.
-
-At this point, three out of four of the previously discussed research projects are some form of a replication of prior work.
-As replications they are mostly critiques of others' work, rather than constructive ideas.
-This is mostly a result of the fact that these projects progress faster.
-For this reason, these research projects have progressed more than the projects which are primarily based on my own ideas.
-However, it is my attention to shift the focus of my thesis to include more original work.
-Here I present two more ideas which are too preliminary to include in the main body of the text, but are based on my own work.
-
-Firstly, I was in charge of setting up a baseline diagnostic into security perceptions in Conakry, Guinea.
-This diagnostic will be used to analyse the impact of a police reform conducted here.
-The reform constitutes of the implementation of a model of `police de proximitee'.
-The baseline consist of 4500 interviews using smartphones in the comune of Conkary as well a large number of interviews in N'Zerekore (east Guinea).
-Some time after the implementation of the police reform as follow up study will be conducted.
-I propose to conduct an impact evaluation using the results from the studies in which I have taken and will take part.
-
-Secondly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy.
-I would like to write one paper about an issue relating to this.
-In particular I would like to at the effect of outliers.
-The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}.
-I would like to see how these principles affect research in development microeconomics.
-
-In this document I have tried to give a description of my research projects.
-None of these projects are near completion and many are in fact in a very early stage.
-The purpose of this has been to describe the direction I am taking with my thesis, and to receive feedback on this.
-As a result of this being work in progress, the articles are still incomplete, this includes lacking the proper attribution of ideas using citations.
-
-\printbibliography
-\end{refsection}
-
-\end{document}

### 2013-12-14 PTD.tex
break lines, add bitcoin data sources

@@
 \tableofcontents
-\listoftables
-\listoffigures
+% \listoftables
+% \listoffigures
 
@@
 
+\section{Data}
+Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
+Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
+Much like the way bank clients have a claim to their money, which is in the bank's vault.
+
+Therefore Bitcoin purchases at exchanges do not lead to transaction being recorded in the blockchain.
+Since the Bitcoins remain in the Exchange's wallet, the only thing which changes is the claims of the clients.
+
+\begin{itemize}
+ \item The blockchain (public ledger)
+ \begin{itemize}
+ 	\item IP address
+ 	\item Language of transaction notice
+ 	\item Transaction times
+ \end{itemize}
+ \item The exchanges
+ \begin{itemize}
+ 	\item Location of exchanges
+ 	\item Transaction costs for each currency
+	\item The order books
+	\item Transaction times
+ 	\item The traded currency
+ \end{itemize}
+ \item Software
+ \begin{itemize}
+ 	\item Downloads
+ 	\item Translation contributions (?)
+ 	\item Connections to server
+ \end{itemize}
+\end{itemize}
+
 \printbibliography
@@
 The discussion of \textcite{morris1998unique} is in a very early stage.
-I have looked at the paper in detail, I have also done a brief analysis of my main critique, namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
+I have looked at the paper in detail, I have also done a brief analysis of my main critique,
+namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
 However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
-In addition to this, this example should demonstrate how the entire `ripe for attack' region is not solved for the unique equilibrium.
+In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.
 

### 2013-12-14 PTD.tex
add ms model

@@
 This study deviates from the Duflo study in several ways.
-First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income, including pension recipient status.
+First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income,
+including pension recipient status.
 Whereas Duflo uses age as a proxy for recipient status.
@@
 I perform three types of analysis.
-The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence) and then compare based on living in the household with an of-pension-eligible adult.
+The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence)
+and then compare based on living in the household with an of-pension-eligible adult.
 Secondly, I use my computed z-scores and the data set provided variable which describes the actual pension received (or lack thereof).
@@
 However, the authors then proceed to introduce a measure of risk around perceptions by investors.
-Investors thus do not now the actual state of the fundamentals, but rather a distored form of it.
+Investors thus do not know the actual state of the fundamentals, but rather a distored form of it.
 As a result, the investors' perception of other investors' perceptions are even more distorted.
@@
 \section{The Model}
+I will give a brief description of the model as it is defined, and some it features.
+There is a state of economic fundamentals $\theta$ which is distributed as $\theta \sim U[0,1]$.
+The exchange rate is the hypothetical situation of no government intervention is a function only of these fundamental ($f(\theta)$),
+it is assumed that $\frac{\partial f}{\partial \theta} > 0$.
+The currency is pegged at a level larger than that derived from the fundamentals ($e* \geq f(\theta)$).
+Speculators can short the currency at a cost $t$, their payoff is thus $e* - f(\theta) - t$.
 

### 2013-12-15 PTD.tex
update labels

@@
 \documentclass[a4paper]{report}
-\usepackage{graphicx}
 \usepackage{color}
@@
 \chapter{Introduction}
+\label{intro}
 In this Preliminary Thesis Defense I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
@@
 \begin{itemize}
-\item Additional South African Evidence on Pensions and Child Growth (\autoref{south-africa})
+\item Additional South African Evidence on Pensions and Child Growth (\autoref{sa})
 % \item Replication: Surviving Andersonville (\ref{andersonville})
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{uncertainty})
-\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{bitcoin})
+\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{unc})
+\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{btc})
 \end{itemize}
@@
 The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
-I will discuss this in \autoref{south-africa}.
+I will discuss this in \autoref{sa}.
 
@@
 I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
-This is done in \autoref{uncertainty}.
+This is done in \autoref{unc}.
 
@@
 \chapter{Pensions and Child Growth in South Africa}
-\label{south-africa}
+\label{sa}
 \section*{Abstract}
@@
 \section{Introduction}
+\label{sa:intro}
 This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa.
@@
 \section{Data}
+\label{sa:data}
 In this paper I use data from two sources.
@@
 \section{Analysis}
-\label{analysis}
+\label{sa:analysis}
 I perform three types of analysis.
@@
 \chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
-\label{uncertainty}
+\label{unc}
 \section*{Abstract}
@@
 \section{The Idea}
+\label{unc:idea}
 This paper addresses the issue multiple equilibria in models of currency attacks.
@@
 \section{The Model}
+\label{unc:model}
 I will give a brief description of the model as it is defined, and some it features.
@@
 \section{The Results}
+\label{unc:results}
 
 \section{The Issues}
+\label{unc:issues}
 By introduction the idea of perceptions of other investors' perceptions, the authors give a more complete picture of such a currency attack.
@@
 \chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
-\label{bitcoin}
+\label{btc}
 In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
@@
 \section{Data}
+\label{btc:data}
 Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.

### 2013-12-15 PTD.tex
update model MS, add result, add discussion

@@
 \usepackage{rotating}
+\usepackage{accents}
 \usepackage{graphicx}
@@
 The currency is pegged at a level larger than that derived from the fundamentals ($e* \geq f(\theta)$).
-Speculators can short the currency at a cost $t$, their payoff is thus $e* - f(\theta) - t$.
+Speculators can short the currency at a cost $t$, their payoff is described by $e* - f(\theta) - t$.
+The government derives a positive value $\nu > 0$ from defending the peg.
+The cost of the peg is determined by the economic fundamentals and the proportion of the speculators ($\alpha$) that attack the currency.
+The payoff the government is thus $\nu - c(\alpha, \theta)$.
+
+The introduction the risk for fundamentals: $ x \sim U[\theta - \epsilon, \theta + \epsilon] $.
 
@@
 \label{unc:results}
+The main result from the paper is:
+\begin{quotation}
+	\noindent THEOREM 1: The is a unique $\theta *$ such that,
+	in any equilibrium of the game with imperfect information,
+	the government abandons the currency peg if and only if $\theta \leq \theta *$. \hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
+\end{quotation}
 
@@
 This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.
+
+\begin{enumerate}
+	\item Multiple equilibria exist in the interval $(\underaccent{\bar}{\theta},\bar{\theta})$.
+	\item The introduction of quantief risk, removes uncertainty with $2 \epsilon$ of $x$.
+	\item Here $u(x,\theta) > 0$ leads to $\pi (x) = 1$.
+	\item Authors claim that $u(x,\theta) < 0$ leads to $\pi (x) = 0$.
+	\item This is assumption is false.
+	\item Outside the certain risk area, the previously existing uncertainty remains.
+	\item Multiple equilibria remain possible here.
+\end{enumerate}
+
+In the technical proof of the paper, we can pinpoint the non sequitur here:
+
+\begin{quotation}
+	\noindent For the next step,
+	consider the strategy profile where every speculator attacks the currency if and only if
+	the message $x$ is less than some fixed number $k$. \hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
+\end{quotation}
+
+The riskprofile of the speculator is being redefined here.
+In the first iteration of the model,
+speculators might decide the attack the currency without knowing what other investors would do.
+In this second iteration,
+speculators will only attack if they believe that there is a sufficient number of other attackers doing the same.
+Yet in the first model, attacks were possible, in absense of this certainty.
+It thus follows that speculators should be willing to attack the currency,
+even in the absense of the quantifiable-risk induced certainty.
 
@@
 then we cannot derive the same results.
+
+We can summarise the issues with the paper as follows:
+
+\begin{enumerate}
+	\item The introduction of risk adds information, rather than removing it.
+	\item This does not in fact lead to a unique equilibrium.
+	\item The assumption of a bounded risk interval is problematic.
+\end{enumerate}
 

### 2013-12-15 PTD.tex
update MS and small preamble stuff

@@
 \usepackage{graphicx}
-\usepackage[authordate,backend=biber]{biblatex-chicago}
+\usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
 \usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
 
-\title{Preliminary Thesis Defense\\~\\
+\title{Preliminary Thesis Defence\\~\\
 \begin{tabular}{rl}
@@
 \label{intro}
-In this Preliminary Thesis Defense I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
+In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
 
@@
 
-Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000child, duflo2003grandmothers}.
+Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds upon \textcite{duflo2000child, duflo2003grandmothers}.
 These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
@@
 In situations of a currency peg, there is the possibility of a currency attack.
-Investors will short the pegged currency, hoping the government will release the peg.
+Speculators will short the pegged currency, hoping the government will release the peg.
 If a sufficiently large proportion of the market participates in this,
@@
 and expand on it by introducting a second-order mechanism.
-Hereby investors do not only look at the economics fundamentals of a currency,
-but also at other investors' perceptions of these fundamentals.
-This leads to a standard situation where there is a stable, unstable, and `ripe for attack' region (based on the economic fundamentals.
+Hereby speculators do not only look at the economics fundamentals of a currency,
+but also at other speculators' perceptions of these fundamentals.
+This leads to a standard situation where there is a stable, unstable,
+and a `ripe for attack' region (based on the economic fundamentals.
 
-However, the authors then proceed to introduce a measure of risk around perceptions by investors.
-Investors thus do not know the actual state of the fundamentals, but rather a distored form of it.
+The authors proceed by introducing a measure of risk around perceptions of the fundamentals by investors.
+Investors do not know the actual state of the fundamentals, but rather a distored form of it.
 As a result, the investors' perception of other investors' perceptions are even more distorted.
@@
 The currency is pegged at a level larger than that derived from the fundamentals ($e* \geq f(\theta)$).
-Speculators can short the currency at a cost $t$, their payoff is described by $e* - f(\theta) - t$.
+Speculators can short the currency at a cost $t$, their payoff is described by:
+\begin{equation}\label{unc:specPO}
+e^* - f(\theta) - t
+\end{equation}
 The government derives a positive value $\nu > 0$ from defending the peg.
 The cost of the peg is determined by the economic fundamentals and the proportion of the speculators ($\alpha$) that attack the currency.
-The payoff the government is thus $\nu - c(\alpha, \theta)$.
+The payoff the government is thus:
+\begin{equation}\label{unc:govPO}
+\nu - c(\alpha, \theta)
+\end{equation}
+Lastly, the following, assumptions are imposed: $c(0,0) > \nu$ (with worst fundamtentals the peg always has to be released),
+$c(1,1) > \nu$ (with all speculators attacking, the peg always has to be released),
+$e^* - f(1) < t$ (with best fundamentals, it is inopportune for speculators to attack).
 
-The introduction the risk for fundamentals: $ x \sim U[\theta - \epsilon, \theta + \epsilon] $.
+\subsection{The possible outcomes}
+When we set \autoref{unc:specPO} and \autoref{unc:govPO} equal to zero,
+we derive the two turning points in the model.
+We define $\underaccent{\bar}{\theta}$ which solves $c(0, \theta) = \nu$.
+Also, $\bar{\theta}$ solves $f(\theta) = e^* - t$.
 
-\section{The Results}
+Using the turning points described above, we can define three possible outcome intervals:
+\begin{enumerate}
+	\item $[0, \underaccent{\bar}{\theta}]$, the cost is always too high, this is the unstable region.
+	\item $[\underaccent{\bar}{\theta}, \bar{\theta}]$, if enough speculators attack, the cost of defending the peg becomes too high,
+	this is the `ripe for attack' region.
+	\item $[\bar{\theta}, 1]$, the cost of shorting the currency will always outway the possible gains,
+	this is the stable region.
+\end{enumerate}
+The two corner intervals have unique equilibria, however, the middle interval, does not. This is thus the multiple equilibria region.
+
+\section{The introduction of risk (replacing uncertainty)}
+The authors expand the model by introducing a measure of risk for fundamentals:
+\begin{equation}
+x \sim U[\theta - \epsilon, \theta + \epsilon]
+\end{equation}
+Where is the $x$ is the state of the fundamentas \textit{observed} by the speculators.
+A speculators observation can thus \textit{at most} deviate from the true value of the fundamentals by $\epsilon$.
+The speculators are also aware of the nature of the distortion.
+This means that they are also aware of the fact that other speculators' perceived value of the fundatmentals can at most,
+deviate from their own with a magnitude of $2\epsilon$.
+
+\subsection{The outcomes with risk}
 \label{unc:results}
-The main result from the paper is:
+Having established the new model, the authors state:
 \begin{quotation}
-	\noindent THEOREM 1: The is a unique $\theta *$ such that,
+	The unique optimal strategy for the government is then to abandon the exchange rate only if the observed fraction of deviators, $\alpha$, is greater than or equal to the critical mass $a(\theta)$ in the prevailing state $\theta$.\hspace{\stretch{1}}\parencite[p.~591]{morris1998unique}
+\end{quotation}
+By solving out this government `optimal' strategy,
+the speculators can ensure themselves of a certain abandonment of the peg,
+for a sufficiently low observed $x$.
+The authors proceed to derivde from this the main result of the paper, which is:
+\begin{quotation}
+	THEOREM 1: The is a unique $\theta *$ such that,
 	in any equilibrium of the game with imperfect information,
@@
 \label{unc:issues}
-By introduction the idea of perceptions of other investors' perceptions, the authors give a more complete picture of such a currency attack.
-It is thus very surprising that the outcome of their more realistic model, correspond less to reality and the more incomplete models.
+By introduction the idea of perceptions of other speculators' perceptions,
+the authors give a more complete picture of such a currency attack.
+It is thus very surprising that the outcome of their more realistic model,
+corresponds less to reality and the more incomplete models.
 That is to say, the nature of currency attacks does seem to be characterised by multiple equilibria.
 This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.
+It is therefore quite surprising that the more realistic leads to a the unrealistic situation of a unique equilibrium,
+whereas the less intricate model gives us the more realistic multiple equilibria.
 
+We can summarise the main problem with the model as follows:
 \begin{enumerate}
@@
 \end{enumerate}
+In the technical proof of the paper, we can pinpoint the non sequitur in two different but related points.
+Firstly, the previously mentioned:
+\begin{quotation}
+	The unique optimal strategy for the government is then to abandon the exchange rate
+	only if the observed fraction of deviators, $\alpha$,
+	is greater than or equal to the critical mass $a(\theta)$
+	in the prevailing state $\theta$.
+	\hspace{\stretch{1}}\parencite[p.~591]{morris1998unique}
+\end{quotation}
+This should say ``...abandon the exchange rate \textit{always} if the observed fraction is great than or equal to...''. Since
 
-In the technical proof of the paper, we can pinpoint the non sequitur here:
-
+Secondly,:
 \begin{quotation}
-	\noindent For the next step,
+	For the next step,
 	consider the strategy profile where every speculator attacks the currency if and only if
-	the message $x$ is less than some fixed number $k$. \hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
+	the message $x$ is less than some fixed number $k$.
+	\hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
 \end{quotation}
 
-The riskprofile of the speculator is being redefined here.
+The risk profile of the speculator is being redefined here.
 In the first iteration of the model,

### 2013-12-15 PTD.tex
finish draft uncertainty, move to separate .tex file

--- 2013-12-15 PTD.tex
@@
 \usepackage{rotating}
+\usepackage{accents}
 \usepackage{graphicx}
-\usepackage[authordate,backend=biber]{biblatex-chicago}
+\usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
 \usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
 
-\title{Preliminary Thesis Defense\\~\\
+\title{Preliminary Thesis Defence\\~\\
 \begin{tabular}{rl}
@@
 
-\begin{refsection}
-\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
-\label{unc}
-\section*{Abstract}
-\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
-The self-fullfilling currency attack model which they propose thus has the suprising feature,
-that with the introduction of risk perceptions, the multiple equilibria region, thus seems to solve to a single equilibrium.
-It is my contention that this is not a surpising result, since the risk factor, replaces a previous existant, Knightian uncertainty, effectively increasing the body of knowledge.
-Furthermore, the quantifiable risk only solves a certain part of the multiple equilibria region.
-Lastly, if we replace the somewhat stange assumption of a bounded uniform distribution of risk perceptions,
-with the more orthodox, normaly distribution, we cannot come to the same results.
-
-\section{The Idea}
-\label{unc:idea}
-This paper addresses the issue multiple equilibria in models of currency attacks.
-In situations of a currency peg, there is the possibility of a currency attack.
-Investors will short the pegged currency, hoping the government will release the peg.
-If a sufficiently large proportion of the market participates in this,
-the cost of maintaining the peg for the government becomes too high,
-which will lead to the government releasing the peg.
-Currency attacks thus have a self-fulling nature,
-which leads to a situation of multiple equilibria,
-as described in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}.
-
-In \textcite{morris1998unique} the authors describe such a model
-and expand on it by introducting a second-order mechanism.
-Hereby investors do not only look at the economics fundamentals of a currency,
-but also at other investors' perceptions of these fundamentals.
-This leads to a standard situation where there is a stable, unstable, and `ripe for attack' region (based on the economic fundamentals.
-
-However, the authors then proceed to introduce a measure of risk around perceptions by investors.
-Investors thus do not know the actual state of the fundamentals, but rather a distored form of it.
-As a result, the investors' perception of other investors' perceptions are even more distorted.
-Paradoxically, the leads to model being solvable to a unique equilibrium.
-
-\section{The Model}
-\label{unc:model}
-I will give a brief description of the model as it is defined, and some it features.
-There is a state of economic fundamentals $\theta$ which is distributed as $\theta \sim U[0,1]$.
-The exchange rate is the hypothetical situation of no government intervention is a function only of these fundamental ($f(\theta)$),
-it is assumed that $\frac{\partial f}{\partial \theta} > 0$.
-The currency is pegged at a level larger than that derived from the fundamentals ($e* \geq f(\theta)$).
-Speculators can short the currency at a cost $t$, their payoff is thus $e* - f(\theta) - t$.
-
-\section{The Results}
-\label{unc:results}
-
-\section{The Issues}
-\label{unc:issues}
-By introduction the idea of perceptions of other investors' perceptions, the authors give a more complete picture of such a currency attack.
-It is thus very surprising that the outcome of their more realistic model, correspond less to reality and the more incomplete models.
-That is to say, the nature of currency attacks does seem to be characterised by multiple equilibria.
-This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.
-
-In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor,
-is the result of the fact that this risk factor eliminates the previously existing uncertainty.
-In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk,
-which is completer body of knowledge.
-This view is enforced by the fact that,
-the equilibrium is most pronounced when the risk factor ($\epsilon$) is minimised (i.e.~set equal to zero),
-as the authors state themselves.
-Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium,
-is in fact the entire `ripe for attack' domain.
-
-Also, the authors assume that the investors perception of other investors perception takes the form of a bounded uniform distribution.
-It is unlikely that perceptions would best be described by a uniform distribution.
-More importantly, it is unlikely that this distribution would be bounded, such as is assumed by the authors.
-If we replace the bounded uniform distribution, with a normal distribution (which is unbounded),
-then we cannot derive the same results.
-
-\nocite{taleb2010black}
-\printbibliography
-\end{refsection}
+\input{uncertainty.tex}
 

### 2013-12-15 uncertainty.tex
finish draft uncertainty, move to separate .tex file

\begin{refsection}

\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
\label{unc}
\section*{Abstract}
\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
The self-fullfilling currency attack model which they propose thus has the suprising feature,
that with the introduction of perception distorion, the multiple equilibria region, seems to solve to a single equilibrium.
It is our contention that this is not a surpising result, 
it a consequence of the second-order effect, where the risk factor replaces a previous existant, Knightian uncertainty.
Furthermore, the quantified-risk only solves a certain part of the multiple equilibria region.
Lastly, if we replace the somewhat stange assumption of a bounded uniform distribution of risk perceptions,
with the more orthodox, normaly distribution, we cannot derive the same result.

\section{The Idea}
\label{unc:idea}
This paper addresses the issue multiple equilibria in models of currency attacks.
In situations of a currency peg, there is the possibility of a currency attack.
Speculators will short the pegged currency, hoping the government will release the peg.
If a sufficiently large proportion of the market participates in this,
the cost of maintaining the peg for the government becomes too high,
which will lead to the government releasing the peg.
Currency attacks thus have a self-fulling nature,
which leads to a situation of multiple equilibria,
as described in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}.

In \textcite{morris1998unique} the authors describe such a model.
This model is characterised by a situation where there is a stable, unstable,
and a `ripe for attack' region (based on the economic fundamentals.
The authors expand on the standard model by introducting second-order expectations.
Hereby speculators do not only look at the economics fundamentals of a currency,
but also at other speculators' perceptions of these fundamentals.

The authors proceed by introducing a measure of risk around perceptions of the fundamentals by investors.
Investors do not know the actual state of the fundamentals, but rather a distored form of it.
As a result, the investors' perception of other investors' perceptions are even more distorted.
Paradoxically, the leads to model being solvable to a unique equilibrium.

\section{The Model}
\label{unc:model}
I will give a brief description of the model as it is defined, and some it features.
There is a state of economic fundamentals $\theta$ which is distributed as $\theta \sim U[0,1]$.
The exchange rate is the hypothetical situation of no government intervention is a function only of these fundamental ($f(\theta)$),
it is assumed that $\frac{\partial f}{\partial \theta} > 0$.
The currency is pegged at a level larger than that derived from the fundamentals ($e* \geq f(\theta)$).
Speculators can short the currency at a cost $t$, their payoff is described by:
\begin{equation}\label{unc:specPO}
e^* - f(\theta) - t
\end{equation}
The government derives a positive value $\nu > 0$ from defending the peg.
The cost of the peg is determined by the economic fundamentals and the proportion of the speculators ($\alpha$) that attack the currency.
The payoff the government is thus:
\begin{equation}\label{unc:govPO}
\nu - c(\alpha, \theta)
\end{equation}
Lastly, the following, assumptions are imposed: $c(0,0) > \nu$ (with worst fundamtentals the peg always has to be released),
$c(1,1) > \nu$ (with all speculators attacking, the peg always has to be released),
$e^* - f(1) < t$ (with best fundamentals, it is inopportune for speculators to attack).

\subsection{The possible outcomes}
When we set \autoref{unc:specPO} and \autoref{unc:govPO} equal to zero,
we derive the two turning points in the model.
We define $\underaccent{\bar}{\theta}$ which solves $c(0, \theta) = \nu$.
Also, $\bar{\theta}$ solves $f(\theta) = e^* - t$.

Using the turning points described above, we can define three possible outcome intervals:
\begin{enumerate}
	\item $[0, \underaccent{\bar}{\theta}]$, the cost is always too high, this is the unstable region.
	\item $[\underaccent{\bar}{\theta}, \bar{\theta}]$, if enough speculators attack, the cost of defending the peg becomes too high,
	this is the `ripe for attack' region.
	\item $[\bar{\theta}, 1]$, the cost of shorting the currency will always outway the possible gains,
	this is the stable region.
\end{enumerate}
The two corner intervals have unique equilibria, however, the middle interval, does not. This is thus the multiple equilibria region.

\section{The introduction of risk (replacing uncertainty)}
The authors expand the model by introducing a measure of risk for fundamentals:
\begin{equation}
x \sim U[\theta - \epsilon, \theta + \epsilon]
\end{equation}
Where is the $x$ is the state of the fundamentas \textit{observed} by the speculators.
A speculators observation can thus \textit{at most} deviate from the true value of the fundamentals by $\epsilon$.
The speculators are also aware of the nature of the distortion.
This means that they are also aware of the fact that other speculators' perceived value of the fundatmentals can at most,
deviate from their own with a magnitude of $2\epsilon$.

\subsection{The outcomes with risk}
\label{unc:results}
Having established the new model, the authors state:
\begin{quotation}
	The unique optimal strategy for the government is then to abandon the exchange rate only if the observed fraction of deviators, $\alpha$, is greater than or equal to the critical mass $a(\theta)$ in the prevailing state $\theta$.\hspace{\stretch{1}}\parencite[p.~591]{morris1998unique}
\end{quotation}
By solving out this government `optimal' strategy,
the speculators can ensure themselves of a certain abandonment of the peg,
for a sufficiently low observed $x$.
The authors proceed to derivde from this the main result of the paper, which is:
\begin{quotation}
	THEOREM 1: The is a unique $\theta *$ such that,
	in any equilibrium of the game with imperfect information,
	the government abandons the currency peg if and only if $\theta \leq \theta *$. \hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
\end{quotation}

\section{The Issues}
\label{unc:issues}
By introduction the idea of perceptions of other speculators' perceptions,
the authors give a more complete picture of such a currency attack.
It is thus very surprising that the outcome of their more realistic model,
corresponds less to reality and the more incomplete models.
That is to say, the nature of currency attacks does seem to be characterised by multiple equilibria.
This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.
It is therefore quite surprising that the more realistic leads to a the unrealistic situation of a unique equilibrium,
whereas the less intricate model gives us the more realistic multiple equilibria.

We itentify three issues with this model:
\begin{enumerate}
	\item The unique equilibrium does not apply to the entire `ripe for attack' region.
	\item The measure of risk replaces uncertainty, since previously there were no second-order perceptions.
	\item The model has the unrealistic assumption that distortion would be on a bounded uniform distribution.
\end{enumerate}
In the following subsections, we will describe these problems in more detail.

\subsection{The `Ripe for Attack' Region}
We can summarise the first problem with the model as follows:
\begin{enumerate}
	\item Multiple equilibria exist in the interval $(\underaccent{\bar}{\theta},\bar{\theta})$.
	\item The introduction of quantief risk, removes uncertainty with $2 \epsilon$ of $x$.
	\item Here $u(x,\theta) > 0$ leads to $\pi (x) = 1$.
	\item Authors claim that i.f.f. $x<k$ (the quantified-risk region) speculators will attack. 
	\item This is assumption does not follow from the model.
	\item Outside the quantified-risk area the previously existing uncertainty remains.
	\item Multiple equilibria remain possible here.
\end{enumerate}
Consider the statement of the authors:
\begin{quotation}
	For the next step,
	consider the strategy profile where every speculator attacks the currency if and only if
	the message $x$ is less than some fixed number $k$.
	\hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
\end{quotation}
The risk profile of the speculator is being redefined here.
In the first iteration of the model,
speculators might decide to the attack the currency without knowing what other investors would do.
In this second iteration,
speculators will only attack if they believe that there is a sufficient number of other speculators doing the same.
Yet in the first model, attacks were possible, in absense of this certainty.
It thus follows that speculators should be willing to attack the currency,
even in outside the quantified-risk region (which now provides certainty).

Secondly, the previously mentioned:
\begin{quotation}
	The unique optimal strategy for the government is then to abandon the exchange rate
	only if the observed fraction of deviators, $\alpha$,
	is greater than or equal to the critical mass $a(\theta)$
	in the prevailing state $\theta$.
	\hspace{\stretch{1}}\parencite[p.~591]{morris1998unique}
\end{quotation}
This should say ``...abandon the exchange rate \textit{always} if the observed fraction is great than or equal to...''.
Since quantified-risk region now gives the speculators certainty about the other speculators behavious,
this will now always lead to an sustainable attack.

However, as described above, outside of the new quantied-risk region, the old `ripe for attack region' remains.
In this region of multiple equilibria, currency attacks may be successful, or they may not be.

The condition the governments action is thus a sufficient, but not a necesarry one.

\subsection{Risk and Uncertainty}
The second problem is the most fundamental. The distortion measure is presented as a function that adds uncertainty.
If we differenciate between Knightian uncertainty and risk, then this is not true.

In relation to the first order effect,
the model introduces a quantifiable risk. (which is not the same as uncertainty)

What is more important, is the effect of this risk on the second-order expectations,
that is to say, a speculator's perception of other speculators perceptions.
In the first iteration of the model, there is no second-order expectation,
we are thus in a situation of Knightian uncertainty.
By introducing the quantifiable risk into the second iteration,
\textbf{and making speculators aware of the maximum magnitude of the distortion},
speculators can quantify second-order expectations.

Summierly, the introduction of the distortion, has two effects,
the first-order effect is moving from perfect information to risk,
the second-order effect is moving from uncertainty to risk.
It is this second order effect which leads to the surprising outcome of this model.

\subsection{A Bounded Uniform Distortion}
The third problem is relatively straightforward.
The assumption of a uniform distortion is unorthodox.
We would normally expect that these distortion would take the shape of e.g.~a normal distribution.
The effect of this is extremely relevant.
A uniform distribution is bounded,
which allows the distortion to the quantied with absolute certainty.
An unbounded distribution, such as the normal distribution,
would not allow a speculator to know the limit of other speculators perception,
with absolute certainty.

the equilibrium is most pronounced when the risk factor ($\epsilon$) is minimised (i.e.~set equal to zero),
as the authors state themselves. % FIND THIS CLAIM!!!!

\section{Conclusion}
\textcite{morris1998unique} presents a model for self-fulfilling currency attacks.
Under perfect information in the first order (and uncertainty in the second order),
this leads to a region of the state of economic fundamentals, where multiple equilibria are possible.
With a introduction of a quantified measure of distortion on the perception of this risk,
the authors claim that the model solves for a unique equilibrium.

We have identified three problems with this model and its outcomes.

Firstly, the new equilibrium, does not cover the entire previously existing multiple equilibria region.
Even though a larger part of the region (w.r.t.~the economic fundamentals) leads to a unique equilibrium,
a part of the old 'ripe for attack' region, remains subject to a situation of multiple equilibria.
It is only through two assumptions which do not follow from the model,
that this region also solves for a unique equilibrium.

Secondly, the most fundamental issue is the distinction between risk and uncertainty.
The first-order effect of the distortion is moving from perfect knowledge to a situation of quantifiable risk.
However, by making speculators aware of the maximum distortion,
they can now form expectations of other speculators expectations.
The second order effect, is thus moving from uncertainty to risk.
This is the driving mechanism behind the new equilibrium in \textbf{part of} the `ripe for attack' region.

Thirdly, the authors introduce a distortion which takes the form of a uniform distribution.
It is only due to the bounded nature of the uniform distribution,
that speculators are able to form bounded quantitative exectatations on other speculators expectations, with absolute certainty.
As mentioned above, it is this absolute certainty on the bounded quantifiable second-order expectations,
that drives the result.

In conclusion, we analyse the model introducted by \textcite{morris1998unique} and find that the results are driven by a second-order effect, as well as certain unjustifiable assumptions.

\nocite{taleb2010black}
\printbibliography
\end{refsection}

### 2013-12-16 uncertainty.tex
complete uncertainty, move to separate .tex file

@@
 \begin{refsection}
+\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
 
-\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
-\label{unc}
 \section*{Abstract}
-\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
-The self-fullfilling currency attack model which they propose thus has the suprising feature,
-that with the introduction of perception distorion, the multiple equilibria region, seems to solve to a single equilibrium.
-It is our contention that this is not a surpising result, 
-it a consequence of the second-order effect, where the risk factor replaces a previous existant, Knightian uncertainty.
-Furthermore, the quantified-risk only solves a certain part of the multiple equilibria region.
-Lastly, if we replace the somewhat stange assumption of a bounded uniform distribution of risk perceptions,
-with the more orthodox, normaly distribution, we cannot derive the same result.
+\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium in their model of self-fulfilling currency attacks.
+The currency attack model thus has the surprising feature, with the introduction of perception distortion, the multiple equilibria region seems to solve to a single equilibrium.
+It is our contention that this is not a surpising result, it a consequence of the second-order effect, where the risk factor replaces a previous existent, Knightian uncertainty.
+Previously, speculators had no expectations on other speculators expectations.
+Here, the risk factor replaces uncertainty, this is the main driver of the surprising result of the paper.
+Also, the new quantified-risk region only solves a certain part of the multiple equilibria region, not the whole of it.
+Lastly, if we replace the somewhat strange assumption of a bounded uniform distribution of risk perceptions, with the more orthodox, normal distribution, we cannot derive the same result.
 
@@
 \label{unc:idea}
-This paper addresses the issue multiple equilibria in models of currency attacks.
+\textcite{morris1998unique} addresses the issue of multiple equilibria in models of currency attacks.
 In situations of a currency peg, there is the possibility of a currency attack.
-Speculators will short the pegged currency, hoping the government will release the peg.
+Speculators are able to short the pegged currency, hoping the government will release the peg.
 If a sufficiently large proportion of the market participates in this,
@@
 This model is characterised by a situation where there is a stable, unstable,
-and a `ripe for attack' region (based on the economic fundamentals.
+and a `ripe for attack' region (based on the underlying economic fundamentals).
 The authors expand on the standard model by introducting second-order expectations.
@@
 
-\section{The introduction of risk (replacing uncertainty)}
+\section{The Introduction of Risk}
 The authors expand the model by introducing a measure of risk for fundamentals:
@@
 
-\subsection{The outcomes with risk}
+\subsection{The Outcomes with Risk}
 \label{unc:results}
@@
 \begin{quotation}
-	THEOREM 1: The is a unique $\theta *$ such that,
+	THEOREM 1: The is a unique $\theta^*$ such that,
 	in any equilibrium of the game with imperfect information,
-	the government abandons the currency peg if and only if $\theta \leq \theta *$. \hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
+	the government abandons the currency peg if and only if $\theta \leq \theta^*$. \hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
 \end{quotation}
+We will now discuss the issues we find in the derivation of this result.
 
@@
 By introduction the idea of perceptions of other speculators' perceptions,
-the authors give a more complete picture of such a currency attack.
-It is thus very surprising that the outcome of their more realistic model,
-corresponds less to reality and the more incomplete models.
-That is to say, the nature of currency attacks does seem to be characterised by multiple equilibria.
-This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.
-It is therefore quite surprising that the more realistic leads to a the unrealistic situation of a unique equilibrium,
-whereas the less intricate model gives us the more realistic multiple equilibria.
+the authors state a more realistic model of such a currency attack.
+It is thus very surprising that the outcome of their more realistic model
+corresponds less to reality, than the more incomplete models do.
+After all, in reality, currency attacks do seem to be characterised by multiple equilibria.
+This is also explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.
 
-We itentify three issues with this model:
+We believe that this is due to a number of issues in the derivation of the results,
+we itentify three issues with this model:
 \begin{enumerate}
@@
 
-Secondly, the previously mentioned:
+To illustrate this, consider the following. The risk factor has a magnitude $\epsilon$,
+where it is assumed that $\epsilon > 0$.
+However, if in stead we state that $\epsilon = 0$, we have eliminated the risk factor.
+By eliminating the risk factor, we return to a state of perfect information.
+Therefore, solving the second iteration of the model, with $\epsilon = 0$ should give us the same result as the first iteration.
+In stead, we find that we end again in a situation of unique equilibria.
+
+As a consequence of this we have the previously mentioned:
 \begin{quotation}
@@
 
-the equilibrium is most pronounced when the risk factor ($\epsilon$) is minimised (i.e.~set equal to zero),
-as the authors state themselves. % FIND THIS CLAIM!!!!
-
 \section{Conclusion}
@@
 
+\vspace{\stretch{1}}
+
 \nocite{taleb2010black}
 \printbibliography
+
 \end{refsection}

### 2013-12-24 PTD.tex
complete uncertainty, move to separate .tex file
add bitcoin attacks

@@
 \usepackage{mathtools}
+% \usepackage{times}
+\usepackage[utf8]{inputenc}
+% \usepackage[T1]{fontenc}
 \usepackage{rotating}
@@
 \usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
-\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
+\usepackage[hidelinks]{hyperref}
 
@@
 
+Recently there has been a shift towards more replication and further analysis of previously published results. E.g. \textcite{ioannidis2005most}.
+
 \printbibliography
@@
 
-\section{Analysis}
+\section{Identification Strategy
+\label{sa:identification}}
+The policy change, a natural experiment
+
+the ATET, etc.
+
+\subsection{The estimation using OLS}
+Our first estimation method uses OLS.
+
+\subsection{Difference in Differences}
+The estimation using diff-in-diff, its equivalence to fixed-effects, and how it is different when using T=3.
+
+\section{Obsolete: Analysis}
 \label{sa:analysis}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% UNCOMMENT TO INCLUDE THE ANDERSONVILLE CHAPTER!!!!!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \input{andersonville.tex}
-
 \input{uncertainty.tex}
@@
 \label{btc}
-In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
+In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
 This currency -the first of a group called cryptocurrencies- has the following economics features:
@@
 \printbibliography
+\end{refsection}
 
+\begin{refsection}
+\chapter{Bitcoin Attacks: Or how cryptocurrencies gain momentum}
+As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies.
+The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}.
+However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed.
+All of these cryptocurrencies are based to a large extend on the Bitcoin protocol, but often introduce small technological innovations.
+
+The most known of all of these alternative crypocurrencies is Litecoin.
+Litecoin introduces a number of small technological innovations, the most import of these is the change that the process of `mining' coins is 4 times faster, this has two consequences, transactions are approved faster than in the bitcoin protocol.
+It also means that the technological limit for the total number of Litecoins ever available is 4x times higher.
+For Bitcoin the technical limit is around 21 million Bitcoin, which is expected to be reached in the year 2140.
+For Litecoin, the limit is around 84 million bitcoin, which is also expected to be reached around this time.
+
+The key thing to note here is the perspective of the new cryptocurrecy adopt.
+Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer.
+The lower valued new cryptocurrency is technologically superior and thus more attractive.
+Most new cryptocurrencies do not gain momentum and their value is only trivialy more than zero.
+However, some currencies have gain momentum, the previously mentioned litecoin introduces a technological innovation and build it base on that.
+However, recently a new cryptocurrency has arisen and become quite popular.
+This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty.
+Dogecoin is a reference to an internet phenomenon called `Doge Meme'.
+Despite the fact that `Dogecoin' does not have a real reason for being considered valuable (in the sense that crypotocurrencies are considered valuable), however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable.
+We thus observe that from the perspective of economic and technological fundamentals, there is a situation of multiple equilibria.
+
+My idea is to adapt standard models of currency attacks such as in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models} to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies.
+Initially we would model how a currency can gain sufficient momentum to establish itself as a stably above zero.
+
+This could later be expended to a model with several cryptocurrencies competing for the investment of the same new cryptocurrency adopt, who is converting his/her fiat currency into one of several cryptocurrencies.
+
+\begin{figure}
+\caption{A Doge Meme}
+\label{doge}
+%\includegraphics[scale=0.8]{doge.jpg}
+\end{figure}
+
+\printbibliography
 \end{refsection}
@@
 
+\appendix
+
+% The Surviving Andersonville replication goes to the appendix
+% \input{andersonville.tex}
+
 \end{document}

### 2013-12-26 PTD.tex
break up chapters

@@
 
-\begin{refsection}
-\chapter{Introduction}
-\label{intro}
-In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
+\input{intro.tex}
 
-\begin{itemize}
-\item Additional South African Evidence on Pensions and Child Growth (\autoref{sa})
-% \item Replication: Surviving Andersonville (\ref{andersonville})
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{unc})
-\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{btc})
-\end{itemize}
-
-These project are in various stages of completion.
-Below I will briefly describe the research idea, the current state, and the potential for each project.
-
-Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds upon \textcite{duflo2000child, duflo2003grandmothers}.
-These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
-A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
-This paper makes use of a Household Survey from 2008, 2012 and 2013. The 
-urvey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
-As it stands now I have analysed the data from 2008 and 2012.
-The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
-I will discuss this in \autoref{sa}.
-
-% Furthermore, in \autoref{andersonville},
-% together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
-% We were able to replicate all results from the paper, save for a few decimal numbers,
-% which we have taken to be the result of rounding errors.
-
-% However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
-% When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
-% As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
-% The authors however, aggregate these two.
-% This leads to overstated magnitudes of the social ties of POWs.
-% This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
-% At this point our replication is quite complete.
-% Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
-
-\textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
-It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
-I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty.
-We thus gain information.
-I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
-This is done in \autoref{unc}.
-
-Lastly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
-Bitcoin transactions are conducted using an electronic process called signing.
-I would like to study the role of Bitcoin in remittances.
-For this I would like to participate in building Bitcoin applications for the type of simple phones common in developing economies (sometimes referred to a stupid phones).
-We could study the spread of bitcoin by looking at the downloads of the apps from regions,
-as well looking at how releasing the app in different languages evolves.
-
-After this the papers follow, in the order listed above.
-A separate citations section is included for each chapter.
-For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
-In the end notes (\autoref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
-I also mention some very preliminary ideas.
-
-Recently there has been a shift towards more replication and further analysis of previously published results. E.g. \textcite{ioannidis2005most}.
-
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{Pensions and Child Growth in South Africa}
-\label{sa}
-\section*{Abstract}
-In this paper I look at differences in child malnutrition levels depending on the gender of the recipient of income.
-
-I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of two surveys,
-which were done before and after the lowering of the pension eligibility age for men to the same age as women.
-
-The main preliminary finding is that the household effect was only significant in 2012.
-
-\section{Introduction}
-\label{sa:intro}
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa.
-The approach is very similar to \textcite{duflo2000child,duflo2003grandmothers}.
-The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status.
-
-The anthropometrics are useful for computing z-scores.
-These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
-
-The South African pension is a useful variable to measure income because of its criteria.
-Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
-The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
-
-This study deviates from the Duflo study in several ways.
-First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income,
-including pension recipient status.
-Whereas Duflo uses age as a proxy for recipient status.
-Secondly, between mid 2008 and the end of 2009 the pension age for men was gradualy lowered to sixty, which is at par with women.
-Another deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child} in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}.
-Since these have superseded the CDC charts, however this should not be of any consequence.
-
-The main preliminary result is that the household effect (i.e. having one or more recipients in the household),
-is very insignificant in the 2008 estimate.
-But in the 2012 estimate it is very significant.
-
-\section{Data}
-\label{sa:data}
-In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite[NIDS]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.
-
-The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South-African households.
-The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
-
-For adults several variables measure the different amounts and sources of income.
-Among those, a variable if the adult receives a state pension, and if so, how much.
-This is a numeric variable, the values of which lie very close together.
-For simplicity I have temporarily used this variable as a dummy.
-
-Children's anthropometrics are taken, these are length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
-However, I have computed the length-for-age z-scores manually.
-
-In 2006 the WHO published its standards for child growth \parencite{who2006child}.
-These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
-The standards provide the means and standards deviations used. 
-These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
-
-\section{Identification Strategy
-\label{sa:identification}}
-The policy change, a natural experiment
-
-the ATET, etc.
-
-\subsection{The estimation using OLS}
-Our first estimation method uses OLS.
-
-\subsection{Difference in Differences}
-The estimation using diff-in-diff, its equivalence to fixed-effects, and how it is different when using T=3.
-
-\section{Obsolete: Analysis}
-\label{sa:analysis}
-I perform three types of analysis.
-The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence)
-and then compare based on living in the household with an of-pension-eligible adult.
-Secondly, I use my computed z-scores and the data set provided variable which describes the actual pension received (or lack thereof).
-Lastly, I use this state pension variable to evaluate the z-scores provided in the dataset.
-
-The first type of analysis is almost identical to Duflo.
-Using an internation set of standard anthropometrics for healthy children between 6 and 60 months old, I standarize observed anthropometrics.
-I then construct a number of dummies of different ages and gender of the pension recipients.
-
-In the second analysis, I use the same z-scores I calculated for the Duflo method.
-However, here I use the state pension recipient variable provided by the NIDS data set.
-For simplicity I change the numerical variable to a dummy variable (as the benefits are virtually identical this is without much loss of information).
-
-This method uses the pre calculated z-scores from the data set and the state pension dummy.
-Unfortunately the 2012 z-scores are missing except for height-for-age.
-I therefore use only the height-for-age z-scores for the 2012 estimates.
-
-In all of these methods the z-scores can be compared on a number of properties.
-Firstly, the status of living in the same household as a state pension recipient or not is the first property to compare.
-Secondly, when living with a recipient,the effects of male and female recipients can be compared.
-Thirdly, the effects based on the gender of the child can be compared.
-
-\printbibliography
-\end{refsection}
+\input{south-africa.tex}
 

### 2013-12-26 intro.tex
break up chapters

\begin{refsection}
\chapter{Introduction}
\label{intro}
In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:

\begin{itemize}
\item Additional South African Evidence on Pensions and Child Growth (\autoref{sa})
% \item Replication: Surviving Andersonville (\ref{andersonville})
\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{unc})
\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{btc})
\end{itemize}

These project are in various stages of completion.
Below I will briefly describe the research idea, the current state, and the potential for each project.

Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds upon \textcite{duflo2000child, duflo2003grandmothers}.
These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
This paper makes use of a Household Survey from 2008, 2012 and 2013. The 
urvey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
As it stands now I have analysed the data from 2008 and 2012.
The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
I will discuss this in \autoref{sa}.

% Furthermore, in \autoref{andersonville},
% together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
% We were able to replicate all results from the paper, save for a few decimal numbers,
% which we have taken to be the result of rounding errors.

% However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
% When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
% As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
% The authors however, aggregate these two.
% This leads to overstated magnitudes of the social ties of POWs.
% This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
% At this point our replication is quite complete.
% Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.

\textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty.
We thus gain information.
I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
This is done in \autoref{unc}.

Lastly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
Bitcoin transactions are conducted using an electronic process called signing.
I would like to study the role of Bitcoin in remittances.
For this I would like to participate in building Bitcoin applications for the type of simple phones common in developing economies (sometimes referred to a stupid phones).
We could study the spread of bitcoin by looking at the downloads of the apps from regions,
as well looking at how releasing the app in different languages evolves.

After this the papers follow, in the order listed above.
A separate citations section is included for each chapter.
For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
In the end notes (\autoref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
I also mention some very preliminary ideas.

Recently there has been a shift towards more replication and further analysis of previously published results. E.g. \textcite{ioannidis2005most}.

\printbibliography
\end{refsection}

### 2013-12-26 south-africa.tex
break up chapters

@@
-\documentclass[draft.tex]{subfiles}
+\begin{refsection}
+\chapter{Pensions and Child Growth in South Africa}
+\label{sa}
+\section*{Abstract}
+In this paper I look at differences in child malnutrition levels depending on the gender of the recipient of income.
 
-\begin{document}
+I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
+This paper exploits the fact that the data set consists of three surveys,
+one of which was done before the lowering of the pension eligibility age for men to the same age as women,
+and two after.
 
-\chapter{Additional South African Evidence on Pensions and Child Growth}
-
-\section{Abstract}
-
-In this paper I look at the effect of the gender of pension recipients
-on the growth of children in the same households.
-
-I do this by comparing z-scores of anthropometrics of South African
-children living in the same household as state pension recipients. This
-paper exploits the fact that the data set consists of two surveys which
-were done before and after the lowering of the pension eligibility age
-for men to the same age as women.
-
-The main preliminary finding is that the household effect was only
-significant in 2012.
+The main preliminary finding is that the household effect was only significant in 2012.
 
 \section{Introduction}
+\label{sa:intro}
+This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa.
+The approach is very similar to \textcite{duflo2000child,duflo2003grandmothers}.
+The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for weight-for-height and length-for-age are computed as z-scores.
+These are then compared for different pension recipient status.
 
-This paper looks at the effect of the gender of pension recipients on
-the growth of children in their household in South Africa. The approach
-is very similar to Duflo
-(\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}).
-The deviation from international standards
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for
-weight-for-height and length-for-age are computed as z-scores. These are
-then compared for different pension recipient status.
+The anthropometrics are useful for computing z-scores.
+These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
 
-The anthropometrics are useful for computing z-scores. These z-scores
-are considered a good representation of short-term or long-term
-malnutrition respectively, especially for children between 6 and 60
-months old.
+The South African pension is a useful variable to measure income because of its criteria.
+Besides a maximum level of income, the only criterium is the age of a person.
+Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
+The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
 
-The South African pension is a useful variable to measure income because
-of its criteria. Besides a maximum level of income, the only criterium
-is the age of a person. Because of this the status as a recipient is
-quite exogenous and there are few selection bias problems. The
-problematic difference between the eligibility age of men and women was
-eliminated between the two surveys which creates an interesting natural
-experiment.
+This study deviates from the Duflo study in several ways.
+First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income,
+including pension recipient status.
+Whereas Duflo uses age as a proxy for recipient status.
+Secondly, between mid 2008 and the end of 2009 the pension age for men was gradualy lowered to sixty, which is at par with women.
+Another deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child} in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}.
+Since these have superseded the CDC charts, however this should not be of any consequence.
 
-Duflo finds evidence in South Africa's 1993
-\href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated
-Household Survey} that girls' short term nutrition (weight-for-height)
-was positively influence by living with the maternal grandmother if the
-grandmother was eligible for a state pension. This is directly after the
-significant increase in the pension sum for blacks. The
-pension-eligibility age at this time was 60 for women and 65 for men.
-
-This study deviates from the Duflo study in several ways. In 2008 and
-2012 the first and second wave of the
-\href{http://www.nids.uct.ac.za/home/}{National Income Dynamics Study}
-have gathered similar data. In the period 2008-2010, the government
-lowered the eligibility age for men from 65 to 60
-(\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
-
-This happened in a few steps. As of July 16th 2008 men aged 63 and 64
-were eligible for a pension. Men aged 61 and 62 became eligible in April
-2009. Finally in January 2010, pension eligibility age was at 60 for all
-citizens.
-
-Another deviation is the usage of
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} in
-stead of CDC's, since these have superseded the CDC charts, however this
-should not be of any consequence.
-
-The main preliminary result is that the household effect (i.e.~having
-one or more recipients in the household) is very insignificant in the
-2008 estimate. But in the 2012 estimate it is very significant.
+The main preliminary result is that the household effect (i.e. having one or more recipients in the household),
+is very insignificant in the 2008 estimate.
+But in the 2012 estimate it is very significant.
 
 \section{Data}
+\label{sa:data}
+In this paper I use data from two sources.
+The first is the South African National Income Dynamics Survey \parencite[NIDS]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.
 
-In this paper I use data from two sources. The first is the South
-African National Income Dynamics Survey and the second is the World
-Health Organization's Child Growth Standards
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.
+The main source of data is the NIDS.
+This survey collects data on a representative set of appproximately 10,000 South-African households.
+The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
 
-The main source of data is the NIDS. This survey collects data on a
-representative set of appproximately 10,000 South African households.
-The primary information types I use are, the child anthropometrics, the
-age and gender of household members, and the status as state pension
-recipients.
+For adults several variables measure the different amounts and sources of income.
+Among those, a variable if the adult receives a state pension, and if so, how much.
+This is a numeric variable, the values of which lie very close together.
+For simplicity I have temporarily used this variable as a dummy.
 
-For adults several variables measure the different amounts and sources
-of income. Among those, a variable if the adult receives a state
-pension, and if so, how much. This is a numeric variable, the values of
-which lie very close together. For simplicity I have temporarily used
-this variable as a dummy.
+Children's anthropometrics are taken, these are length/height, weight, and waist.
+Using these anthropometics and WHO growth standards, z-scores have been calculated.
+Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
+However, I have computed the length-for-age z-scores manually.
 
-Children's anthropometrics are taken, these are length/height, weight,
-and waist. Using these anthropometics and WHO growth standards, z-scores
-have been calculated. Unfortunately wave 2 (2012) accidentally omitted
-the z-scores, so that these cannot be evaluated until an updated version
-is published. However, I have computed the length-for-age z-scores
-manually.
+In 2006 the WHO published its standards for child growth \parencite{who2006child}.
+These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
+The standards provide the means and standards deviations used. 
+These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
 
-In 2006 the WHO published its standards for child growth
-\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}. These
-standards are based on the scores of children from different ethnic
-populations in households which observed a healthy lifestyle. The
-standards provide the means and standards deviations used. These are on
-a monthly basis for height-for-age, and on a semi-centimeter level for
-weight-for-height scores.
+\section{Identification Strategy
+\label{sa:identification}}
+The policy change, a natural experiment
 
-\texttt{\{r, include=FALSE\} load("w1w2.RData") library(sem) library(ggplot2)}
+the ATET, etc.
 
-\texttt{\{r\} p1 \textless{}- ggplot(subset(w1\_child,w1\_woman\_60 == 1), aes(w1\_c\_age\_m, w1\_zhfa, colour=factor(w1\_c\_woman))) p1 + stat\_smooth(method="loess")\# + geom\_point()}
+\subsection{The estimation using OLS}
+Our first estimation method uses OLS.
 
-\section{Results}
+\subsection{Difference in Differences}
+The estimation using diff-in-diff, its equivalence to fixed-effects, and how it is different when using T=3.
 
-Basic HAZ (2008). \texttt{\{r\} summary(w1\_haz0)}
+\section{Obsolete: Analysis}
+\label{sa:analysis}
+I perform three types of analysis.
+The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence)
+and then compare based on living in the household with an of-pension-eligible adult.
+Secondly, I use my computed z-scores and the data set provided variable which describes the actual pension received (or lack thereof).
+Lastly, I use this state pension variable to evaluate the z-scores provided in the dataset.
 
-HAZ 2008, with 2012 eligiblity as an IV
-\texttt{\{r\} summary(tsls\_w1w2\_haz0)}
+The first type of analysis is almost identical to Duflo.
+Using an internation set of standard anthropometrics for healthy children between 6 and 60 months old, I standarize observed anthropometrics.
+I then construct a number of dummies of different ages and gender of the pension recipients.
 
-HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-\texttt{\{r\} summary(tsls\_w1w2\_haz1)}
+In the second analysis, I use the same z-scores I calculated for the Duflo method.
+However, here I use the state pension recipient variable provided by the NIDS data set.
+For simplicity I change the numerical variable to a dummy variable (as the benefits are virtually identical this is without much loss of information).
 
-\end{document}
+This method uses the pre calculated z-scores from the data set and the state pension dummy.
+Unfortunately the 2012 z-scores are missing except for height-for-age.
+I therefore use only the height-for-age z-scores for the 2012 estimates.
+
+In all of these methods the z-scores can be compared on a number of properties.
+Firstly, the status of living in the same household as a state pension recipient or not is the first property to compare.
+Secondly, when living with a recipient,the effects of male and female recipients can be compared.
+Thirdly, the effects based on the gender of the child can be compared.
+
+\printbibliography
+\end{refsection}

### 2013-12-28 PTD.tex
add results, rewrite data section

@@
 \tableofcontents
-% \listoftables
-% \listoffigures
 
@@
 
-\begin{refsection}
-\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
-\label{btc}
-In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
-This currency -the first of a group called cryptocurrencies- has the following economics features:
+\input{bitremit.tex}
 
-\begin{itemize}
-\item public transactions
-\item anonymous addresses
-\item fixed amount of units
-\item high granularity (1 Bitcoin = 100,000,000 Satoshi)
-\item no or low transaction costs
-\end{itemize}
+\input{bitattack.tex}
 
-An addition to these economic features, the key feature of Bitcoin is decentralisation.
-All transactions are kept in a public ledger called the blockchain. An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
-Conflict resolution, in this system, is done through majority consensus of blockchain copy holders.
-
-There are a number of features which make Bitcoin attractive for remittances.
-Firstly, the low transaction costs are a huge step up from the current facilitators, which charge high percentages.
-Secondly, government intervention (especially in the recipient country) is prevented by the anonymity.
-Thirdly, recipients can choose to keep their remittance in a currency which is not controlled by their government.
-Fourthly, the granularity ensures very small transactions can be conducted.
-
-Bitcoin initially because popular in advanced economies such as those in Europe and North America.
-However, since mid 2013 there has been a large shift towards developing economies,
-in which comparative advantages of Bitcoin are more pronounced.
-For example, since its inception, Mt.Gox (located in Japan) was the largest Bitcoin exchange (marketplace), however in October 2013, Mt.Gox was overtaken by a Chinese exchange.
-
-Bitcoin transactions are conducted by the electronic `signing' of a transaction.
-This is a very simple electronic process.
-Currently many smartphone apps are available to this purpose.
-However, in the targeted developing economies, many phones are not smartphones, the vast majority using Nokia Operating System (Nokia OS).
- These phone can also run applications, using the Java Mobile App platform. Currently there are no Bitcoin apps available for this platform.
-
-I propose to participate in the development of open-source applications which would enable the users of stupid phones.
-We can then exploit the temporal difference when releasing the applications in different languages at different times,
-as well the downloads from traceable IP addresses.
-
-\section{Data}
-\label{btc:data}
-Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
-Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
-Much like the way bank clients have a claim to their money, which is in the bank's vault.
-
-Therefore Bitcoin purchases at exchanges do not lead to transaction being recorded in the blockchain.
-Since the Bitcoins remain in the Exchange's wallet, the only thing which changes is the claims of the clients.
-
-\begin{itemize}
- \item The blockchain (public ledger)
- \begin{itemize}
- 	\item IP address
- 	\item Language of transaction notice
- 	\item Transaction times
- \end{itemize}
- \item The exchanges
- \begin{itemize}
- 	\item Location of exchanges
- 	\item Transaction costs for each currency
-	\item The order books
-	\item Transaction times
- 	\item The traded currency
- \end{itemize}
- \item Software
- \begin{itemize}
- 	\item Downloads
- 	\item Translation contributions (?)
- 	\item Connections to server
- \end{itemize}
-\end{itemize}
-
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{Bitcoin Attacks: Or how cryptocurrencies gain momentum}
-As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies.
-The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}.
-However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed.
-All of these cryptocurrencies are based to a large extend on the Bitcoin protocol, but often introduce small technological innovations.
-
-The most known of all of these alternative crypocurrencies is Litecoin.
-Litecoin introduces a number of small technological innovations, the most import of these is the change that the process of `mining' coins is 4 times faster, this has two consequences, transactions are approved faster than in the bitcoin protocol.
-It also means that the technological limit for the total number of Litecoins ever available is 4x times higher.
-For Bitcoin the technical limit is around 21 million Bitcoin, which is expected to be reached in the year 2140.
-For Litecoin, the limit is around 84 million bitcoin, which is also expected to be reached around this time.
-
-The key thing to note here is the perspective of the new cryptocurrecy adopt.
-Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer.
-The lower valued new cryptocurrency is technologically superior and thus more attractive.
-Most new cryptocurrencies do not gain momentum and their value is only trivialy more than zero.
-However, some currencies have gain momentum, the previously mentioned litecoin introduces a technological innovation and build it base on that.
-However, recently a new cryptocurrency has arisen and become quite popular.
-This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty.
-Dogecoin is a reference to an internet phenomenon called `Doge Meme'.
-Despite the fact that `Dogecoin' does not have a real reason for being considered valuable (in the sense that crypotocurrencies are considered valuable), however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable.
-We thus observe that from the perspective of economic and technological fundamentals, there is a situation of multiple equilibria.
-
-My idea is to adapt standard models of currency attacks such as in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models} to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies.
-Initially we would model how a currency can gain sufficient momentum to establish itself as a stably above zero.
-
-This could later be expended to a model with several cryptocurrencies competing for the investment of the same new cryptocurrency adopt, who is converting his/her fiat currency into one of several cryptocurrencies.
-
-\begin{figure}
-\caption{A Doge Meme}
-\label{doge}
-%\includegraphics[scale=0.8]{doge.jpg}
-\end{figure}
-
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{End notes}
-\label{end-notes}
-In the previous chapters I have presented my current research projects.
-These projects are in various stages of completions.
-
-I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey,
-done before and after a highly relevant policy change.
-Especially since the methodology and location are the same as in \textcite{duflo2000child, duflo2003grandmothers}.
-In addition to this there is now a third data wave which has become available.
-This provides us with more data, and mostly the opportunity to use more interesting methodology.
-The text of the paper still has to be written.
-
-% The replication of Surviving Andersonville is already completed in term of the replication in Stata.
-% We would like to redo the analysis in R \parencite{R}.
-% The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
-% The findings of this replication can summarised as:
-
-%\begin{quote}
-%``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
-It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
-This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
-%\end{quote}
-
-% We do not expect to find anything similar to Bell and Miller,
-% but think that it can nevertheless be interesting to replicate findings using a different software package.
-% In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
-% In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
-
-The discussion of \textcite{morris1998unique} is in a very early stage.
-I have looked at the paper in detail, I have also done a brief analysis of my main critique,
-namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
-However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
-In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.
-
-Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin.
-I would like to analyse the spread of this.
-I propose to follow the spread of applications for platforms which are popular in developing economies.
-
-At this point, three out of four of the previously discussed research projects are some form of a replication of prior work.
-As replications they are mostly critiques of others' work, rather than constructive ideas.
-This is mostly a result of the fact that these projects progress faster.
-For this reason, these research projects have progressed more than the projects which are primarily based on my own ideas.
-However, it is my attention to shift the focus of my thesis to include more original work.
-Here I present two more ideas which are too preliminary to include in the main body of the text, but are based on my own work.
-
-Firstly, I was in charge of setting up a baseline diagnostic into security perceptions in Conakry, Guinea.
-This diagnostic will be used to analyse the impact of a police reform conducted here.
-The reform constitutes of the implementation of a model of `police de proximitee'.
-The baseline consist of 4500 interviews using smartphones in the comune of Conkary as well a large number of interviews in N'Zerekore (east Guinea).
-Some time after the implementation of the police reform as follow up study will be conducted.
-I propose to conduct an impact evaluation using the results from the studies in which I have taken and will take part.
-
-Secondly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy.
-I would like to write one paper about an issue relating to this.
-In particular I would like to at the effect of outliers.
-The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}.
-I would like to see how these principles affect research in development microeconomics.
-
-In this document I have tried to give a description of my research projects.
-None of these projects are near completion and many are in fact in a very early stage.
-The purpose of this has been to describe the direction I am taking with my thesis, and to receive feedback on this.
-As a result of this being work in progress, the articles are still incomplete, this includes lacking the proper attribution of ideas using citations.
-
-\printbibliography
-\end{refsection}
+\input{endnotes.tex}
 

### 2013-12-28 south-africa.tex
add results, rewrite data section

@@
 This study deviates from the Duflo study in several ways.
+% MAIN DEVIATION, PANEL NATURAL EXPERIMENT
 First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income,
@@
 
-The main preliminary result is that the household effect (i.e. having one or more recipients in the household),
-is very insignificant in the 2008 estimate.
-But in the 2012 estimate it is very significant.
+% THE IMPERTUS FOR THE PAPER IS THE GENDER IN CCTs and OPTIMAL DESIGN
+% RELATES TO THE ISSUE OF HOUSEHOLD AS A UNIT
+% THEY ARE NO LONGER THAT RARE IN DEVELOPING COUNTRIES ???
+
+% HISTORY OF APARTHEID AND CHANGE IN PENSION SCHEME
+
+% STATE THE MAIN RESULT
 
@@
 \label{sa:data}
+% DESCRIPTIVE STATISTICS OF THE DATASET AND POSSIBLY THE GROWTH STANDARDS
 In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite[NIDS]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.
+The first is the South African National Income Dynamics Survey \parencite[NIDS][]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.
 
-The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South-African households.
-The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
+\subsection{South Africa: National Income Dynamics Survey}
+The main source of data is the National Income Dynamics Survey of South Africa \parencite{saldru2008nids, saldru2012nids, saldru2013nids}.
+This survey collects data on a representative set of appproximately 10,000 South-African households over time.
+The primary information types I use are:
+\begin{itemize}
+  \item child anthropometrics,
+  \item child age (in days)
+  \item adult pension recipient status
+  \item adult pension recipient gender
+\end{itemize}
 
@@
 Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
-However, I have computed the length-for-age z-scores manually.
 
+\subsection{WHO: Child Growth Standards}
 In 2006 the WHO published its standards for child growth \parencite{who2006child}.
-These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
-The standards provide the means and standards deviations used. 
-These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
+These standards measure the difference between a child's anthropometrics
+standardised against an ideal score.
 
-\section{Identification Strategy
-\label{sa:identification}}
-The policy change, a natural experiment
+Z-score anthropometrics are used since they are considered to be a good representation of a child's health,
+and by extension, the household in which they grow up.
+These ideal scores are based on a sample of children from different ethnic populations,
+in households which observed a healthy lifestyle.
+Any health issues, such as malnutrition or disease will affect these metrics,
+by causing the child to be shorter or lighter.
+However, it is impossible to distinquish between the causes of an observed slow growth.
 
-the ATET, etc.
+We stay with the best practice of using only metrics for children between the ages of 6 months and 60 months.
 
-\subsection{The estimation using OLS}
-Our first estimation method uses OLS.
+In general, can distinquish between two types of anthropometric z-scores, the age-based z-scores and the height-based z-scores.
+Whereby `based' refers to the reference point at which anthropometrics are standardised.
+
+\subsubsection{Age-Based Z-scores}
+The age-based z-scores are the Height-for-Age Z-score (HAZ) and the Weight-for-Age Z-score (WAZ).
+Since these metrics are age-based, they provide information about all past growth issues,
+any past issues such a malnutrition and disease will have impaired growth,
+and these effects will still be captured by today's height.
+
+The age-based z-scores are constructed on a weekly basis up to the age of 60 months, and on a monthly basis thereafer.
+
+\subsubsection{Height-Based Z-scores}
+The height-based z-scores are the Weight-for-Height Z-score (WHZ)
+and Body Mass Index Z-score (BMIZ).
+Where the BMI (or Quetelet) is a transformed version of the WHZ, which has a quadratic height effect.
+The equation for BMI is:
+\[
+\textbf{BMI} = \frac{\textbf{weight(kg)}}{\textbf{height(m)}^2}
+\]
+
+These scores compare children with others of the same height, irrispective of their age.
+As a results we only observe the relatively short-term effect of weight.
+The height-based metrics thus provide is with a short-term insight.
+
+The height-based z-scores are available on a semi-centimeter level throughout all heights.
+
+\subsection{Data Structure}
+The NIDS uses a file and data structure which is ill suied for panel data analysis.
+We therefore transform the data to a format which is more conducive to our analysis.
+In doing so, we try to stay as close as possible to the`Tidy data' structure, as described in \textcite{wickham2014tidy}.
+This is easiest using the R package `Reshape2' by the same author \parencite[Reshape2 implementation]{wickham2007reshaping}.
+
+\section{Research Design}
+\label{sa:identification}
+% The policy change, a natural experiment
+
+\subsection{Ordinary Least Squares}
+We first perform an Ordinary Least Squares estimation (OLS).
+This is done using the linear model (lm) procedure from the R package `Base' \parencite{R}.
 
 \subsection{Difference in Differences}
-The estimation using diff-in-diff, its equivalence to fixed-effects, and how it is different when using T=3.
+In order to fully exploit the available data and the policy change,
+we also employ a `Difference-in-Differences' estimator (DiD).
+This estimator operationalised by using the fixed-effects (within) estimator, with a time-effect\footnote{The time effect estimated here is symmetric to the individual effect.
+We use the term `time effect', since this is a more meaningful description of the policy change.}.
 
-\section{Obsolete: Analysis}
-\label{sa:analysis}
-I perform three types of analysis.
-The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence)
-and then compare based on living in the household with an of-pension-eligible adult.
-Secondly, I use my computed z-scores and the data set provided variable which describes the actual pension received (or lack thereof).
-Lastly, I use this state pension variable to evaluate the z-scores provided in the dataset.
+We perform the estimations using the R package `PLM' \parencite[see][]{croissant2008panel}.
+It is worth noting  that questions have been raised about the Difference-in-Difference estimator being employed in certain situations,
+for example by (ironically) \textcite{bertrand2004much}.
 
-The first type of analysis is almost identical to Duflo.
-Using an internation set of standard anthropometrics for healthy children between 6 and 60 months old, I standarize observed anthropometrics.
-I then construct a number of dummies of different ages and gender of the pension recipients.
+\subsubsection{Formal DiD Specification}
+% ATET etc.
 
-In the second analysis, I use the same z-scores I calculated for the Duflo method.
-However, here I use the state pension recipient variable provided by the NIDS data set.
-For simplicity I change the numerical variable to a dummy variable (as the benefits are virtually identical this is without much loss of information).
+\section{Results}
+In \autoref{sa:hazwaz} we present our estimation results for the age-based z-scores,
+and in \autoref{sa:whzbmiz} we present our estimation results for the height-based z-scores.
 
-This method uses the pre calculated z-scores from the data set and the state pension dummy.
-Unfortunately the 2012 z-scores are missing except for height-for-age.
-I therefore use only the height-for-age z-scores for the 2012 estimates.
+% LaTeX table created manually
+% Fri Dec 27 23:22:00 2013
+\begin{table}[h!]
+\centering
+\caption{Estimation Results: HAZ \& WAZ}
+\label{sa:hazwaz}
+\begin{tabular}{l|rrr|rrr}
+% \hline
+& \multicolumn{3}{c}{Height for Age Z-score} & \multicolumn{3}{c}{Weight for Age Z-score}\\
+\hline
+specification & 1 & 2 & 3 & 1 & 2 & 3\\
+\hline
+w\_spen\_m & 0.2366 & *0.8228 & 0.7908 & 0.2366 & 0.2981 & 0.4780 \\
+w\_spen\_w & -0.2331 & 0.1053 & 0.1072 & -0.2331 & -0.3112 & -0.3280 \\
+elig.men.60 & & **-0.3419 & **-0.3465 & & ***-0.3475 & **-0.3243 \\
+w\_spen\_m1:elig.men.60 & & & 0.0446 & & & -0.2545 \\
+% \hline
+w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 \\
+\end{tabular}
+\end{table}
 
-In all of these methods the z-scores can be compared on a number of properties.
-Firstly, the status of living in the same household as a state pension recipient or not is the first property to compare.
-Secondly, when living with a recipient,the effects of male and female recipients can be compared.
-Thirdly, the effects based on the gender of the child can be compared.
+% LaTeX table created manually
+% Fri Dec 27 23:53 2013
+\begin{table}[h!]
+\centering
+\caption{Estimation Results: WHZ \& BMIZ}
+\label{sa:whzbmiz}
+\begin{tabular}{l|rrr|rrr}
+& \multicolumn{3}{c}{Weight for Height Z-score} & \multicolumn{3}{c}{Body Mass Index Z-score}\\
+\hline
+specification & 1 & 2 & 3 & 1 & 2 & 3 \\
+\hline
+w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 & *-0.8058 & *-0.7905 & *-1.0226 \\
+w\_spen\_w & 0.0655 & 0.0371 & 0.0478 & -0.1592 & -0.1956 & -0.1742 \\
+elig.men.60 & & -0.1417 & -0.1574 & & -0.1674 & -0.2049 \\
+w\_spen\_m1:elig.men.60 & & & 0.1484 & & & 0.3407 \\
+w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & 0.0000 & 0.0000
+\end{tabular}
+\end{table}
+
+\subsection{Robustness Checks}
+
+\subsubsection{OLS Robustness}
+
+\subsubsection{DiD Robustness}
+% HAUSMAN TEST FOR FE / RE
+
+\section{Conclusion}
 

### 2013-12-28 uncertainty.tex
add bitcoin attacks
add results, rewrite data section

@@
 \chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
+\label{unc}
 
@@
 
-\section{The Idea}
+\section{The Paper}
 \label{unc:idea}
@@
 
-\subsection{The possible outcomes}
+\subsection{The Possible Outcomes}
 When we set \autoref{unc:specPO} and \autoref{unc:govPO} equal to zero,

### 2013-12-28 bitattack.tex
break away chapters

\begin{refsection}
\chapter{Bitcoin Attacks: Or How Cryptocurrencies Gain Momentum}
As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies. The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}. However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed. All of these cryptocurrencies are based to a large extend on the Bitcoin protocol, but often introduce small technological innovations.

The most known of all of these alternative crypocurrencies is Litecoin. Litecoin introduces a number of small technological innovations, the most import of these is the change that the process of `mining' coins is 4 times faster, this has two consequences, transactions are approved faster than in the bitcoin protocol. It also means that the technological limit for the total number of Litecoins ever available is 4x times higher. For Bitcoin the technical limit is around 21 million Bitcoin, which is expected to be reached in the year 2140. For Litecoin, the limit is around 84 million bitcoin, which is also expected to be reached around this time.

The key thing to note here is the perspective of the new cryptocurrecy adopt. Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer. The lower valued new cryptocurrency is technologically superior and thus more attractive. Most new cryptocurrencies do not gain momentum and their value is only trivialy more than zero. However, some currencies have gain momentum, the previously mentioned litecoin introduces a technological innovation and build it base on that. However, recently a new cryptocurrency has arisen and become quite popular. This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty. Dogecoin is a reference to an internet phenomenon called `Doge Meme'. Despite the fact that `Dogecoin' does not have a real reason for being considered valuable (in the sense that crypotocurrencies are considered valuable), however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable. We thus observe that from the perspective of economic and technological fundamentals, there is a situation of multiple equilibria.

My idea is to adapt standard models of currency attacks such as in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models} to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies. Initially we would model how a currency can gain sufficient momentum to establish itself as a stably above zero.

This could later be expended to a model with several cryptocurrencies competing for the investment of the same new cryptocurrency adopt, who is converting his/her fiat currency into one of several cryptocurrencies.

\begin{figure}
\caption{A Doge Meme}
\label{doge}
%\includegraphics[scale=0.8]{doge.jpg}
\end{figure}

\printbibliography
\end{refsection}

### 2013-12-28 bitremit.tex
break away chapters

--- 2013-11-22 draft.tex
@@
-\documentclass[a4paper]{report}\usepackage{graphicx, color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
-\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
-\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
-\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
-\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
-\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
-\newcommand{\hlslot}[1]{\textit{#1}}%
-\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\usepackage{mathtools}
-\usepackage{rotating}
-\usepackage{graphicx}
-\usepackage{cleveref}
-\usepackage[authordate,backend=biber]{biblatex-chicago}
-\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
-
-\title{Preliminary Thesis Defence\\~\\
-\begin{tabular}{rl}
-Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
-Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
-\end{tabular}
-}
-
-\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}\\~\\
-The Graduate Institute, Geneva}
-
-\let\oldmarginpar\marginpar
-\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]
-{\raggedright\footnotesize #1}}
-
-\addglobalbib{bibliography.bib}
-
-\newbibmacro{string+doiurlisbn}[1]{%
-  \iffieldundef{doi}{%
-    \iffieldundef{url}{%
-      \iffieldundef{isbn}{%
-        \iffieldundef{issn}{%
-          #1%
-        }{%
-          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
-        }%
-      }{%
-        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
-      }%
-    }{%
-      \href{\thefield{url}}{#1}%
-    }%
-  }{%
-    \href{http://dx.doi.org/\thefield{doi}}{#1}%
-  }%
-}
-
-\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
-\DeclareFieldFormat[article,incollection]{title}%
-    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
-\begin{document}
-
-\maketitle
-\tableofcontents
-\listoftables
-\listoffigures
-
-\begin{refsection}
-\chapter{Introduction}
-In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
-
-\begin{itemize}
-\item Additional South African Evidence on Pensions and Child Growth (\ref{south-africa})
-\item Replication: Surviving Andersonville (\ref{andersonville})
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\ref{currency})
-\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\ref{bitcoin})
-\end{itemize}
-
-These project are in various stages of completion. Below I will briefly describe the research idea, the current state, and the potential for each project.
-
-Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}.
-These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
-A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
-This paper makes use of a Household Survey from 2008, 2012 and 2013.
-The survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
-As it stands now I have analysed the data from 2008 and 2012.
-The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
-
-Secondly, together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
-We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors.
-However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
-When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
-As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
-The authors however, aggregate these two.
-This leads to overstated magnitudes of the social ties of POWs.
-This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
-At this point our replication is quite complete.
-Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
-
-Thirdly, \textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
-It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
-I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty.
-We thus gain information.
-I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
-
-Fourthly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies.
-Bitcoin transactions are conducted using an electronic process called signing.
-I would like to study the role of Bitcoin in remittances.
-For this I would like to participate in building Bitcoin applications for the simple type of phones common in developing economies (sometimes referred to stupid phones).
-We could study the spread of bitcoin by looking at the downloads of the apps from regions, as well looking at how releasing the app in different languages evolves.
-
-After this the papers follow, in the order listed above.
-A separate citations section is included for each chapter.
-For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
-In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
-I also mention some very preliminary ideas.
-
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{Pensions and Child Growth in South Africa}
-\label{south-africa}
-\section*{Abstract}
-
-In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.
-
-I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.
-
-The main preliminary finding is that the household effect was only significant in 2012.
-
-\section{Introduction}
-
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
-is very similar to \textcite{duflo2000, duflo2003}.
-The deviation from international standards \parencite{who2006child} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status and gender.
-
-The anthropometrics are useful for computing z-scores.
-These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
-
-The South African pension is a interesting variable to measure income because of its criteria.
-Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias issues.
-The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
-
-Duflo finds evidence in South Africa's 1993 \href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated Household Survey} that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension.
-This is directly after the significant increase in the pension sum for blacks.
-The pension-eligibility age at this time was 60 for women and 65 for men.
-
-This study deviates from the Duflo study in several ways.
-In 2008 and 2012, the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
-In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
-
-This happened in a few steps.
-As of July 16th 2008 men aged 63 and 64 were eligible for a pension.
-Men aged 61 and 62 became eligible in April 2009.
-Finally in January 2010, pension eligibility age was at 60 for all citizens.
-
-Another deviation is the usage of WHO z-scores \parencite{who2006child} in stead of CDC z-scores \parencite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence, as long as we use the same standards consistently.
-
-The main preliminary result is that the household effect (i.e.~having one or more recipients in the household) is very insignificant in the 2008 estimate.
-But in the 2012 estimate it is very significant.
-
-\section{Data}
-
-In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \parencite{who2006child}.
-
-The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South African households.
-The primary information variables that I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
-
-For adults, several variables measure the different amounts and sources of income.
-Among those, a variable for the adult receiving a state pension, and if so, how much.
-This is a numeric variable, the values of which lie very close together.
-For simplicity I have temporarily used this variable as a dummy.
-
-The children's anthropometrics taken are, length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately, the latest version of wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
-However, I have computed the length-for-age z-scores manually.
-
-In 2006 the WHO published its standards for child growth.
-These standards are based on the scores of children from different ethnic populations in households which maintained a healthy lifestyle.
-The standards provide the means and standards deviations used.
-These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1))
-p1 <- p1 + \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman))
-p1 <- p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
-p1
-\end{alltt}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 324 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 263 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 51 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 638 rows containing missing values (geom\_point).}}\end{kframe}
-\includegraphics[width=\maxwidth]{figure/r-p1}
-
-\end{knitrout}
-
-\section{Results}
-
-Basic HAZ (2008)
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(w1_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-## Call:
-## lm(formula = w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + 
-##     w1_best_age_yrs, data = w1_child, subset = w1_c_age_m >= 
-##     6 & w1_c_age_m <= 60)
-## 
-## Residuals:
-##    Min     1Q Median     3Q    Max 
-## -4.779 -1.036 -0.169  0.834  7.060 
-## 
-## Coefficients:
-##                  Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.43e+00   1.44e-01   -9.87   <2e-16 ***
-## w1_spen_w        2.32e-02   1.15e-01    0.20   0.8402    
-## w1_spen_m        1.36e-01   1.72e-01    0.79   0.4281    
-## w1_h_tinc        3.62e-05   9.99e-06    3.62   0.0003 ***
-## w1_best_edu      1.63e-03   7.84e-03    0.21   0.8355    
-## w1_best_age_yrs  7.61e-03   3.64e-03    2.09   0.0369 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.77 on 1436 degrees of freedom
-##   (1936 observations deleted due to missingness)
-## Multiple R-squared:  0.0134,	Adjusted R-squared:  0.00994 
-## F-statistic: 3.89 on 5 and 1436 DF,  p-value: 0.00164
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.835  -0.050   0.000   0.788   7.070 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.172e+00  7.388e-02 -15.861  < 2e-16 ***
-## w1_spen_w        1.748e-02  9.477e-02   0.184   0.8536    
-## w1_spen_m       -1.374e-01  1.444e-01  -0.952   0.3414    
-## w1_h_tinc        2.995e-05  5.606e-06   5.342 9.69e-08 ***
-## w1_best_edu      2.410e-03  3.532e-03   0.682   0.4951    
-## w1_best_age_yrs  4.127e-03  1.863e-03   2.215   0.0268 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4889 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz1)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m_65 + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.836  -0.050   0.000   0.786   7.040 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.173e+00  7.387e-02 -15.880  < 2e-16 ***
-## w1_spen_w        8.576e-03  9.541e-02   0.090   0.9284    
-## w1_spen_m       -9.189e-02  1.348e-01  -0.681   0.4956    
-## w1_h_tinc        2.992e-05  5.605e-06   5.339 9.85e-08 ***
-## w1_best_edu      2.443e-03  3.531e-03   0.692   0.4890    
-## w1_best_age_yrs  4.092e-03  1.860e-03   2.200   0.0278 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4885 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\printbibliography
-
-\end{refsection}
-
-\begin{refsection}
-\chapter{Replication: Surviving Andersonville}
-\label{andersonville}
-\textbf{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}
-
-\section*{Abstract}
-We replicate \textcite{costa2007surviving}.
-We are able to replicate all the result from the paper.
-The authors make a number of choices in order to arrive to the results published.
-We raise some concerns regarding some of these choices.
-For example, the authors treat the POWs of the two Andersonville camps as if they were in the same camp.
-This inflates size of the POWs social network, which is used as the explanatory variable.
-When we make choices which to us seem more defendable, we cannot, quantitatively and qualitatively, replicate the authors' results.
-
-\section{Summary of the paper}
-\textcite{costa2007surviving} try to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps.
-To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.
-
-The empirical specification for the longitudinal data that measures the effect of the size of the network is as follows:
-
-\begin{equation} \label{eq:ht}
-h(t) = \exp ( \beta_1 F + \beta_2 I + \beta_3 M )
-\end{equation}
-
-where $h$ is hazard at time $t$, $F$ is the number of friends (=social network), $I$ are individual characteristics and $M$ macro camp conditions.
-The number of friends is measured as the number of POWs of the same company and varies by month due to deaths or camp transfers.
-As it might capture the lagged mortality of the group, the authors use as second strategy the initial number of friends as a time-invariant proxy.
-In addition, they instrument for the number of friends using the number of net camp transfers combined with a dummy indicating whether the POW was transferred to account for omitted variables.
-The specification for the Andersonville data in turn is a probit model:
-
-\begin{align}
-Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F) \label{s1} \\
-Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j) \label{s1b} 
-\end{align}
-
-where equation (3.2) examines quantity and equation (3.3) quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
-
-The longitudinal data indicates that POWs had special characteristics.
-For instance, they were likely to be volunteers, and from companies with more wounded or dead.
-POWs with more friends were typically US-born and wealthier while Irish and older men had less friends.
-Concerning survival rates, Kaplan-Meier hazard rates show that POWs captured later (after 1963 when the Union and the Confederate Army stopped exchanging POWs) have lower survival rates.
-They also show that survival rates were higher for POWs with 10 or more friends.
-In addition, the rates show that it takes 50 days until there is a divergence in survival between POWs with and without friends.
-The exponential function estimates that an additional friend leads to a 0.98 times lower mortality hazard.
-An increase in the number of friends from 0 to 5 (5 to 10), decreases the predicted probability of death from 0.31 to 0.28 (0.26) while a spline specification provides evidence that the effect is greatest for the first two friends.
-In addition, survival is more likely for POWs that had survived at least one or two months.
-Factors increasing mortality are the number of men in the camp, low rank, high age, and height among others.
-Insignificant variables are for instance wealth and marital status.
-There is no evidence for individual heterogeneity.
-The use of a Weibull specification indicates no duration dependence (toughen up effects).
-Interestingly though, a Cox model gives no significant effect of friends which the authors interpret as a result of their loss of power due to the small sample size.
-Robustness checks, including the IV approach and the effect of friends transferred in, confirms the significant effect of friends.
-Finally, the cross-sectional results provide evidence that having the same last name, being from the same town for smaller towns, ethnic similarity and having a sergeant or a higher rank in one's network are all important factors in raising survival probabilities which in turn shows that the quality of social networks matters.
-
-In summary, Costa and Kahn are able to show that quantity and quality of social networks mattered for survival in civil war POW camps.
-Potential explanations for this are the sharing of scarce resources, moral support and protection from other prisoners.
-
-\section{Data}
-The raw data for the first part of the paper is extracted from the Union Army dataset readily accessible at \url{http://www.cpe.uchicago.edu}.
-This dataset draws information from censuses, medical records and military pension records linking military, socioeconomic and health information for nearly $40,000$ white males that served in the Union Army during the Civil War.
-For the second part, the Andersonville database is available at \url{http://www.itd.nps.gov/cwss} but only as a ``searchable version'', which allows viewing the information for one soldier at a time, and more convenient formats are not readily available.
-
-The datasets provided for the estimations alongside with the publication are already partially processed parts of the raw data available online.
-No clear guidance is given as to what steps were taken to go from the raw data to the files provided, and matching both things proved to be less than straightforward.
-In view of this, we decided to proceed with the replication using the files provided by the authors, pointing out along the way the cases where potential problems in them seemed likely given the raw data we observed.
-Taking those files as starting points, it is possible to reproduce the tables and graphs published in the paper, so in this sense we can say that the data set is complete.
-Originally, some of the data required by the published .do files was not included in the published data files, but the authors provided it promptly upon our request and added it subsequently to the online files of the publishing journal.
-
-The data and .do files provided do not describe or label many of the variables used, nor does the limited variable description in the Appendix cover all of them.
-A very thorough description of the variables in the raw data set can be found at its online source, but the match between this and the variables in the files provided is not straightforward or complete, since some of them are already created by the authors from the raw data.
-The description of the data itself, mainly of the variables that are used most often, is succinct but adequate, with Table 1 and Table 2 presenting some relevant descriptive traits.
-Despite this, some attention should be drawn to the fact that some of the variables have a relevant share of missing values (only the highest number of observations is reported), a point that will be commented in detail later on.
-
-\section{Stata code and interpretation}
-All codes run to their full extent, and produce the estimations presented in the paper, with minor differences that we describe in detail below.
-The codes themselves are not commented at all and include plenty of estimations and specifications not included in the published paper, as well as unexplained data processing steps.
-No exporting commands were set up, or log files kept, which might be the root of some of the rounding and significance discrepancies we have found.
-
-In what follows, all reproduced tables are presented with a comment on the differences found (in bold), whenever there were any.
-
-\subsection{Tables}
-Table 1: This table presents the means of most variables later used for estimation, dividing observations in POWs and NON POWs, to illustrate ex ante differences in observables between them.
-
-\begin{table}[bt]
-\centering
-\caption{Characteristics of Soldiers by POW Status}
-\label{characteristics}
-\begin{tabular}{lllllll}
-\hline
-                           & All   & Obs.  & Never POW & Obs.  & POW   & Obs. \\
-US born                    & 0.745 & 35007 & 0.745     & 31967 & 0.743 & 3040 \\
-US born corrected          & 0.747 & 34941 & 0.745     & 31966 & 0.759 & 2975 \\
-Irish                      & 0.087 & 34941 & 0.086     & 31966 & 0.102 & 2975 \\
-German                     & 0.074 & 34941 & 0.075     & 31966 & 0.062 & 2975 \\
-British                    & 0.039 & 34941 & 0.039     & 31966 & 0.033 & 2975 \\
-Other                      & 0.054 & 34941 & 0.055     & 31966 & 0.043 & 2975 \\
-Artisan                    & 0.2   & 34941 & 0.199     & 31966 & 0.211 & 2975 \\
-Farmer corrected           & 0.505 & 34941 & 0.505     & 31966 & 0.508 & 2975 \\
-Professional or proprietor & 0.075 & 34941 & 0.077     & 31966 & 0.061 & 2975 \\
-Laborer                    & 0.212 & 34941 & 0.212     & 31966 & 0.212 & 2975 \\
-Unknown                    & 0.007 & 34941 & 0.007     & 31966 & 0.008 & 2975 \\
-Enlisted in 1861           & 0.21  & 35007 & 0.205     & 31967 & 0.263 & 3040 \\
-Enlisted in 1861 corrected & 0.21  & 34878 & 0.205     & 31906 & 0.269 & 2972 \\
-Enlisted in 1862                  & 0.344   & 34878 & 0.331   & 31906 & 0.487  & 2972 \\
-Enlisted in 1863                  & 0.068   & 34878 & 0.066   & 31906 & 0.087  & 2972 \\
-Enlisted in 1864                  & 0.256   & 34878 & 0.266   & 31906 & 0.147  & 2972 \\
-Enlisted in 1865                  & 0.122   & 34878 & 0.132   & 31906 & 0.009  & 2972 \\
-Volunteer                         & 0.909   & 34941 & 0.905   & 31966 & 0.951  & 2975 \\
-Height in inches                  & 67.599  & 34941 & 67.589  & 31966 & 67.709 & 2975 \\
-Household property income in 1860 & 534.155 & 13769 & 531.734 & 12509 & 558.2  & 1260 \\
-Company birthplace fragmentation  & 0.642   & 34941 & 0.644   & 31966 & 0.62   & 2975 \\
-Company occupation fragmentation  & 0.559   & 34941 & 0.558   & 31966 & 0.57   & 2975 \\
-Fraction company died as non-POWs & 0.135   & 34941 & 0.131   & 31966 & 0.182  & 2975 \\
-\end{tabular}
-\end{table}
-
-We have added to \autoref{characteristics} the number of observations per variable, not originally included in the paper, in order to highlight the fact that some of them have significant amounts of missing values, something that should be kept in mind later at the estimation stage.
-In this table, the case in point is Household property income in 1860, which is used in most of the specifications proposed, but as will be discussed for later tables, this is a pattern common to all the variables imported from census data.
-Additionally, considering the number of observations for each of the variables leads to the suggestion of a small correction for three of the dummy variables describing categories: US born, farmer and enlisted in 1861.
-The initial data file is missing these variables, which are likely to have been dropped as the basis category for estimation purposes in some other use of the data.
-They were then rebuilt in the .do file from the remaining categories in such a way that generated zeroes for some observations that should have been missing (except for farmer, which is not included at all in the file).
-For example: as provided by the code, US born has $35,007$ observations, whereas other nationality dummies, all built from the same original variable, have $34,941$.
-The correction proposed then, is to set these dummies to missing whenever the other categories of their class are missing, which slightly changes their descriptive statistics (for example the mean of US born goes from $0.745$ to $0.747$ when this correction is implemented).
-
-Remaining discrepancies are minor and could be due to some kind of rounding difference.
-An alternative explanation for these differences is that the table was produced from a slightly different dataset.
-Considering that even the most populous variables present over 500 observations less than the amount declared in the paper, and the fact that one of the variables (farmer) is not included in the data file at all, we consider the second option to be more likely, which would also explain the minor differences in the means of Artisan, British, Height in inches, etc.
-
-A last and minor comment is that the inclusion of the variable volunteer is surprising, since by sample design the Union Army dataset was restricted to white volunteer infantry regiments.
-The inclusion of this variable when comparing POWs and non POWs probably responds to the point raised in the paper about POWs not being representative of all soldiers, for example in ideology (p.1471).
-A variable that reflects that both POWs and non POWs volunteered in similar proportions would suggest homogeneity between POWs and non POWs in this dimension and, hence, increase  external validity.
-The similarities observed in Table 1 between POWs and non POWs in their mean of volunteer do not reflect that, since they are both close to one by construction.
-Any individuals not listed as volunteers, either correspond to the very few drafted men, or are actually soldiers that re-enlisted as commissioned officers, but were originally volunteers, as explained in the codebooks for the source data.
-
-\ref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.
-It also presents separately their mean and standard errors for the subsamples of POWs with few (less than 3) and many friends (three or more).
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity}
-\label{friends}
-\begin{tabular}{llllllllll}
-
-                                  & \multicolumn{3}{l}{All} & \multicolumn{3}{l}{Few friends ($<3$)} & \multicolumn{3}{l}{Many friends ($>=3$)} \\
-                                  & Mean                    & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-\\
-US born                           & 0.731                   & 0.444                                & 1976                                   & 0.708 & 0.455 & 990 & 0.754 & 0.431 & 986 \\
-Irish                             & 0.12                    & 0.325                                & 1976                                   & 0.115 & 0.319 & 990 & 0.125 & 0.331 & 986 \\
-German                            & 0.063                   & 0.243                                & 1976                                   & 0.081 & 0.273 & 990 & 0.045 & 0.207 & 986 \\
-British                           & 0.034                   & 0.182                                & 1976                                   & 0.042 & 0.202 & 990 & 0.026 & 0.16 & 986 \\
-Other                             & 0.05                    & 0.217                                & 1976                                   & 0.053 & 0.223 & 990 & 0.047 & 0.211 & 986 \\
-Artisan                           & 0.209                   & 0.407                                & 1976                                   & 0.214 & 0.41 & 990 & 0.204 & 0.403 & 986 \\
-Farmer                            & 0.421                   & 0.494                                & 1976                                   & 0.44 & 0.497 & 990 & 0.401 & 0.49 & 986 \\
-Professional or propietor         & 0.07                    & 0.256                                & 1976                                   & 0.077 & 0.266 & 990 & 0.064 & 0.245 & 986 \\
-Laborer                           & 0.266                   & 0.442                                & 1976                                   & 0.243 & 0.429 & 990 & 0.288 & 0.453 & 986 \\
-Unknown                           & 0.034                   & 0.182                                & 1976                                   & 0.025 & 0.157 & 990 & 0.044 & 0.204 & 986 \\
-Enlisted in big city              & 0.475                   & 0.5                                  & 1976                                   & 0.493 & 0.5 & 990 & 0.457 & 0.498 & 986 \\
-Household property income in 1860 & 576.475                 & 1855.699                             & 817                                    & 483.609 & 1084.987 & 391 & 661.711 & 2348.676 & 426 \\
-Age when captured                 & 25.96                   & 7.056                                & 1966                                   & 26.645 & 7.415 & 990 & 25.265 & 6.604 & 976 \\
-Height when captured                 & 171.576 & 6.612 & 1925 & 171.79 & 6.384 & 974 & 171.356 & 6.833 & 951 \\
-Commisoned or noncommisoned officer  & 0.076   & 0.266 & 1976 & 0.083  & 0.276 & 990 & 0.07    & 0.255 & 986 \\
-Married in 1860                      & 0.257   & 0.437 & 817  & 0.276  & 0.448 & 391 & 0.239   & 0.427 & 426 \\
-Wounded 10 days before capture       & 0.118   & 0.323 & 1976 & 0.148  & 0.356 & 990 & 0.088   & 0.284 & 986 \\
-Fraction company dead before capture & 0.089   & 0.064 & 1976 & 0.093  & 0.07  & 990 & 0.085   & 0.057 & 986 \\
-Company birthplace fragmentation     & 0.542   & 0.2   & 1923 & 0.547  & 0.193 & 985 & 0.536   & 0.206 & 938 \\
-Company occupational fragmentation   & 0.596   & 0.173 & 1923 & 0.586  & 0.173 & 985 & 0.607   & 0.172 & 938 \\
-\end{tabular}
-\end{sidewaystable}
-
-This table is almost exactly reproduced, except for the minor differences set in bold, which appear to be rounding differences (and a typo in the case of Laborer).
-The number of observations stated on the table in the paper (1923) corresponds to the last variable in this case as well, even though, as mentioned for the previous table, it is relevant to keep in mind that some of the other variables of interest show a considerably lower count of observations, as can be seen in the added columns.
-For this table, this is the case of variables Married in 1860 and Household property income in 1860, which are both variables from the 1860 census.
-The main concern regarding this table is the process of organizing the data, particularly one step in which a merge to the file ``transfer.dta'' is conducted.
-This file contains the prisoner identifier variable, month, year, and a dummy variable reflecting whether the prisoner was transferred (transferin).
-This variable is not needed for \autoref{friends}, and we can only speculate that it was incorporated, as some other steps were, in an attempt to exactly reproduce the dataset used in \autoref{corrected}.
-The problem in this case is that the file ``transfer.dta'' contains duplicate observations, which in turn duplicates observations in the main data set via the merge, artificially inflating the number of observations in the data used for \autoref{friends}\footnote{Duplicate observations per month-year-prisoner are natural in the context of \autoref{corrected}, because in there capture time is measured per fortnight.
-Including additional observations because of this in a stage of data description such as this one is hardly appropriate.}.
-
-If these duplicate observations are eliminated from the ``transfer.dta'' file before the merge, the statistics presented do not seem to defer significantly, and certainly neither do the conclusions drawn from them, but the number of observations in the subsample considered is significantly lower.
-This exercise is presented in the table below.
-
-\begin{sidewaystable}
-\centering
-\caption{corrected}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{corrected}
-\begin{tabular}{llllllllll}
-\hline
-                                  & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. \\
-US born                           & 0.732   & 0.443     & 1470     & 0.715   & 0.452     & 727      & 0.748   & 0.434     & 743      \\
-Irish                             & 0.122   & 0.327     & 1470     & 0.113   & 0.317     & 727      & 0.131   & 0.337     & 743      \\
-German                            & 0.06    & 0.237     & 1470     & 0.074   & 0.262     & 727      & 0.046   & 0.209     & 743      \\
-British                           & 0.034   & 0.181     & 1470     & 0.04    & 0.196     & 727      & 0.028   & 0.166     & 743      \\
-Other                             & 0.05    & 0.219     & 1470     & 0.056   & 0.231     & 727      & 0.044   & 0.206     & 743      \\
-Artisan                           & 0.212   & 0.409     & 1470     & 0.217   & 0.413     & 727      & 0.207   & 0.406     & 743      \\
-Farmer                            & 0.427   & 0.495     & 1470     & 0.442   & 0.497     & 727      & 0.413   & 0.493     & 743      \\
-Professional or proprietor        & 0.065   & 0.247     & 1470     & 0.073   & 0.26      & 727      & 0.058   & 0.234     & 743      \\
-Laborer                           & 0.265   & 0.441     & 1470     & 0.242   & 0.429     & 727      & 0.287   & 0.453     & 743      \\
-Unknown                           & 0.031   & 0.172     & 1470     & 0.026   & 0.16      & 727      & 0.035   & 0.184     & 743      \\
-Enlisted in big city              & 0.48    & 0.5       & 1470     & 0.486   & 0.5       & 727      & 0.475   & 0.5       & 743      \\
-Household property income in 1860 & 547.314 & 1637.903  & 615      & 476.274 & 1107.659  & 299      & 614.532 & 2014.738  & 316      \\
-Age when captured                 & 25.834  & 6.931     & 1465     & 26.4    & 7.263     & 727      & 25.276  & 6.544     & 738      \\
-Height when captured              & 171.526 & 6.624     & 1439     & 171.683 & 6.433     & 717      & 171.37  & 6.81      & 722      \\
-Commisioned or noncommisioned officer\footnote{Related to the point about the variable Volunteer made before, the name Commisioned or non commissioned officer may be misleading, since commissioned officers are excluded from the sample by construction.} & 0.074 & 0.262 & 1470 & 0.078 & 0.269 & 727 & 0.07  & 0.255 & 743 \\
-Married in 1860                       & 0.252 & 0.435 & 615  & 0.264 & 0.442 & 299 & 0.241 & 0.428 & 316 \\
-Wounded 10 days before capture        & 0.125 & 0.331 & 1470 & 0.155 & 0.363 & 727 & 0.096 & 0.294 & 743 \\
-Fraction company dead before capture  & 0.091 & 0.063 & 1470 & 0.094 & 0.069 & 727 & 0.089 & 0.056 & 743 \\
-Company birthplace fragmentation      & 0.542 & 0.198 & 1442 & 0.55  & 0.189 & 723 & 0.534 & 0.207 & 719 \\
-Company occupational fragmentation    & 0.593 & 0.175 & 1442 & 0.585 & 0.173 & 723 & 0.601 & 0.178 & 719 \\
-\end{tabular}
-\end{sidewaystable}
-
-Two additional remarks related to this are: a) whenever month was larger than 12, it is set to missing, b) all observations marked as having occurred in 1861 are shifted to 1862.
-Neither month nor year are directly used for this table, but they are the matching points for the merge to the ``transfer.dta'' file discussed above.
-The file “transfer.dta” also contains month>12 and observations for 1861, and they are not replaced in a similar fashion, introducing some additional artificial matching problems into the merge operation.3 Besides the potential distortions in the merge that these asymmetric replacements may cause, the switch of 1861 to 1862 seems particularly surprising given that no explanation for it is offered.
-
-Additionally, if the aim of this table is to have a general impression of the variables used in the main regressions (\autoref{corrected}), the same observations should have been considered in both accounts.
-This is not the case, since the observations with an unknown number of friends are dropped for this table, but not for the next one.
-
-\autoref{corrected}: This table shows the results of the hazard rate analysis using a set of covariates described in the previous tables and alternating two measures of friends: number of friends at the time of the observation and initial number of friends.
-
-\begin{sidewaystable}
-\caption{Social Networks and Individual Characteristics on Mortality}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{social}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{specification I} & \multicolumn{2}{l}{specification II} & \multicolumn{2}{l}{specification III} \\
-VARIABLES                                & Hazard rate                         & Std. err.                            & Hazard rate                           & Std. err. & Hazard rate & Std. err. \\
-Current number of friends                & 0.983                               & -0.008                               & 0.977++                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                      &                                       &  & 0.976++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                      & 1.536++                               & -0.14 & 1.521++ & -0.139 \\
-Fraction of company dying before capture & 1.091                               & -0.782                               & 0.892                                 & -0.636 & 0.63 & -0.449 \\
-Professional or proprietor               & 0.567                               & -0.146                               & 0.563                                 & -0.143 & 0.556 & -0.141 \\
-Artisan                                  & 0.944                               & -0.119                               & 0.947                                 & -0.119 & 0.937 & -0.117 \\
-Laborer                                  & 1.298                               & -0.154                               & 1.295                                 & -0.152 & 1.287 & -0.152 \\
-German                                   & 1.197                               & -0.215                               & 1.166                                 & -0.209 & 1.149 & -0.206 \\
-Irish                                    & 0.768*                              & -0.121                               & 0.762*                                & -0.118 & 0.750* & -0.117 \\
-British                       & 0.641*    & -0.171 & 0.654     & -0.174 & 0.656    & -0.177 \\
-Other                         & 0.658*    & -0.154 & 0.645*    & -0.153 & 0.642*   & -0.151 \\
-Sergeant, corporal or officer & 0.549++   & -0.115 & 0.543++   & -0.111 & 0.541++  & -0.111 \\
-Age at captivity              & 1.045++   & -0.007 & 1.044++   & -0.007 & 1.044++  & -0.007 \\
-Height at enlistment          & 1.01      & -0.007 & 1.01      & -0.007 & 1.011    & -0.007 \\
-Observations                  & 23256     &        & 23256     &        & 23256    &        \\
-Number of subjects            & 3026      &        & 3026      &        & 3026     &        \\
-Log pseudo likelihood         & -1324.607 &        & -1308.229 &        & -1307.17 &        \\
-\end{tabular}
-\end{sidewaystable}
-
-\autoref{corrected} is reproduced almost completely, except for the results in bold, for which the significance level differs from the one presented in the publication.
-
-In this case, month larger than 12 is replaced by 99, and in this case as well this might generate distortions since an equivalent change was not performed in the file to which this is merged (``Died.dta'').
-The observations for which the number of friends is unknown are not dropped here, but set to zero.
-Whenever the number of deaths in the prisoners' company before capture is unknown, it is set to zero.
-Whenever the number of men in camp is unknown it is set to 40.
-Whenever the variables imported from the 1860 census are missing (i.e.
-there was no match to the census) they are still included in the regression by setting their value to zero in the case of dummy variables (married and illiterate), and by taking log(1+variable) in the case of Household property.
-In all of these cases, dummy variables are included in the regression indicating whether the data is actually missing (e.g.
-a dummy variable that takes value one if the observation was not matched to the 1860 census, link60).
-It is understandable that in order to maintain a healthy sample size, and to use as much of the information as possible, some assumptions are made, but the trade off related to this point is that these assumptions may create artificial noise in the data that would not be fully captured by these control dummies.
-
-\autoref{social}: This table presents an alternative estimation strategy.
-As a benchmark, the effect of the number of friends in the camp is estimated including company fixed effects and the same covariates as before.
-To avoid endogeneity issues that may arise due to the potential correlation between the current number of friends and the prisoner’s own unobservable health (via its correlation to the lagged mortality of the group), an IV-hazard rate strategy is pursued next.
-The instruments chosen are the new number of friends the prisoner has in each period (the newly captured soldiers of his company) and a dummy variable that reflects whether the POW was transferred.
-Both variables clearly affect the number of friends a POW has, and are meant to be uncorrelated with his unobservable health, since transfers and the amount of newly captured men assigned to each camp were determined by camp needs or evolution of war events5.
-In the first stage, the number of friends is regressed on the instruments, as well as the whole set of covariates and fixed effects.
-The predicted residuals of this first stage are then included in the second stage, along with all covariates, fixed effects and the number of friends.
-This procedure is repeated 100 times, preserving the coefficients and standard errors of the number of friends, the number of men in the camp and the residuals, as well as the R-squared of the first stage.
-The final result of this Montecarlo procedure is obtained by computing the mean of those variables among the 100 repetitions.
-
-\begin{sidewaystable}
-\caption{Effect of Social Networks on Mortality, with Company Fixed Effects and Instrumented}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effect}
-\begin{tabular}{lllll}
-\hline
-                                    & \multicolumn{2}{l}{Original} & \multicolumn{2}{l}{IV} \\
-                                    & Haz. Rate                    & Std. Err.              & Haz. Rate & Std. Err. \\
-Number of friends                   & 0.978*                       & -0.012                 & 0.895 & -0.055 \\
-Ln(total number of men in the camp) & 1.437++                      & -0.122                 & 1.537 & -0.196 \\
-Residual                            &                              &                        & 1.06 & -0.071 \\
-\end{tabular}
-\end{sidewaystable}
-
-Here, the results are replicated entirely.
-
-A concern raised is that it is not clear how the variable that reflects transfers was constructed, since this information is not directly provided in the raw data available online.
-In some cases, the variable that reflects the camp contains multiple entries per individual, and we can only assume that those were used to infer that the POW was transferred between those camps.
-This is most likely an accurate interpretation of the data, the only problem being that there is no information about the date of transfer, which makes the instrument weaker.
-
-In the following section, the authors use The National Park Service's cross-sectional data of the population of Andersonville and estimate probit models of the probability of survival on the number of friends and various demographic characteristics as described in the summary.
-
-\autoref{effect}: This table estimates the effect of social networks on probability of survival controlling for a large of variables that measure existing networks outside of the company.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectsocial}
-\begin{tabular}{lllllll}
-\hline
-                                                              &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                              & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment÷10                                  & 9.157   & 0.004++ &         &         &                                     &  \\
-                                                              & -10.358 & -0.001  &         &         &                                     &  \\
-Number of men in company                                      & 12.899  &         & 0.003++ & 0.002++ & 0.003++                             & 0.002++ \\
-                                                              & -15.39  &         & -0.001  & -0.001  & -0.001                              & -0.001 \\
-Fraction of company with              rank sergeant or higher & 0.073   & 0.120++ & 0.128++ & 0.079   & 0.152                               & 0.085 \\
-                                                              &         & -0.034  & -0.034  & -0.032  & -0.061                              & -0.056 \\
-Number of men with same last name in regiment                 & 1.19    & 0.033++ & 0.033++ & 0.036++ & 0.018*                              & 0.023++ \\
-                                                              & -0.599  & -0.007  & -0.007  & -0.006  & -0.009                              & -0.009 \\
-Log(number of men in camp from same town)                     & 5.101   & -0.003  & -0.002  & 0       & 0.018*                              & 0.026++ \\
-                                                              & -1.994  & -0.005  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-Dummy=1 if town population<9552                               & 0.423   & 0.037+  & 0.034+  & 0.032+  &                                     &  \\
-                                                              &         & -0.014  & -0.014  & -0.013  &                                     &  \\
-Private                                                       & 0.824   &         &         &         &                                     &  \\
-Officer             & 0.003 & 0.347++ & 0.347++ & 0.354++ & 0.311++ & 0.328++ \\
-                    &       & -0.027  & -0.027  & -0.021  & -0.038  & -0.025  \\
-Sergeant            & 0.068 & 0.080++ & 0.080++ & 0.083++ & 0.084++ & 0.088++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Other rank          & 0.01  & 0.028   & 0.034   & 0.03    & 0.067   & 0.046   \\
-                    &       & -0.03   & -0.03   & -0.03   & -0.049  & -0.05   \\
-Corporal            & 0.078 & 0.055++ & 0.055++ & 0.046++ & 0.064++ & 0.054++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Irish surname       & 0.023 & 0.02    & 0.022   & 0.017   & 0.069   & 0.059*  \\
-                    &       & -0.019  & -0.019  & -0.019  & -0.03   & -0.03   \\
-German surname      & 0.043 & -0.009  & -0.009  & -0.016  & -0.001  & -0.025  \\
-                    &       & -0.015  & -0.015  & -0.015  & -0.024  & -0.025  \\
-French surname      & 0.028 & 0.028   & 0.028*  & 0.028   & 0.033   & 0.032   \\
-                    &       & -0.017  & -0.017  & -0.017  & -0.027  & -0.028  \\
-Continental surname & 0.029 & 0.006   & 0.007   & -0.004  & -0.021  & -0.029  \\
-                    &       & -0.018  & -0.018  & -0.018  & -0.032  & -0.032  \\
-State fixed effects? &       & N     & N     & Y     & N     & Y     \\
-Pseudo R2            &       & 0.043 & 0.044 & 0.087 & 0.048 & 0.115 \\
-Observations         & 31336 & 31336 & 31336 & 31330 & 12002 & 12002 \\
-\end{tabular}
-\end{sidewaystable}
-
-All figures on the table are replicated perfectly.
-However, the coefficients in bold are estimated with different significance levels (even though the coefficients and their standard errors are the same).
-For example, we find that the coefficient on Dummy=1 if town population $<9,552$ is significant at the 5 percent level whereas the table in the original paper indicates that it is significant at the 1 percent level in specifications 1, 2, and 3.
-It is important to note that the difference is not always in the same direction.
-For instance, we find that the coefficient on French surname in specification 2 is significant at the 10 percent level whereas the original table does not show any significance.
-Thus, we suspect that this discrepancy might be due to rounding error.
-
-\autoref{effectsocial}: Here, the authors estimate the same equation in logs and include the two outlier companies that were excluded in Table 5 to show the resulting nonlinearity.
-In the .do file, the outliers are dropped early on and thus their estimations never include these outliers.
-We save the dataset with the outliers at an early stage so that we can include them in the estimation.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectLog}
-\begin{tabular}{lllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.014++ &         &         &                                     &  \\
-                                                   & -1.29  & -0.005  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.021++ & 0.012   & 0.029                               & 0.022 \\
-                                                   & -1.18  &         & -0.007  & -0.006  & -0.012                              & -0.009 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.134++ & 0.134++ & 0.08    & 0.153                               & 0.084 \\
-                                                   & -0.127 & -0.034  & -0.034  & -0.032  & -0.061                              & -0.057 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.101++ & 0.095++ & 0.096++ & 0.061++                             & 0.063++ \\
-                                                   & -0.305 & -0.012  & -0.012  & -0.011  & -0.018                              & -0.017 \\
-Log(number of men in camp from same town)          & 5.114  & -0.004  & 0       & 0.002   & 0.024                               & 0.030++ \\
-                                                   & -1.991 & -0.004  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.114 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002                               & 12002 \\
-                                                   &        &         &         &         &                                     &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The first thing to notice is that the number of observations is different.
-The original paper shows a total of 31,678 observations for the first three specifications, and a total of 12,025 observations for specifications 4 and 5.
-We have less number of observations mostly due to the 83 observations with missing Fraction of company with rank sergeant or higher variable.
-We don’t know how the authors included these observations in their estimation.
-A minor difference in the first descriptive column is the mean for Log(number of men with same last name in regiment), which is $0.113$ in the paper paper and $0.112$ in our data.
-
-All the coefficients in bold are slightly different from the original table; some are different only in their magnitude but some are also different in their level of significance.
-For example, the coefficient on Log(number of men in regiment) in specification 1 is $0.011$ with $5\%$ significance level in the paper, whereas we find a higher and more significant effect.
-Despite these quantitative differences, the results are not qualitatively different.
-
-\autoref{effectLog}: Here, the authors estimate the effect of ethnic networks on probability of survival to show that the quality of the network matters.
-
-\begin{sidewaystable}
-\caption{Effect of ethnic network on probability of survival}\footnote{Company clustered standard errors.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethnic}
-\begin{tabular}{lllllll}
-\hline
-
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.003*                    & 0.002                      & 0.003                      & 0.001 & 0.002 & 0.002 \\
-Number of men of own ethnicity in company & 0.03                      & 0.036                      & 0.03                       & 0.013 & 0.019 & 0.026 \\
-Dummy = 1 if Private                      & -0.046                    & 0.049                      & -0.078+                    & 0.037 & -0.093+ & 0.043 \\
-From small town                           & 0.1                       & 0.04                       & 0.036                      & 0.031 & 0.054 & 0.036 \\
-Captured 1864 or 1865                     & 0.239++                   & 0.077                      & 0.282++                    & 0.049 & 0.388++ & 0.058 \\
-Pseudo R2                                 & 0.036                     &                            & 0.059                      &  & 0.058 &  \\
-Joint significance test                   & 8.6                       &                            & 22.01                      &  & 3.2 &  \\
-Observations                              & 735                       &                            & 1355                       &  & 869 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The bold coefficients in \autoref{effectLog} are different in significance levels than what the authors report in their original table (all coefficients and standard errors are the same).
-The most striking one is the Captured 1864 or 1865 variable for French POWs where the authors find no significance at all and we find significance at the 1 percent level.
-Since this is too large of a difference to be a rounding error, we suspect that it is a typo.
-
-\subsection{Robustness check - Logit instead of Probit}
-
-As a robustness check, we estimate tables 5-7 with logit instead of probit and results are qualitatively similar.
-Bold coefficients below show differing levels of significance (only 1-level) when compared to probit.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logit}\footnote{There is no explanation in the paper as to why probit was preferred to logit.}
-\label{logit}
-\begin{tabular}{lllllll}
-\hline
-                                                 &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                 & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment ÷10                    & 9.157   & 0.018++ &         &         &                                     &  \\
-                                                 & -10.358 & -0.003  &         &         &                                     &  \\
-Number of men in company                         & 12.899  &         & 0.013++ & 0.009++ & 0.014++                             & 0.010++ \\
-                                                 & -15.39  &         & -0.003  & -0.002  & -0.004                              & -0.003 \\
-Fraction of company with rank sergeant or higher & 0.073   & 0.495++ & 0.526++ & 0.336   & 0.647                               & 0.387 \\
-                                                 &         & -0.145  & -0.144  & -0.139  & -0.266                              & -0.251 \\
-Number of men with same last name in regiment    & 1.19    & 0.149++ & 0.147++ & 0.158++ & 0.081*                              & 0.101++ \\
-                                                 & -0.599  & -0.03   & -0.03   & -0.028  & -0.042                              & -0.038 \\
-Log(number of men in camp from same town)        & 5.101   & -0.012  & -0.01   & 0       & 0.075                               & 0.114++ \\
-                                                 & -1.994  & -0.019  & -0.019  & -0.019  & -0.038                              & -0.034 \\
-Dummy=1 if town population<9552                  & 0.423   & 0.154   & 0.145   & 0.133   &                                     &  \\
-                                                 &         & -0.06   & -0.056  & -0.054  &                                     &  \\
-Private                                          & 0.824   &         &         &         &                                     &  \\
-Officer & 0.003 & 2.342++ & 2.339++ & 2.481++ & 2.043++ & 2.342++ \\
-        &       & -0.454  & -0.455  & -0.426  & -0.562  & -0.502  \\
-Sergeant             & 0.068 & 0.344++ & 0.344++ & 0.367++ & 0.377++ & 0.407++ \\
-                     &       & -0.05   & -0.05   & -0.053  & -0.081  & -0.087  \\
-Other rank           & 0.01  & 0.109   & 0.135   & 0.12    & 0.295   & 0.2     \\
-                     &       & -0.128  & -0.128  & -0.132  & -0.232  & -0.231  \\
-Corporal             & 0.078 & 0.236++ & 0.235++ & 0.201++ & 0.283++ & 0.244++ \\
-                     &       & -0.046  & -0.046  & -0.048  & -0.077  & -0.084  \\
-Irish surname        & 0.023 & 0.086   & 0.095   & 0.072   & 0.31    & 0.264*  \\
-                     &       & -0.081  & -0.081  & -0.082  & -0.14   & -0.146  \\
-German surname       & 0.043 & -0.039  & -0.036  & -0.07   & -0.003  & -0.111  \\
-                     &       & -0.061  & -0.06   & -0.061  & -0.103  & -0.106  \\
-French surname       & 0.028 & 0.113   & 0.117   & 0.119   & 0.14    & 0.152   \\
-                     &       & -0.073  & -0.073  & -0.075  & -0.12   & -0.127  \\
-Continental surname  & 0.029 & 0.026   & 0.031   & -0.015  & -0.093  & -0.126  \\
-                     &       & -0.075  & -0.075  & -0.076  & -0.134  & -0.135  \\
-State fixed effects? &       & N       & N       & Y       & N       & Y       \\
-Pseudo R2            &       & 0.043   & 0.044   & 0.086   & 0.047   & 0.114   \\
-Observations         & 31336 & 31336   & 31336   & 31330   & 12002   & 12002   \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form, logit}\footnote{Company clustered standard errors are in parentheses.
-The number of observations for the Fraction of company with rank sergeant or higher variable in the first column is 31605.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{logLogit}
-\begin{tabular}{llllllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.057   &         &         &                                     &  \\
-                                                   & -1.29  & -0.022  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.088++ & 0.047   & 0.124                               & 0.085 \\
-                                                   & -1.18  &         & -0.028  & -0.024  & -0.051                              & -0.04 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.559++ & 0.552++ & 0.342   & 0.652                               & 0.383 \\
-                                                   & -0.127 & -0.147  & -0.145  & -0.139  & -0.266                              & -0.251 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.438++ & 0.409++ & 0.416++ & 0.267++                             & 0.277++ \\
-                                                   & -0.305 & -0.052  & -0.052  & -0.049  & -0.078                              & -0.074 \\
-Log(number of men in camp from same town)          & 5.114  & -0.018  & 0       & 0.006   & 0.100++                             & 0.131++ \\
-                                                   & -1.991 & -0.018  & -0.019  & -0.019  & -0.039                              & -0.036 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.113 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002 
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of ethnic networks on probability of survival, logit}\footnote{Standard errors are clustered on the company.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethLogit}
-\begin{tabular}{lllllll}
-\hline
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.009                     & 0.007                      & 0.011*                     & 0.006 & -0.001 & 0.007 \\
-Number of men of own ethnicity in company & 0.011                     & 0.11                       & 0.139                      & 0.06 & 0.154 & 0.116 \\
-Dummy =1 if Private                       & -0.228                    & 0.214                      & -0.337+                    & 0.162 & -0.445+ & 0.2 \\
-From small town                           & 0.417                     & 0.173                      & 0.154                      & 0.131 & 0.23 & 0.154 \\
-Captured 1864 or 1865                     & 1.082++                   & 0.347                      & 1.223++                    & 0.227 & 1.826++ & 0.307 \\
-Pseudo R2                                 & 0.032                     &                            & 0.058                      &  & 0.055 &  \\
-Joint significance test                   & 3.81                      &                            & 18.22                      &  & 2.16 &  \\
-Observations                              & 752                       &                            & 1357                       &  & 874 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\section{Conclusion}
-To sum up our replication, our key message is that while we do find small differences between our results and the published results of \textcite{costa2007surviving}, we find no evidence that would call their conclusions into question, either qualitatively or quantitatively.
-
-Furthermore, the interpretation of the results seems convincing to us.
-While they cannot test for how friends ensured survival the mentioned explanations from the supply of food to moral support are very comprehensible.
-In addition, their study is clearly and quite literally made for survival analysis so we do not see space to improve upon the results by applying a different estimation technique.
-\textcite{costa2007surviving} also apply a wide set of survival analysis tools (e.g.
-from non-parametric to parametric estimation) so we did not come up with many ideas for robustifying their paper in this direction.
-Potential future extensions could build on the use of different data sets.
-A weakness of the paper is clearly that external validity is limited because the authors look at a civil war of the 19th century.
-For instance, looking at World War I or II data could prove to be fruitful and lead to further insight.
-While we tried to start with such an extension, we were not able to find a sufficient dataset within this period of time.
-
-To come back to the differences between our replication and the original paper, we consider the most relevant issue the difference in significance levels.
-Interestingly, when looking into this matter in more detail we find that in almost all cases the p-values are at the margin which clearly points in the direction of a rounding error.
-We can only speculate that given the lack of exporting commands the reason for this is a certain degree of carelessness and, therefore, would like to emphasize the need of these very exporting commands.
-Nevertheless, and as mentioned before, the differences do not affect the general message of the paper.
-
-%\appendix
-
-\section*{Appendix: In-text estimation}
-Most in-text estimations are not included in the .do files provided, therefore some of the results to follow do not exactly reproduce the ones published, probably due to differences in specifications.
-They can nonetheless generally be replicated in terms of signs and significance.
-
-\paragraph{Probit statement}
-page 1474, line 21 ``When we run a Probit, in which the dependent variable is POW status and the independent variables are economic and geographic characteristics and the number of men in the company who were ever wounded or who ever died, we find that these two company characteristics were the main predictors of POW status.
-The derivative on the number of men in the company who were ever wounded or who ever died, was $0.257$ (robust $= 0.257$) and the derivative on the number of men who were ever wounded was $0.139$ (robust $= 0.042$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of POW Status}
-\begin{tabular}{lll}
-\hline
-                          & Marginal Effect & Marginal Effect \\
-\% in comp who died        & 0.359***        & 0.430***        \\
-                          & -0.021          & -0.0331         \\
-\% in comp who wounded     & 0.123***        & 0.140***        \\
-                          & -0.0136         & -0.022          \\
-Includes property in 1860 & No              & Yes             \\
-Observations              & 34878           & 13754           \\
-\end{tabular}
-\end{table}
-
-\paragraph{Comment on late capture}
-page 1474, line 77 ``We also found no evidence of group surrender to become a POW - men who were captured in 1864 and 1865 had more friends, even though a group who surrendered during these years would have no hope of a quick exchange.''
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity and Late or Early Capture}
-\begin{tabular}{lllllllll}
-\hline
-                     & \multicolumn{4}{c}{Early capture} & \multicolumn{4}{c}{Late capture} \\
-                     & \multicolumn{2}{c}{$< 3$}           & \multicolumn{2}{c}{$>= 3$}         & \multicolumn{2}{c}{$< 3$} & \multicolumn{2}{c}{$>= 3$} \\
-                     & Mean                              & Std. err.                        & Mean & Std. err. & Mean & Std. err. & Mean & Std. err. \\
-US born              & 0.706                             & 0.456                            & 0.77 & 0.421 & 0.709 & 0.455 & 0.738 & 0.44 \\
-Irish                & 0.082                             & 0.275                            & 0.109 & 0.311 & 0.136 & 0.343 & 0.14 & 0.347 \\
-German               & 0.108                             & 0.311                            & 0.046 & 0.21 & 0.064 & 0.244 & 0.043 & 0.204 \\
-British              & 0.053                             & 0.224                            & 0.021 & 0.143 & 0.036 & 0.186 & 0.032 & 0.175 \\
-Other                & 0.048                             & 0.213                            & 0.046 & 0.21 & 0.056 & 0.229 & 0.047 & 0.213 \\
-Artisan              & 0.233                             & 0.423                            & 0.2 & 0.401 & 0.203 & 0.402 & 0.207 & 0.406 \\
-Farmer               & 0.423                             & 0.495                            & 0.355 & 0.479 & 0.451 & 0.498 & 0.444 & 0.497 \\
-Prof. or proprietor  & 0.09                              & 0.286                            & 0.075 & 0.264 & 0.069 & 0.253 & 0.053 & 0.225 \\
-Laborer              & 0.235                             & 0.425                            & 0.288 & 0.453 & 0.248 & 0.432 & 0.288 & 0.453 \\
-Unknown              & 0.019                             & 0.135                            & 0.081 & 0.274 & 0.029 & 0.169 & 0.008 & 0.089 \\
-Enlisted in big city & 0.545                             & 0.499                            & 0.497 & 0.501 & 0.461 & 0.499 & 0.42 & 0.494 \\
-Property inc in 1860 & 444.889                           & 1056.215                         & 703.517 & 2190.478 & 502.019 & 1099.896 & 620.684 & 2498.66 \\
-Age when captured    & 26.079                            & 7.152                            & 24.848 & 6.588 & 26.995 & 7.558 & 25.658 & 6.601 \\
-Height when captured & 171.518                           & 6.2                              & 171.377 & 6.914 & 171.959 & 6.495 & 171.338 & 6.765 \\
-Officer              & 0.111                             & 0.315                            & 0.092 & 0.289 & 0.065 & 0.247 & 0.049 & 0.217 \\
-Married in 1860      & 0.27                              & 0.446                            & 0.246 & 0.432 & 0.279 & 0.449 & 0.233 & 0.423 \\
-Fraction company dead before capture & 0.056 & 0.054 & 0.057 & 0.046 & 0.116 & 0.069 & 0.112 & 0.054 \\
-Company birthplace fragmentation     & 0.554 & 0.183 & 0.516 & 0.238 & 0.543 & 0.199 & 0.553 & 0.173 \\
-Company occupational fragmentation   & 0.587 & 0.173 & 0.614 & 0.177 & 0.586 & 0.173 & 0.601 & 0.168 \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{OLS statement}
-page 1474 line 65 and footnote 22.
-``When we ran an OLS regression of the number of friends on the covariates we later use in our hazard specification, we found that professionals and proprietors, the Irish, older men, and the recently wounded were less likely to have many friends, whereas those from a large city had more friends''...
-``The coefficient on recently wounded was $-0.879$ ($= 0.397$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of number of friends}
-\begin{tabular}{ll}
-\hline
-Professional or proprietor     & -0.913***  \\
-                               & -0.0979    \\
-Irish                          & -0.267***  \\
-                               & -0.0984    \\
-Age at capture                 & -0.0391*** \\
-                               & -0.00504   \\
-Wounded 10 days before capture & -0.831***  \\
-                               & -0.0876    \\
-Large city                     & 0.553***   \\
-                               & -0.0649    \\
-Observations                   & 23256      \\
-R-squared                      & 0.152      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Predicted probability of death}
-page 1475, line 24.
-``As the number of friends increases from 0 to 5, the predicted probability of death, using the second specification in Table 3, decreases from $0.31$ to $0.28$, and as the number of friends increases to $10$, the predicted mortality probability falls to $0.26$.
-(The mean number of friends in each month was $5.6$, with a standard deviation of $9.2$, and the median was $2$.)''
-
-\begin{table}[ht]
-\centering
-\caption{Number of Friends}
-\begin{tabular}{lll}
-\hline
-          & Initial & In estimation \\
-Mean      & 5.58    & 2.87          \\
-Std. Dev. & 9.22    & 5.12          \\
-Median    & 2       & 1             \\
-\end{tabular}
-\end{table}
-
-The summary statistics mentioned for the variable friends match the initial file, but not the data that is actually included in the regression.
-
-\begin{figure}[ht]
-\centering
-\caption{Exponential specification}
-\label{exponential}
-\includegraphics[scale=0.65]{exponential.png}
-\end{figure}
-
-The file ``survival.dta'' contains the predicted survival probability for individuals with 0, 5 and 10 friends (evaluated at means for the other covariates).
-The statement did not specify a point in time, but we find a coincidence with the statement at $t=330.76$ (average days of imprisonment was $131.62$).
-
-\paragraph{Table 3 with regiment fixed effects}
-page 1476, line 2.
-``Even when we included state of regiment fixed effects, the hazard ratio on the number of friends remained virtually unchanged (e.g.
-the hazard ratio on the initial number of friends was $0.976$, $=0.009$).''
-
-\begin{sidewaystable}
-\caption{Table 3 with regiment state effects}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err & Hazard rate & Std. err & Hazard rate & Std. err \\
-Number of friends                        & 0.984*      & -0.009   & 0.978       & -0.009   &             &          \\
-Initial number of friends                &             &          &             &          & 0.976++     & -0.009   \\
-Ln(number of prisoners in camp)          &             &          & 1.538++     & -0.141   & 1.525++     & -0.14    \\
-Fraction of company dying before capture & 1.427       & -1.227   & 1.19        & -1.011   & 0.787       & -0.653   \\
-Professional or proprietor               & 0.512       & -0.134   & 0.506++     & -0.131   & 0.502++     & -0.13    \\
-Artisan                                  & 0.862       & -0.114   & 0.862       & -0.114   & 0.851       & -0.112   \\
-Laborer                                  & 1.163       & -0.148   & 1.154       & -0.146   & 1.141       & -0.145   \\
-German                                   & 1.135       & -0.213   & 1.116       & -0.21    & 1.103       & -0.206   \\
-Irish                                    & 0.731*      & -0.118   & 0.723       & -0.116   & 0.723       & -0.115   \\
-British                                  & 0.616*      & -0.167   & 0.630*      & -0.17    & 0.637*      & -0.174   \\
-Other                                    & 0.612       & -0.145   & 0.603       & -0.144   & 0.602       & -0.143   \\
-Sergeant, corporal or officer            & 0.570++     & -0.117   & 0.561++     & -0.113   & 0.557++     & -0.112   \\
-Age at captivity                         & 1.042++     & -0.008   & 1.040++     & -0.007   & 1.040++     & -0.007   \\
-Height at enlistment                     & 1.014*      & -0.007   & 1.014*      & -0.007   & 1.014*      & -0.007   \\
-Observations                             & 3026        &          & 3026        &          & 3026        &          \\
-Number of subjects                       & 23174       &          & 23174       &          & 23174       &          \\
-Log pseudo likelihood                    & -1307.77    &          & -1291.45    &          & -1290.674   &          \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Table 3 with splines}
-page 1476, line 6 and footnote 23 ``Our experiments with splines suggested that the marginal effect of a friend on survival was greater for the first two friends than for more."  Footnote 23: "The hazard rate on the marginal effect of fewer than three friends was $0.956$ ($=0.044$) and the hazard rate on the marginal effect of three or more friends was $0.980$ ($=0.011$).
-Although the first hazard rate was not statistically significantly different from one, the two terms together were jointly significant.''
-
-\begin{table}[ht]
-\centering
-\caption{Spline at 3}
-\begin{tabular}{ll}
-\hline
-                     & Hazard rate \\
-Fewer than 3 friends & 0.956       \\
-                     & -0.0443     \\
-3 or more friends    & 0.980*      \\
-                     & -0.0108     \\
-Observations         & 23256       \\
-Chi-sq               & 7.789       \\
-Prob > chi-sq        & 0.0204      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Weibull specification}
-page 1477, line 12. ``When we use a Weibull rather than an exponential specification, we found no evidence of duration dependence...''
-
-\begin{sidewaystable}
-\caption{Weibul}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llllllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-VARIABLES                                & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.986                               & -0.009                              & 0.979                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.531++                             & -0.139 & 1.517++ & -0.139 \\
-Fraction of company dying before capture & 1.242                               & -0.897                              & 1.008                               & -0.722 & 0.733 & -0.525 \\
-Professional or propietor                & 0.566                               & -0.147                              & 0.562                               & -0.144 & 0.554 & -0.142 \\
-Artisan                                  & 0.95                                & -0.121                              & 0.952                               & -0.12 & 0.942 & -0.119 \\
-Laborer                                  & 1.308                               & -0.157                              & 1.303                               & -0.154 & 1.296 & -0.154 \\
-German                                   & 1.198                               & -0.218                              & 1.169                               & -0.212 & 1.153 & -0.209 \\
-Irish                                    & 0.771                               & -0.123                              & 0.765*                              & -0.12 & 0.753* & -0.118 \\
-British                                  & 0.630*                              & -0.17                               & 0.644                               & -0.174 & 0.646 & -0.176 \\
-Other                                    & 0.656*                              & -0.155                              & 0.643*                              & -0.153 & 0.640* & -0.151 \\
-Sargeant, corporal or officer            & 0.536++                             & -0.114                              & 0.531++                             & -0.11 & 0.528++ & -0.11 \\
-Age at captivity                         & 1.046++                             & -0.008                              & 1.045++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1322.852                           &                                     & -1306.836                           &  & -1305.627 &  \\
-Duration dependence                      & 1.088                               &                                     & 1.08                                &  & 1.084 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Month dummies}
-page 1477, line 19.
-``When we included dummy variables in our specification indicating that an individual had survived 1, 2, 3 or more months, we found that those who had survived one or two months were less likely to die than those still in their first month of captivity, but that the advantage of having survived a third month was small and there was no advantage to having survived a fourth month.''
-
-\begin{sidewaystable}
-\caption{controlling for months survived}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-                                         & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.989                               & -0.009                              & 0.982*                              & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.612++                             & -0.146 & 1.604++ & -0.145 \\
-Fraction of company dying before capture & 1.368                               & -1.001                              & 1.117                               & -0.811 & 0.832 & -0.603 \\
-Professional or propietor                & 0.56                                & -0.145                              & 0.557                               & -0.142 & 0.547 & -0.14 \\
-Artisan                                  & 0.946                               & -0.121                              & 0.951                               & -0.121 & 0.939 & -0.12 \\
-Laborer                                  & 1.302                               & -0.158                              & 1.302                               & -0.156 & 1.298 & -0.156 \\
-German                                   & 1.22                                & -0.223                              & 1.195                               & -0.216 & 1.178 & -0.213 \\
-Irish                                    & 0.774                               & -0.125                              & 0.770*                              & -0.122 & 0.756* & -0.12 \\
-British                                  & 0.618*                              & -0.168                              & 0.632*                              & -0.172 & 0.634* & -0.174 \\
-Other                                    & 0.658*                              & -0.156                              & 0.650*                              & -0.156 & 0.647* & -0.154 \\
-Sargeant, corporal or officer            & 0.533++                             & -0.114                              & 0.531++                             & -0.111 & 0.526++ & -0.11 \\
-Age at captivity                         & 1.047++                             & -0.008                              & 1.046++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Survived 1 month                         & 0.407++                             & -0.08                               & 0.362++                             & -0.072 & 0.352++ & -0.071 \\
-Survived 2 months                        & 0.472++                             & -0.092                              & 0.401++                             & -0.08 & 0.393++ & -0.078 \\
-Survived 3 months                        & 0.74                                & -0.137                              & 0.64                                & -0.12 & 0.631 & -0.118 \\
-Survived 4 or more months                & 0.833                               & -0.134                              & 0.745*                              & -0.12 & 0.740* & -0.119 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1307.333                           &                                     & -1287.9                             &  & -1285.595 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Cox Proportional Hazard Model}
-page 1477, line 26 footnote.
-``We also investigated the use of a Cox proportional hazard model to allow the baseline hazard to rise or fall in any month.
-Controlling for camp conditions, we obtained a statistically insignificant hazard ratio on friends of $0.987$ ($=0.009$).
-We suspect that we are losing power because of our small sample size.''
-
-\begin{sidewaystable}
-\caption{Cox proportional models}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err. & Hazard rate & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.992       & -0.009    & 0.987       & -0.009    &             &           \\
-Initial number of friends                &             &           &             &           & 0.978       & -0.009    \\
-Ln(number of prisoners in camp)          &             &           & 1.593++     & -0.149    & 1.587++     & -0.149    \\
-Fraction of company dying before capture & 1.751       & -1.298    & 1.558       & -1.148    & 1.179       & -0.867    \\
-Professional or propietor                & 0.557       & -0.144    & 0.556       & -0.142    & 0.546       & -0.139    \\
-Artisan                                  & 0.942       & -0.121    & 0.952       & -0.122    & 0.938       & -0.12     \\
-Laborer                                  & 1.284       & -0.157    & 1.287       & -0.157    & 1.284       & -0.156    \\
-German                                   & 1.241       & -0.228    & 1.218       & -0.223    & 1.2         & -0.22     \\
-Irish                                    & 0.765       & -0.126    & 0.763*      & -0.123    & 0.746*      & -0.121    \\
-British                                  & 0.613*      & -0.166    & 0.625*      & -0.169    & 0.626*      & -0.171    \\
-Other                                    & 0.658*      & -0.159    & 0.652*      & -0.159    & 0.649*      & -0.158    \\
-Sargeant, corporal or officer            & 0.538++     & -0.115    & 0.537++     & -0.113    & 0.532++     & -0.112    \\
-Age at captivity                         & 1.048++     & -0.008    & 1.046++     & -0.008    & 1.046++     & -0.008    \\
-Height at entlistment                    & 1.01        & -0.008    & 1.01        & -0.007    & 1.011       & -0.007    \\
-Observations                             & 23256       &           & 23256       &           & 23256       &           \\
-Log pseudo likelihood                    & -3102.845   &           & -3086.134   &           & -3083.63    &           \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{table}[ht]
-\centering
-\caption{table 4 net transfer}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lll}
-\hline
-VARIABLES               & Hazard Rate & Std. err. \\
-Net transfer of friends & 0.946**     & -0.024    \\
-Observations            & 15998       &           \\
-\end{tabular}
-\end{table}
-
-\paragraph{On limiting the sample}
-page 1480, line 17.
-``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged.
-The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).''
-
-\paragraph{On the mortality of privates}
-page 1480, line 54.
-``The fraction of sergeants or higher rank is not a reflection of own officer mortality.
-When we restricted the sample to privates, we found that the derivative of this coefficient was 0.115 (sdev=0.054).''
-
-\paragraph{On the role of networks in predicting escape from Andersonville}
-page 1482, line 25.
-``Also suggestive of friends not always helping survival is that, among the men at Andersonville, we find no evidence that the number of friends predicted whether an individual was one of the 140 escaped.''
-
-See table below for the final three verifications:
-
-\begin{sidewaystable}
-\caption{Final three specifications}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llll}
-\hline
-                                                 & Dependent variable: Lived & Dependent variable: Lived & Dependent variable: Escaped \\
-                                                 & Shorter time period       & Privates only             &                             \\
-Number of men in company                         & 0.003++                   & 0.003++                   & 0                           \\
-                                                 & -0.001                    & -0.001                    & 0                           \\
-Fraction of company with rank sergeant or higher & 0.115                     & 0.139++                   & -0.001                      \\
-                                                 & -0.054                    & -0.036                    & -0.002                      \\
-Number of men with same last name in regiment    & 0.033++                   & 0.035++                   & 0                           \\
-                                                 & -0.007                    & -0.007                    & 0                           \\
-Log(number of men in camp from same town)        & -0.003                    & -0.001                    & 0                           \\
-                                                 & -0.005                    & -0.005                    & 0                           \\
-Pseudo R2                                        & 0.036                     & 0.047                     & 0.015                       \\
-Observations                                     & 25880                     & 27923                     & 28190                       \\
-\end{tabular}
-\end{sidewaystable}
-
-The only in-text claim that we are not able to confirm is their statement that there is no mortality difference between the colored non-officers and the rest of the Andersonville POWs (page 1480, footnote 29) as we don’t have any information on the race of the POWs.
-
-\section*{Appendix: Non-parametric estimation}
-The following figures are our replications of the Kaplan-Meier survival estimates which show no differences to the original:
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimate}
-\label{kmSurvival}
-\includegraphics[scale=0.3]{kaplan1.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by early and late capture date}
-\label{kmCapture}
-\includegraphics[scale=0.3]{kaplan2.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by camp for late captures}
-\label{kmCamp}
-\includegraphics[scale=0.3]{kaplan3.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by number of friends for Anderson}
-\label{kmNumber}
-\includegraphics[scale=0.3]{kaplan4.png}
-\end{figure}
-
-\printbibliography
-
-\end{refsection}
-
-\begin{refsection}
-
-\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
-\label{currency}
-\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
-
-In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor, is the result of the fact that this risk factor eliminates the previously existing uncertainty.
-In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
-This view is enforced by the fact that the equilibrium is most pronounced when the risk factor (epsilon) is minimised (i.e.~set equal to zero), as the authors state themselves.
-Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium is in fact the entire `ripe for attack' domain.
-
-\nocite{taleb2010black}
-\printbibliography
-\end{refsection}
-
 \begin{refsection}
 \chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
-\label{bitcoin}
-In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
+\label{btc}
+In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
 This currency -the first of a group called cryptocurrencies- has the following economics features:
@@
 However, in the targeted developing economies, many phones are not smartphones, the vast majority using Nokia Operating System (Nokia OS).
-These phone can also run applications, using the Java Mobile App platform.
-Currently there are no Bitcoin apps available for this platform.
+ These phone can also run applications, using the Java Mobile App platform. Currently there are no Bitcoin apps available for this platform.
 
 I propose to participate in the development of open-source applications which would enable the users of stupid phones.
-We can then exploit the temporal difference when releasing the applications in different languages at different times, as well the downloads from traceable IP addresses.
+We can then exploit the temporal difference when releasing the applications in different languages at different times,
+as well the downloads from traceable IP addresses.
 
-\printbibliography
+\section{Data}
+\label{btc:data}
+Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
+Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
+Much like the way bank clients have a claim to their money, which is in the bank's vault.
 
-\end{refsection}
+Therefore Bitcoin purchases at exchanges do not lead to transaction being recorded in the blockchain.
+Since the Bitcoins remain in the Exchange's wallet, the only thing which changes is the claims of the clients.
 
-\begin{refsection}
-\chapter{End notes}
-\label{end-notes}
-In the previous chapters I have presented my current research projects. These projects are in various stages of completions.
-
-I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey done before and after a highly relevant policy change.
-Especially since the methodology and location are the same as in \textcite{duflo2000, duflo2003} In addition to this there is now a third data wave which has become available.
-This provides us with more data, and mostly the opportunity to use more interesting methodology.
-The text of the paper still has to be written.
-
-The replication of Surviving Andersonville is already completed in term of the replication in Stata.
-We would like to redo the analysis in R \parencite{R}.
-The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
-The findings of this replication can summarised as:
-
-\begin{quote}
-``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
-It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
-This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
-\end{quote}
-
-We do not expect to find anything similar to Bell and Miller, but think that it can nevertheless be interesting to replicate findings using a different software package.
-In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
-In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
-
-The discussion of \textcite{morris1998unique} is in a very early stage.
-I have looked at the paper in detail, I have also done a brief analysis of my main critique, namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
-However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
-In addition to this, this example should demonstrate how the entire `ripe for attack' region is not solved for the unique equilibrium.
-
-Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin.
-I would like to analyse the spread of this.
-I propose to follow the spread of applications for platforms which are popular in developing economies.
-
-At this point, three out of four of the previously discussed research projects are some form of a replication of prior work.
-As replications they are mostly critiques of others' work, rather than constructive ideas.
-This is mostly a result of the fact that these projects progress faster.
-For this reason, these research projects have progressed more than the projects which are primarily based on my own ideas.
-However, it is my attention to shift the focus of my thesis to include more original work.
-Here I present two more ideas which are too preliminary to include in the main body of the text, but are based on my own work.
-
-Firstly, I was in charge of setting up a baseline diagnostic into security perceptions in Conakry, Guinea.
-This diagnostic will be used to analyse the impact of a police reform conducted here.
-The reform constitutes of the implementation of a model of `police de proximitee'.
-The baseline consist of 4500 interviews using smartphones in the comune of Conkary as well a large number of interviews in N'Zerekore (east Guinea).
-Some time after the implementation of the police reform as follow up study will be conducted.
-I propose to conduct an impact evaluation using the results from the studies in which I have taken and will take part.
-
-Secondly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy.
-I would like to write one paper about an issue relating to this.
-In particular I would like to at the effect of outliers.
-The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}.
-I would like to see how these principles affect research in development microeconomics.
-
-In this document I have tried to give a description of my research projects.
-None of these projects are near completion and many are in fact in a very early stage.
-The purpose of this has been to describe the direction I am taking with my thesis, and to receive feedback on this.
-As a result of this being work in progress, the articles are still incomplete, this includes lacking the proper attribution of ideas using citations.
+\begin{itemize}
+ \item The blockchain (public ledger)
+ \begin{itemize}
+ 	\item IP address
+ 	\item Language of transaction notice
+ 	\item Transaction times
+ \end{itemize}
+ \item The exchanges
+ \begin{itemize}
+ 	\item Location of exchanges
+ 	\item Transaction costs for each currency
+	\item The order books
+	\item Transaction times
+ 	\item The traded currency
+ \end{itemize}
+ \item Software
+ \begin{itemize}
+ 	\item Downloads
+ 	\item Translation contributions (?)
+ 	\item Connections to server
+ \end{itemize}
+\end{itemize}
 
@@
 \end{refsection}
-
-\end{document}

### 2013-12-28 endnotes.tex
break away chapters

--- 2013-11-22 draft.tex
@@
-\documentclass[a4paper]{report}\usepackage{graphicx, color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
-\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
-\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
-\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
-\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
-\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
-\newcommand{\hlslot}[1]{\textit{#1}}%
-\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\usepackage{mathtools}
-\usepackage{rotating}
-\usepackage{graphicx}
-\usepackage{cleveref}
-\usepackage[authordate,backend=biber]{biblatex-chicago}
-\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
-
-\title{Preliminary Thesis Defence\\~\\
-\begin{tabular}{rl}
-Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
-Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
-\end{tabular}
-}
-
-\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}\\~\\
-The Graduate Institute, Geneva}
-
-\let\oldmarginpar\marginpar
-\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]
-{\raggedright\footnotesize #1}}
-
-\addglobalbib{bibliography.bib}
-
-\newbibmacro{string+doiurlisbn}[1]{%
-  \iffieldundef{doi}{%
-    \iffieldundef{url}{%
-      \iffieldundef{isbn}{%
-        \iffieldundef{issn}{%
-          #1%
-        }{%
-          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
-        }%
-      }{%
-        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
-      }%
-    }{%
-      \href{\thefield{url}}{#1}%
-    }%
-  }{%
-    \href{http://dx.doi.org/\thefield{doi}}{#1}%
-  }%
-}
-
-\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
-\DeclareFieldFormat[article,incollection]{title}%
-    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
-\begin{document}
-
-\maketitle
-\tableofcontents
-\listoftables
-\listoffigures
-
-\begin{refsection}
-\chapter{Introduction}
-In this Preliminary Thesis Defence I present the research projects that I intend to use for my PhD dissertation. These projects are titled:
-
-\begin{itemize}
-\item Additional South African Evidence on Pensions and Child Growth (\ref{south-africa})
-\item Replication: Surviving Andersonville (\ref{andersonville})
-\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\ref{currency})
-\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\ref{bitcoin})
-\end{itemize}
-
-These project are in various stages of completion. Below I will briefly describe the research idea, the current state, and the potential for each project.
-
-Firstly, the paper Additional South African Evidence of Pensions and Child Growth builds \textcite{duflo2000, duflo2003}.
-These papers look at the effect of the gender of grandparents on the growth metrics of their grandchildren.
-A problem in this comparison lies in the fact that pension eligibility of men was at 65 years, whereas it was 60 for women.
-This paper makes use of a Household Survey from 2008, 2012 and 2013.
-The survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
-As it stands now I have analysed the data from 2008 and 2012.
-The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
-
-Secondly, together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
-We were able to replicate all results from the paper, save for a few decimal numbers, which we have taken to be the result of rounding errors.
-However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
-When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
-As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
-The authors however, aggregate these two.
-This leads to overstated magnitudes of the social ties of POWs.
-This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
-At this point our replication is quite complete.
-Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
-
-Thirdly, \textcite{morris1998unique} claims that introducing a measure of risk in a model of currency attacks, leads to a unique equilibrium.
-It thus solves the previous multiple-equilibrium zone called `ripe for attack' for a unique equilibrium.
-I believe that this is a result of the fact that the risk factor introduces replaces uncertainty, not certainty.
-We thus gain information.
-I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
-
-Fourthly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies.
-Bitcoin transactions are conducted using an electronic process called signing.
-I would like to study the role of Bitcoin in remittances.
-For this I would like to participate in building Bitcoin applications for the simple type of phones common in developing economies (sometimes referred to stupid phones).
-We could study the spread of bitcoin by looking at the downloads of the apps from regions, as well looking at how releasing the app in different languages evolves.
-
-After this the papers follow, in the order listed above.
-A separate citations section is included for each chapter.
-For ease of reference, the titles of the citations in the bibliography link to the online articles using DOIs and URLs.
-In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.
-I also mention some very preliminary ideas.
-
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{Pensions and Child Growth in South Africa}
-\label{south-africa}
-\section*{Abstract}
-
-In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.
-
-I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of two surveys which were done before and after the lowering of the pension eligibility age for men to the same age as women.
-
-The main preliminary finding is that the household effect was only significant in 2012.
-
-\section{Introduction}
-
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
-is very similar to \textcite{duflo2000, duflo2003}.
-The deviation from international standards \parencite{who2006child} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status and gender.
-
-The anthropometrics are useful for computing z-scores.
-These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
-
-The South African pension is a interesting variable to measure income because of its criteria.
-Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias issues.
-The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
-
-Duflo finds evidence in South Africa's 1993 \href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated Household Survey} that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension.
-This is directly after the significant increase in the pension sum for blacks.
-The pension-eligibility age at this time was 60 for women and 65 for men.
-
-This study deviates from the Duflo study in several ways.
-In 2008 and 2012, the first and second wave of the \textcite{saldru2008nids, saldru2012nids} have gathered similar data.
-In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 (\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).
-
-This happened in a few steps.
-As of July 16th 2008 men aged 63 and 64 were eligible for a pension.
-Men aged 61 and 62 became eligible in April 2009.
-Finally in January 2010, pension eligibility age was at 60 for all citizens.
-
-Another deviation is the usage of WHO z-scores \parencite{who2006child} in stead of CDC z-scores \parencite{nchs2000cdc}, since these have superseded the CDC charts, however this should not be of any consequence, as long as we use the same standards consistently.
-
-The main preliminary result is that the household effect (i.e.~having one or more recipients in the household) is very insignificant in the 2008 estimate.
-But in the 2012 estimate it is very significant.
-
-\section{Data}
-
-In this paper I use data from two sources.
-The first is the South African National Income Dynamics Survey \parencite{saldru2008nids, saldru2012nids} and the second is the World Health Organization's Child Growth Standards \parencite{who2006child}.
-
-The main source of data is the NIDS.
-This survey collects data on a representative set of appproximately 10,000 South African households.
-The primary information variables that I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.
-
-For adults, several variables measure the different amounts and sources of income.
-Among those, a variable for the adult receiving a state pension, and if so, how much.
-This is a numeric variable, the values of which lie very close together.
-For simplicity I have temporarily used this variable as a dummy.
-
-The children's anthropometrics taken are, length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores have been calculated.
-Unfortunately, the latest version of wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
-However, I have computed the length-for-age z-scores manually.
-
-In 2006 the WHO published its standards for child growth.
-These standards are based on the scores of children from different ethnic populations in households which maintained a healthy lifestyle.
-The standards provide the means and standards deviations used.
-These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-p1 <- \hlfunctioncall{ggplot}(\hlfunctioncall{subset}(w1_child, w1_woman_60 == 1))
-p1 <- p1 + \hlfunctioncall{aes}(w1_c_age_m, w1_zhfa, colour = \hlfunctioncall{factor}(w1_c_woman))
-p1 <- p1 + \hlfunctioncall{stat_smooth}(method = \hlstring{"loess"}) + \hlfunctioncall{geom_point}()
-p1
-\end{alltt}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 324 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 263 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 51 rows containing missing values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 638 rows containing missing values (geom\_point).}}\end{kframe}
-\includegraphics[width=\maxwidth]{figure/r-p1}
-
-\end{knitrout}
-
-\section{Results}
-
-Basic HAZ (2008)
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(w1_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-## Call:
-## lm(formula = w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + 
-##     w1_best_age_yrs, data = w1_child, subset = w1_c_age_m >= 
-##     6 & w1_c_age_m <= 60)
-## 
-## Residuals:
-##    Min     1Q Median     3Q    Max 
-## -4.779 -1.036 -0.169  0.834  7.060 
-## 
-## Coefficients:
-##                  Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.43e+00   1.44e-01   -9.87   <2e-16 ***
-## w1_spen_w        2.32e-02   1.15e-01    0.20   0.8402    
-## w1_spen_m        1.36e-01   1.72e-01    0.79   0.4281    
-## w1_h_tinc        3.62e-05   9.99e-06    3.62   0.0003 ***
-## w1_best_edu      1.63e-03   7.84e-03    0.21   0.8355    
-## w1_best_age_yrs  7.61e-03   3.64e-03    2.09   0.0369 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.77 on 1436 degrees of freedom
-##   (1936 observations deleted due to missingness)
-## Multiple R-squared:  0.0134,	Adjusted R-squared:  0.00994 
-## F-statistic: 3.89 on 5 and 1436 DF,  p-value: 0.00164
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz0)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.835  -0.050   0.000   0.788   7.070 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.172e+00  7.388e-02 -15.861  < 2e-16 ***
-## w1_spen_w        1.748e-02  9.477e-02   0.184   0.8536    
-## w1_spen_m       -1.374e-01  1.444e-01  -0.952   0.3414    
-## w1_h_tinc        2.995e-05  5.606e-06   5.342 9.69e-08 ***
-## w1_best_edu      2.410e-03  3.532e-03   0.682   0.4951    
-## w1_best_age_yrs  4.127e-03  1.863e-03   2.215   0.0268 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4889 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlfunctioncall{summary}(tsls_w1w2_haz1)
-\end{alltt}
-\begin{verbatim}
-## 
-##  2SLS Estimates
-## 
-## Model Formula: w1_zhfa ~ w1_spen_w + w1_spen_m + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Instruments: ~w2_spen_w + w2_spen_m_65 + w1_h_tinc + w1_best_edu + w1_best_age_yrs
-## 
-## Residuals:
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
-##  -4.990  -0.836  -0.050   0.000   0.786   7.040 
-## 
-##                   Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)     -1.173e+00  7.387e-02 -15.880  < 2e-16 ***
-## w1_spen_w        8.576e-03  9.541e-02   0.090   0.9284    
-## w1_spen_m       -9.189e-02  1.348e-01  -0.681   0.4956    
-## w1_h_tinc        2.992e-05  5.605e-06   5.339 9.85e-08 ***
-## w1_best_edu      2.443e-03  3.531e-03   0.692   0.4890    
-## w1_best_age_yrs  4.092e-03  1.860e-03   2.200   0.0278 *  
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 1.4885 on 4227 degrees of freedom
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\printbibliography
-
-\end{refsection}
-
-\begin{refsection}
-\chapter{Replication: Surviving Andersonville}
-\label{andersonville}
-\textbf{Aksel Erbahar, Cecilia Heuser, Victor K\"ummritz, Bastiaan Quast}
-
-\section*{Abstract}
-We replicate \textcite{costa2007surviving}.
-We are able to replicate all the result from the paper.
-The authors make a number of choices in order to arrive to the results published.
-We raise some concerns regarding some of these choices.
-For example, the authors treat the POWs of the two Andersonville camps as if they were in the same camp.
-This inflates size of the POWs social network, which is used as the explanatory variable.
-When we make choices which to us seem more defendable, we cannot, quantitatively and qualitatively, replicate the authors' results.
-
-\section{Summary of the paper}
-\textcite{costa2007surviving} try to estimate the effect of quality and size of social networks on ensuring the survival of prisoners of war (POW) in POW camps.
-To examine the relationship the authors combine two datasets, a longitudinal dataset of Union Army soldiers and a cross-sectional dataset of the POW camp in Andersonville.
-
-The empirical specification for the longitudinal data that measures the effect of the size of the network is as follows:
-
-\begin{equation} \label{eq:ht}
-h(t) = \exp ( \beta_1 F + \beta_2 I + \beta_3 M )
-\end{equation}
-
-where $h$ is hazard at time $t$, $F$ is the number of friends (=social network), $I$ are individual characteristics and $M$ macro camp conditions.
-The number of friends is measured as the number of POWs of the same company and varies by month due to deaths or camp transfers.
-As it might capture the lagged mortality of the group, the authors use as second strategy the initial number of friends as a time-invariant proxy.
-In addition, they instrument for the number of friends using the number of net camp transfers combined with a dummy indicating whether the POW was transferred to account for omitted variables.
-The specification for the Andersonville data in turn is a probit model:
-
-\begin{align}
-Pr(S = 1) &= \Phi (\beta_1 F + \beta_2 F) \label{s1} \\
-Pr(S = 1) &= \Phi (\beta_1 F_i + \beta_2 F_{ij} + \beta_3 I | ethnicity = j) \label{s1b} 
-\end{align}
-
-where equation (3.2) examines quantity and equation (3.3) quality of the social network. The measure for number of friends here is the number of POWs from the same company in Andersonville.
-
-The longitudinal data indicates that POWs had special characteristics.
-For instance, they were likely to be volunteers, and from companies with more wounded or dead.
-POWs with more friends were typically US-born and wealthier while Irish and older men had less friends.
-Concerning survival rates, Kaplan-Meier hazard rates show that POWs captured later (after 1963 when the Union and the Confederate Army stopped exchanging POWs) have lower survival rates.
-They also show that survival rates were higher for POWs with 10 or more friends.
-In addition, the rates show that it takes 50 days until there is a divergence in survival between POWs with and without friends.
-The exponential function estimates that an additional friend leads to a 0.98 times lower mortality hazard.
-An increase in the number of friends from 0 to 5 (5 to 10), decreases the predicted probability of death from 0.31 to 0.28 (0.26) while a spline specification provides evidence that the effect is greatest for the first two friends.
-In addition, survival is more likely for POWs that had survived at least one or two months.
-Factors increasing mortality are the number of men in the camp, low rank, high age, and height among others.
-Insignificant variables are for instance wealth and marital status.
-There is no evidence for individual heterogeneity.
-The use of a Weibull specification indicates no duration dependence (toughen up effects).
-Interestingly though, a Cox model gives no significant effect of friends which the authors interpret as a result of their loss of power due to the small sample size.
-Robustness checks, including the IV approach and the effect of friends transferred in, confirms the significant effect of friends.
-Finally, the cross-sectional results provide evidence that having the same last name, being from the same town for smaller towns, ethnic similarity and having a sergeant or a higher rank in one's network are all important factors in raising survival probabilities which in turn shows that the quality of social networks matters.
-
-In summary, Costa and Kahn are able to show that quantity and quality of social networks mattered for survival in civil war POW camps.
-Potential explanations for this are the sharing of scarce resources, moral support and protection from other prisoners.
-
-\section{Data}
-The raw data for the first part of the paper is extracted from the Union Army dataset readily accessible at \url{http://www.cpe.uchicago.edu}.
-This dataset draws information from censuses, medical records and military pension records linking military, socioeconomic and health information for nearly $40,000$ white males that served in the Union Army during the Civil War.
-For the second part, the Andersonville database is available at \url{http://www.itd.nps.gov/cwss} but only as a ``searchable version'', which allows viewing the information for one soldier at a time, and more convenient formats are not readily available.
-
-The datasets provided for the estimations alongside with the publication are already partially processed parts of the raw data available online.
-No clear guidance is given as to what steps were taken to go from the raw data to the files provided, and matching both things proved to be less than straightforward.
-In view of this, we decided to proceed with the replication using the files provided by the authors, pointing out along the way the cases where potential problems in them seemed likely given the raw data we observed.
-Taking those files as starting points, it is possible to reproduce the tables and graphs published in the paper, so in this sense we can say that the data set is complete.
-Originally, some of the data required by the published .do files was not included in the published data files, but the authors provided it promptly upon our request and added it subsequently to the online files of the publishing journal.
-
-The data and .do files provided do not describe or label many of the variables used, nor does the limited variable description in the Appendix cover all of them.
-A very thorough description of the variables in the raw data set can be found at its online source, but the match between this and the variables in the files provided is not straightforward or complete, since some of them are already created by the authors from the raw data.
-The description of the data itself, mainly of the variables that are used most often, is succinct but adequate, with Table 1 and Table 2 presenting some relevant descriptive traits.
-Despite this, some attention should be drawn to the fact that some of the variables have a relevant share of missing values (only the highest number of observations is reported), a point that will be commented in detail later on.
-
-\section{Stata code and interpretation}
-All codes run to their full extent, and produce the estimations presented in the paper, with minor differences that we describe in detail below.
-The codes themselves are not commented at all and include plenty of estimations and specifications not included in the published paper, as well as unexplained data processing steps.
-No exporting commands were set up, or log files kept, which might be the root of some of the rounding and significance discrepancies we have found.
-
-In what follows, all reproduced tables are presented with a comment on the differences found (in bold), whenever there were any.
-
-\subsection{Tables}
-Table 1: This table presents the means of most variables later used for estimation, dividing observations in POWs and NON POWs, to illustrate ex ante differences in observables between them.
-
-\begin{table}[bt]
-\centering
-\caption{Characteristics of Soldiers by POW Status}
-\label{characteristics}
-\begin{tabular}{lllllll}
-\hline
-                           & All   & Obs.  & Never POW & Obs.  & POW   & Obs. \\
-US born                    & 0.745 & 35007 & 0.745     & 31967 & 0.743 & 3040 \\
-US born corrected          & 0.747 & 34941 & 0.745     & 31966 & 0.759 & 2975 \\
-Irish                      & 0.087 & 34941 & 0.086     & 31966 & 0.102 & 2975 \\
-German                     & 0.074 & 34941 & 0.075     & 31966 & 0.062 & 2975 \\
-British                    & 0.039 & 34941 & 0.039     & 31966 & 0.033 & 2975 \\
-Other                      & 0.054 & 34941 & 0.055     & 31966 & 0.043 & 2975 \\
-Artisan                    & 0.2   & 34941 & 0.199     & 31966 & 0.211 & 2975 \\
-Farmer corrected           & 0.505 & 34941 & 0.505     & 31966 & 0.508 & 2975 \\
-Professional or proprietor & 0.075 & 34941 & 0.077     & 31966 & 0.061 & 2975 \\
-Laborer                    & 0.212 & 34941 & 0.212     & 31966 & 0.212 & 2975 \\
-Unknown                    & 0.007 & 34941 & 0.007     & 31966 & 0.008 & 2975 \\
-Enlisted in 1861           & 0.21  & 35007 & 0.205     & 31967 & 0.263 & 3040 \\
-Enlisted in 1861 corrected & 0.21  & 34878 & 0.205     & 31906 & 0.269 & 2972 \\
-Enlisted in 1862                  & 0.344   & 34878 & 0.331   & 31906 & 0.487  & 2972 \\
-Enlisted in 1863                  & 0.068   & 34878 & 0.066   & 31906 & 0.087  & 2972 \\
-Enlisted in 1864                  & 0.256   & 34878 & 0.266   & 31906 & 0.147  & 2972 \\
-Enlisted in 1865                  & 0.122   & 34878 & 0.132   & 31906 & 0.009  & 2972 \\
-Volunteer                         & 0.909   & 34941 & 0.905   & 31966 & 0.951  & 2975 \\
-Height in inches                  & 67.599  & 34941 & 67.589  & 31966 & 67.709 & 2975 \\
-Household property income in 1860 & 534.155 & 13769 & 531.734 & 12509 & 558.2  & 1260 \\
-Company birthplace fragmentation  & 0.642   & 34941 & 0.644   & 31966 & 0.62   & 2975 \\
-Company occupation fragmentation  & 0.559   & 34941 & 0.558   & 31966 & 0.57   & 2975 \\
-Fraction company died as non-POWs & 0.135   & 34941 & 0.131   & 31966 & 0.182  & 2975 \\
-\end{tabular}
-\end{table}
-
-We have added to \autoref{characteristics} the number of observations per variable, not originally included in the paper, in order to highlight the fact that some of them have significant amounts of missing values, something that should be kept in mind later at the estimation stage.
-In this table, the case in point is Household property income in 1860, which is used in most of the specifications proposed, but as will be discussed for later tables, this is a pattern common to all the variables imported from census data.
-Additionally, considering the number of observations for each of the variables leads to the suggestion of a small correction for three of the dummy variables describing categories: US born, farmer and enlisted in 1861.
-The initial data file is missing these variables, which are likely to have been dropped as the basis category for estimation purposes in some other use of the data.
-They were then rebuilt in the .do file from the remaining categories in such a way that generated zeroes for some observations that should have been missing (except for farmer, which is not included at all in the file).
-For example: as provided by the code, US born has $35,007$ observations, whereas other nationality dummies, all built from the same original variable, have $34,941$.
-The correction proposed then, is to set these dummies to missing whenever the other categories of their class are missing, which slightly changes their descriptive statistics (for example the mean of US born goes from $0.745$ to $0.747$ when this correction is implemented).
-
-Remaining discrepancies are minor and could be due to some kind of rounding difference.
-An alternative explanation for these differences is that the table was produced from a slightly different dataset.
-Considering that even the most populous variables present over 500 observations less than the amount declared in the paper, and the fact that one of the variables (farmer) is not included in the data file at all, we consider the second option to be more likely, which would also explain the minor differences in the means of Artisan, British, Height in inches, etc.
-
-A last and minor comment is that the inclusion of the variable volunteer is surprising, since by sample design the Union Army dataset was restricted to white volunteer infantry regiments.
-The inclusion of this variable when comparing POWs and non POWs probably responds to the point raised in the paper about POWs not being representative of all soldiers, for example in ideology (p.1471).
-A variable that reflects that both POWs and non POWs volunteered in similar proportions would suggest homogeneity between POWs and non POWs in this dimension and, hence, increase  external validity.
-The similarities observed in Table 1 between POWs and non POWs in their mean of volunteer do not reflect that, since they are both close to one by construction.
-Any individuals not listed as volunteers, either correspond to the very few drafted men, or are actually soldiers that re-enlisted as commissioned officers, but were originally volunteers, as explained in the codebooks for the source data.
-
-\ref{friends}: This table describes the variables later used in the main regressions, focusing in this case only on POWs.
-It also presents separately their mean and standard errors for the subsamples of POWs with few (less than 3) and many friends (three or more).
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity}
-\label{friends}
-\begin{tabular}{llllllllll}
-
-                                  & \multicolumn{3}{l}{All} & \multicolumn{3}{l}{Few friends ($<3$)} & \multicolumn{3}{l}{Many friends ($>=3$)} \\
-                                  & Mean                    & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-& Mean & Std.
-err.
-& No.
-obs.
-\\
-US born                           & 0.731                   & 0.444                                & 1976                                   & 0.708 & 0.455 & 990 & 0.754 & 0.431 & 986 \\
-Irish                             & 0.12                    & 0.325                                & 1976                                   & 0.115 & 0.319 & 990 & 0.125 & 0.331 & 986 \\
-German                            & 0.063                   & 0.243                                & 1976                                   & 0.081 & 0.273 & 990 & 0.045 & 0.207 & 986 \\
-British                           & 0.034                   & 0.182                                & 1976                                   & 0.042 & 0.202 & 990 & 0.026 & 0.16 & 986 \\
-Other                             & 0.05                    & 0.217                                & 1976                                   & 0.053 & 0.223 & 990 & 0.047 & 0.211 & 986 \\
-Artisan                           & 0.209                   & 0.407                                & 1976                                   & 0.214 & 0.41 & 990 & 0.204 & 0.403 & 986 \\
-Farmer                            & 0.421                   & 0.494                                & 1976                                   & 0.44 & 0.497 & 990 & 0.401 & 0.49 & 986 \\
-Professional or propietor         & 0.07                    & 0.256                                & 1976                                   & 0.077 & 0.266 & 990 & 0.064 & 0.245 & 986 \\
-Laborer                           & 0.266                   & 0.442                                & 1976                                   & 0.243 & 0.429 & 990 & 0.288 & 0.453 & 986 \\
-Unknown                           & 0.034                   & 0.182                                & 1976                                   & 0.025 & 0.157 & 990 & 0.044 & 0.204 & 986 \\
-Enlisted in big city              & 0.475                   & 0.5                                  & 1976                                   & 0.493 & 0.5 & 990 & 0.457 & 0.498 & 986 \\
-Household property income in 1860 & 576.475                 & 1855.699                             & 817                                    & 483.609 & 1084.987 & 391 & 661.711 & 2348.676 & 426 \\
-Age when captured                 & 25.96                   & 7.056                                & 1966                                   & 26.645 & 7.415 & 990 & 25.265 & 6.604 & 976 \\
-Height when captured                 & 171.576 & 6.612 & 1925 & 171.79 & 6.384 & 974 & 171.356 & 6.833 & 951 \\
-Commisoned or noncommisoned officer  & 0.076   & 0.266 & 1976 & 0.083  & 0.276 & 990 & 0.07    & 0.255 & 986 \\
-Married in 1860                      & 0.257   & 0.437 & 817  & 0.276  & 0.448 & 391 & 0.239   & 0.427 & 426 \\
-Wounded 10 days before capture       & 0.118   & 0.323 & 1976 & 0.148  & 0.356 & 990 & 0.088   & 0.284 & 986 \\
-Fraction company dead before capture & 0.089   & 0.064 & 1976 & 0.093  & 0.07  & 990 & 0.085   & 0.057 & 986 \\
-Company birthplace fragmentation     & 0.542   & 0.2   & 1923 & 0.547  & 0.193 & 985 & 0.536   & 0.206 & 938 \\
-Company occupational fragmentation   & 0.596   & 0.173 & 1923 & 0.586  & 0.173 & 985 & 0.607   & 0.172 & 938 \\
-\end{tabular}
-\end{sidewaystable}
-
-This table is almost exactly reproduced, except for the minor differences set in bold, which appear to be rounding differences (and a typo in the case of Laborer).
-The number of observations stated on the table in the paper (1923) corresponds to the last variable in this case as well, even though, as mentioned for the previous table, it is relevant to keep in mind that some of the other variables of interest show a considerably lower count of observations, as can be seen in the added columns.
-For this table, this is the case of variables Married in 1860 and Household property income in 1860, which are both variables from the 1860 census.
-The main concern regarding this table is the process of organizing the data, particularly one step in which a merge to the file ``transfer.dta'' is conducted.
-This file contains the prisoner identifier variable, month, year, and a dummy variable reflecting whether the prisoner was transferred (transferin).
-This variable is not needed for \autoref{friends}, and we can only speculate that it was incorporated, as some other steps were, in an attempt to exactly reproduce the dataset used in \autoref{corrected}.
-The problem in this case is that the file ``transfer.dta'' contains duplicate observations, which in turn duplicates observations in the main data set via the merge, artificially inflating the number of observations in the data used for \autoref{friends}\footnote{Duplicate observations per month-year-prisoner are natural in the context of \autoref{corrected}, because in there capture time is measured per fortnight.
-Including additional observations because of this in a stage of data description such as this one is hardly appropriate.}.
-
-If these duplicate observations are eliminated from the ``transfer.dta'' file before the merge, the statistics presented do not seem to defer significantly, and certainly neither do the conclusions drawn from them, but the number of observations in the subsample considered is significantly lower.
-This exercise is presented in the table below.
-
-\begin{sidewaystable}
-\centering
-\caption{corrected}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{corrected}
-\begin{tabular}{llllllllll}
-\hline
-                                  & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. & Mean    & Std. err. & No. obs. \\
-US born                           & 0.732   & 0.443     & 1470     & 0.715   & 0.452     & 727      & 0.748   & 0.434     & 743      \\
-Irish                             & 0.122   & 0.327     & 1470     & 0.113   & 0.317     & 727      & 0.131   & 0.337     & 743      \\
-German                            & 0.06    & 0.237     & 1470     & 0.074   & 0.262     & 727      & 0.046   & 0.209     & 743      \\
-British                           & 0.034   & 0.181     & 1470     & 0.04    & 0.196     & 727      & 0.028   & 0.166     & 743      \\
-Other                             & 0.05    & 0.219     & 1470     & 0.056   & 0.231     & 727      & 0.044   & 0.206     & 743      \\
-Artisan                           & 0.212   & 0.409     & 1470     & 0.217   & 0.413     & 727      & 0.207   & 0.406     & 743      \\
-Farmer                            & 0.427   & 0.495     & 1470     & 0.442   & 0.497     & 727      & 0.413   & 0.493     & 743      \\
-Professional or proprietor        & 0.065   & 0.247     & 1470     & 0.073   & 0.26      & 727      & 0.058   & 0.234     & 743      \\
-Laborer                           & 0.265   & 0.441     & 1470     & 0.242   & 0.429     & 727      & 0.287   & 0.453     & 743      \\
-Unknown                           & 0.031   & 0.172     & 1470     & 0.026   & 0.16      & 727      & 0.035   & 0.184     & 743      \\
-Enlisted in big city              & 0.48    & 0.5       & 1470     & 0.486   & 0.5       & 727      & 0.475   & 0.5       & 743      \\
-Household property income in 1860 & 547.314 & 1637.903  & 615      & 476.274 & 1107.659  & 299      & 614.532 & 2014.738  & 316      \\
-Age when captured                 & 25.834  & 6.931     & 1465     & 26.4    & 7.263     & 727      & 25.276  & 6.544     & 738      \\
-Height when captured              & 171.526 & 6.624     & 1439     & 171.683 & 6.433     & 717      & 171.37  & 6.81      & 722      \\
-Commisioned or noncommisioned officer\footnote{Related to the point about the variable Volunteer made before, the name Commisioned or non commissioned officer may be misleading, since commissioned officers are excluded from the sample by construction.} & 0.074 & 0.262 & 1470 & 0.078 & 0.269 & 727 & 0.07  & 0.255 & 743 \\
-Married in 1860                       & 0.252 & 0.435 & 615  & 0.264 & 0.442 & 299 & 0.241 & 0.428 & 316 \\
-Wounded 10 days before capture        & 0.125 & 0.331 & 1470 & 0.155 & 0.363 & 727 & 0.096 & 0.294 & 743 \\
-Fraction company dead before capture  & 0.091 & 0.063 & 1470 & 0.094 & 0.069 & 727 & 0.089 & 0.056 & 743 \\
-Company birthplace fragmentation      & 0.542 & 0.198 & 1442 & 0.55  & 0.189 & 723 & 0.534 & 0.207 & 719 \\
-Company occupational fragmentation    & 0.593 & 0.175 & 1442 & 0.585 & 0.173 & 723 & 0.601 & 0.178 & 719 \\
-\end{tabular}
-\end{sidewaystable}
-
-Two additional remarks related to this are: a) whenever month was larger than 12, it is set to missing, b) all observations marked as having occurred in 1861 are shifted to 1862.
-Neither month nor year are directly used for this table, but they are the matching points for the merge to the ``transfer.dta'' file discussed above.
-The file “transfer.dta” also contains month>12 and observations for 1861, and they are not replaced in a similar fashion, introducing some additional artificial matching problems into the merge operation.3 Besides the potential distortions in the merge that these asymmetric replacements may cause, the switch of 1861 to 1862 seems particularly surprising given that no explanation for it is offered.
-
-Additionally, if the aim of this table is to have a general impression of the variables used in the main regressions (\autoref{corrected}), the same observations should have been considered in both accounts.
-This is not the case, since the observations with an unknown number of friends are dropped for this table, but not for the next one.
-
-\autoref{corrected}: This table shows the results of the hazard rate analysis using a set of covariates described in the previous tables and alternating two measures of friends: number of friends at the time of the observation and initial number of friends.
-
-\begin{sidewaystable}
-\caption{Social Networks and Individual Characteristics on Mortality}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{social}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{specification I} & \multicolumn{2}{l}{specification II} & \multicolumn{2}{l}{specification III} \\
-VARIABLES                                & Hazard rate                         & Std. err.                            & Hazard rate                           & Std. err. & Hazard rate & Std. err. \\
-Current number of friends                & 0.983                               & -0.008                               & 0.977++                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                      &                                       &  & 0.976++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                      & 1.536++                               & -0.14 & 1.521++ & -0.139 \\
-Fraction of company dying before capture & 1.091                               & -0.782                               & 0.892                                 & -0.636 & 0.63 & -0.449 \\
-Professional or proprietor               & 0.567                               & -0.146                               & 0.563                                 & -0.143 & 0.556 & -0.141 \\
-Artisan                                  & 0.944                               & -0.119                               & 0.947                                 & -0.119 & 0.937 & -0.117 \\
-Laborer                                  & 1.298                               & -0.154                               & 1.295                                 & -0.152 & 1.287 & -0.152 \\
-German                                   & 1.197                               & -0.215                               & 1.166                                 & -0.209 & 1.149 & -0.206 \\
-Irish                                    & 0.768*                              & -0.121                               & 0.762*                                & -0.118 & 0.750* & -0.117 \\
-British                       & 0.641*    & -0.171 & 0.654     & -0.174 & 0.656    & -0.177 \\
-Other                         & 0.658*    & -0.154 & 0.645*    & -0.153 & 0.642*   & -0.151 \\
-Sergeant, corporal or officer & 0.549++   & -0.115 & 0.543++   & -0.111 & 0.541++  & -0.111 \\
-Age at captivity              & 1.045++   & -0.007 & 1.044++   & -0.007 & 1.044++  & -0.007 \\
-Height at enlistment          & 1.01      & -0.007 & 1.01      & -0.007 & 1.011    & -0.007 \\
-Observations                  & 23256     &        & 23256     &        & 23256    &        \\
-Number of subjects            & 3026      &        & 3026      &        & 3026     &        \\
-Log pseudo likelihood         & -1324.607 &        & -1308.229 &        & -1307.17 &        \\
-\end{tabular}
-\end{sidewaystable}
-
-\autoref{corrected} is reproduced almost completely, except for the results in bold, for which the significance level differs from the one presented in the publication.
-
-In this case, month larger than 12 is replaced by 99, and in this case as well this might generate distortions since an equivalent change was not performed in the file to which this is merged (``Died.dta'').
-The observations for which the number of friends is unknown are not dropped here, but set to zero.
-Whenever the number of deaths in the prisoners' company before capture is unknown, it is set to zero.
-Whenever the number of men in camp is unknown it is set to 40.
-Whenever the variables imported from the 1860 census are missing (i.e.
-there was no match to the census) they are still included in the regression by setting their value to zero in the case of dummy variables (married and illiterate), and by taking log(1+variable) in the case of Household property.
-In all of these cases, dummy variables are included in the regression indicating whether the data is actually missing (e.g.
-a dummy variable that takes value one if the observation was not matched to the 1860 census, link60).
-It is understandable that in order to maintain a healthy sample size, and to use as much of the information as possible, some assumptions are made, but the trade off related to this point is that these assumptions may create artificial noise in the data that would not be fully captured by these control dummies.
-
-\autoref{social}: This table presents an alternative estimation strategy.
-As a benchmark, the effect of the number of friends in the camp is estimated including company fixed effects and the same covariates as before.
-To avoid endogeneity issues that may arise due to the potential correlation between the current number of friends and the prisoner’s own unobservable health (via its correlation to the lagged mortality of the group), an IV-hazard rate strategy is pursued next.
-The instruments chosen are the new number of friends the prisoner has in each period (the newly captured soldiers of his company) and a dummy variable that reflects whether the POW was transferred.
-Both variables clearly affect the number of friends a POW has, and are meant to be uncorrelated with his unobservable health, since transfers and the amount of newly captured men assigned to each camp were determined by camp needs or evolution of war events5.
-In the first stage, the number of friends is regressed on the instruments, as well as the whole set of covariates and fixed effects.
-The predicted residuals of this first stage are then included in the second stage, along with all covariates, fixed effects and the number of friends.
-This procedure is repeated 100 times, preserving the coefficients and standard errors of the number of friends, the number of men in the camp and the residuals, as well as the R-squared of the first stage.
-The final result of this Montecarlo procedure is obtained by computing the mean of those variables among the 100 repetitions.
-
-\begin{sidewaystable}
-\caption{Effect of Social Networks on Mortality, with Company Fixed Effects and Instrumented}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effect}
-\begin{tabular}{lllll}
-\hline
-                                    & \multicolumn{2}{l}{Original} & \multicolumn{2}{l}{IV} \\
-                                    & Haz. Rate                    & Std. Err.              & Haz. Rate & Std. Err. \\
-Number of friends                   & 0.978*                       & -0.012                 & 0.895 & -0.055 \\
-Ln(total number of men in the camp) & 1.437++                      & -0.122                 & 1.537 & -0.196 \\
-Residual                            &                              &                        & 1.06 & -0.071 \\
-\end{tabular}
-\end{sidewaystable}
-
-Here, the results are replicated entirely.
-
-A concern raised is that it is not clear how the variable that reflects transfers was constructed, since this information is not directly provided in the raw data available online.
-In some cases, the variable that reflects the camp contains multiple entries per individual, and we can only assume that those were used to infer that the POW was transferred between those camps.
-This is most likely an accurate interpretation of the data, the only problem being that there is no information about the date of transfer, which makes the instrument weaker.
-
-In the following section, the authors use The National Park Service's cross-sectional data of the population of Andersonville and estimate probit models of the probability of survival on the number of friends and various demographic characteristics as described in the summary.
-
-\autoref{effect}: This table estimates the effect of social networks on probability of survival controlling for a large of variables that measure existing networks outside of the company.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectsocial}
-\begin{tabular}{lllllll}
-\hline
-                                                              &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                              & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment÷10                                  & 9.157   & 0.004++ &         &         &                                     &  \\
-                                                              & -10.358 & -0.001  &         &         &                                     &  \\
-Number of men in company                                      & 12.899  &         & 0.003++ & 0.002++ & 0.003++                             & 0.002++ \\
-                                                              & -15.39  &         & -0.001  & -0.001  & -0.001                              & -0.001 \\
-Fraction of company with              rank sergeant or higher & 0.073   & 0.120++ & 0.128++ & 0.079   & 0.152                               & 0.085 \\
-                                                              &         & -0.034  & -0.034  & -0.032  & -0.061                              & -0.056 \\
-Number of men with same last name in regiment                 & 1.19    & 0.033++ & 0.033++ & 0.036++ & 0.018*                              & 0.023++ \\
-                                                              & -0.599  & -0.007  & -0.007  & -0.006  & -0.009                              & -0.009 \\
-Log(number of men in camp from same town)                     & 5.101   & -0.003  & -0.002  & 0       & 0.018*                              & 0.026++ \\
-                                                              & -1.994  & -0.005  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-Dummy=1 if town population<9552                               & 0.423   & 0.037+  & 0.034+  & 0.032+  &                                     &  \\
-                                                              &         & -0.014  & -0.014  & -0.013  &                                     &  \\
-Private                                                       & 0.824   &         &         &         &                                     &  \\
-Officer             & 0.003 & 0.347++ & 0.347++ & 0.354++ & 0.311++ & 0.328++ \\
-                    &       & -0.027  & -0.027  & -0.021  & -0.038  & -0.025  \\
-Sergeant            & 0.068 & 0.080++ & 0.080++ & 0.083++ & 0.084++ & 0.088++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Other rank          & 0.01  & 0.028   & 0.034   & 0.03    & 0.067   & 0.046   \\
-                    &       & -0.03   & -0.03   & -0.03   & -0.049  & -0.05   \\
-Corporal            & 0.078 & 0.055++ & 0.055++ & 0.046++ & 0.064++ & 0.054++ \\
-                    &       & -0.011  & -0.011  & -0.011  & -0.017  & -0.018  \\
-Irish surname       & 0.023 & 0.02    & 0.022   & 0.017   & 0.069   & 0.059*  \\
-                    &       & -0.019  & -0.019  & -0.019  & -0.03   & -0.03   \\
-German surname      & 0.043 & -0.009  & -0.009  & -0.016  & -0.001  & -0.025  \\
-                    &       & -0.015  & -0.015  & -0.015  & -0.024  & -0.025  \\
-French surname      & 0.028 & 0.028   & 0.028*  & 0.028   & 0.033   & 0.032   \\
-                    &       & -0.017  & -0.017  & -0.017  & -0.027  & -0.028  \\
-Continental surname & 0.029 & 0.006   & 0.007   & -0.004  & -0.021  & -0.029  \\
-                    &       & -0.018  & -0.018  & -0.018  & -0.032  & -0.032  \\
-State fixed effects? &       & N     & N     & Y     & N     & Y     \\
-Pseudo R2            &       & 0.043 & 0.044 & 0.087 & 0.048 & 0.115 \\
-Observations         & 31336 & 31336 & 31336 & 31330 & 12002 & 12002 \\
-\end{tabular}
-\end{sidewaystable}
-
-All figures on the table are replicated perfectly.
-However, the coefficients in bold are estimated with different significance levels (even though the coefficients and their standard errors are the same).
-For example, we find that the coefficient on Dummy=1 if town population $<9,552$ is significant at the 5 percent level whereas the table in the original paper indicates that it is significant at the 1 percent level in specifications 1, 2, and 3.
-It is important to note that the difference is not always in the same direction.
-For instance, we find that the coefficient on French surname in specification 2 is significant at the 10 percent level whereas the original table does not show any significance.
-Thus, we suspect that this discrepancy might be due to rounding error.
-
-\autoref{effectsocial}: Here, the authors estimate the same equation in logs and include the two outlier companies that were excluded in Table 5 to show the resulting nonlinearity.
-In the .do file, the outliers are dropped early on and thus their estimations never include these outliers.
-We save the dataset with the outliers at an early stage so that we can include them in the estimation.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form}\footnote{Like in the paper, the estimations exclude the two outlier companies.
-Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{effectLog}
-\begin{tabular}{lllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.014++ &         &         &                                     &  \\
-                                                   & -1.29  & -0.005  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.021++ & 0.012   & 0.029                               & 0.022 \\
-                                                   & -1.18  &         & -0.007  & -0.006  & -0.012                              & -0.009 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.134++ & 0.134++ & 0.08    & 0.153                               & 0.084 \\
-                                                   & -0.127 & -0.034  & -0.034  & -0.032  & -0.061                              & -0.057 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.101++ & 0.095++ & 0.096++ & 0.061++                             & 0.063++ \\
-                                                   & -0.305 & -0.012  & -0.012  & -0.011  & -0.018                              & -0.017 \\
-Log(number of men in camp from same town)          & 5.114  & -0.004  & 0       & 0.002   & 0.024                               & 0.030++ \\
-                                                   & -1.991 & -0.004  & -0.005  & -0.005  & -0.009                              & -0.008 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.114 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002                               & 12002 \\
-                                                   &        &         &         &         &                                     &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The first thing to notice is that the number of observations is different.
-The original paper shows a total of 31,678 observations for the first three specifications, and a total of 12,025 observations for specifications 4 and 5.
-We have less number of observations mostly due to the 83 observations with missing Fraction of company with rank sergeant or higher variable.
-We don’t know how the authors included these observations in their estimation.
-A minor difference in the first descriptive column is the mean for Log(number of men with same last name in regiment), which is $0.113$ in the paper paper and $0.112$ in our data.
-
-All the coefficients in bold are slightly different from the original table; some are different only in their magnitude but some are also different in their level of significance.
-For example, the coefficient on Log(number of men in regiment) in specification 1 is $0.011$ with $5\%$ significance level in the paper, whereas we find a higher and more significant effect.
-Despite these quantitative differences, the results are not qualitatively different.
-
-\autoref{effectLog}: Here, the authors estimate the effect of ethnic networks on probability of survival to show that the quality of the network matters.
-
-\begin{sidewaystable}
-\caption{Effect of ethnic network on probability of survival}\footnote{Company clustered standard errors.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethnic}
-\begin{tabular}{lllllll}
-\hline
-
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.003*                    & 0.002                      & 0.003                      & 0.001 & 0.002 & 0.002 \\
-Number of men of own ethnicity in company & 0.03                      & 0.036                      & 0.03                       & 0.013 & 0.019 & 0.026 \\
-Dummy = 1 if Private                      & -0.046                    & 0.049                      & -0.078+                    & 0.037 & -0.093+ & 0.043 \\
-From small town                           & 0.1                       & 0.04                       & 0.036                      & 0.031 & 0.054 & 0.036 \\
-Captured 1864 or 1865                     & 0.239++                   & 0.077                      & 0.282++                    & 0.049 & 0.388++ & 0.058 \\
-Pseudo R2                                 & 0.036                     &                            & 0.059                      &  & 0.058 &  \\
-Joint significance test                   & 8.6                       &                            & 22.01                      &  & 3.2 &  \\
-Observations                              & 735                       &                            & 1355                       &  & 869 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-The bold coefficients in \autoref{effectLog} are different in significance levels than what the authors report in their original table (all coefficients and standard errors are the same).
-The most striking one is the Captured 1864 or 1865 variable for French POWs where the authors find no significance at all and we find significance at the 1 percent level.
-Since this is too large of a difference to be a rounding error, we suspect that it is a typo.
-
-\subsection{Robustness check - Logit instead of Probit}
-
-As a robustness check, we estimate tables 5-7 with logit instead of probit and results are qualitatively similar.
-Bold coefficients below show differing levels of significance (only 1-level) when compared to probit.
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logit}\footnote{There is no explanation in the paper as to why probit was preferred to logit.}
-\label{logit}
-\begin{tabular}{lllllll}
-\hline
-                                                 &         &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                 & Mean    & 1       & 2       & 3       & 4                                   & 5 \\
-Number of men in regiment ÷10                    & 9.157   & 0.018++ &         &         &                                     &  \\
-                                                 & -10.358 & -0.003  &         &         &                                     &  \\
-Number of men in company                         & 12.899  &         & 0.013++ & 0.009++ & 0.014++                             & 0.010++ \\
-                                                 & -15.39  &         & -0.003  & -0.002  & -0.004                              & -0.003 \\
-Fraction of company with rank sergeant or higher & 0.073   & 0.495++ & 0.526++ & 0.336   & 0.647                               & 0.387 \\
-                                                 &         & -0.145  & -0.144  & -0.139  & -0.266                              & -0.251 \\
-Number of men with same last name in regiment    & 1.19    & 0.149++ & 0.147++ & 0.158++ & 0.081*                              & 0.101++ \\
-                                                 & -0.599  & -0.03   & -0.03   & -0.028  & -0.042                              & -0.038 \\
-Log(number of men in camp from same town)        & 5.101   & -0.012  & -0.01   & 0       & 0.075                               & 0.114++ \\
-                                                 & -1.994  & -0.019  & -0.019  & -0.019  & -0.038                              & -0.034 \\
-Dummy=1 if town population<9552                  & 0.423   & 0.154   & 0.145   & 0.133   &                                     &  \\
-                                                 &         & -0.06   & -0.056  & -0.054  &                                     &  \\
-Private                                          & 0.824   &         &         &         &                                     &  \\
-Officer & 0.003 & 2.342++ & 2.339++ & 2.481++ & 2.043++ & 2.342++ \\
-        &       & -0.454  & -0.455  & -0.426  & -0.562  & -0.502  \\
-Sergeant             & 0.068 & 0.344++ & 0.344++ & 0.367++ & 0.377++ & 0.407++ \\
-                     &       & -0.05   & -0.05   & -0.053  & -0.081  & -0.087  \\
-Other rank           & 0.01  & 0.109   & 0.135   & 0.12    & 0.295   & 0.2     \\
-                     &       & -0.128  & -0.128  & -0.132  & -0.232  & -0.231  \\
-Corporal             & 0.078 & 0.236++ & 0.235++ & 0.201++ & 0.283++ & 0.244++ \\
-                     &       & -0.046  & -0.046  & -0.048  & -0.077  & -0.084  \\
-Irish surname        & 0.023 & 0.086   & 0.095   & 0.072   & 0.31    & 0.264*  \\
-                     &       & -0.081  & -0.081  & -0.082  & -0.14   & -0.146  \\
-German surname       & 0.043 & -0.039  & -0.036  & -0.07   & -0.003  & -0.111  \\
-                     &       & -0.061  & -0.06   & -0.061  & -0.103  & -0.106  \\
-French surname       & 0.028 & 0.113   & 0.117   & 0.119   & 0.14    & 0.152   \\
-                     &       & -0.073  & -0.073  & -0.075  & -0.12   & -0.127  \\
-Continental surname  & 0.029 & 0.026   & 0.031   & -0.015  & -0.093  & -0.126  \\
-                     &       & -0.075  & -0.075  & -0.076  & -0.134  & -0.135  \\
-State fixed effects? &       & N       & N       & Y       & N       & Y       \\
-Pseudo R2            &       & 0.043   & 0.044   & 0.086   & 0.047   & 0.114   \\
-Observations         & 31336 & 31336   & 31336   & 31330   & 12002   & 12002   \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of social networks on probability of survival, logarithmic form, logit}\footnote{Company clustered standard errors are in parentheses.
-The number of observations for the Fraction of company with rank sergeant or higher variable in the first column is 31605.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{logLogit}
-\begin{tabular}{llllllllll}
-\hline
-                                                   &        &         &         &         & \multicolumn{2}{l}{From small town} \\
-                                                   & Mean   & 1       & 2       & 3       & 4                                   & 5 \\
-Log(number of men in regiment)                     & 3.865  & 0.057   &         &         &                                     &  \\
-                                                   & -1.29  & -0.022  &         &         &                                     &  \\
-Log(number of men in company)                      & 2.052  &         & 0.088++ & 0.047   & 0.124                               & 0.085 \\
-                                                   & -1.18  &         & -0.028  & -0.024  & -0.051                              & -0.04 \\
-Fraction of company with rank sergeant or higher   & 0.072  & 0.559++ & 0.552++ & 0.342   & 0.652                               & 0.383 \\
-                                                   & -0.127 & -0.147  & -0.145  & -0.139  & -0.266                              & -0.251 \\
-Log(number of men with same last name in regiment) & 0.112  & 0.438++ & 0.409++ & 0.416++ & 0.267++                             & 0.277++ \\
-                                                   & -0.305 & -0.052  & -0.052  & -0.049  & -0.078                              & -0.074 \\
-Log(number of men in camp from same town)          & 5.114  & -0.018  & 0       & 0.006   & 0.100++                             & 0.131++ \\
-                                                   & -1.991 & -0.018  & -0.019  & -0.019  & -0.039                              & -0.036 \\
-State fixed effects?                               &        & N       & N       & Y       & N                                   & Y \\
-Pseudo R2                                          &        & 0.038   & 0.04    & 0.084   & 0.044                               & 0.113 \\
-Observations                                       & 31688  & 31605   & 31604   & 31598   & 12002 
-\end{tabular}
-\end{sidewaystable}
-
-\begin{sidewaystable}
-\caption{Effect of ethnic networks on probability of survival, logit}\footnote{Standard errors are clustered on the company.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\label{ethLogit}
-\begin{tabular}{lllllll}
-\hline
-                                          & \multicolumn{2}{l}{Irish} & \multicolumn{2}{l}{German} & \multicolumn{2}{l}{French} \\
-                                          & b                         & se                         & b                          & se & b & se \\
-Number of men in company                  & 0.009                     & 0.007                      & 0.011*                     & 0.006 & -0.001 & 0.007 \\
-Number of men of own ethnicity in company & 0.011                     & 0.11                       & 0.139                      & 0.06 & 0.154 & 0.116 \\
-Dummy =1 if Private                       & -0.228                    & 0.214                      & -0.337+                    & 0.162 & -0.445+ & 0.2 \\
-From small town                           & 0.417                     & 0.173                      & 0.154                      & 0.131 & 0.23 & 0.154 \\
-Captured 1864 or 1865                     & 1.082++                   & 0.347                      & 1.223++                    & 0.227 & 1.826++ & 0.307 \\
-Pseudo R2                                 & 0.032                     &                            & 0.058                      &  & 0.055 &  \\
-Joint significance test                   & 3.81                      &                            & 18.22                      &  & 2.16 &  \\
-Observations                              & 752                       &                            & 1357                       &  & 874 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\section{Conclusion}
-To sum up our replication, our key message is that while we do find small differences between our results and the published results of \textcite{costa2007surviving}, we find no evidence that would call their conclusions into question, either qualitatively or quantitatively.
-
-Furthermore, the interpretation of the results seems convincing to us.
-While they cannot test for how friends ensured survival the mentioned explanations from the supply of food to moral support are very comprehensible.
-In addition, their study is clearly and quite literally made for survival analysis so we do not see space to improve upon the results by applying a different estimation technique.
-\textcite{costa2007surviving} also apply a wide set of survival analysis tools (e.g.
-from non-parametric to parametric estimation) so we did not come up with many ideas for robustifying their paper in this direction.
-Potential future extensions could build on the use of different data sets.
-A weakness of the paper is clearly that external validity is limited because the authors look at a civil war of the 19th century.
-For instance, looking at World War I or II data could prove to be fruitful and lead to further insight.
-While we tried to start with such an extension, we were not able to find a sufficient dataset within this period of time.
-
-To come back to the differences between our replication and the original paper, we consider the most relevant issue the difference in significance levels.
-Interestingly, when looking into this matter in more detail we find that in almost all cases the p-values are at the margin which clearly points in the direction of a rounding error.
-We can only speculate that given the lack of exporting commands the reason for this is a certain degree of carelessness and, therefore, would like to emphasize the need of these very exporting commands.
-Nevertheless, and as mentioned before, the differences do not affect the general message of the paper.
-
-%\appendix
-
-\section*{Appendix: In-text estimation}
-Most in-text estimations are not included in the .do files provided, therefore some of the results to follow do not exactly reproduce the ones published, probably due to differences in specifications.
-They can nonetheless generally be replicated in terms of signs and significance.
-
-\paragraph{Probit statement}
-page 1474, line 21 ``When we run a Probit, in which the dependent variable is POW status and the independent variables are economic and geographic characteristics and the number of men in the company who were ever wounded or who ever died, we find that these two company characteristics were the main predictors of POW status.
-The derivative on the number of men in the company who were ever wounded or who ever died, was $0.257$ (robust $= 0.257$) and the derivative on the number of men who were ever wounded was $0.139$ (robust $= 0.042$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of POW Status}
-\begin{tabular}{lll}
-\hline
-                          & Marginal Effect & Marginal Effect \\
-\% in comp who died        & 0.359***        & 0.430***        \\
-                          & -0.021          & -0.0331         \\
-\% in comp who wounded     & 0.123***        & 0.140***        \\
-                          & -0.0136         & -0.022          \\
-Includes property in 1860 & No              & Yes             \\
-Observations              & 34878           & 13754           \\
-\end{tabular}
-\end{table}
-
-\paragraph{Comment on late capture}
-page 1474, line 77 ``We also found no evidence of group surrender to become a POW - men who were captured in 1864 and 1865 had more friends, even though a group who surrendered during these years would have no hope of a quick exchange.''
-
-\begin{sidewaystable}
-\caption{Characteristics of POWs by Number of Friends in First Two Weeks of Captivity and Late or Early Capture}
-\begin{tabular}{lllllllll}
-\hline
-                     & \multicolumn{4}{c}{Early capture} & \multicolumn{4}{c}{Late capture} \\
-                     & \multicolumn{2}{c}{$< 3$}           & \multicolumn{2}{c}{$>= 3$}         & \multicolumn{2}{c}{$< 3$} & \multicolumn{2}{c}{$>= 3$} \\
-                     & Mean                              & Std. err.                        & Mean & Std. err. & Mean & Std. err. & Mean & Std. err. \\
-US born              & 0.706                             & 0.456                            & 0.77 & 0.421 & 0.709 & 0.455 & 0.738 & 0.44 \\
-Irish                & 0.082                             & 0.275                            & 0.109 & 0.311 & 0.136 & 0.343 & 0.14 & 0.347 \\
-German               & 0.108                             & 0.311                            & 0.046 & 0.21 & 0.064 & 0.244 & 0.043 & 0.204 \\
-British              & 0.053                             & 0.224                            & 0.021 & 0.143 & 0.036 & 0.186 & 0.032 & 0.175 \\
-Other                & 0.048                             & 0.213                            & 0.046 & 0.21 & 0.056 & 0.229 & 0.047 & 0.213 \\
-Artisan              & 0.233                             & 0.423                            & 0.2 & 0.401 & 0.203 & 0.402 & 0.207 & 0.406 \\
-Farmer               & 0.423                             & 0.495                            & 0.355 & 0.479 & 0.451 & 0.498 & 0.444 & 0.497 \\
-Prof. or proprietor  & 0.09                              & 0.286                            & 0.075 & 0.264 & 0.069 & 0.253 & 0.053 & 0.225 \\
-Laborer              & 0.235                             & 0.425                            & 0.288 & 0.453 & 0.248 & 0.432 & 0.288 & 0.453 \\
-Unknown              & 0.019                             & 0.135                            & 0.081 & 0.274 & 0.029 & 0.169 & 0.008 & 0.089 \\
-Enlisted in big city & 0.545                             & 0.499                            & 0.497 & 0.501 & 0.461 & 0.499 & 0.42 & 0.494 \\
-Property inc in 1860 & 444.889                           & 1056.215                         & 703.517 & 2190.478 & 502.019 & 1099.896 & 620.684 & 2498.66 \\
-Age when captured    & 26.079                            & 7.152                            & 24.848 & 6.588 & 26.995 & 7.558 & 25.658 & 6.601 \\
-Height when captured & 171.518                           & 6.2                              & 171.377 & 6.914 & 171.959 & 6.495 & 171.338 & 6.765 \\
-Officer              & 0.111                             & 0.315                            & 0.092 & 0.289 & 0.065 & 0.247 & 0.049 & 0.217 \\
-Married in 1860      & 0.27                              & 0.446                            & 0.246 & 0.432 & 0.279 & 0.449 & 0.233 & 0.423 \\
-Fraction company dead before capture & 0.056 & 0.054 & 0.057 & 0.046 & 0.116 & 0.069 & 0.112 & 0.054 \\
-Company birthplace fragmentation     & 0.554 & 0.183 & 0.516 & 0.238 & 0.543 & 0.199 & 0.553 & 0.173 \\
-Company occupational fragmentation   & 0.587 & 0.173 & 0.614 & 0.177 & 0.586 & 0.173 & 0.601 & 0.168 \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{OLS statement}
-page 1474 line 65 and footnote 22.
-``When we ran an OLS regression of the number of friends on the covariates we later use in our hazard specification, we found that professionals and proprietors, the Irish, older men, and the recently wounded were less likely to have many friends, whereas those from a large city had more friends''...
-``The coefficient on recently wounded was $-0.879$ ($= 0.397$).''
-
-\begin{table}[ht]
-\centering
-\caption{Determinants of number of friends}
-\begin{tabular}{ll}
-\hline
-Professional or proprietor     & -0.913***  \\
-                               & -0.0979    \\
-Irish                          & -0.267***  \\
-                               & -0.0984    \\
-Age at capture                 & -0.0391*** \\
-                               & -0.00504   \\
-Wounded 10 days before capture & -0.831***  \\
-                               & -0.0876    \\
-Large city                     & 0.553***   \\
-                               & -0.0649    \\
-Observations                   & 23256      \\
-R-squared                      & 0.152      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Predicted probability of death}
-page 1475, line 24.
-``As the number of friends increases from 0 to 5, the predicted probability of death, using the second specification in Table 3, decreases from $0.31$ to $0.28$, and as the number of friends increases to $10$, the predicted mortality probability falls to $0.26$.
-(The mean number of friends in each month was $5.6$, with a standard deviation of $9.2$, and the median was $2$.)''
-
-\begin{table}[ht]
-\centering
-\caption{Number of Friends}
-\begin{tabular}{lll}
-\hline
-          & Initial & In estimation \\
-Mean      & 5.58    & 2.87          \\
-Std. Dev. & 9.22    & 5.12          \\
-Median    & 2       & 1             \\
-\end{tabular}
-\end{table}
-
-The summary statistics mentioned for the variable friends match the initial file, but not the data that is actually included in the regression.
-
-\begin{figure}[ht]
-\centering
-\caption{Exponential specification}
-\label{exponential}
-\includegraphics[scale=0.65]{exponential.png}
-\end{figure}
-
-The file ``survival.dta'' contains the predicted survival probability for individuals with 0, 5 and 10 friends (evaluated at means for the other covariates).
-The statement did not specify a point in time, but we find a coincidence with the statement at $t=330.76$ (average days of imprisonment was $131.62$).
-
-\paragraph{Table 3 with regiment fixed effects}
-page 1476, line 2.
-``Even when we included state of regiment fixed effects, the hazard ratio on the number of friends remained virtually unchanged (e.g.
-the hazard ratio on the initial number of friends was $0.976$, $=0.009$).''
-
-\begin{sidewaystable}
-\caption{Table 3 with regiment state effects}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err & Hazard rate & Std. err & Hazard rate & Std. err \\
-Number of friends                        & 0.984*      & -0.009   & 0.978       & -0.009   &             &          \\
-Initial number of friends                &             &          &             &          & 0.976++     & -0.009   \\
-Ln(number of prisoners in camp)          &             &          & 1.538++     & -0.141   & 1.525++     & -0.14    \\
-Fraction of company dying before capture & 1.427       & -1.227   & 1.19        & -1.011   & 0.787       & -0.653   \\
-Professional or proprietor               & 0.512       & -0.134   & 0.506++     & -0.131   & 0.502++     & -0.13    \\
-Artisan                                  & 0.862       & -0.114   & 0.862       & -0.114   & 0.851       & -0.112   \\
-Laborer                                  & 1.163       & -0.148   & 1.154       & -0.146   & 1.141       & -0.145   \\
-German                                   & 1.135       & -0.213   & 1.116       & -0.21    & 1.103       & -0.206   \\
-Irish                                    & 0.731*      & -0.118   & 0.723       & -0.116   & 0.723       & -0.115   \\
-British                                  & 0.616*      & -0.167   & 0.630*      & -0.17    & 0.637*      & -0.174   \\
-Other                                    & 0.612       & -0.145   & 0.603       & -0.144   & 0.602       & -0.143   \\
-Sergeant, corporal or officer            & 0.570++     & -0.117   & 0.561++     & -0.113   & 0.557++     & -0.112   \\
-Age at captivity                         & 1.042++     & -0.008   & 1.040++     & -0.007   & 1.040++     & -0.007   \\
-Height at enlistment                     & 1.014*      & -0.007   & 1.014*      & -0.007   & 1.014*      & -0.007   \\
-Observations                             & 3026        &          & 3026        &          & 3026        &          \\
-Number of subjects                       & 23174       &          & 23174       &          & 23174       &          \\
-Log pseudo likelihood                    & -1307.77    &          & -1291.45    &          & -1290.674   &          \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Table 3 with splines}
-page 1476, line 6 and footnote 23 ``Our experiments with splines suggested that the marginal effect of a friend on survival was greater for the first two friends than for more."  Footnote 23: "The hazard rate on the marginal effect of fewer than three friends was $0.956$ ($=0.044$) and the hazard rate on the marginal effect of three or more friends was $0.980$ ($=0.011$).
-Although the first hazard rate was not statistically significantly different from one, the two terms together were jointly significant.''
-
-\begin{table}[ht]
-\centering
-\caption{Spline at 3}
-\begin{tabular}{ll}
-\hline
-                     & Hazard rate \\
-Fewer than 3 friends & 0.956       \\
-                     & -0.0443     \\
-3 or more friends    & 0.980*      \\
-                     & -0.0108     \\
-Observations         & 23256       \\
-Chi-sq               & 7.789       \\
-Prob > chi-sq        & 0.0204      \\
-\end{tabular}
-\end{table}
-
-\paragraph{Weibull specification}
-page 1477, line 12. ``When we use a Weibull rather than an exponential specification, we found no evidence of duration dependence...''
-
-\begin{sidewaystable}
-\caption{Weibul}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llllllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-VARIABLES                                & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.986                               & -0.009                              & 0.979                               & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.531++                             & -0.139 & 1.517++ & -0.139 \\
-Fraction of company dying before capture & 1.242                               & -0.897                              & 1.008                               & -0.722 & 0.733 & -0.525 \\
-Professional or propietor                & 0.566                               & -0.147                              & 0.562                               & -0.144 & 0.554 & -0.142 \\
-Artisan                                  & 0.95                                & -0.121                              & 0.952                               & -0.12 & 0.942 & -0.119 \\
-Laborer                                  & 1.308                               & -0.157                              & 1.303                               & -0.154 & 1.296 & -0.154 \\
-German                                   & 1.198                               & -0.218                              & 1.169                               & -0.212 & 1.153 & -0.209 \\
-Irish                                    & 0.771                               & -0.123                              & 0.765*                              & -0.12 & 0.753* & -0.118 \\
-British                                  & 0.630*                              & -0.17                               & 0.644                               & -0.174 & 0.646 & -0.176 \\
-Other                                    & 0.656*                              & -0.155                              & 0.643*                              & -0.153 & 0.640* & -0.151 \\
-Sargeant, corporal or officer            & 0.536++                             & -0.114                              & 0.531++                             & -0.11 & 0.528++ & -0.11 \\
-Age at captivity                         & 1.046++                             & -0.008                              & 1.045++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1322.852                           &                                     & -1306.836                           &  & -1305.627 &  \\
-Duration dependence                      & 1.088                               &                                     & 1.08                                &  & 1.084 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Month dummies}
-page 1477, line 19.
-``When we included dummy variables in our specification indicating that an individual had survived 1, 2, 3 or more months, we found that those who had survived one or two months were less likely to die than those still in their first month of captivity, but that the advantage of having survived a third month was small and there was no advantage to having survived a fourth month.''
-
-\begin{sidewaystable}
-\caption{controlling for months survived}\footnote{Company clustered standard errors are in parentheses.
-Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & \multicolumn{2}{l}{Specification 1} & \multicolumn{2}{l}{Specification 2} & \multicolumn{2}{l}{Specification 3} \\
-                                         & Hazard rate                         & Std. err.                           & Hazard rate                         & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.989                               & -0.009                              & 0.982*                              & -0.009 &  &  \\
-Initial number of friends                &                                     &                                     &                                     &  & 0.977++ & -0.009 \\
-Ln(number of prisoners in camp)          &                                     &                                     & 1.612++                             & -0.146 & 1.604++ & -0.145 \\
-Fraction of company dying before capture & 1.368                               & -1.001                              & 1.117                               & -0.811 & 0.832 & -0.603 \\
-Professional or propietor                & 0.56                                & -0.145                              & 0.557                               & -0.142 & 0.547 & -0.14 \\
-Artisan                                  & 0.946                               & -0.121                              & 0.951                               & -0.121 & 0.939 & -0.12 \\
-Laborer                                  & 1.302                               & -0.158                              & 1.302                               & -0.156 & 1.298 & -0.156 \\
-German                                   & 1.22                                & -0.223                              & 1.195                               & -0.216 & 1.178 & -0.213 \\
-Irish                                    & 0.774                               & -0.125                              & 0.770*                              & -0.122 & 0.756* & -0.12 \\
-British                                  & 0.618*                              & -0.168                              & 0.632*                              & -0.172 & 0.634* & -0.174 \\
-Other                                    & 0.658*                              & -0.156                              & 0.650*                              & -0.156 & 0.647* & -0.154 \\
-Sargeant, corporal or officer            & 0.533++                             & -0.114                              & 0.531++                             & -0.111 & 0.526++ & -0.11 \\
-Age at captivity                         & 1.047++                             & -0.008                              & 1.046++                             & -0.008 & 1.045++ & -0.008 \\
-Height at entlistment                    & 1.01                                & -0.007                              & 1.01                                & -0.007 & 1.011 & -0.007 \\
-Survived 1 month                         & 0.407++                             & -0.08                               & 0.362++                             & -0.072 & 0.352++ & -0.071 \\
-Survived 2 months                        & 0.472++                             & -0.092                              & 0.401++                             & -0.08 & 0.393++ & -0.078 \\
-Survived 3 months                        & 0.74                                & -0.137                              & 0.64                                & -0.12 & 0.631 & -0.118 \\
-Survived 4 or more months                & 0.833                               & -0.134                              & 0.745*                              & -0.12 & 0.740* & -0.119 \\
-Observations                             & 23256                               &                                     & 23256                               &  & 23256 &  \\
-Log pseudo likelihood                    & -1307.333                           &                                     & -1287.9                             &  & -1285.595 &  \\
-\end{tabular}
-\end{sidewaystable}
-
-\paragraph{Cox Proportional Hazard Model}
-page 1477, line 26 footnote.
-``We also investigated the use of a Cox proportional hazard model to allow the baseline hazard to rise or fall in any month.
-Controlling for camp conditions, we obtained a statistically insignificant hazard ratio on friends of $0.987$ ($=0.009$).
-We suspect that we are losing power because of our small sample size.''
-
-\begin{sidewaystable}
-\caption{Cox proportional models}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lllllll}
-\hline
-                                         & Hazard rate & Std. err. & Hazard rate & Std. err. & Hazard rate & Std. err. \\
-Number of friends                        & 0.992       & -0.009    & 0.987       & -0.009    &             &           \\
-Initial number of friends                &             &           &             &           & 0.978       & -0.009    \\
-Ln(number of prisoners in camp)          &             &           & 1.593++     & -0.149    & 1.587++     & -0.149    \\
-Fraction of company dying before capture & 1.751       & -1.298    & 1.558       & -1.148    & 1.179       & -0.867    \\
-Professional or propietor                & 0.557       & -0.144    & 0.556       & -0.142    & 0.546       & -0.139    \\
-Artisan                                  & 0.942       & -0.121    & 0.952       & -0.122    & 0.938       & -0.12     \\
-Laborer                                  & 1.284       & -0.157    & 1.287       & -0.157    & 1.284       & -0.156    \\
-German                                   & 1.241       & -0.228    & 1.218       & -0.223    & 1.2         & -0.22     \\
-Irish                                    & 0.765       & -0.126    & 0.763*      & -0.123    & 0.746*      & -0.121    \\
-British                                  & 0.613*      & -0.166    & 0.625*      & -0.169    & 0.626*      & -0.171    \\
-Other                                    & 0.658*      & -0.159    & 0.652*      & -0.159    & 0.649*      & -0.158    \\
-Sargeant, corporal or officer            & 0.538++     & -0.115    & 0.537++     & -0.113    & 0.532++     & -0.112    \\
-Age at captivity                         & 1.048++     & -0.008    & 1.046++     & -0.008    & 1.046++     & -0.008    \\
-Height at entlistment                    & 1.01        & -0.008    & 1.01        & -0.007    & 1.011       & -0.007    \\
-Observations                             & 23256       &           & 23256       &           & 23256       &           \\
-Log pseudo likelihood                    & -3102.845   &           & -3086.134   &           & -3083.63    &           \\
-\end{tabular}
-\end{sidewaystable}
-
-\begin{table}[ht]
-\centering
-\caption{table 4 net transfer}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{lll}
-\hline
-VARIABLES               & Hazard Rate & Std. err. \\
-Net transfer of friends & 0.946**     & -0.024    \\
-Observations            & 15998       &           \\
-\end{tabular}
-\end{table}
-
-\paragraph{On limiting the sample}
-page 1480, line 17.
-``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged.
-The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).''
-
-\paragraph{On the mortality of privates}
-page 1480, line 54.
-``The fraction of sergeants or higher rank is not a reflection of own officer mortality.
-When we restricted the sample to privates, we found that the derivative of this coefficient was 0.115 (sdev=0.054).''
-
-\paragraph{On the role of networks in predicting escape from Andersonville}
-page 1482, line 25.
-``Also suggestive of friends not always helping survival is that, among the men at Andersonville, we find no evidence that the number of friends predicted whether an individual was one of the 140 escaped.''
-
-See table below for the final three verifications:
-
-\begin{sidewaystable}
-\caption{Final three specifications}\footnote{Company clustered standard errors are in parentheses. Symbols ++, +, and * indicate statistical significance levels of 1, 5, and 10 percent respectively.}
-\begin{tabular}{llll}
-\hline
-                                                 & Dependent variable: Lived & Dependent variable: Lived & Dependent variable: Escaped \\
-                                                 & Shorter time period       & Privates only             &                             \\
-Number of men in company                         & 0.003++                   & 0.003++                   & 0                           \\
-                                                 & -0.001                    & -0.001                    & 0                           \\
-Fraction of company with rank sergeant or higher & 0.115                     & 0.139++                   & -0.001                      \\
-                                                 & -0.054                    & -0.036                    & -0.002                      \\
-Number of men with same last name in regiment    & 0.033++                   & 0.035++                   & 0                           \\
-                                                 & -0.007                    & -0.007                    & 0                           \\
-Log(number of men in camp from same town)        & -0.003                    & -0.001                    & 0                           \\
-                                                 & -0.005                    & -0.005                    & 0                           \\
-Pseudo R2                                        & 0.036                     & 0.047                     & 0.015                       \\
-Observations                                     & 25880                     & 27923                     & 28190                       \\
-\end{tabular}
-\end{sidewaystable}
-
-The only in-text claim that we are not able to confirm is their statement that there is no mortality difference between the colored non-officers and the rest of the Andersonville POWs (page 1480, footnote 29) as we don’t have any information on the race of the POWs.
-
-\section*{Appendix: Non-parametric estimation}
-The following figures are our replications of the Kaplan-Meier survival estimates which show no differences to the original:
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimate}
-\label{kmSurvival}
-\includegraphics[scale=0.3]{kaplan1.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by early and late capture date}
-\label{kmCapture}
-\includegraphics[scale=0.3]{kaplan2.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by camp for late captures}
-\label{kmCamp}
-\includegraphics[scale=0.3]{kaplan3.png}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{Kaplan-Meier survival estimates by number of friends for Anderson}
-\label{kmNumber}
-\includegraphics[scale=0.3]{kaplan4.png}
-\end{figure}
-
-\printbibliography
-
-\end{refsection}
-
-\begin{refsection}
-
-\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
-\label{currency}
-\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
-
-In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor, is the result of the fact that this risk factor eliminates the previously existing uncertainty.
-In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk, which is a much fuller set of information.
-This view is enforced by the fact that the equilibrium is most pronounced when the risk factor (epsilon) is minimised (i.e.~set equal to zero), as the authors state themselves.
-Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium is in fact the entire `ripe for attack' domain.
-
-\nocite{taleb2010black}
-\printbibliography
-\end{refsection}
-
-\begin{refsection}
-\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
-\label{bitcoin}
-In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called ``\citetitle{nakamoto2008bitcoin}'' an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
-This currency -the first of a group called cryptocurrencies- has the following economics features:
-
-\begin{itemize}
-\item public transactions
-\item anonymous addresses
-\item fixed amount of units
-\item high granularity (1 Bitcoin = 100,000,000 Satoshi)
-\item no or low transaction costs
-\end{itemize}
-
-An addition to these economic features, the key feature of Bitcoin is decentralisation.
-All transactions are kept in a public ledger called the blockchain.
-An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
-Conflict resolution, in this system, is done through majority consensus of blockchain copy holders.
-
-There are a number of features which make Bitcoin attractive for remittances.
-Firstly, the low transaction costs are a huge step up from the current facilitators, which charge high percentages.
-Secondly, government intervention (especially in the recipient country) is prevented by the anonymity.
-Thirdly, recipients can choose to keep their remittance in a currency which is not controlled by their government.
-Fourthly, the granularity ensures very small transactions can be conducted.
-
-Bitcoin initially because popular in advanced economies such as those in Europe and North America.
-However, since mid 2013 there has been a large shift towards developing economies, in which comparative advantages of Bitcoin are more pronounced.
-For example, since its inception, Mt.Gox (located in Japan) was the largest Bitcoin exchange (marketplace), however in October 2013, Mt.Gox was overtaken by a Chinese exchange.
-
-Bitcoin transactions are conducted by the electronic `signing' of a transaction.
-This is a very simple electronic process.
-Currently many smartphone apps are available to this purpose.
-However, in the targeted developing economies, many phones are not smartphones, the vast majority using Nokia Operating System (Nokia OS).
-These phone can also run applications, using the Java Mobile App platform.
-Currently there are no Bitcoin apps available for this platform.
-
-I propose to participate in the development of open-source applications which would enable the users of stupid phones.
-We can then exploit the temporal difference when releasing the applications in different languages at different times, as well the downloads from traceable IP addresses.
-
-\printbibliography
-
-\end{refsection}
-
 \begin{refsection}
@@
 
-The replication of Surviving Andersonville is already completed in term of the replication in Stata.
-We would like to redo the analysis in R \parencite{R}.
-The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
-The findings of this replication can summarised as:
+% The replication of Surviving Andersonville is already completed in term of the replication in Stata.
+% We would like to redo the analysis in R \parencite{R}.
+% The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
+% The findings of this replication can summarised as:
 
-\begin{quote}
-``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
+%\begin{quote}
+%``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
 It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
 This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
-\end{quote}
+%\end{quote}
 
-We do not expect to find anything similar to Bell and Miller, but think that it can nevertheless be interesting to replicate findings using a different software package.
-In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
-In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
+% We do not expect to find anything similar to Bell and Miller,
+% but think that it can nevertheless be interesting to replicate findings using a different software package.
+% In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
+% In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
 
 The discussion of \textcite{morris1998unique} is in a very early stage.
-I have looked at the paper in detail, I have also done a brief analysis of my main critique, namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
+I have looked at the paper in detail, I have also done a brief analysis of my main critique,
+namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
 However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
-In addition to this, this example should demonstrate how the entire `ripe for attack' region is not solved for the unique equilibrium.
+In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.
 

### 2013-12-28 south-africa.tex
update intro, add bibliography

@@
 \section*{Abstract}
-In this paper I look at differences in child malnutrition levels depending on the gender of the recipient of income.
+In this paper we look at variation in the health of young children driven by the gender of the household income recipient.
+We do this by comparing z-scores of anthropometrics of South-African children living in the same household as state pension recipients.
 
-I do this by comparing z-scores of anthropometrics of South African children living in the same household as state pension recipients.
-This paper exploits the fact that the data set consists of three surveys,
-one of which was done before the lowering of the pension eligibility age for men to the same age as women,
-and two after.
+This paper exploits the lowering of the state-pension eligibility-age of men, 
+to the same age as women (60, previously 65).
+This takes place between two waves in the South-African National Income Dynamics Survey.
+This enables us to perform a Difference-in-Difference estimation on the panel data set.
 
-The main preliminary finding is that the household effect was only significant in 2012.
+Our finding is that policy change had a negative effect on long-term growth metrics of young children
+and the general mens pension income had a negative effect on young children's BMI.
 
@@
 \label{sa:intro}
-This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa.
-The approach is very similar to \textcite{duflo2000child,duflo2003grandmothers}.
-The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for weight-for-height and length-for-age are computed as z-scores.
-These are then compared for different pension recipient status.
+This paper looks at the effect of the gender of pension recipients on the growth of children in the same household.
+The study is based on South-African data and the approach is very similar to \textcite{duflo2000child,duflo2003grandmothers}.
+The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for anthropometrics are computed as z-scores.
+Using these standardised metrics, we compare children living in household with pension recipients of different gender.
+
+This study deviates from the Duflo study in several ways.
+The core contribution of this paper is the analyis of exogenous change in men's pension eligibility age,
+which is the main explanatum.
+The pension eligibility age for men was lowered from 65 to 60 between mid 2009 and 1-1-2011.
+This brought the pension eligibility age for men at par with women.
+We employ a Difference-in-Difference (or Fixed Effects) analysis of this change.
+Under then assumptions of the Difference-in-Difference model,
+this enables us to make a causal inference on the policy variable.
+
+Furthermore, the data from the \textcite{saldru2008nids,saldru2012nids} surveys contains actual information on income,
+including pension recipient status, whereas Duflo uses age as a proxy for recipient status.
+Another minor deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child},
+in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}, since these have superseded the CDC charts.
+As long as all observations are held against the same standards, this should not be of any consequence.
+
+% THE IMPERTUS FOR THE PAPER IS THE GENDER IN CCTs and OPTIMAL DESIGN
+The impertus for this paper lies in the optimal design of cash transfer schemes such as CCTs and UCTs.
+% RELATES TO THE ISSUE OF HOUSEHOLD AS A UNIT
+The lack Paretto optimal allocation of resources within households is discussed in i.a.
+\textcite{udry1995gender}, \textcite{udry1996gender}, and \textcite{duflo2004intrahousehold}.
+Based on this lack of Paretto optimal allocation,
+we have to reject the idea of households acting as a unit in an economic sense.
+For the design of cash transfer schemes it is therefore necisarry to determine the prefered recipient within the household.
+
+The South African pension system is an interesting object of study because of its eligibility criteria.
+The primary criterium is the age of the recipient.
+In adition to this there is a maximum income threshold.
+Because of these few criteria there are few selection bias issues in this study.
 
 The anthropometrics are useful for computing z-scores.
-These z-scores are considered a good representation of short-term or long-term malnutrition respectively, especially for children between 6 and 60 months old.
-
-The South African pension is a useful variable to measure income because of its criteria.
-Besides a maximum level of income, the only criterium is the age of a person.
-Because of this the status as a recipient is quite exogenous and there are few selection bias problems.
-The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.
-
-This study deviates from the Duflo study in several ways.
-% MAIN DEVIATION, PANEL NATURAL EXPERIMENT
-First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income,
-including pension recipient status.
-Whereas Duflo uses age as a proxy for recipient status.
-Secondly, between mid 2008 and the end of 2009 the pension age for men was gradualy lowered to sixty, which is at par with women.
-Another deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child} in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}.
-Since these have superseded the CDC charts, however this should not be of any consequence.
-
-% THE IMPERTUS FOR THE PAPER IS THE GENDER IN CCTs and OPTIMAL DESIGN
-% RELATES TO THE ISSUE OF HOUSEHOLD AS A UNIT
-% THEY ARE NO LONGER THAT RARE IN DEVELOPING COUNTRIES ???
+These z-scores are considered a good representation of short-term or long-term health issues, respectively.
+This relation is especially well observed for children between 6 and 60 months old.
+We therefore stay with the best practice and only include those individuals in our analysis.
 
@@
 
-% STATE THE MAIN RESULT
+% ESTIMATION
+
+Our main finding is that we find a negative effect of the policy change on the age-based growth metrics on children (HAZ and WAZ).
+In the height-based metrics we find a negative effect of the state pension income of men on the body mass index (though not on the WHZ).
+Our results seems to indicate that the policy change had a negative impact on the long-term growth of children.
+Furthermore, we see a negative effect of the mens pension income on the BMI of children.
+These results provide support for the theory that exogenous incomes in a poverty relief context,
+such as CCTs and UCTs are best transfered to women in the households.
 
@@
 % DESCRIPTIVE STATISTICS OF THE DATASET AND POSSIBLY THE GROWTH STANDARDS
-In this paper I use data from two sources.
+In this paper we use data from two sources.
 The first is the South African National Income Dynamics Survey \parencite[NIDS][]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.
@@
 The main source of data is the National Income Dynamics Survey of South Africa \parencite{saldru2008nids, saldru2012nids, saldru2013nids}.
-This survey collects data on a representative set of appproximately 10,000 South-African households over time.
-The primary information types I use are:
+Like the 1993 survey used by \textcite{duflo2000child, duflo2003grandmothers}, this survey is conducted in cooperation with the World Bank.
+Unlike the 1993 survey, this survey does not use a random selection household,
+rather it collects data on a representative set of appproximately 10,000 South-African households over time.
+Currently three `waves' of data are available, these waves data from 2008, 2012, and 2013 respectively.
+
+The primary information types we use are:
 \begin{itemize}
@@
 \subsubsection{Age-Based Z-scores}
-The age-based z-scores are the Height-for-Age Z-score (HAZ) and the Weight-for-Age Z-score (WAZ).
-Since these metrics are age-based, they provide information about all past growth issues,
-any past issues such a malnutrition and disease will have impaired growth,
+The Age-Based Z-scores (ABZs) are consistituted by the Height-for-Age Z-score (HAZ) and the Weight-for-Age Z-score (WAZ).
+Since these metrics are age-based, they provide information about all past growth issues.
+Any past issues such a malnutrition and disease will have impaired growth,
 and these effects will still be captured by today's height.
 
-The age-based z-scores are constructed on a weekly basis up to the age of 60 months, and on a monthly basis thereafer.
+The ABZs are constructed on a weekly basis up to the age of 60 months, and on a monthly basis thereafer.
 
 \subsubsection{Height-Based Z-scores}
-The height-based z-scores are the Weight-for-Height Z-score (WHZ)
+The Height-Based Z-scores (HBZs) are the Weight-for-Height Z-score (WHZ)
 and Body Mass Index Z-score (BMIZ).
@@
 
-The height-based z-scores are available on a semi-centimeter level throughout all heights.
+The HBZs are available on a semi-centimeter level throughout all heights.
 
@@
 \section{Research Design}
+
+\subsection{Identification Strategy}
 \label{sa:identification}
-% The policy change, a natural experiment
+The identification strategy in this paper is based on a policy change in the pension eligibility age for men,
+which was introduced between mid 2009 and January 1st 2011.
+This policy change thus fall between waves 1 and 2 (2008 and 2012 respectively) of the NIDS data sets.
 
-\subsection{Ordinary Least Squares}
-We first perform an Ordinary Least Squares estimation (OLS).
-This is done using the linear model (lm) procedure from the R package `Base' \parencite{R}.
+Before this policy change, the eligibility age for men was 65 years old.
+Post the policy change, the eligibility age is 60 years old,
+which bring it at par with the pension eligibility age for women.
+
+We operationalise this natural experiment, by constructing a policy dummy.
+This policy dummy is called \textbf{elig.men.60}, and takes the value \textbf{1}
+for data after the policy change (i.e.~waves 2 \& 3), and the value \textbf{0} otherwise (i.e.~wave 1).
 
@@
 In order to fully exploit the available data and the policy change,
-we also employ a `Difference-in-Differences' estimator (DiD).
+we employ a `Difference-in-Differences' estimator (DiD).
 This estimator operationalised by using the fixed-effects (within) estimator, with a time-effect\footnote{The time effect estimated here is symmetric to the individual effect.
-We use the term `time effect', since this is a more meaningful description of the policy change.}.
+We employ the term `time effect', since it is a more meaningful description of the policy change.}.
 
@@
 % Fri Dec 27 23:22:00 2013
-\begin{table}[h!]
+\begin{table}[!ht]
 \centering
-\caption{Estimation Results: HAZ \& WAZ}
+\caption{Age-Based Z-scores}
 \label{sa:hazwaz}
@@
 % Fri Dec 27 23:53 2013
-\begin{table}[h!]
+\begin{table}[!ht]
 \centering
-\caption{Estimation Results: WHZ \& BMIZ}
+\caption{Height-Based Z-scores}
 \label{sa:whzbmiz}
@@
 \subsection{Robustness Checks}
-
-\subsubsection{OLS Robustness}
-
-\subsubsection{DiD Robustness}
 % HAUSMAN TEST FOR FE / RE

### 2013-12-29 south-africa.tex
spelling and brief intro research design

@@
 
-Furthermore, the data from the \textcite{saldru2008nids,saldru2012nids} surveys contains actual information on income,
+The other deviations are of a more practical nature.
+Firstly, the data from the \textcite{saldru2008nids,saldru2012nids} surveys contains actual information on income,
 including pension recipient status, whereas Duflo uses age as a proxy for recipient status.
-Another minor deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child},
+Secondly, another minor deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child},
 in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}, since these have superseded the CDC charts.
@@
 
-% THE IMPERTUS FOR THE PAPER IS THE GENDER IN CCTs and OPTIMAL DESIGN
 The impertus for this paper lies in the optimal design of cash transfer schemes such as CCTs and UCTs.
-% RELATES TO THE ISSUE OF HOUSEHOLD AS A UNIT
-The lack Paretto optimal allocation of resources within households is discussed in i.a.
-\textcite{udry1995gender}, \textcite{udry1996gender}, and \textcite{duflo2004intrahousehold}.
+The lack Paretto optimal allocation of resources within households as discussed in i.a.
+\textcite{udry1995gender}, \textcite{udry1996gender}, and \textcite{duflo2004intrahousehold},
+indicates the necesity of optimal design in such schemes.
 Based on this lack of Paretto optimal allocation,
 we have to reject the idea of households acting as a unit in an economic sense.
-For the design of cash transfer schemes it is therefore necisarry to determine the prefered recipient within the household.
+For the design of cash transfer schemes it is therefore necessary to determine the prefered recipient within the household.
 
@@
 In adition to this there is a maximum income threshold.
-Because of these few criteria there are few selection bias issues in this study.
+Outside of this, there are very few criteria.
+The reletive general applicablility of the program makes that there are few selection bias issues when studying this.
 
@@
 This relation is especially well observed for children between 6 and 60 months old.
-We therefore stay with the best practice and only include those individuals in our analysis.
+We therefore stay with the best practice and only include those observations in our analysis.
 
@@
 rather it collects data on a representative set of appproximately 10,000 South-African households over time.
-Currently three `waves' of data are available, these waves data from 2008, 2012, and 2013 respectively.
+Currently three `waves' of data are available, these waves date from 2008, 2012, and 2013 respectively.
 
@@
   \item child age (in days)
+  \item child gender
   \item adult pension recipient status
-  \item adult pension recipient gender
+  \item adult gender
+\end{itemize}
+In addition to these variables of interest, we include a number of covariates in the analysis. These are
+\begin{itemize}
+  \item Household income
+  \item Parent's education
 \end{itemize}
@@
 This is a numeric variable, the values of which lie very close together.
-For simplicity I have temporarily used this variable as a dummy.
 
 Children's anthropometrics are taken, these are length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores have been calculated.
+Using these anthropometics and WHO growth standards, z-scores are calculated.
 
@@
 by causing the child to be shorter or lighter.
-However, it is impossible to distinquish between the causes of an observed slow growth.
+However, it is impossible to distinquish between the different causes of an observed slowed growth.
 
@@
 and these effects will still be captured by today's height.
+This also applies to the WAZ, as standard weight is a function of the height,
+which is in turn a function of the age.
 
@@
 \section{Research Design}
+This study focuses on a policy change in the South-African state pension system.
+Until mid 2009, men became eligible for pension at the age of 65.
+Between mid 2009 and January 1st 2011, this was gradually lowered to 60.
+The South-African National Income Dynamics Survey is a full-panel dataset,
+which contains information on household from before and after this policy change.
+We study the effect of the policy change,
+as well as the general effect on the pension system,
+on the health of children in the same household.
+The research setup in discussed in further detail below.
 
@@
 
-\subsection{Difference in Differences}
+\subsection{Estimator}
 In order to fully exploit the available data and the policy change,
@@
 We perform the estimations using the R package `PLM' \parencite[see][]{croissant2008panel}.
-It is worth noting  that questions have been raised about the Difference-in-Difference estimator being employed in certain situations,
+It is worth noting  that questions have been raised about the Difference-in-Differences estimator being employed in certain situations,
 for example by (ironically) \textcite{bertrand2004much}.

### 2013-12-29 south-africa.tex
include formal specification SA, clear chapter pages

@@
 \label{sa}
+\vspace{\stretch{1}}
 \section*{Abstract}
@@
 and the general mens pension income had a negative effect on young children's BMI.
+\pagebreak
 
@@
 \subsubsection{Formal DiD Specification}
-% ATET etc.
+We can now formally specify our estimation as:
+\begin{equation}
+y_{it} = \gamma_i + \lambda_t + \delta T_{it} + P^f_{it} + P^m_{it} + X_{it} + \epsilon_{it}
+\end{equation}
+The outcome variable is $y_{it}$, this outcome variable takes the form of the of the z-scores,
+such as HAZ or WAZ.
+Where $t$ denotes the time and $i$ the individual.
+The individual and time fixes effects are denoted by $\gamma_i$ and $\lambda_t$ respectively.
+Dummies for living in a household with a female or a male pension recipient are included as $P^f_{it}$ and $P^m_{it}$ respectively.
+The dummy variable $T_{it}$ denoted the treatment status.
+Lastly, $\epsilon_{it}$ is the error term, which is assumed to be distributed as:
+\[
+\epsilon_{it} \sim N(0,\sigma)
+\]
+As we have only one time period before the treatment goes into effect,
+we cannot establish a common trend.
+The assumption here made is thus that the effects of $P^f_{it}$ and $P^m_{it}$ are level over time.
 

### 2013-12-29 bitattack.tex
clean chapter pages

@@
 \chapter{Bitcoin Attacks: Or How Cryptocurrencies Gain Momentum}
+\label{bitatt}
+\vspace{\stretch{1}}
+\section*{Abstract}
+In this chapter I set out the idea of employing the models used for currency attacks,
+to analyse how cryptocurrencies gain momentum.
+Additionaly, I discuss how inflation in the cryptocurrency economy is possible.
+\pagebreak
+
+\section{Introduction}
 As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies.
@@
 However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed.
-All of these cryptocurrencies are based to a large extend on the Bitcoin protocol, but often introduce small technological innovations.
+All of these cryptocurrencies are based to a large extend on the Bitcoin protocol,
+but often introduce small technological innovations.
 
-The most known of all of these alternative crypocurrencies is Litecoin.
-Litecoin introduces a number of small technological innovations, the most import of these is the change that the process of `mining' coins is 4 times faster, this has two consequences, transactions are approved faster than in the bitcoin protocol.
+The most known of all of these alternative crypocurrencies is Litecoin. Litecoin introduces a number of small technological innovations,
+the most import of these is the change that the process of `mining' coins is 4 times faster,
+this has two consequences, transactions are approved faster than in the bitcoin protocol.
 It also means that the technological limit for the total number of Litecoins ever available is 4x times higher.
@@
 Most new cryptocurrencies do not gain momentum and their value is only trivialy more than zero.
-However, some currencies have gain momentum, the previously mentioned litecoin introduces a technological innovation and build it base on that.
+However, some currencies have gain momentum,
+the previously mentioned litecoin introduces a technological innovation and build it base on that.
 However, recently a new cryptocurrency has arisen and become quite popular.
@@
 Dogecoin is a reference to an internet phenomenon called `Doge Meme'.
-Despite the fact that `Dogecoin' does not have a real reason for being considered valuable (in the sense that crypotocurrencies are considered valuable), however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable.
-We thus observe that from the perspective of economic and technological fundamentals, there is a situation of multiple equilibria.
+Despite the fact that `Dogecoin' does not have a real reason for being considered valuable
+(in the sense that crypotocurrencies are considered valuable),
+however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable.
+We thus observe that from the perspective of economic and technological fundamentals,
+there is a situation of multiple equilibria.
 
-My idea is to adapt standard models of currency attacks such as in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models} to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies.
+\section{Positive Currency Attacks}
+My idea is to adapt standard models of currency attacks such as in 
+\textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}
+to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies.
 Initially we would model how a currency can gain sufficient momentum to establish itself as a stably above zero.
 
-This could later be expended to a model with several cryptocurrencies competing for the investment of the same new cryptocurrency adopt, who is converting his/her fiat currency into one of several cryptocurrencies.
+\subsection{A Multi-currency Model}
+This could later be expended to a model with several cryptocurrencies,
+competing for the investment of the same new cryptocurrency adopt,
+who is converting his/her fiat currency into one of several cryptocurrencies.
+
+\section{Multi-cryptocurrency Economy and Inflation}
+Finally, an extension of such a multi-cryptocurrency model can provide a valuable insight into the issue of inflation.
+
+On of the key selling points of the cryptocurrencies, and equally one of the key critisism of many economics
+(e.g.~Paul Krugman), is that there is no inflation in a crypocurrency.
+The crypocurrencies are designed specifically so that inflation eventually becomes impossible (once all coines are mined).
+
+However, it is key here to understand the economy as a multi-cryptocurrency object.
+Since creating a currency can be done at negligable cost,
+and the only value of the cryptocurrency lies in its utility as a mechanism for transactions,
+more cryptocurrencies will come into existance.
+Especially since it is very simple for a merchant to accept several cryptocurrencies as a form of payment.
+The effect of this will be that inflation in each cryptocurrency will remain as defined,
+however, the cryptocurrency economy as a whole, will be able to experience inflation.
+
+Additionaly, this partly addresses one of social critiques of Bitcoin,
+namely the issue of bitcoin mining being excessively wastful.
+Bitcoin mining does not produce anything of any social value (not unlike gold mining),
+the higher value of bitcoin, the more computing power (and electricity) will be diverted to this.
+However, in a multi-currency model, it will be more effective to mine alternative cryptocurrencies,
+as these can initially be mined with relative ease.
 

### 2013-12-29 bitremit.tex
clean chapter pages

@@
 \chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
-\label{btc}
+\label{bitremit}
+\vspace{\stretch{1}}
+\section*{Abstract}
+In this chapter I describe the basis of cryptocurrencies, particularly Bitcoin.
+I give an overview of what sources of data are available for analysis, and how these can be employed.
+I propose a project which enables simple telephones or `stupid phones' to perform bitcoin transaction,
+this can provide insights into the remittances that are transacted in Bitcoin.
+\pagebreak
+
+\section{Introduction}
 In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).

### 2014-01-02 south-africa.tex
updates from chromebook

@@
 
-\subsubsection{Formal DiD Specification}
-We can now formally specify our estimation as:
-\begin{equation}
-y_{it} = \gamma_i + \lambda_t + \delta T_{it} + P^f_{it} + P^m_{it} + X_{it} + \epsilon_{it}
-\end{equation}
+\subsubsection{Models and Variations}
+We define the variables for our estimation equations.
 The outcome variable is $y_{it}$, this outcome variable takes the form of the of the z-scores,
@@
 \]
+
+We can now formally specify our base estimations as in \autoref{sa:eq:base}, this represents model 1.
+\begin{equation}
+\label{sa:eq:base}
+y_{it} = \gamma_i + \lambda_t + \mu P^f_{it} + \nu P^m_{it} + X_{it} + \epsilon_{it}
+\end{equation}
+
+In \autoref{sa:eq:policy} we include our policy dummy variable, this variation is denoted as model 2 in our results.
+\begin{equation}
+\label{sa:eq:policy}
+y_{it} = \gamma_i + \lambda_t + \mu P^f_{it} + \nu P^m_{it} + X_{it} + \delta T_{it} + \epsilon_{it}
+\end{equation}
+
+Lastly, we formulate a variant of the model which includes an interaction term of the policy dummy with the male pension-recipien dummy
+(as well as the variables themselves).
+We refer to this as model 3, and the formal specification is given in \autoref{sa:eq:interaction}
+\begin{equation}
+\label{sa:eq:interaction}
+y_{it} = \gamma_i + \lambda_t + \mu P^f_{it} + \nu P^m_{it} + X_{it} + \delta T_{it} + \rho T_{it}*P^m_{it} + \epsilon_{it}
+\end{equation}
+These three models the are variations that we use on the Right-Hand Side (RHS) of the estimation equations.
+
+As described above, we have a total of four z-scores available as dependent variables, Height-for-Age (HAZ), Weight-for-Age (WAZ), Weight-for-Height (WHZ), and Body Mass Index (BMI).
+Each of these is used in a different estimation as the Left-Hand Side (LHS).
+Combining these four LHSs with each of the three RHSs, gives a total of twelve estimation equations.
+The results of the estimation of each of these twelve equations is presented in autoref{sa:results}.
+
 As we have only one time period before the treatment goes into effect,
@@
 \section{Results}
+\label{sa:results}
 In \autoref{sa:hazwaz} we present our estimation results for the age-based z-scores,
 and in \autoref{sa:whzbmiz} we present our estimation results for the height-based z-scores.
+
+In these tables the dependent variable used it defined on the top row.
+The second row defines the model used (as defined in \autoref{sa:models}).
+The other rows represent the independent variables.
+Where \textbf{w\_spen\_w} represents the dummy variable for children living in a household with a state pension eligible woman.
+The variable \textbf{w\_spen\_m} is the dummy for the child living in the same household as a male state mension recipient.
+The policy variable \textbf{elig.men.60} is a dummy which takes the value \textbf{1} for waves 2 and 3.
+An interaction term of the later two is also included as \textbf{eli.men.60:w\_spen\_m}.
+Lastly, we unclude de covariate \textbf{w\_h\_tinc} which represents total household income.
 
@@
 
+As \autoref{sa:hazwaz} shows both the Height-for-Age and the Weight-for-Age estmations for all three Right-Hand Side variations give similar results.
+For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
+In all cases the estimate has a p-value of less that \textbf{0.01}.
+Meaning that (meta-discussion aside) the probabiliy that this coefficient represents a non-existant relation (Type II error) is less than one percent.
+In the model 2 specification of the Weight-for-Height dependent variable, the p-value is even less that 0.001.
+However, upon the inclusion of the interaction term (model 3) this falls back to below 0.01.
+
+The fact that this outcome is consistent across different Right-Hand Side,
+as well as Left-Hand Side specifications, further lends credibility of there not being a Type II error.
+As mentioned above, the HAZ and the WAZ Z-scores capture long-term or past health issues.
+
+Furthermore, when using Height-for-Age as the LHS, and the model 2 on the HRS, we find a positive effect of living with a male pension recipient.
+The coefficient output here is no longer significant when we include the interaction term in the model 3 specification.
+
+The interpretation of the coefficients of these dummy variables is as follows.
+The coefficient represents the change in the expected value of a child's deviation for the standard growth anthropometics in standard deviations. 
+A coefficient of \textbf{-0.3419} of the dummy \textbf{elig.men.60} in HAZ model 2,  thus indicates that,
+after the lowering of the male pension eligibility age, ceteris paribus, a child's expected Height-for-Age Z-score is 0.3410 standard deviation lower than before the lowering of the eligibility age.
+
 % LaTeX table created manually
@@
 
-\subsection{Robustness Checks}
-% HAUSMAN TEST FOR FE / RE
+In \autoref{sa:whzbmiz} we do not find an effect of the \textbf{elig.men.60} variable.
+In the WHZ estimation we do not find any significant variables.
+However, the \textbf{BMIZ} estimation we find \textbf{w\_spen\_m} to be significant at a 5\% level of all specifications.
 
-\section{Conclusion}
+\section{Conclusions and Limitations}
+We find two results from out estimations.
+Firstly, we find that there is a significant and consistant negative effect of the policy variable \textbf{elig.men.60} on the age-based z-scores
+(i.e. Height for Age and Weight for Height).
+Secondly, we find a consistent and negative effect of the men's pension variable (\textbf{w\_spen\_m}) on the Body-Mass-Index Z-scores.
+Both of these effect are consistent across the different specifications used in our estimations.
 

### 2014-01-02 south-africa.tex
add intro etc.

@@
 Our finding is that policy change had a negative effect on long-term growth metrics of young children
-and the general mens pension income had a negative effect on young children's BMI.
+and the general male pension income had a negative effect on young children's BMI.
 \pagebreak
@@
 
+As mentioned above, we follow \textcite{duflo2000child,duflo2003grandmothers} general design.
+Looking at the gender of pension recipients gives a relatively clean analysis,
+because of it's relative exogeneity.
+We therefore use these as the Right-Hand Side variables, or explanata.
+Anthopometrics for children are used, since these capture well, the effects of both malnutrition and disease,
+the two most common health issues that we are addressing.
+
 The South African pension system is an interesting object of study because of its eligibility criteria.
@@
 The anthropometrics are useful for computing z-scores.
+With z-scores we refer to the practice of standardising the anthropometrics using an `idea' standard \parencite{who2006child}.
+
+For example, if we measure a height $x$ for a child of age $y$ (in weeks/months),
+then we refer the to WHO tables, find the relevant ideal height and standard deviation for a child of age $y$.
+We then substract the ideal height ($\mu_y$) from the observed height,
+and divide by the standard devation ($\sigma_y$), like so:
+\[
+z_{xy} = \frac{x - \mu_y}{\sigma_{y}}
+\]
+We distinquish between Age Based Z-scores (ABZ) and Height-Based Z-scores (HBZ).
+This is described in futher detail in \autoref{sa:data:who}.
+
 These z-scores are considered a good representation of short-term or long-term health issues, respectively.
@@
 
+The income from the pension system is just above 1000 SAR.
+There are a number of different exact amount, which we have simplified to a dummy.
+Since the variation in the amount is around 5\% this should not be without much loss of generality.
+\autoref{sa:ta:income} gives a description of the distribution of income as found in the NIDS data sets.
+
+\begin{table}[hb!]
+\centering
+\caption{NIDS Income distribution}
+\label{sa:ta:income}
+\begin{tabular}{l|r}
+\hline
+  Min. & 0 \\
+  1st Qu. & 1,070 \\
+  Median & 1,870 \\
+  Mean & 3,939 \\
+  3rd Qu. & 3,150 \\
+  Max. & 3,413,000 \\
+\end{tabular}
+\end{table}
+
 Children's anthropometrics are taken, these are length/height, weight, and waist.
 Using these anthropometics and WHO growth standards, z-scores are calculated.
+The following z-scores are included:
 
 \subsection{WHO: Child Growth Standards}
+\label{sa:data:who}
 In 2006 the WHO published its standards for child growth \parencite{who2006child}.

### 2014-01-02 south-africa.tex
more intro

@@
 We distinquish between Age Based Z-scores (ABZ) and Height-Based Z-scores (HBZ).
+We use two types ABZs and two types of HBZs, for a total of four types of z-scores.
 This is described in futher detail in \autoref{sa:data:who}.
@@
 
+We formulate three models. One without the treatment dummy,
+one with the treatment dummy, and one with the treatment dummy,
+and an interaction term with male pension recipient status.
+Each of these models is estimated with all four types of z-scores,
+which gives a total of twelve estimation equations.
+
 % HISTORY OF APARTHEID AND CHANGE IN PENSION SCHEME
 
-% ESTIMATION
-
-Our main finding is that we find a negative effect of the policy change on the age-based growth metrics on children (HAZ and WAZ).
+Our main finding is a negative effect of the policy change on the age-based growth metrics on children (HAZ and WAZ).
 In the height-based metrics we find a negative effect of the state pension income of men on the body mass index (though not on the WHZ).

### 2014-01-02 south-africa.tex
summary of results

@@
 and the general male pension income had a negative effect on young children's BMI.
+
+These results provide support for the idea that it is preferable to use female recipients in poverty-relief projects such as CCTs.
 \pagebreak
@@
 This paper looks at the effect of the gender of pension recipients on the growth of children in the same household.
-The study is based on South-African data and the approach is very similar to \textcite{duflo2000child,duflo2003grandmothers}.
+The study is based on South-African data and the approach is very similar to \textcite{duflo2000child,duflo2003grandmothers},
+and orignally based on the work of \textcite{thomas1994like}.
 The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for anthropometrics are computed as z-scores.
@@
 we have to reject the idea of households acting as a unit in an economic sense.
-For the design of cash transfer schemes it is therefore necessary to determine the prefered recipient within the household.
+For the design of cash transfer schemes it is therefore necessary to determine the prefered recipient within the household
+\footnote{For a good overview see e.g.~\textcite{haddad1997intrahousehold}}.
 
 As mentioned above, we follow \textcite{duflo2000child,duflo2003grandmothers} general design.
-Looking at the gender of pension recipients gives a relatively clean analysis,
+Looking at the gender of pension recipients gives a reasonably clean analysis,
 because of it's relative exogeneity.
-We therefore use these as the Right-Hand Side variables, or explanata.
+We therefore use these pension receipts as the Right-Hand Side variables, or explanata.
 Anthopometrics for children are used, since these capture well, the effects of both malnutrition and disease,
-the two most common health issues that we are addressing.
+the two most common health impediments that we are addressing.
 
@@
 The reletive general applicablility of the program makes that there are few selection bias issues when studying this.
+A thorough, though a points somewhat dated, discussion can be found in \textcite{case1998large}.
+Although the pension system was intended as a form of poverty relief for the elder population,
+it has also become that for the South-African rural population\parencite{tangwe2013impact}.
+Average household income in rural area is much lower than in urban areas.
+Pension receipt have therefore formed a large share of household income.
+Upon the initial expension to include the black population, in 1991,
+this was a much as twice the mean monthly income.
 
-The anthropometrics are useful for computing z-scores.
-With z-scores we refer to the practice of standardising the anthropometrics using an `idea' standard \parencite{who2006child}.
-
-For example, if we measure a height $x$ for a child of age $y$ (in weeks/months),
-then we refer the to WHO tables, find the relevant ideal height and standard deviation for a child of age $y$.
-We then substract the ideal height ($\mu_y$) from the observed height,
-and divide by the standard devation ($\sigma_y$), like so:
-\[
-z_{xy} = \frac{x - \mu_y}{\sigma_{y}}
-\]
-We distinquish between Age Based Z-scores (ABZ) and Height-Based Z-scores (HBZ).
+The anthropometrics taken in the NIDS are useful for computing z-scores.
+We distinguish between Age Based Z-scores (ABZ) and Height-Based Z-scores (HBZ).
 We use two types ABZs and two types of HBZs, for a total of four types of z-scores.
@@
 
-We formulate three models. One without the treatment dummy,
-one with the treatment dummy, and one with the treatment dummy,
+We formulate three models. One model without the treatment dummy,
+one model with the treatment dummy, and finally one model with the treatment dummy,
 and an interaction term with male pension recipient status.
@@
 which gives a total of twelve estimation equations.
-
-% HISTORY OF APARTHEID AND CHANGE IN PENSION SCHEME
+All twelve equation are estimated as fixed-effect panel models, with, where included, a time effect.
+We have only one data period before the policy change, which means that we cannot test for a common trend.
+The implicit assumption here is thus that the effects are level over the time period studied here.
 
@@
 \end{itemize}
-In addition to these variables of interest, we include a number of covariates in the analysis. These are
+In addition to these variables of interest, we include a number of covariates in the analysis, these are:
 \begin{itemize}
@@
 and by extension, the household in which they grow up.
+With z-scores we refer to the practice of standardising the anthropometrics using an `idea' standard \parencite{who2006child}.
+
+For example, if we measure a height $x$ for a child of age $y$ (in weeks/months),
+then we refer the to WHO tables, find the relevant ideal height and standard deviation for a child of age $y$.
+We then substract the ideal height ($\mu_y$) from the observed height,
+and divide by the standard devation ($\sigma_y$), like so:
+\[
+z_{xy} = \frac{x - \mu_y}{\sigma_{y}}
+\]
 These ideal scores are based on a sample of children from different ethnic populations,
@@
 
-\subsection{Estimator}
+\subsection{Estimation}
 In order to fully exploit the available data and the policy change,
@@
 
+% ASSUMPTIONS
+
+% LIMITATIONS
+
+% ROBUSTNESS
+
+% RECOMMENDATIONS
+
 \printbibliography

### 2014-01-02 south-africa.tex
data description

@@
 
+\begin{table}[hb!]
+\centering
+\caption{Z-score distributions}
+\label{sa:ta:zscore}
+    \begin{tabular}{l|rrrr}
+    \hline
+    & HAZ & WAZ & WHZ & BMIZ\\
+    \hline
+    Min.   & -5.972 & -6.000  & -4.916 & -4.994 \\
+    1st    & -1.768 & -1.110  & -0.302 & -0.602 \\
+    Median & -0.941 & -0.310  &  0.491  & 0.207  \\
+    Mean   & -0.956 & -0.296  &  0.501  & 0.240   \\
+    3rd    & -0.132 &  0.516  &  1.351  & 1.069  \\
+    Max.   &  5.975 &  4.958  &  4.967  & 4.992  \\
+    \end{tabular}
+\end{table}
+
 For adults several variables measure the different amounts and sources of income.
@@
 This is a numeric variable, the values of which lie very close together.
+We observe that 22.99\% of household in our dataset have a female pension recipient as part of the household.
+Furthermore, we observe that 9.06\% of households in our dataset have a male pension recipient.
+This implies that, despite the fact that men are now eligible at the same age as women,
+the vast majority of pension recipients is female.
+Therefore, there is still a selection bias issue in the data we are analysing.
 
@@
 Using these anthropometics and WHO growth standards, z-scores are calculated.
-The following z-scores are included:
 

### 2014-01-05 south-africa.tex
update results, add tables ratios

@@
 \subsubsection{Height-Based Z-scores}
+\label{sa:se:hbz}
 The Height-Based Z-scores (HBZs) are the Weight-for-Height Z-score (WHZ)
@@
 
-As \autoref{sa:hazwaz} shows both the Height-for-Age and the Weight-for-Age estmations for all three Right-Hand Side variations give similar results.
+As \autoref{sa:hazwaz} shows both the Height-for-Age and the Weight-for-Age estimations for all three Right-Hand Side variations give similar results.
 For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
@@
 
+We thus find a negative effect of the treatment on growth metrics.
+Furthermore, for one height-based z-score we also find a negative effect of male pension recipients on growth metrics.
+Additionaly, it is suprising that we find significant coefficients for \textbf{w\_spen\_m} in one height-based z-score (\textbf{BMIZ}), but not in the other \textbf{WHZ}.
+
+The last results is especially surprising,
+considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
+and roughtly half of the estimates of the \textbf{BMIZ} estimations.
+
+For the lower coefficient estimates, it is important to note that \textbf{BMIZ} is essentially a convex mapping of \textbf{WHZ},
+since height is squared in the denominator of the BMI function, as described in \autoref{sa:se:hbz}.
+In other words, the fact that the estimators, which give transformed coefficient estimates can have different significance levels,
+can be explained as follows.
+The squaring of the height in the denominator of the Body-Mass Index function, makes it a non-linear mapping of the Weight-for-Height Z-scores.
+Furthermore, from the significance of the coefficients in the \textbf{BMIZ} estimations,
+we can conclude that the coefficient estimates are higher that the standard error estimates,
+by a factor of several times (for Degrees of Freedom $\sim 380$).
+Combining the small estimates of the standard errors, with the convex mapping,
+gives the results that the standard errors are scaled up to a lesser degree than the coefficient estimates.
+This then gives the results, that with t-testing the significance of the convexly mapped coefficients and standard errors,
+we can find significance at the 5\% level for the convexly mapped \textbf{BMIZ} estimates of \textbf{w\_spen\_m},
+where for the \textbf{WHZ} estimates of \textbf{w\_spen\_m} we could not.
+
+% DROP IN FEMALE RECIPIENTS, REMAIN LEVEL FOR MEN
+
+\begin{table}[ht!]
+\centering
+\caption{Households with and without Male Pension Recipients}
+\label{sa:ta:hmr}
+    \begin{tabular}{l|rrrr}
+    \hline
+    Year              & 2008   & 2012   & 2013   & Overall \\
+    \hline
+    Male Recipient    & 612    & 595    & 623    & 1830    \\
+    No Male Recipient & 6121   & 6138   & 6110   & 18369   \\
+    Ratio of Male Recipients & 0.0909 & 0.0884 & 0.0925 & 0.0906  \\
+    \end{tabular}
+\end{table}
+
+\begin{table}[ht!]
+\centering
+\caption{Households with and without Female Pension Recipients}
+\label{sa:ta:fmr}
+    \begin{tabular}{l|rrrr}
+    \hline
+    Year                & 2008   & 2012   & 2013   & Overall \\
+    \hline
+    Female Recipient    & 1637   & 1498   & 1509   & 4644    \\
+    No Female Recipient & 5096   & 5235   & 5224   & 15555   \\
+    Ratio               & 0.2431 & 0.2225 & 0.2241 & 0.2299  \\
+    \end{tabular}
+\end{table}
+
 \section{Conclusions and Limitations}
@@
 Firstly, we find that there is a significant and consistant negative effect of the policy variable \textbf{elig.men.60} on the age-based z-scores
-(i.e. Height for Age and Weight for Height).
+(i.e.~Height for Age and Weight for Height).
 Secondly, we find a consistent and negative effect of the men's pension variable (\textbf{w\_spen\_m}) on the Body-Mass-Index Z-scores.

### 2014-01-05 south-africa.tex
add more on evolution to results section

@@
 
-The last results is especially surprising,
+The last result is surprising,
 considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
@@
 
-% DROP IN FEMALE RECIPIENTS, REMAIN LEVEL FOR MEN
+Regarding the negative effect of the expansionary policy change, we need to further disseminate the change in the independent variables.
+\autoref{sa:ta:hmr} and \autoref{sa:ta:hfr} describe the evolution of the number of children living in a household with a pension recipient.
+We observe a substantial drop in both children living with male and female pension recipients.
+The change for the number of children living in the same household as a male pension recipient is from 612 children in 2008 to 595 children in 2012. A drop of 17 or -2.79 percent.
+However, if we compare the number of children living in the same household as a male pension recipient for the year 2013,
+the results are quite different.
+In the year 2013 we observe 623 children living with a male pension recipient, a rise of 1.8 percent vis-a-vis the year 2008.
+When comparing the number of children living in the same household as a female pension recipient, we see a different picture.
+In 2008 we observe 1637 children living with a female pension recipient,
+and in the year 2012 we observe a number of 1498, a drop of 8.49 percent.
+In the year 2013 we observe 1509 children living with female recipients in 2013,
+a drop of 8.48 oercent vis-a-vis 2008.
+We thus observe a drop in both the number of children living with male recipients,
+of children living with female recipients between the years 2008 and 2012.
+However, for male recipients the number rises to above 2008 levels in 2013,
+where as the number for female recipients remains around the lower 2012 levels.
+
+We thus observe a drop even in the number of children living with female pension recipients,
+despite the fact that female pension recipients were unaffected by the policy change.
+
+One of the reason for this drop in life expectancy in South Africa.
+ % Include graph
+The predominant reason for the this drop in life expectancy is taken to be HIV/AIDS.
+% stats of people over 65.
 
@@
 \centering
-\caption{Households with and without Male Pension Recipients}
+\caption{Children in Households with and without Male Pension Recipients}
 \label{sa:ta:hmr}
@@
 \centering
-\caption{Households with and without Female Pension Recipients}
-\label{sa:ta:fmr}
+\caption{Children in Households with and without Female Pension Recipients}
+\label{sa:ta:hfr}
     \begin{tabular}{l|rrrr}
@@
 % ASSUMPTIONS
+% level effects
 
 % LIMITATIONS
+% simultanuous movement in recipient numbers.
 
 % ROBUSTNESS
+% questionable regarding the levelness.
+
+% CONCLUSIONS
+% which hold? what do we think?
 
 % RECOMMENDATIONS
+% estimate using by weighting the drop for women with life exp. evolution, and male also
+% or use the drop for women (unaffected) to scale men and women back to 2008 levels.
 

### 2014-01-06 south-africa.tex
intro, results and conclusions

@@
 This brought the pension eligibility age for men at par with women.
-We employ a Difference-in-Difference (or Fixed Effects) analysis of this change.
+There are two reasons why this warants a further look at this topic in this dataset.
+
+Firstly, life expectancy is South Africa is substantialy below the pension eligibility age.
+Around the end of the first decade of the century, which is when our data was collected,
+the average life expectancy at birth was only slighly above 50 years old.
+In the year 1993, when \textcite{duflo2000child,duflo2003grandmothers} are analysed,
+the average life expectancy at birth was somewhat higher (slightly above 55 years old).
+A further discussion of this can be found is \autoref{sa:results}
+However, in both cases, there is a substantial selection bias in the pension recipient base.
+Moreover, the fact that men receive pension only at 65, and women at sixty,
+causes an even more pronounced selection bias in the male pension recipient base.
+This also makes the comparing of the effect of male pension reicipient and female pension recipients,
+on the anthropometrics of children in the same household problematic,
+since much more attrition will have take place in the male pension base.
+The drop in life expectancy also aggravates the issue of attrition,
+and the associated selection bias.
+However, since pension eligibility becomes equal, for both men and women, at least,
+provides us with effects which internally more comparable.
+We say more, because the difference in attribition between the male and female pension base in our sample has not entirely been eliminated.
+Throughout the evolution of the average life expectancy at birth in South Africa,
+female life expectancy has been higher than male life expectancy by about one year.
+Bearing in mind that the difference between average life expectancy and pension eligibility is around 9 years,
+this additional selection bias effect, should not be underestimated.
+Furthermore, is seems likely that a healthy lifestyle, which increases the chance of becoming a pension recipient,
+also has an effect on the lifestyle of household members.
+In this is so, then our observed attrition will be an actual cause of a selection bias \textbf{effect}.
+
+Secondly, we employ a Difference-in-Difference (or Fixed Effects) analysis of this change.
 Under then assumptions of the Difference-in-Difference model,
@@
 The other deviations are of a more practical nature.
-Firstly, the data from the \textcite{saldru2008nids,saldru2012nids} surveys contains actual information on income,
+Firstly, the data from the \textcite{saldru2008nids,saldru2012nids,saldru2013} surveys contains actual information on income,
 including pension recipient status, whereas Duflo uses age as a proxy for recipient status.
@@
 
-The impertus for this paper lies in the optimal design of cash transfer schemes such as CCTs and UCTs.
+The impetus for this paper lies in the optimal design of cash transfer schemes such as CCTs and UCTs.
 The lack Paretto optimal allocation of resources within households as discussed in i.a.
@@
 Currently three `waves' of data are available, these waves date from 2008, 2012, and 2013 respectively.
-
 The primary information types we use are:
@@
   \item Household income
-  \item Parent's education
+  \item Parents education
 \end{itemize}
@@
 
-The last result is surprising,
-considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
+The last result is surprising, in the sense that it is significant for one dependent variable, but not the other.
+Especially considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
 and roughtly half of the estimates of the \textbf{BMIZ} estimations.
 
-For the lower coefficient estimates, it is important to note that \textbf{BMIZ} is essentially a convex mapping of \textbf{WHZ},
+For the higher coefficient estimates, it is important to note that \textbf{BMIZ} is essentially a convex mapping of \textbf{WHZ},
 since height is squared in the denominator of the BMI function, as described in \autoref{sa:se:hbz}.
@@
 The squaring of the height in the denominator of the Body-Mass Index function, makes it a non-linear mapping of the Weight-for-Height Z-scores.
-Furthermore, from the significance of the coefficients in the \textbf{BMIZ} estimations,
+Furthermore, from the significance at the 5\% level of the coefficients in the \textbf{BMIZ} estimations,
 we can conclude that the coefficient estimates are higher that the standard error estimates,
@@
 
-One of the reason for this drop in life expectancy in South Africa.
+The most immediate explanation for this is the life expectancy in South Africa.
+Since the year 1990 the life expectancy for both women and men has consistently been dropping.
+The predominant reason for the this drop in life expectancy is taken to be HIV/AIDS.
+
+Around the year 2005 the life expectancy at birth was slighly above 50 years.
+Since pension eligibility age is 60 years (and 65 for men until 2009),
+there is an almost ten year gap between average life expectancy and pension eligibility.
+This gap causes a delayed in the effect of the drop in life expectancy.
+The attribition effect of a person passing away at the age of fifty, on the pension recipient base,
+will thus only be observed ten years after death.
+
+After the year 2005, life expectancy started rising slowly,
+however, as explained above, it will take some time for this effect to disseminate into the pension base.
+
 % Include graph
-The predominant reason for the this drop in life expectancy is taken to be HIV/AIDS.
+
 % stats of people over 65.
@@
 
-% ASSUMPTIONS
-% level effects
+The main impetus for this paper lies in the optimal design of cash transfer schemes,
+such as Conditional Cash Transfers (CCTs) and the newly fashionable Uncondional Cash Transfers (UCTs).
+Which is the optimal manner in which these grants are distributed, measured along the bars of health,
+as well as education and work force participation.
+In this paper \parencite[like in][]{duflo2000child,duflo2003grandmothers} we try to address of the issue of differential effects relating to the gender of the cash recipient.
 
-% LIMITATIONS
-% simultanuous movement in recipient numbers.
+We do this by evaluating the z-scores of anthropometrics of children between the ages of six and sixty months old, living in the same household as recipients of the South-African old-age state pension system.
+We then compare the z-scores for children living with male pension recipients, which the z-scores of children living with female pension recipients.
 
-% ROBUSTNESS
-% questionable regarding the levelness.
+This approach is identical to \textcite{duflo2000child,duflo2003grandmothers}, however this analysis offers some additional value.
+Firstly, we analyse data around a policy change, which lowers the pension eligibility age for men from 65 to 60,
+which brings it at par with women's pension eligibility age.
+There are two impeti for further analysis of this data.
+
+Firstly, this partly overcomes major issues with attrition and the associated selection bias.
+Since average life expectancy is well below pension eligibility age,
+there is a strong indication that such a selection bias issue would be present.
+It is also very likely that confounding variables would be effecting both the selection bias, as well as the dependent variable.
+With the differential in pension eligibility age, this would make the effect incomparable,
+however, as the men's eligibility age is brought to the same as women's, this makes comparison less problematic.
+Considering the fact that selection bias in our analysis is comparable, but nevertheless still present,
+we note that we cannot automatically draw inferences about the external validity of the results presented here.
+
+Secondly, analysing data around the policy change allows us to employ a Difference-in-Differences estimation (DiD).
+Which enables us to draw a causal inference from the treatment effect,
+which is onthologically more intersting than a correlation.
+
+We use the South-African National Income Dynamics Survey data
+\parencite[in collaboration with The World Bank]{saldru2008nids,saldru2012nids,saldru2013nids}.
+This full-panel dataset provides observations from 2008, 2012, and 2013.
+The treatment, a policy change which lowers the pension elgilibity age for men from 65 to 60, takes place around 2009.
+Since we have only one time period before the treatment (the year 2008), we cannot establish the common trend.
+This common trend is used to validate the common trend assumption, which unpins the Difference-in-Differences method.
+As discussed in \autoref{sa:results}, we find that not establishing the trend proves problematic for our analysis.
+Between the years 2008 and 2012,
+we see a substantial drop in the number of children living in the same household as a female pension recipient.
+Since female pension recipients are unaffected by the policy change, we have to assume that a further exogenous factor is the cause of this drop.
 

### 2014-01-06 south-africa.tex
conclusion

@@
 The other deviations are of a more practical nature.
-Firstly, the data from the \textcite{saldru2008nids,saldru2012nids,saldru2013} surveys contains actual information on income,
+Firstly, the data from the \textcite{saldru2008nids,saldru2012nids,saldru2013nids} surveys contains actual information on income,
 including pension recipient status, whereas Duflo uses age as a proxy for recipient status.
@@
 \subsubsection{Models and Variations}
+\label{sa:models}
 We define the variables for our estimation equations.
@@
 
-% CONCLUSIONS
-% which hold? what do we think?
+In our estimations we use the Difference-in-Differences method,
+which is operationalised a fixed-effect panel estimation with a time effect.
+The contruct three Right-Hand Side (RHS) model.
+The first model is a fixed-effect estimation without the treatment dummy.
+The second model is a fixed-effects estimation with the treatment dummy (\textbf{elig.men.60}).
+the third model is a fixed-effects estimation with the treatment dummy,
+as well as an interaction term with the male pension recipient dummy (\textbf{w\_spen\_m}).
+
+On the Left-Hand Side (LHS) we use four different anthropometric z-scores,
+Height-for-Age (HAZ), Weight-for-Age (WAZ), Weight-for-Height (WHZ), and BMI (BMIZ).
+The first two z-scores are age based (ABZ), the latter two height based (since height factors in the BMI equation, HBZ).
+
+Combining the three RHS models with the four LHS z-scores gives us twelve estimation equations.
+In the estimation of these twelve equations, we find two effects.
+
+Firstly, we find that in for both the Age-Based Z-scores (ABZs),
+the treatment dummy is significant for the models 2 and the models 3
+(we do not find this in model 1, since it is not included the model 1 equation).
+In all cases, the coefficient for the treatment dummy is negative.
+Since both these Age-Based Z-scores (ABZs) reflect long-term or past health issues,
+this seems to indicate a negative correlation between the policy change on the long-term anthropometrics.
+Since this is the treatment dummy, this would suggest a negative causal effect of male pension receipts on child health.
+However, as discussed in \autoref{sa:results},
+this is likely to be a consequence of the common trend not having been established.
+Since we also observe a sharp drop in the number of children living with female pension recipients,
+despite the fact that the female pension recipient base in unaffected by the policy change.
+
+Secondly, we find that living with male pension recipient (\textbf{w\_spen\_m}),
+is negatively correlated with a the BMI z-scores (\textbf{BMIZ}).
+As discussed in \autoref{sa:results}, the Body-Mass-Index Z-score is a convex mapping of the Weight-for-Height z-score.
+This can explain the fact that these essentialy similar estimations, give different significance levels.
+Considering that the use of the Body Mass Index is far more wide spread than the Weight for Height metric,
+we believe that the significance of these coefficients carries more weight.
+The fact that these coefficients are negative, indicates that for this short-term z-score,
+the prefered recipient would be female household members.
+
+In conclusion, we find a negative correlation between the treatment dummy and the long-term ABZs.
+This is likely to be a consequence of the common trend not having been established,
+since there is also a drop in the number of children living with female pension recipients, which serves as the control group.
+Furthermore, we find a negative correlation between the male pension recipient variable (\textbf{w\_spen\_m}) and the short-run \textbf{BMIZ}.
+
+The later result seems to indicate that, at least in the short-run,
+the prefered recipient of cash transfers would be a female household member.
+As discussed, the selection bias issue in age,
+leads to the need for a careful interpretation of the possible external validity of this results.
+
+Regarding the former result, the significant negative coefficient of the treatment variable,
+the analysis in \autoref{sa:results} seems to indicate a need to establish the common trend,
+at least over the period 2008-2012.
+Since the female recipient base in this period serves as a control group, we possibly could establish this, using the evolution here.
+Alternatively, it would be possible to establish a trend using statistics on nationwide pension recipients.
 

### 2014-01-06 south-africa.tex
finish SA

@@
 \subsubsection{Height-Based Z-scores}
-\label{sa:se:hbz}
+\label{sa:hbz}
 The Height-Based Z-scores (HBZs) are the Weight-for-Height Z-score (WHZ)
@@
 \label{sa:results}
-In \autoref{sa:hazwaz} we present our estimation results for the age-based z-scores,
-and in \autoref{sa:whzbmiz} we present our estimation results for the height-based z-scores.
+In \autoref{sa:ta:haz} and \autoref{sa:ta:waz} we present our estimation results for the age-based z-scores.
+In \autoref{sa:ta:whz} and \autoref{sa:ta:bmiz} we present our estimation results for the height-based z-scores.
 
@@
 \centering
-\caption{Age-Based Z-scores}
-\label{sa:hazwaz}
-\begin{tabular}{l|rrr|rrr}
-% \hline
-& \multicolumn{3}{c}{Height for Age Z-score} & \multicolumn{3}{c}{Weight for Age Z-score}\\
+\caption{Height-for-Age Z-score}
+\label{sa:ta:haz}
+\begin{tabular}{l|rrr}
 \hline
-specification & 1 & 2 & 3 & 1 & 2 & 3\\
+specification & 1 & 2 & 3\\
 \hline
-w\_spen\_m & 0.2366 & *0.8228 & 0.7908 & 0.2366 & 0.2981 & 0.4780 \\
-w\_spen\_w & -0.2331 & 0.1053 & 0.1072 & -0.2331 & -0.3112 & -0.3280 \\
-elig.men.60 & & **-0.3419 & **-0.3465 & & ***-0.3475 & **-0.3243 \\
-w\_spen\_m1:elig.men.60 & & & 0.0446 & & & -0.2545 \\
-% \hline
-w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 \\
+w\_spen\_m & 0.2366 & *0.8228 & 0.7908 \\
+w\_spen\_w & -0.2331 & 0.1053 & 0.1072 \\
+elig.men.60 & & **-0.3419 & **-0.3465 \\
+w\_spen\_m1:elig.men.60 & & & 0.0446 \\
+w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
 \end{tabular}
@@
 
-As \autoref{sa:hazwaz} shows both the Height-for-Age and the Weight-for-Age estimations for all three Right-Hand Side variations give similar results.
+% LaTeX table created manually
+% Fri Dec 27 23:22:00 2013
+\begin{table}[!ht]
+\centering
+\caption{Weight-for-Age Z-score}
+\label{sa:ta:waz}
+\begin{tabular}{l|rrr}
+\hline
+specification & 1 & 2 & 3\\
+\hline
+w\_spen\_m & 0.2366 & 0.2981 & 0.4780 \\
+w\_spen\_w & -0.2331 & -0.3112 & -0.3280 \\
+elig.men.60 & & ***-0.3475 & **-0.3243 \\
+w\_spen\_m1:elig.men.60 & & & -0.2545 \\
+w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
+\end{tabular}
+\end{table}
+
+As \autoref{sa:ta:haz} and \autoref{sa:ta:waz} shows the Height-for-Age and the Weight-for-Age estimations for all three Right-Hand Side variations give similar results.
 For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
@@
 
-Furthermore, when using Height-for-Age as the LHS, and the model 2 on the HRS, we find a positive effect of living with a male pension recipient.
-The coefficient output here is no longer significant when we include the interaction term in the model 3 specification.
+Furthermore, when using Height-for-Age as the LHS, and the model 2 on the RHS,
+we find a positive effect of living with a male pension recipient.
+However, the coefficient output here is no longer significant when we include the interaction term in the model 3 specification.
 
@@
 \centering
-\caption{Height-Based Z-scores}
-\label{sa:whzbmiz}
-\begin{tabular}{l|rrr|rrr}
-& \multicolumn{3}{c}{Weight for Height Z-score} & \multicolumn{3}{c}{Body Mass Index Z-score}\\
+\caption{Weight-for-Height Z-score}
+\label{sa:ta:whz}
+\begin{tabular}{l|rrr}
 \hline
-specification & 1 & 2 & 3 & 1 & 2 & 3 \\
+specification & 1 & 2 & 3 \\
 \hline
-w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 & *-0.8058 & *-0.7905 & *-1.0226 \\
-w\_spen\_w & 0.0655 & 0.0371 & 0.0478 & -0.1592 & -0.1956 & -0.1742 \\
-elig.men.60 & & -0.1417 & -0.1574 & & -0.1674 & -0.2049 \\
-w\_spen\_m1:elig.men.60 & & & 0.1484 & & & 0.3407 \\
-w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & 0.0000 & 0.0000
+w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 \\
+w\_spen\_w & 0.0655 & 0.0371 & 0.0478 \\
+elig.men.60 & & -0.1417 & -0.1574 \\
+w\_spen\_m1:elig.men.60 & & & 0.1484 \\
+w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
 \end{tabular}
@@
 
-In \autoref{sa:whzbmiz} we do not find an effect of the \textbf{elig.men.60} variable.
+% LaTeX table created manually
+% Fri Dec 27 23:53 2013
+\begin{table}[!ht]
+\centering
+\caption{Body-Mass-Index Z-score}
+\label{sa:ta:bmiz}
+\begin{tabular}{l|rrr}
+\hline
+specification & 1 & 2 & 3 \\
+\hline
+w\_spen\_m & *-0.8058 & *-0.7905 & *-1.0226 \\
+w\_spen\_w & -0.1592 & -0.1956 & -0.1742 \\
+elig.men.60 & & -0.1674 & -0.2049 \\
+w\_spen\_m1:elig.men.60 & & & 0.3407 \\
+w\_h\_tinc & -0.0000 & 0.0000 & 0.0000\\
+\end{tabular}
+\end{table}
+
+In \autoref{sa:ta:whz} and \autoref{sa:ta:bmiz} we do not find an effect of the \textbf{elig.men.60} variable.
 In the WHZ estimation we do not find any significant variables.
@@
 For the higher coefficient estimates, it is important to note that \textbf{BMIZ} is essentially a convex mapping of \textbf{WHZ},
-since height is squared in the denominator of the BMI function, as described in \autoref{sa:se:hbz}.
+since height is squared in the denominator of the BMI function, as described in \autoref{sa:hbz}.
 In other words, the fact that the estimators, which give transformed coefficient estimates can have different significance levels,
@@
 
-% RECOMMENDATIONS
-% estimate using by weighting the drop for women with life exp. evolution, and male also
-% or use the drop for women (unaffected) to scale men and women back to 2008 levels.
-
 \printbibliography

### 2014-01-06 bitattack.tex
updates from chromebook
spelling

@@
 to analyse how cryptocurrencies gain momentum.
-Additionaly, I discuss how inflation in the cryptocurrency economy is possible.
+Additionally, I discuss how inflation in the cryptocurrency economy is possible.
 \pagebreak
@@
 \section{Introduction}
-As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies.
+As discussed in \autoref{bitremit}, there has been a new phenomenon in international finance called cryptocurrencies.
 The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}.
-However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed.
+However, soon after Bitcoin started gaining momentum, alternative cryptocurrencies where being designed.
 All of these cryptocurrencies are based to a large extend on the Bitcoin protocol,
@@
 
-The most known of all of these alternative crypocurrencies is Litecoin. Litecoin introduces a number of small technological innovations,
+The most known of all of these alternative cryptocurrencies is Litecoin. Litecoin introduces a number of small technological innovations,
 the most import of these is the change that the process of `mining' coins is 4 times faster,
@@
 
-The key thing to note here is the perspective of the new cryptocurrecy adopt.
+The key thing to note here is the perspective of the new cryptocurrency adopt.
 Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer.
 The lower valued new cryptocurrency is technologically superior and thus more attractive.
-Most new cryptocurrencies do not gain momentum and their value is only trivialy more than zero.
+Most new cryptocurrencies do not gain momentum and their value is only trivially more than zero.
 However, some currencies have gain momentum,
@@
 Despite the fact that `Dogecoin' does not have a real reason for being considered valuable
-(in the sense that crypotocurrencies are considered valuable),
-however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable.
+(in the sense that cryptocurrencies are considered valuable),
+however, by utilising a previously existing internet phenomenon, and it's fan base, this currencies has become valuable.
 We thus observe that from the perspective of economic and technological fundamentals,
@@
 
-On of the key selling points of the cryptocurrencies, and equally one of the key critisism of many economics
-(e.g.~Paul Krugman), is that there is no inflation in a crypocurrency.
-The crypocurrencies are designed specifically so that inflation eventually becomes impossible (once all coines are mined).
+On of the key selling points of the cryptocurrencies, and equally one of the key criticism of many economics
+(e.g.~Paul Krugman), is that there is no inflation in a cryptocurrency.
+The cryptocurrencies are designed specifically so that inflation eventually becomes impossible (once all coins are mined).
 
 However, it is key here to understand the economy as a multi-cryptocurrency object.
-Since creating a currency can be done at negligable cost,
+Since creating a currency can be done at negligible cost,
 and the only value of the cryptocurrency lies in its utility as a mechanism for transactions,
-more cryptocurrencies will come into existance.
+more cryptocurrencies will come into existence.
 Especially since it is very simple for a merchant to accept several cryptocurrencies as a form of payment.
@@
 
-Additionaly, this partly addresses one of social critiques of Bitcoin,
-namely the issue of bitcoin mining being excessively wastful.
+Additionally, this partly addresses one of social critiques of Bitcoin,
+namely the issue of bitcoin mining being excessively wasteful.
 Bitcoin mining does not produce anything of any social value (not unlike gold mining),

### 2014-01-06 bitremit.tex
spelling

@@
 \begin{refsection}
-\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
+\chapter{Bitcoin and Remittances: The Potential of `Stupid Phones'}
 \label{bitremit}
@@
 \section{Introduction}
-In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
+In the 2009 white paper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC).
 This currency -the first of a group called cryptocurrencies- has the following economics features:

### 2014-01-06 endnotes.tex
spelling

@@
 
-% The replication of Surviving Andersonville is already completed in term of the replication in Stata.
-% We would like to redo the analysis in R \parencite{R}.
-% The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
-% The findings of this replication can summarised as:
-
-%\begin{quote}
-%``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R.
-It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data).
-This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
-%\end{quote}
-
-% We do not expect to find anything similar to Bell and Miller,
-% but think that it can nevertheless be interesting to replicate findings using a different software package.
-% In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
-% In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.
-
 The discussion of \textcite{morris1998unique} is in a very early stage.
 I have looked at the paper in detail, I have also done a brief analysis of my main critique,
-namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
-However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
+namely the conflation of risk (quantifiable) and Knightian uncertainty (unquantifiable).
+However, I would like to present a worked out example which demonstrates how this convolution leads to the main result of the paper.
 In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.
 
-Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin.
+Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potential for uncontrolled low-cost remittances using Bitcoin.
 I would like to analyse the spread of this.
@@
 The reform constitutes of the implementation of a model of `police de proximitee'.
-The baseline consist of 4500 interviews using smartphones in the comune of Conkary as well a large number of interviews in N'Zerekore (east Guinea).
+The baseline consist of 4500 interviews using smartphones in the commune of Conakry as well a large number of interviews in N'Zerekore (east Guinea).
 Some time after the implementation of the police reform as follow up study will be conducted.
@@
 In particular I would like to at the effect of outliers.
-The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}.
+The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as individual behaviour \parencite{kahneman2011thinking}.
 I would like to see how these principles affect research in development microeconomics.

### 2014-01-06 intro.tex
updates from chromebook
spelling

@@
 \item Additional South African Evidence on Pensions and Child Growth (\autoref{sa})
-% \item Replication: Surviving Andersonville (\ref{andersonville})
 \item Risk and Uncertainty in Unique Equilibria in Currency Attacks (\autoref{unc})
-\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{btc})
+\item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{bitremit})
 \end{itemize}
@@
 This paper makes use of a Household Survey from 2008, 2012 and 2013. The 
-urvey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
+survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
 As it stands now I have analysed the data from 2008 and 2012.
@@
 I will discuss this in \autoref{sa}.
-
-% Furthermore, in \autoref{andersonville},
-% together with several other PhD students we have replicated the paper ``\citetitle{costa2007surviving}'' by \textcite{costa2007surviving}.
-% We were able to replicate all results from the paper, save for a few decimal numbers,
-% which we have taken to be the result of rounding errors.
-
-% However, replicating these numbers required us to take a number of unorthodox steps in our analysis.
-% When in stead, we take more orthodox steps, we find that we cannot quantitatively and qualitatively replicate the authors' results.
-% As an example, we find that the dataset distinguishes between two different POW camps both located in the town of Andersonville.
-% The authors however, aggregate these two.
-% This leads to overstated magnitudes of the social ties of POWs.
-% This is problematic because the main finding of the paper is that the size of these social networks is relevant to an individual's odds of survival.
-% At this point our replication is quite complete.
-% Before rewriting this paper, I will redo the analysis in R \parencite{R}, currently the original and our replication are in Stata.
 
@@
 For this I would like to participate in building Bitcoin applications for the type of simple phones common in developing economies (sometimes referred to a stupid phones).
-We could study the spread of bitcoin by looking at the downloads of the apps from regions,
+We could study the spread of Bitcoin by looking at the downloads of the apps from regions,
 as well looking at how releasing the app in different languages evolves.
@@
 
-Recently there has been a shift towards more replication and further analysis of previously published results. E.g. \textcite{ioannidis2005most}.
-
 \printbibliography

### 2014-01-06 south-africa.tex
spelling

@@
 The study is based on South-African data and the approach is very similar to \textcite{duflo2000child,duflo2003grandmothers},
-and orignally based on the work of \textcite{thomas1994like}.
+and originally based on the work of \textcite{thomas1994like}.
 The difference from international standards \parencite[WHO Child Growth Standards]{who2006child} for anthropometrics are computed as z-scores.
@@
 This study deviates from the Duflo study in several ways.
-The core contribution of this paper is the analyis of exogenous change in men's pension eligibility age,
+The core contribution of this paper is the analysis of exogenous change in men's pension eligibility age,
 which is the main explanatum.
@@
 This brought the pension eligibility age for men at par with women.
-There are two reasons why this warants a further look at this topic in this dataset.
+There are two reasons why this warrants a further look at this topic in this dataset.
 
-Firstly, life expectancy is South Africa is substantialy below the pension eligibility age.
+Firstly, life expectancy is South Africa is substantially below the pension eligibility age.
 Around the end of the first decade of the century, which is when our data was collected,
-the average life expectancy at birth was only slighly above 50 years old.
+the average life expectancy at birth was only slightly above 50 years old.
 In the year 1993, when \textcite{duflo2000child,duflo2003grandmothers} are analysed,
@@
 causes an even more pronounced selection bias in the male pension recipient base.
-This also makes the comparing of the effect of male pension reicipient and female pension recipients,
+This also makes the comparing of the effect of male pension recipient and female pension recipients,
 on the anthropometrics of children in the same household problematic,
@@
 provides us with effects which internally more comparable.
-We say more, because the difference in attribition between the male and female pension base in our sample has not entirely been eliminated.
+We say more, because the difference in attrition between the male and female pension base in our sample has not entirely been eliminated.
 Throughout the evolution of the average life expectancy at birth in South Africa,
@@
 The impetus for this paper lies in the optimal design of cash transfer schemes such as CCTs and UCTs.
-The lack Paretto optimal allocation of resources within households as discussed in i.a.
+The lack Pareto optimal allocation of resources within households as discussed in i.a.
 \textcite{udry1995gender}, \textcite{udry1996gender}, and \textcite{duflo2004intrahousehold},
-indicates the necesity of optimal design in such schemes.
-Based on this lack of Paretto optimal allocation,
+indicates the necessity of optimal design in such schemes.
+Based on this lack of Pareto optimal allocation,
 we have to reject the idea of households acting as a unit in an economic sense.
-For the design of cash transfer schemes it is therefore necessary to determine the prefered recipient within the household
+For the design of cash transfer schemes it is therefore necessary to determine the preferred recipient within the household
 \footnote{For a good overview see e.g.~\textcite{haddad1997intrahousehold}}.
@@
 We therefore use these pension receipts as the Right-Hand Side variables, or explanata.
-Anthopometrics for children are used, since these capture well, the effects of both malnutrition and disease,
+Anthropometrics for children are used, since these capture well, the effects of both malnutrition and disease,
 the two most common health impediments that we are addressing.
@@
 The primary criterium is the age of the recipient.
-In adition to this there is a maximum income threshold.
+In addition to this there is a maximum income threshold.
 Outside of this, there are very few criteria.
-The reletive general applicablility of the program makes that there are few selection bias issues when studying this.
+The relative general applicability of the program makes that there are few selection bias issues when studying this.
 A thorough, though a points somewhat dated, discussion can be found in \textcite{case1998large}.
@@
 Pension receipt have therefore formed a large share of household income.
-Upon the initial expension to include the black population, in 1991,
+Upon the initial expansion to include the black population, in 1991,
 this was a much as twice the mean monthly income.
@@
 We use two types ABZs and two types of HBZs, for a total of four types of z-scores.
-This is described in futher detail in \autoref{sa:data:who}.
+This is described in further detail in \autoref{sa:data:who}.
 
@@
 Unlike the 1993 survey, this survey does not use a random selection household,
-rather it collects data on a representative set of appproximately 10,000 South-African households over time.
+rather it collects data on a representative set of approximately 10,000 South-African households over time.
 Currently three `waves' of data are available, these waves date from 2008, 2012, and 2013 respectively.
@@
 Children's anthropometrics are taken, these are length/height, weight, and waist.
-Using these anthropometics and WHO growth standards, z-scores are calculated.
+Using these anthropometrics and WHO growth standards, z-scores are calculated.
 
@@
 then we refer the to WHO tables, find the relevant ideal height and standard deviation for a child of age $y$.
-We then substract the ideal height ($\mu_y$) from the observed height,
-and divide by the standard devation ($\sigma_y$), like so:
+We then subtract the ideal height ($\mu_y$) from the observed height,
+and divide by the standard deviation ($\sigma_y$), like so:
 \[
@@
 by causing the child to be shorter or lighter.
-However, it is impossible to distinquish between the different causes of an observed slowed growth.
+However, it is impossible to distinguish between the different causes of an observed slowed growth.
 
@@
 
-In general, can distinquish between two types of anthropometric z-scores, the age-based z-scores and the height-based z-scores.
+In general, can distinguish between two types of anthropometric z-scores, the age-based z-scores and the height-based z-scores.
 Whereby `based' refers to the reference point at which anthropometrics are standardised.
@@
 \subsubsection{Age-Based Z-scores}
-The Age-Based Z-scores (ABZs) are consistituted by the Height-for-Age Z-score (HAZ) and the Weight-for-Age Z-score (WAZ).
+The Age-Based Z-scores (ABZs) are constituted by the Height-for-Age Z-score (HAZ) and the Weight-for-Age Z-score (WAZ).
 Since these metrics are age-based, they provide information about all past growth issues.
@@
 
-The ABZs are constructed on a weekly basis up to the age of 60 months, and on a monthly basis thereafer.
+The ABZs are constructed on a weekly basis up to the age of 60 months, and on a monthly basis thereafter.
 
@@
 Where \textbf{w\_spen\_w} represents the dummy variable for children living in a household with a state pension eligible woman.
-The variable \textbf{w\_spen\_m} is the dummy for the child living in the same household as a male state mension recipient.
+The variable \textbf{w\_spen\_m} is the dummy for the child living in the same household as a male state pension recipient.
 The policy variable \textbf{elig.men.60} is a dummy which takes the value \textbf{1} for waves 2 and 3.
 An interaction term of the later two is also included as \textbf{eli.men.60:w\_spen\_m}.
-Lastly, we unclude de covariate \textbf{w\_h\_tinc} which represents total household income.
+Lastly, we include the covariate \textbf{w\_h\_tinc} which represents total household income.
 
@@
 As \autoref{sa:ta:haz} and \autoref{sa:ta:waz} shows the Height-for-Age and the Weight-for-Age estimations for all three Right-Hand Side variations give similar results.
-For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
+For all the height-based z-score estimations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
 In all cases the estimate has a p-value of less that \textbf{0.01}.
-Meaning that (meta-discussion aside) the probabiliy that this coefficient represents a non-existant relation (Type II error) is less than one percent.
+Meaning that (meta-discussion aside) the probability that this coefficient represents a non-existent relation (Type II error) is less than one percent.
 In the model 2 specification of the Weight-for-Height dependent variable, the p-value is even less that 0.001.
@@
 Furthermore, for one height-based z-score we also find a negative effect of male pension recipients on growth metrics.
-Additionaly, it is suprising that we find significant coefficients for \textbf{w\_spen\_m} in one height-based z-score (\textbf{BMIZ}), but not in the other \textbf{WHZ}.
+Additionally, it is surprising that we find significant coefficients for \textbf{w\_spen\_m} in one height-based z-score (\textbf{BMIZ}), but not in the other \textbf{WHZ}.
 
@@
 Especially considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
-and roughtly half of the estimates of the \textbf{BMIZ} estimations.
+and roughly half of the estimates of the \textbf{BMIZ} estimations.
 
@@
 Which enables us to draw a causal inference from the treatment effect,
-which is onthologically more intersting than a correlation.
+which is ontologically more interesting than a correlation.
 
@@
 This full-panel dataset provides observations from 2008, 2012, and 2013.
-The treatment, a policy change which lowers the pension elgilibity age for men from 65 to 60, takes place around 2009.
+The treatment, a policy change which lowers the pension eligibility age for men from 65 to 60, takes place around 2009.
 Since we have only one time period before the treatment (the year 2008), we cannot establish the common trend.
@@
 which is operationalised a fixed-effect panel estimation with a time effect.
-The contruct three Right-Hand Side (RHS) model.
+The construct three Right-Hand Side (RHS) model.
 The first model is a fixed-effect estimation without the treatment dummy.
@@
 As discussed in \autoref{sa:results}, the Body-Mass-Index Z-score is a convex mapping of the Weight-for-Height z-score.
-This can explain the fact that these essentialy similar estimations, give different significance levels.
+This can explain the fact that these essentially similar estimations, give different significance levels.
 Considering that the use of the Body Mass Index is far more wide spread than the Weight for Height metric,
@@
 The fact that these coefficients are negative, indicates that for this short-term z-score,
-the prefered recipient would be female household members.
+the preferred recipient would be female household members.
 
@@
 The later result seems to indicate that, at least in the short-run,
-the prefered recipient of cash transfers would be a female household member.
+the preferred recipient of cash transfers would be a female household member.
 As discussed, the selection bias issue in age,

### 2014-01-06 uncertainty.tex
include formal specification SA, clear chapter pages
spelling

@@
 \label{unc}
-
+\vspace{\stretch{1}}
 \section*{Abstract}
 \textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium in their model of self-fulfilling currency attacks.
-The currency attack model thus has the surprising feature, with the introduction of perception distortion, the multiple equilibria region seems to solve to a single equilibrium.
-It is our contention that this is not a surpising result, it a consequence of the second-order effect, where the risk factor replaces a previous existent, Knightian uncertainty.
+The currency attack model thus has the surprising feature, with the introduction of perception distortion,
+the multiple equilibria region seems to solve to a unique equilibrium.
+
+It is our contention that this is not a surprising result, it a consequence of the second-order effect,
+where the risk factor replaces a previous existent, Knightian uncertainty.
 Previously, speculators had no expectations on other speculators expectations.
@@
 Also, the new quantified-risk region only solves a certain part of the multiple equilibria region, not the whole of it.
-Lastly, if we replace the somewhat strange assumption of a bounded uniform distribution of risk perceptions, with the more orthodox, normal distribution, we cannot derive the same result.
+Lastly, if we replace the somewhat strange assumption of a bounded uniform distribution of risk perceptions,
+with the more orthodox, normal distribution, we cannot derive the same result.
+\pagebreak
 
@@
 and a `ripe for attack' region (based on the underlying economic fundamentals).
-The authors expand on the standard model by introducting second-order expectations.
+The authors expand on the standard model by introducing second-order expectations.
 Hereby speculators do not only look at the economics fundamentals of a currency,
@@
 The authors proceed by introducing a measure of risk around perceptions of the fundamentals by investors.
-Investors do not know the actual state of the fundamentals, but rather a distored form of it.
+Investors do not know the actual state of the fundamentals, but rather a distorted form of it.
 As a result, the investors' perception of other investors' perceptions are even more distorted.
@@
 \end{equation}
-Lastly, the following, assumptions are imposed: $c(0,0) > \nu$ (with worst fundamtentals the peg always has to be released),
+Lastly, the following, assumptions are imposed: $c(0,0) > \nu$ (with worst fundamentals the peg always has to be released),
 $c(1,1) > \nu$ (with all speculators attacking, the peg always has to be released),
@@
 	this is the `ripe for attack' region.
-	\item $[\bar{\theta}, 1]$, the cost of shorting the currency will always outway the possible gains,
+	\item $[\bar{\theta}, 1]$, the cost of shorting the currency will always outweigh the possible gains,
 	this is the stable region.
@@
 \end{equation}
-Where is the $x$ is the state of the fundamentas \textit{observed} by the speculators.
+Where is the $x$ is the state of the fundamentals \textit{observed} by the speculators.
 A speculators observation can thus \textit{at most} deviate from the true value of the fundamentals by $\epsilon$.
 The speculators are also aware of the nature of the distortion.
-This means that they are also aware of the fact that other speculators' perceived value of the fundatmentals can at most,
+This means that they are also aware of the fact that other speculators' perceived value of the fundamentals can at most,
 deviate from their own with a magnitude of $2\epsilon$.
@@
 for a sufficiently low observed $x$.
-The authors proceed to derivde from this the main result of the paper, which is:
+The authors proceed to derive from this the main result of the paper, which is:
 \begin{quotation}
@@
 	\item Multiple equilibria exist in the interval $(\underaccent{\bar}{\theta},\bar{\theta})$.
-	\item The introduction of quantief risk, removes uncertainty with $2 \epsilon$ of $x$.
+	\item The introduction of quantied risk, removes uncertainty with $2 \epsilon$ of $x$.
 	\item Here $u(x,\theta) > 0$ leads to $\pi (x) = 1$.
@@
 speculators will only attack if they believe that there is a sufficient number of other speculators doing the same.
-Yet in the first model, attacks were possible, in absense of this certainty.
+Yet in the first model, attacks were possible, in absence of this certainty.
 It thus follows that speculators should be willing to attack the currency,
@@
 In stead, we find that we end again in a situation of unique equilibria.
+This thus indicates that the second order effect are not really taken into account in the first iteration of the model.
 
@@
 This should say ``...abandon the exchange rate \textit{always} if the observed fraction is great than or equal to...''.
-Since quantified-risk region now gives the speculators certainty about the other speculators behavious,
+Since quantified-risk region now gives the speculators certainty about the other speculators behaviour,
 this will now always lead to an sustainable attack.
 
-However, as described above, outside of the new quantied-risk region, the old `ripe for attack region' remains.
+However, as described above, outside of the new quantified-risk region, the old `ripe for attack region' remains.
 In this region of multiple equilibria, currency attacks may be successful, or they may not be.
 
-The condition the governments action is thus a sufficient, but not a necesarry one.
+The condition the governments action is thus a sufficient, but not a necessary one.
 
@@
 The second problem is the most fundamental. The distortion measure is presented as a function that adds uncertainty.
-If we differenciate between Knightian uncertainty and risk, then this is not true.
+If we differentiate between Knightian uncertainty and risk, then this is not true.
 
@@
 A uniform distribution is bounded,
-which allows the distortion to the quantied with absolute certainty.
+which allows the distortion to the quantified with absolute certainty.
 An unbounded distribution, such as the normal distribution,
@@
 Even though a larger part of the region (w.r.t.~the economic fundamentals) leads to a unique equilibrium,
-a part of the old 'ripe for attack' region, remains subject to a situation of multiple equilibria.
+a part of the old `ripe for attack' region, remains subject to a situation of multiple equilibria.
 It is only through two assumptions which do not follow from the model,
@@
 It is only due to the bounded nature of the uniform distribution,
-that speculators are able to form bounded quantitative exectatations on other speculators expectations, with absolute certainty.
+that speculators are able to form bounded quantitative expectations on other speculators expectations, with absolute certainty.
 As mentioned above, it is this absolute certainty on the bounded quantifiable second-order expectations,
@@
 
-In conclusion, we analyse the model introducted by \textcite{morris1998unique} and find that the results are driven by a second-order effect, as well as certain unjustifiable assumptions.
+In conclusion, we analyse the model introduced by \textcite{morris1998unique} and find that the results are driven by a second-order effect, as well as certain unjustifiable assumptions.
 

### 2014-01-06 bitattack.tex
update pictures and bitremit conclusion

@@
 Dogecoin is a reference to an internet phenomenon called `Doge Meme'.
+
 Despite the fact that `Dogecoin' does not have a real reason for being considered valuable
-(in the sense that cryptocurrencies are considered valuable),
-however, by utilising a previously existing internet phenomenon, and it's fan base, this currencies has become valuable.
+(and a name that does not inspire much trust), it has become quite valuable.
+This has been done by utilising a previously existing internet phenomenon, and it's existant fan base.
 We thus observe that from the perspective of economic and technological fundamentals,
@@
 
-\begin{figure}
-\caption{A Doge Meme}
-\label{doge}
-%\includegraphics[scale=0.8]{doge.jpg}
-\end{figure}
-
 \printbibliography

### 2014-01-06 bitremit.tex
update pictures and bitremit conclusion

@@
 \section{Data}
+In this section I briefly describe the data which is available to us, in order to undertake such a project.
 \label{btc:data}
-Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
-Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
-Much like the way bank clients have a claim to their money, which is in the bank's vault.
-
-Therefore Bitcoin purchases at exchanges do not lead to transaction being recorded in the blockchain.
-Since the Bitcoins remain in the Exchange's wallet, the only thing which changes is the claims of the clients.
-
 \begin{itemize}
@@
  	\item Downloads
- 	\item Translation contributions (?)
  	\item Connections to server
@@
 \end{itemize}
+Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
+Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
+Much like the way bank clients have a claim to their money, which is in the bank's vault.
+
+Therefore Bitcoin purchases at exchanges do not lead to transaction being recorded in the blockchain.
+Since the Bitcoins remain in the Exchange's wallet, the only thing which changes is the claims of the clients.
+
+\section{Conclusion}
+The Bitcoin transaction mechanism is often mentioned as being interesting for remittances, which are plagued by high costs.
+The much more efficient protocol would be a major improvement over established systems.
+
+There are existing networks in many developing (especially African) countries which enable phone to phone transactions.
+However, these network (and thus entire economies) are privately owned by telecom providers.
+Enableing these phones to conduct Bitcoin transactions would thus have two benefits.
+Firstly, the cost of remittances can go down.
+Secondly, the economies of phone to phone transactions would no longer be privately owned.
+
+The idea lies thus in linking these two networks, and analysing how the this new mechanism would disseminate itself.
+The public nature of the Bitcoin network provides us with a wealth of information which we can use to analyse this dissemination.
 

### 2014-01-06 intro.tex
update intro to reflect new chapters

@@
   \item Bitcoin and Remittances: The Potential of `Stupid Phones' (\autoref{bitremit})
+  \item Bitcoin Attacks: Or How Cryptocurrencies Gain Momentum (\autoref{bitatt})
 \end{itemize}
@@
 survey is especially of interest, because the pension eligibility age for men was lowered from 65 to 60 in 2009.
-As it stands now I have analysed the data from 2008 and 2012.
-The 2013 data was released several weeks ago, I will incorporate these data in future versions of my analysis.
+I have analysed this data using a Difference-in-Differences approach.
 I will discuss this in \autoref{sa}.
@@
 We thus gain information.
-I want to discuss MS1998 in light of the distinction between Knightian uncertainty and quantified risk.
+I discuss this paper in light of the distinction between Knightian uncertainty and quantified risk,
+and find there to be three major issues in the paper, each of which leads to the results not being replicable.
 This is done in \autoref{unc}.
 
-Lastly, Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
+Bitcoin is the first of a new breed of currencies, commonly referred to as a cryptocurrencies. 
 Bitcoin transactions are conducted using an electronic process called signing.
@@
 as well looking at how releasing the app in different languages evolves.
+This is discussed in \autoref{bitremit}
+
+Lastly, I present a number of idea for modelling Bitcoin and alternative cryptocurrencies.
+These idea include, a model on how a cryptocurrency gains momentum,
+a model on how multiple models can gain momentum,
+and finally a model which describes a multi cryptocurrency economy.
+This last model will also enable us to address to issues about cryptocurrencies.
+Firstly, about how there supposedly there is no possibility for inflation,
+and secondly, how eventually an enormous amount of resources will be directed at the socially wasteful cryptocurrency mining.
+I discuss this idea in \autoref{bitatt}.
 

### 2014-01-06 endnotes.tex
end notes

@@
 
-I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey,
+The South Africa paper provides an interesting opportunity to exploit the data from the household survey,
 done before and after a highly relevant policy change.
 Especially since the methodology and location are the same as in \textcite{duflo2000child, duflo2003grandmothers}.
-In addition to this there is now a third data wave which has become available.
-This provides us with more data, and mostly the opportunity to use more interesting methodology.
-The text of the paper still has to be written.
+We find results that are highly relevant for the optimal design of cash transfer schemes.
+At this point, the analysis is troubled by the non establishment of the common trend, prior to the treatment.
+Using additional data or the control group this can be remedied, which will make the results more relevant still.
 
-The discussion of \textcite{morris1998unique} is in a very early stage.
-I have looked at the paper in detail, I have also done a brief analysis of my main critique,
-namely the conflation of risk (quantifiable) and Knightian uncertainty (unquantifiable).
+\textcite{morris1998unique} is analysed in detail.
+The main issue is the conflation of risk (quantifiable) and Knightian uncertainty (unquantifiable).
+However, there are two more issues in this paper which I also discuss, each of these invalidate the results.
 However, I would like to present a worked out example which demonstrates how this convolution leads to the main result of the paper.
@@
 
-Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potential for uncontrolled low-cost remittances using Bitcoin.
+Relating to Bitcoin \parencite{nakamoto2008bitcoin}, I present two ideas.
+I think that there is a enormous potential for uncontrolled low-cost remittances using Bitcoin.
 I would like to analyse the spread of this.
@@
 
-At this point, three out of four of the previously discussed research projects are some form of a replication of prior work.
-As replications they are mostly critiques of others' work, rather than constructive ideas.
-This is mostly a result of the fact that these projects progress faster.
-For this reason, these research projects have progressed more than the projects which are primarily based on my own ideas.
-However, it is my attention to shift the focus of my thesis to include more original work.
-Here I present two more ideas which are too preliminary to include in the main body of the text, but are based on my own work.
+Lastly, I present a proposal for a theoretical model on how cryptocurrencies gain momentum, this model can be extended to address two issues relating to Bitcoin, namely the supposed non-inflation, as well as the unlimited socially wasteful coin mining.
+
+Here I present two more ideas which are too preliminary to include in the main body of the text.
 

### 2014-02-25 presentationPTD.tex
add bitcoin attacks
presentation

@@
 
-\usecolortheme[colortext]{geneva}
+\usecolortheme[]{geneva}
 
@@
 \usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage{times}
-\usepackage[T1]{fontenc}
+%\usepackage[utf8]{inputenc}
+%\usepackage{times}
+%\usepackage[T1]{fontenc}
+\usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
+\usepackage[]{hyperref}
+
+\addbibresource{bibliography.bib}
+
+\setbeamertemplate{bibliography item}{}
 
@@
 \subtitle{December 18, 2013}
-
-% Supervisor:&\footnote{Professor of Economics, The Graduate Institute, Geneva; }\\
-% Second Reader:&\footnote{Professor of Economics, The Graduate Institute, Geneva; }
 
@@
 
-\institute[The Graduate Institute, Geneva] % (optional, but mostly needed)
+\institute[The Graduate Institute, Geneva]
 {
@@
 
-\section[Pensions, Child Growth]{Pensions and Child Growth: Additional Evidence from South-Africa}
-
-\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa}
-using the new data
+\begin{frame}{Questions}
+Cryptocurrency Inflation
+	\begin{itemize}
+		\item Relevant enough for Development Economics?
+	\end{itemize}
+Knightian Uncertainty:
+	\begin{itemize}
+		\item What to do with this critique?
+	\end{itemize}
+Pensions and  Child Growth:
+	\begin{itemize}
+		\item Defining of Age-Based and Height-Based Z-scores,\\ correct?
+		\item BMI as convex mapping of Weight-for-Height,\\ significance?
+		\item Drop in children living with recipient 2008-2012,\\ 		how to account for this?
+	\end{itemize}
 \end{frame}
 
-\section[Surviving Andersonville]{Replication: Surviving Andersonville}
+\section{Cryptocurrency Inflation}
 
-\begin{frame}{Replication: Surviving Andersonville}
-these guys mislabeled everything
+\begin{frame}{Cryptocurrency Inflation}
+Often heard problems Bitcoin:
+\begin{enumerate}
+	\item There is no inflation
+	\item Mining is wasteful
+\end{enumerate}
+Consider Bitcoin together with other Cryptocurrencies
+\begin{itemize}
+	\item Expansion in no. of coins, but expansion in no. of currencies
+	\item Miners will move to less-mined currencies, leading to less waste
+	\item Model as positive currency attack \parencite{obstfeld1986rational,obstfeld1996models}
+\end{itemize}
+
 \end{frame}
@@
 \begin{frame}{Uncertainty and Risk in Currency Attacks}{Knightian Uncertainty in Morris and Shin (1998)}
-This paper makes no sense!!
+A review of \citetitle{morris1998unique} \parencite{morris1998unique}
+\begin{itemize}
+	\item Based on currency models \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}
+	\item Finds a unique equilibrium when `uncertainy' is added
+\end{itemize}
+Critiques:
+\begin{itemize}
+	\item Strange result, does not correspond to reality
+	\item The `distortion' changes uncertainty to risk, effectively increasing the body of knowledge
+	\item The distortion of perception has a uniform distribution, results do not hold under e.g. Gaussian
+	\item Speculator risk profile is redefined:
+\end{itemize}
+\begin{quotation}
+	For the next step,
+	consider the strategy profile where every speculator attacks the currency if and only if
+	the message $x$ is less than some fixed number $k$.
+	\hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
+\end{quotation}
 \end{frame}
 
-\section[Bitcoin, Stupid Phones]{Bitcoin and Remittances: Stupid Phone Potential}
+\section[Pensions, Child Growth]{Pensions and Child Growth: Additional Evidence from South-Africa}
 
-\begin{frame}{Bitcoin and Remittances}{Stupid Phone Potential}
-stupid phones rock!!
+\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa I}
+	\begin{itemize}
+		\item Based on \citetitle{duflo2003grandmothers} \parencite{duflo2000child,duflo2003grandmothers} methodology
+		\item Address the issue of eligibility-age discrepancy
+		\item South African Household Survey \parencite{saldru2008nids,saldru2012nids,saldru2013nids}
+		\item Elibility-age equalisation in 2009
+	\end{itemize}
+	Model:
+	\setcounter{equation}{2}
+	\begin{equation}
+		\label{sa:eq:interaction}
+		y_{it} = \gamma_i + \lambda_t + \mu P^f_{it} + \nu P^m_{it} + X_{it} + \delta T_{it} + \rho T_{it}*P^m_{it} + \epsilon_{it}
+		\end{equation}
+\end{frame}
+
+\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa II}
+	\begin{table}[!ht]
+	\centering
+	\caption{Height-for-Age Z-score}
+	\label{sa:ta:haz}
+		\begin{tabular}{l|rrr}
+		\hline
+		specification & 1 & 2 & 3\\
+		\hline
+		w\_spen\_m & 0.2366 & *0.8228 & 0.7908 \\
+		w\_spen\_w & -0.2331 & 0.1053 & 0.1072 \\
+		elig.men.60 & & **-0.3419 & **-0.3465 \\
+		w\_spen\_m1:elig.men.60 & & & 0.0446 \\
+		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
+		\end{tabular}
+	\end{table}
+\end{frame}
+
+\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa III}
+	\begin{table}[!ht]
+	\centering
+	\caption{Weight-for-Age Z-score}
+	\label{sa:ta:waz}
+	\begin{tabular}{l|rrr}
+		\hline
+		specification & 1 & 2 & 3\\
+		\hline
+		w\_spen\_m & 0.2366 & 0.2981 & 0.4780 \\
+		w\_spen\_w & -0.2331 & -0.3112 & -0.3280 \\
+		elig.men.60 & & ***-0.3475 & **-0.3243 \\
+		w\_spen\_m1:elig.men.60 & & & -0.2545 \\
+		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
+		\end{tabular}
+	\end{table}
+\end{frame}
+
+\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa IV}
+% LaTeX table created manually
+% Fri Dec 27 23:53 2013
+\begin{table}[!ht]
+\centering
+\caption{Weight-for-Height Z-score}
+\label{sa:ta:whz}
+\begin{tabular}{l|rrr}
+\hline
+specification & 1 & 2 & 3 \\
+\hline
+w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 \\
+w\_spen\_w & 0.0655 & 0.0371 & 0.0478 \\
+elig.men.60 & & -0.1417 & -0.1574 \\
+w\_spen\_m1:elig.men.60 & & & 0.1484 \\
+\end{tabular}
+\end{table}
+\begin{table}[!ht]
+\centering
+\caption{Body-Mass-Index Z-score}
+\label{sa:ta:bmiz}
+\begin{tabular}{l|rrr}
+\hline
+specification & 1 & 2 & 3 \\
+\hline
+w\_spen\_m & *-0.8058 & *-0.7905 & *-1.0226 \\
+w\_spen\_w & -0.1592 & -0.1956 & -0.1742 \\
+elig.men.60 & & -0.1674 & -0.2049 \\
+w\_spen\_m1:elig.men.60 & & & 0.3407 \\
+\end{tabular}
+\end{table}
 \end{frame}
@@
 \begin{frame}{End Notes}
+Summary
   \begin{itemize}
   \item
-    The \alert{first main message} of your talk in one or two lines.
+    Cryptocurrency Inflation, through multiplicity
   \item
-    The \alert{second main message} of your talk in one or two lines.
+	Currency Attacks: uncertainty vs. risk, redefining risk profile, uniform distribution 
   \item
-    Perhaps a \alert{third message}, but not more than that.
+    Pensions and Child Growth: negative effect
   \end{itemize}
 
-  % The following outlook is optional.
-  \vskip0pt plus.5fill
+Questions  
 	\begin{itemize}
 	\item
-    Outlook
-    \begin{itemize}
+		Cryptocurrency Inflation: relevant for Development Economics?
 	\item
-      Something you haven't solved.
+		Knightian Uncertainty: What to do with this critique?
 	\item
-      Something else you haven't solved.
-    \end{itemize}
+		Pensions and  Child Growth: Account for drop in no. children?
 	\end{itemize}
@@
 
+\begin{frame}[allowframebreaks]{References}
+	\printbibliography
+\end{frame}
+
 \end{document}

### 2014-02-26 presentationPTD.tex
update presentation

@@
 \usepackage[english]{babel}
+\usepackage{mathtools}
+\usepackage{accents}
 %\usepackage[utf8]{inputenc}
@@
 \title[]{Preliminary Thesis Defence}
-\subtitle{December 18, 2013}
+\subtitle{\today}
 
@@
 	\begin{itemize}
+		\item Negative policy effect \\ explanation?
 		\item Defining of Age-Based and Height-Based Z-scores,\\ correct?
 		\item BMI as convex mapping of Weight-for-Height,\\ significance?
-		\item Drop in children living with recipient 2008-2012,\\ 		how to account for this?
 	\end{itemize}
@@
 	\end{itemize}
+	Model:
+	\begin{itemize}
+		\item State of economic fundamentals: $\theta \sim U[0,1]$
+		\item Pegged at a level larger than fundamentals: ($e* \geq f(\theta)$)
+		\item Speculators can short, their payoff: $e^* - f(\theta) - t$
+		\item Peg cost: economic fund. and speculators attacking ($\alpha$)
+		\item Government derives value: $\nu - c(\alpha, \theta)$ from defending peg
+	\end{itemize}
+	Outcomes:
+	\begin{enumerate}
+		\item $ [0, \underaccent{\bar}{\theta} ] $, cost always too high, unstable region
+		\item $[\underaccent{\bar}{\theta}, \bar{\theta}]$, enough attack, cost too high, `ripe for attack'
+		\item $[\bar{\theta}, 1]$, cost of shorting always outweigh gains, stable region
+	\end{enumerate}
+\end{frame}
+
+\begin{frame}{Uncertainty and Risk in Currency Attacks}
 	Critiques:
-\begin{itemize}
+	\begin{enumerate}
+
 		\item Strange result, does not correspond to reality
@@
 		\item Speculator risk profile is redefined:
-\end{itemize}
+	\end{enumerate}
 	\begin{quotation}
@@
 
-\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa I}
+\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa}
 	\begin{itemize}
@@
 
-\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa II}
+\begin{frame}{Pensions and Child Growth}{Results: Age-Based Z-scores}
 	\begin{table}[!ht]
@@
 		w\_spen\_m1:elig.men.60 & & & 0.0446 \\
-		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
 		\end{tabular}
 	\end{table}
-\end{frame}
-
-\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa III}
 	\begin{table}[!ht]
@@
 		w\_spen\_m1:elig.men.60 & & & -0.2545 \\
-		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
 		\end{tabular}
@@
 
-\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa IV}
+\begin{frame}{Pensions and Child Growth}{Results: Height-Based Z-scores}
 % LaTeX table created manually
@@
 	\item
+		Negative policy effect: explanation?
+	\item
 		Cryptocurrency Inflation: relevant for Development Economics?
@@
 		Knightian Uncertainty: What to do with this critique?
-	\item
-		Pensions and  Child Growth: Account for drop in no. children?
 	\end{itemize}
